### 2016-05-05 plosOneJordanousKeller/PlosONE2/plos_JordanousKeller.tex
initial commit

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{Creativity is what we say it is: identifying key components of creativity}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Anna Jordanous\textsuperscript{1,\Yinyang, *},
Bill Keller\textsuperscript{2,\Yinyang}
\\
\bigskip
\bf{1} School of Computing, University of Kent, Chatham Maritime, Kent, UK
\\
\bf{2} Department of Informatics, University of Sussex, Falmer, Brighton, UK
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
%\ddag These authors also contributed equally to this work.

% Current address notes
%\textcurrency a Insert current address of first author with an address update
% \textcurrency b Insert current address of second author with an address update
% \textcurrency c Insert current address of third author with an address update

% Deceased author note
%\dag Deceased

% Group/Consortium Author Note
%\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* a.k.jordanous@kent.ac.uk / billk@sussex.ac.uk

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}

Creativity is a complex multi-dimensional concept which resists definition; it is accessible to us at a subjective, multi-faceted and dynamic level rather than being fixed and clearly defined. If we wish to study creativity scientifically using computational models, or simulate it computationally, then a tractable and accurate interpretation of creativity is needed. Creativity encompasses many related aspects, abilities, properties and behaviours. This paper uses techniques from the field of statistical natural language processing to identify a collection of fourteen key components of creativity through an analysis of what is considered to be important in talking about creativity. Words were identified which appeared significantly often in connection with discussions of the concept. Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerged, which collectively contribute to a comprehensive and multi-perspective definition of creativity. The components provide an ontology of creativity: a set of building blocks which, in evaluation, have proven useful for making the concept easier to understand and more tractable to study and evaluate.

\linenumbers

\section*{Introduction}\label{intro}

%Currently, most content on the Semantic Web is in the form of ontologies of `things': semantically structured collections of factual or objective data on topics as diverse as people \cite{foaf}, places \cite{geonames}, music \cite{musicOntology} or manuscripts \cite{sawsOntology}. The focus in Semantic Web research has generally been on reducing ambiguity in representations of these more structured domains and concepts, rather than directly tackling the representation and machine-readable representation of subjective, unstructured concepts in an ontology. However, cognitive science research and work on lexical resources such as WordNet \cite{fellbaum98,wordnetRKB} have laid foundations for more definitionally troublesome concepts to be considered in detail. The time is ripe for developing ontologies of subjective concepts such as creativity.

What is creativity, and how can we better understand and learn about creativity using computational modelling? Computational creativity is a relatively youthful research area that has been growing with significant pace in recent years. Computational creativity is: 
\begin{quote}`The philosophy, science and engineering of computational systems which, by taking on particular responsibilities, exhibit behaviours that unbiased observers would deem to be creative.' 
\cite[p. 21]{coltonwiggins12}
\end{quote}

Computational creativity research follows both theoretical and practical directions and crosses several disciplinary boundaries between the arts, sciences and engineering. Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling \cite[provide examples]{colton08,widmerAIM09,leon10MM,perezyperez99}. The evaluation of computational {\emph creative systems} that have been developed by researchers in the field has proven non-trivial. Creativity evaluation, a recurring topic for discussion, has been described as one of the `Grand Challenges' of computational creativity research \cite{cardoso09}. Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what is meant when we talk about creativity and what does it constitute?

Creativity is a complex, multi-faceted concept encompassing many related aspects, abilities, properties and behaviours. There have been many attempts to capture the nature of creativity in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in Fig. 1).  %\ref{S1_Fig}). 
Yet despite many efforts to provide a workable and comprehensive definition of the concept, no real consensus has yet been reached. In the academic literature on creativity, many repeated themes have emerged. However, multiple viewpoints exist, prioritising different aspects of the concept according to what are traditionally considered to be the primary factors for a particular discipline. The need for a more comprehensive, inclusive, multi-dimensional  account has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}. Such an account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.

There are many challenges to modelling a concept like creativity in a computational setting. As a concept, creativity seems inherently fuzzy or vague, with a meaning that shifts depending on the domain of application. Tackling these challenges affords two key advantages. First, we can take advantage of computing and artificial intelligence to perform and/or enhance creative activities using computational power and research expertise. Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept. Both these advantages motivate this current paper.

The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components representing key dimensions, as recognised across a combination of different viewpoints. The paper presents a novel, empirical approach focusing on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept. Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive account of creativity \cite{lakoff87,wittgenstein58}. The current work is intended as a significant, practical methodological contribution towards addressing this Grand Challenge of computational creativity and should provide researchers with a first foundation for evaluating exactly how creative so-called {\emph creative systems} actually are.

In our approach, statistical language processing techniques are used to identify words significantly associated with creativity in a corpus of academic papers on the subject. A corpus spanning some 60 years of research into the nature of creativity was collected together. The papers were gathered from a wide variety of disciplines including psychology, educational testing and computational creativity, amongst others. The language data drawn from this collection was then analysed and contrasted with data from a corpus of matched papers on subjects unrelated to creativity. From this analysis, a set of 694 {\em creativity words\/} was identified, where each creativity word appeared significantly more often than expected in the corpus of creativity papers. A measure of lexical similarity provided a basis for clustering the creativity words into groups of words with similar or shared aspects of meaning. Through inspection of these clusters, a total of fourteen {\em key components of creativity\/} was identified, where each represents a key theme or aspect of creativity. The set of components yields information about the nature of creativity, based on what is collectively emphasised in discussions about the concept.

% The Semantic Web has emerged as a way to address the troublesome but important issue \cite{boden99} of articulating values, concepts and information using an open and  {\em machine-understandable} vocabulary. Encoding the creativity components in an OWL ontology has enabled this {\em ontology of creativity} to be made publicly available to the wider research community as a resource in the Semantic Web, under the permanent URL:
%\begin{quote}
%{\small \texttt{http://purl.org/creativity/ontology}}
%\end{quote}

The remainder of this section considers the problem of providing a definition of creativity and reviews previous attempts to do so. The representation of subjective, ambiguous, loosely structured concepts is also considered.
%, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
Details are provided of the methodology used to identify components of creativity from an analysis of language data and the results of this analysis are presented in terms of fourteen key components or dimensions of creativity. The derived set of components is evaluated in terms of how well it satisies the need for a shared, inclusive and comprehensive acount of creativity and provides a vocabulary of creativity that is acessible to both people and machines. Finally, conclusions are drawn and some directions for further work are outlined.

\subsection*{Background: A question of definition} \label{background}

We begin by considering the problem of definition. As Torrance observes:

\begin{quote}
`[c]reativity defies precise definition ... even if we had a precise conception of creativity, I am certain we would have difficulty putting it into words' \cite[p. 43]{torrance88}. 
\end{quote}

Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. Currently, no one definition has been adopted as standard, either in everyday use (as evidenced by the dictionary definitions considered below), for research purposes \cite{rhodes61,taylor88,plucker04defn} or even in legal practice \cite{clifford04,mandel11}, where one would expect a term critical to legal judgements  -- as creativity surely is \cite{feist91,karjala08,schafer15} -- to be precisely and unambiguously defined.

The difficulty of formulating an adequate definition of creativity in words should not discourage us from the attempt, however  \cite{rhodes61,plucker04defn,kaufman09}. Even if other researchers have been swayed away from this task \cite[for example]{sternberg99a,veale06preface},  care must be taken that we `do not throw out the baby with the bath water just because the water is cloudy' \cite[p. 310]{rhodes61}. Some of the issues concerning the problem of defining creativity have been debated for decades. The following sections consider the need for an explicit and comprehensive definition of creativity and the difficulties researchers encounter in providing one.

\paragraph{The need for a more tangible understanding of creativity}

Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research. He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited' \cite[p.87]{plucker04defn} and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding' \cite[p.92]{plucker04defn}. In fact, `Rather than being a strength of the field, as many believe, the lack of a common definition is a major, debilitating weakness. ... we feel that an agreed-on definition is long overdue and has placed the field in a crisis of legitimacy. ... This change in the focus and direction of creativity research is needed if the field is to move from a shadowy past into the forefront of constructive approaches' \cite[p. 93]{plucker04defn}. Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear'
\cite[p. 310]{rhodes61}.

In their review of research into human creativity, Hennessey and Amabile ask a significant question: 
\begin{quote}
`Even if this mysterious phenomenon can be isolated, quantified, and dissected, why bother? Wouldn't it make more sense to revel in the mystery and wonder of it all?' 
\cite[p. 570]{hennessey10}
\end{quote}

\noindent Two answers to this question are offered by Hennessey and Amabile, both of which are identified as desirable: to gain a deeper understanding of creativity and to learn how to boost people's creativity.

Creativity can and should be studied and measured scientifically, but the lack of a commonly-agreed understanding causes problems for measurement \cite{kaufman09}. Plucker et al. make recommendations about best practice based on their own survey of the creativity literature:
\begin{quote}
\noindent
`we argue that creativity researchers must

\begin{enumerate}
\renewcommand{\labelenumi}{(\alph{enumi})}
\item explicitly define what they mean by creativity,
\item avoid using scores of creativity measures as the sole definition of creativity (e.g., creativity is what creativity tests measure and creativity tests measure creativity, therefore we will use a score on a creativity test as our outcome variable),
\item discuss how the definition they are using is similar to or different from other definitions, and
\item address the question of creativity for whom and in what context.' \cite[p.92]{plucker04defn}
\end{enumerate}
\end{quote}

\noindent In short, we need to specify and justify the standards that we use to judge creativity. A more objective and well-articulated definition of creativity enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.

\paragraph{Existing definitions}
\label{existing_defs}

To find out the meaning of a word, a natural first step might be to consult a dictionary. Dictionary definitions of `creativity' provide a brief introduction to  the meaning of the word. However, for the purposes of research, the utility of such definitions is severely restricted by their format and brevity, and they generally provide only cursory, shallow insights into the nature of creativity. More problematic still, dictionary entries are often self-referential or circular,  defining creativity in terms of ``being creative'' or ``creative ability''. To illustrate these limitations, there follow several typical dictionary definitions of creativity and the related words creative and create:\footnote{For readability, some definitions are edited slightly to standardise formats and remove etymological/grammatical annotations.}
\begin{quotation}
\begin{description}
\item {\em Oxford English Dictionary} 2nd ed. (1989) pp. 1134-5:
	\begin{enumerate}
	\item[creativity:] creative power or faculty; ability to create
	\item [creative:] Having the quality of creating, able to create; of or relating to creation; originative. b. Inventive, imaginative; of, relating to, displaying, using, or involving imagination or original ideas as well as routine skill or intellect, esp. in literature or art. c. Esp. of a financial or other strategy: ingenious, esp. in a misleading way. 2. Providing the cause or occasion of, productive of.
\item [create:] 1.a. Said of the divine agent: To bring into being, cause to exist; esp. to produce where nothing was before, 'to form out of nothing'. b. with complemental extension. 2. To make, form, constitute, or bring into legal existence (an institution, condition, action, mental product, or form, not existing before). Sometimes of material works. 3. To constitute (a personage of rank or dignity); to invest with rank, title, etc. 4. To cause, occasion, produce, give rise to (a condition or set of circumstances).
	\end{enumerate}
\item {\em The Penguin English Dictionary} 2nd ed. (1969) p. 174:
	\begin{enumerate}
	\item[creativity:] creative power or faculty; ability to create
	\item[creative:] having power to create; related to process of creation; constructive, original, producing an essentially new product; produced by original intellectual or artistic effort 
	\item [create:] make out of nothing, bestow existence on; cause, bring about; produce or make something new or original; confer new rank etc on; (theat) be the first to act (a certain part); make a fuss
	\end{enumerate}
\item {\em Webster's 3rd New International Dictionary} (1961) p. 532:
	\begin{enumerate}
	\item[creativity:] the quality of being creative; ability to create 
	\item[creative:] 1. having the power or quality of creating; given to creation 2: PRODUCTIVE - used with 3: having the quality of something created rather than imitated or assembled; expressive of the maker; IMAGINATIVE 
	\item[create:] 1: to bring into existence; make out of nothing and for the first time 2: to cause to be or to produce by fiat or by mental, moral, or legal action 3: to cause or occasion - used of natural or physical causes and esp. of social and evolutionary or emergent forces 4a: to produce (as a work of art or of dramatic interpretation) along new or unconventional lines) b: to design (as a costume or dress)
	\end{enumerate}
\end{description}
\end{quotation}

Given the problems inherent in dictionary definitions of creativity, it is not surprising that a number of creativity researchers have set out  to provide their own definitions of the concept.  Some examples are:

\begin{quotation}
\begin{quote}
 `creativity is that process which results in a novel work that is accepted as tenable or useful or satisfying by a group at some point in time' %By this definition we limit ourselves to the study of individuals who are regarded as creative by ``significant others'' in their environment.'
\cite[p. 218]{stein63}
\end{quote}
%\begin{quote}
%`A product or response will be judged as creative to the extent that (a) it is both a novel and appropriate, useful, correct or valuable response to the task at hand, and (b) the task is heuristic rather than algorithmic.'
%\cite[p. 35]{amabile96}
%\end{quote}
\begin{quote}
`Creativity is the ability to produce work that is both novel (i.e., original, unexpected) and appropriate (i.e., useful, adaptive concerning task constraints)'
\cite[p. 3]{sternberg99a}
\end{quote}
\begin{quote}
`Creativity is the ability to come up with ideas or artefacts that are {\em new}, {\em surprising and valuable}'
\cite[p. 1]{boden04}
\end{quote}
\begin{quote}
`Creativity is the interaction among \emph{aptitude, process, and environment} by which an individual or group produces a \emph{perceptible product} that is both \emph{novel and useful} as defined within a \emph{social context}'
\cite[p. 90]{plucker04defn}
\end{quote}
\begin{quote}
`Creativity: the generation of products or ideas that are both novel and appropriate' 
\cite[p. 570]{hennessey10}
\end{quote}
\begin{quote}
`The word creativity is a noun naming the phenomenon in which a person communicates a new concept (which is the product). Mental activity (or mental process) is implicit in this definition, and of course no one could conceive of a person living or operating in a vacuum, so the term \emph{press} is also implicit'
\cite[p. 305]{rhodes61}
\end{quote}
\end{quotation}

These more research-oriented definitions avoid the problems of self-reference and circularity noted for the dictionary entries given previously. However, whilst the definitions may provide somewhat deeper insight into the nature of creativity, the brevity of the definitions means that they still only succeed in providing shallow, summary accounts of the concept.

\paragraph{A multitude of different perspectives} \label{perspectives}

The problem of identifying and quantifying creativity exists across many disciplines. How creative is this person? Does this person have the creative abilities to boost my business? Is this pupil's story creative? Is this computational system an example of computational creativity? As a consequence, when attempts are made to define creativity, it is often from the perspective of a particular domain or research discipline. For example, psychometric tests for creativity such as \cite{guilford50,torrance74} focus on {\em problem solving} and {\em divergent thinking} as key attributes of a creative person. In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} places emphasis on the {\em novelty} and {\em value} of creative products. Whilst there is some consensus across academic fields, the differing emphases contribute to variations in the interpretation of creativity. These variations affect consistency across creativity research in different disciplines and potentially hinder interdisciplinary collaborations and cross-application of findings.

Several competing interpretations of creativity exist in the literature. Sometimes these differences of opinion do not need to be directly resolved but can be included alongside each other. Examples include whether creativity is centred around mental processes \cite{boden04,dietrich10} or embodied and situated in an interactive environment \cite{mccormack07,sosa09}. Another example is whether creativity is domain-independent \cite{plucker98}, or dependent on domain-specific context \cite{baer98}, or (as both Plucker and Baer have concluded) a combination of both \cite{plucker04,baer10}.

Other conflicts arise where a previously narrow view of creativity has been widened in perspective. To resolve the conflict, an inclusive, all-encompassing view of creativity should adopt the wider perspective and incorporate the narrower perspective. For example rather than focussing narrowly on creative {\em genius}, through the study of people with exceptional creative achievements \cite[for example]{poincare29,hadamard45} emphasis has shifted to encompass the broader study of {\em everyday} creativity, with genius as a special case: the notion that everyone can be creative to some degree \cite{weisberg88,bryankinns09}.

Similarly, researchers distinguish between {\em little-c} and {\em Big-C} creativity, or {\em psychological/P-creativity} and  {\em historical/H-creativity} \cite{boden04}, adjusting their focus accordingly to make their research more manageable. This is particularly the case in computational creativity, where endowing the computer with elements of general, human knowledge and experience is a major challenge. Little-c creative or p-creative work is perceived as creative by the creator personally but may replicate existing work (unknown to the creator) so is not necessarily creative in a wider social context. This encompasses the concept of Big-C creativity or h-creativity, where the work makes a creative contribution both to the creator and to society. To be Big-C creative/h-creative is to be little-c creative/p-creative in a way which has not been done before by anyone.

The preceeding discussion indicates that creativity is a complex, multi-faceted concept that requires a broad and inclusive treatment. The {\em Four Ps} framework \cite{rhodes61,stein63,mooney63,odena09,jordanous16cs} ensures we pay attention to four key aspects of creativity:

\begin{description}
\setlength{\labelwidth}{1.5cm}
\setlength{\itemindent}{1.5cm}
\item[Person/Producer:] The individual that is creative
\item[Process:] What the creative individual does to be creative
\item[Product:] What is produced as a result of the creative process
\item[Press:] The environment in which creative activity takes place
\end{description}

\noindent This framework presents creativity in a broader context, making our understanding of the concept more generally applicable and less specific to a domain or academic discipline. In contrast, models of the creative process \cite{wallas26,poincare29,hadamard45}, tests of people's creativity \cite{goldman64,guilford67,torrance74} or tests based on creative artefact generation \cite{amabile96,ritchie07} are useful only within a limited sphere. Jordanous \cite{jordanous16cs} has contextualised the Four Ps in a computational context, referring to the creative Producer (person or computational agent) carrying out Processes within the environmental context of a Press, to create computational Products.

\subsection*{The challenges of modelling creativity} \label{cogPhil}

% Was Reflections on the semantics of subjective concepts. Merge this together and make it more relevant to modelling creativity (specifically) rather than the general treatment it is now.

Creativity can be seen as an essentially contested concept \cite{gallie56}: it is subjective, abstract and can be interpreted in a variety of acceptable ways, such that a fixed `proper general use' is elusive \cite[p. 167]{gallie56}. Gallie defines an essentially contested concept through several features: being internally complex in nature, but amenable to being broken down into identifiable constituent elements of varying relative importance, and dependent on a number of factors such as context and individual preference. Although there may be consensus on the meaning of such concepts in very general terms, they may defy precise interpretation. There is not a single agreed instantiation, but instead many reasonable possibilities, influenced by changing circumstances and contexts. It is more productive to acknowledge that these different interpretations exist and refer to `the respective contributions of its various parts or features' \cite[p. 172]{gallie56}, rather than to argue for a single interpretation. Thus, different types of creativity manifest themselves in different ways while sharing certain characteristics (not necessarily the same across all creative instances): what Wittgenstein refers to as `family resemblances' \cite{wittgenstein58}:

\begin{quote}
[On discussing the example of what a `game' is] `we see a complicated network of similarities overlapping and criss-crossing: sometimes overall similarities, sometimes similarities of detail. ... I can think of no better expression to characterize these similarities than ``family resemblances''; for the various resemblances between members of a family: build, features, colour of eyes, gait, temperament, etc. etc. overlap and criss-cross in the same way. And I shall say: ``games'' form a family.'
\cite[Part 1, Paragraphs 66-67]{wittgenstein58}
\end{quote}

Similarly, with creativity, different manifestations of creativity are not all necessarily required to share the same common, core elements in order to be identified as part of the creativity `family', but relationships between different manifestations reveal various shared characteristics emerging similar to Wittgenstein's `family resemblances' in language. We need to identify what those family resemblances are. So to understand creativity, we can investigate what resemblances exist across different instantiations of creativity.

Wittgenstein \cite{wittgenstein58} has argued that `a clear view of the aim and functioning of the words' helps us `dispers[e] the fog' that obscures a clear vision of the `working of language' \cite[Part 1, Paragraph 5]{wittgenstein58}. To understand the use of a word, one must have background information and context. Wittgenstein gives the example of a chess piece, which is introduced to someone as a `king' \cite[paragraph 31]{wittgenstein58}: to understand this usage the person must already know the rules of chess, or must at least know what it means to have a piece in a game. To Wittgenstein, the semantics of words and statements are determined by how we use them, grounded in rules set by our habitual use of a word and our shared consensual practices, rather than being fixed by static, pre-assigned meanings.

%Waismann, a contemporary of Wittgenstein, has reflected on the impact of `open texture' on language, where certain words or phrases simply cannot be completely defined for all possible scenarios:

%\begin{quote}
%`Every description stretches, as it were, into a horizon of open possibilities: however far I go, I shall always carry this horizon with me.'
%\cite[p. 122]{waismann68}
%\end{quote}
Linguistics research advocates that the meaning of a word is dependent on the context it is used in \cite{firth57}. In particular, Lakoff has argued that the study of language helps reveal how people think \cite{lakoff87,lakoff80}. Words used frequently in discussions of the nature of a concept provide the context for the commonly understood meaning of that concept, as has been shown in various corpus linguistics contributions \cite{oakes98,rayson00,kilgarriff01,kilgarriff06}.

%We acknowledge that semantic ambiguity is unlikely to be resolved to a single agreed definition. Meanings can be dynamic, evolving over time and contextually dependent, rather than being fixed, with a static and unchanging prescribed definition. 
The key principle emerging across these present discussions is that the meaning of words like creativity can be modelled by identifying different aspects that collectively contribute to the meaning of the concept of creativity.

%\subsection*{Subjectivity and ambiguity on the semantic web} \label{SWsubjectivity}

%Ambiguity in semantic interpretation of terms is not an area that Semantic Web research shies away from. Ontologies are widely used to pinpoint and define what {\em things} mean in a machine-readable way, for greater clarity and precision in using various vocabularies and identifiers. Such research does not concentrate merely on those areas of interest which are simple to define and objectively clear to interpret; for example SKOS \cite{skos} provides vocabulary to organise and taxonomise knowledge, whether explicit or tacit, while FRBR-oo \cite{doerr07} defines various terms to do with bibliographical records and the works and ideas expressed within them, on various conceptual levels beyond merely the physical instantiation of a book or other written document. Upper ontologies such as Dolce \cite{gangemi02}, SUMO \cite{niles01} and Cyc \cite{reed02} have guided the objective, disambiguated expression of higher-level, cross-domain, general concepts and abstract knowledge.% An upper ontology defines higher-level vocabularies and concepts necessary to implement ontologies themselves, providing the meta-vocabulary to link specific ontologies to more general concepts.

%What is not often tackled within Semantic Web research are the types of topic discussed above, where ambiguity is unlikely to be resolved to a single agreed definition and meanings are dynamic, changing over time and contextual interpretations, rather than being fixed to a static and unchanging prescribed definition. To date, there is a lack of suitable methodologies applied in Semantic Web research to enable or assist the building of ontological representations of such topics. Existing ontology construction methodologies tend to concentrate on how to extract and represent data objectively rather than retain subjectivity in the data \cite{fernandez97,noy01,haase08}; the focus is on how best to construct ontologies in an appropriate manner rather than how to tackle {\em moving-target} issues of dynamic, perhaps unresolvable, semantics.

%There is of course much work still to be done in representing semantics on the Semantic Web; much information with fixed semantics is still to be represented in a machine readable form. With the growth of the Semantic Web, this ongoing collation and representation of knowledge is work-in-progress. As discussed above, advances in other research disciplines can assist progress in areas where there is less agreement generally over semantics. The representation of these areas and concepts on the Semantic Web is troublesome, particularly in a framework which is geared towards resolving semantic ambiguity to static, pre-assigned meanings. More established disciplines in cognitive science and related areas of research would not claim to have solved all such issues and challenges; however Semantic Web researchers can learn from advances that have been made in these disciplines. An approach informed by cross-disciplinary contributions helps Semantic Web research progress towards a broader and more complex coverage of data and their semantics.

\subsection*{Towards a clearer understanding of creativity}\label{progressingForwards}

Returning to the concept under investigation, the need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed. There is a large quantity of material contributory to a satisfactory definition of creativity and a number of key contributions have been discussed during this section. What must be done now is to marshal this assortment of material and to unify different perspectives where possible, in order to avoid the disciplinary `blinkers' or compartmentalisation that is often seen in creativity research \cite{hennessey10}. In approaching the semantic representation of subjective and multi-faceted concepts, some useful guidance is offered through philosophical reflections on the meaning of such concepts. 
%Further, cognitive science methodologies, {\bf IS THIS NEXT BIT TO GO?} as well as approaches to ontology learning from texts \cite{gomezperez04} {\bf END} can be harnessed to enable the representation of more semantically ambiguous concepts such as creativity

%To date, however, the Semantic Web research community has largely focused on the representation of objective concepts and resources that are relatively clearly defined.

The proposed approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept. In addition, following from the observations above, a {\em  confluence approach\/} to creativity is adopted \cite{sternberg99a,mayer99,ivcevic09}. This works on the principle that creativity results from several components converging and goes on to examine what these components are. Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted. This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Methods}
\label{methodology}

 Tools from natural language processing and statistical analysis are used to identify words that appear to be highly associated with dimensions of creativity, as represented in a sample of academic papers on the topic. A key innovation is the use of a statistical measure of lexical similarity, which allows the words to be clustered into semantically-related groups. Clustering reveals a number of common themes or factors of creativity, allowing the identification of a set of fourteen components that serve as building blocks for creativity.

\subsection*{Corpus data}\label{corpusData}

A sample of academic papers discussing the nature of creativity was assembled. This {\em creativity corpus\/} consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.

\vspace{0.25cm}
\begin{center}
\fbox{
\begin{minipage}{0.8\linewidth}
\textbf{Creativity corpus}: \\ a collection of thirty academic papers which explicitly discuss the nature of creativity.
\end{minipage}
}
\end{center}
\vspace{0.25cm}

The 30 papers selected for the creativity corpus are listed in Fig. 1. %\ref{S1_Fig}. 
The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines. A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors. For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.

The creativity corpus is relatively small and necessarily selective  in terms of the papers that are included. As such it constitutes just a small fraction of the many academic works on creativity that have been published in the last 60 or so years. Indeed, the 30 papers in the creativity corpus cannot be regarded as comprehensively representative of the wide range of academic positions on creativity that have been discussed in the literature over the decades. However, the goal of this work is not to present a fine-grained analysis of language use drawn from this complete literature, nor to provide a comprehensive lexicon or dictionary of creativity. Rather, the goal is to identify the broader ontological themes or factors that recur in our understanding of the concept of creativity. For this purpose, what is required is a sufficiently representative sample of the academic discourse on creativity. This sample can be used to identify the way in which word use reflects key themes or factors that persist across different perspectives.

Our objective is to identify what is distinctive in the language used to discuss creativity, in contrast to the language used to discuss other topics. As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled.

\vspace{0.25cm}
\begin{center}
\fbox{
\begin{minipage}{0.8\linewidth}
\textbf{Non-creativity corpus}: \\ 60 academic papers on topics unrelated to creativity, from the  same range of academic disciplines and publication years as  the creativity corpus papers.
\end{minipage}
}
\end{center}
\vspace{0.25cm}

The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline\footnote{As categorised by the literature database {\em Scopus} \texttt{http://www.scopus.com/})} published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e. {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).

The non-creativity corpus is twice the size of the creativity corpus ($\approx$ 700,000 words and $\approx$ 300,000 words respectively), in acknowledgement of the fact that in general the set of academic papers on creativity is only a small subset of all academic papers. Both corpora are very small in comparison to corpora such as the British National Corpus, a large  ($\approx$ 100M words) corpus of written and spoken English in general usage across a number of different contexts, and tiny in comparison to more recent web-derived text collections containing billions of words. There are, however, several benefits associated with using a corpus derived from specialist academic literature:

\begin{itemize}
\item Ease of locating relevant and appropriate papers: e.g. availability of tools to perform targeted literature searches, electronic publication of papers for download, tagging of paper content by keywords, citations in papers to other related papers.
\item Ability to access timestamped textual materials over a range of decades.
\item Publication of academic papers in an appropriate format for computational analysis: most papers that are available electronically are in formats such as PDF or HTML, which can be converted to text fairly easily.
\item Availability of citation data as a measure of how influential a paper is on others: whilst not a perfect reflection of a paper's influence, citation data is often used for measuring the impact of a journal \cite{garfield72} or an individual researcher's output \cite{hirsch05}.
\item Availability of provenance data, such as who wrote the paper and for what audience (from the disciplinary classification of the journal).
\end{itemize}
\noindent

\subsection*{Natural language processing}

The corpus data was first pre-processed using the RASP natural language processing toolkit \cite{briscoe06} in order to perform {\em lemmatisation} and {\em part-of-speech} tagging.  Lemmatisation permits inflectional variants of a given word to be identified with a common `dictonary headword' form or `lemma'.  For example,  {\em performs\/}, {\em performed\/}  and {\em performing\/} all occur in the creativity corpus as distinct morphological variants of  the  verb, {\em perform\/}.  Intuitively, we would like to count each of these inflectional variants as an instance of the same word, rather than as separate and distinct lexical tokens. Lemmatisation software enables us to do this by mapping such variants to a cannonical lemma form. As a further refinement, each lemma was also mapped to lower case to ensure that capitalised word forms (e.g. {\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).

Each word was assigned a part-of-speech tag identifying its grammatical category (i.e. whether the word was a noun, verb, preposition, etc.). Such tagging is useful because it allows us to distinguish between different grammatical uses of a common orthographic form. For example, the use of {\em novel\/} as a noun in {\em a good novel\/} can be properly differentiated from its use as an adjective in {\em a novel idea\/}.  The data was further simplified and filtered so that only words of the four `major' categories (i.e. noun, verb, adjective and adverb) were represented. Note that the major categories bear the semantic content of the papers making up the creativity corpus. They may be distinguished from minor categories or `function words', such as pronouns ({\em something\/}, {\em itself\/}) prepositions (e.g. {\em upon\/}, {\em by\/}) conjunctions ({\em but\/}, {\em or\/}) and quantifiers (e.g. {\em many\/}, {\em more\/}). Such words have little independent semantic content so are of limited interest for the present study and may be removed from the data.

Following processing with RASP, a list of words found in the creativity corpus, together with their frequency counts was generated. The non-creativity corpus was pre-processed in the same way and a corresponding list of words and frequencies also generated.

\subsection*{Identifying words associated with creativity}

The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus. This in turn can be regarded as providing evidence of which words are salient to the definition of creativity. Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic). The log-likelihood ratio is a measure of how well observed data fits a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}. It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}. This is a particular issue when analysing smaller corpora, such as those used in the present work (see Fig. 1). %\ref{S1_Fig}). 
The log likelihood ratio statistic is more accurate in its treatment of infrequent words in the data,  which often hold useful information. By contrast, the $\chi^2$ statistic tends to under-emphasise such outliers at the expense of very frequently occurring data points.

Our use of the log-likelihood ratio follows that of Rayson and Garside \cite{rayson00}.
Given two corpora (in our case, the creativity corpus $cc$ and the non-creativity corpus $nc$) the log-likelihood score for a given word is calculated as shown in equation~(\ref{LLR}) below:

\begin{equation}
\mbox{\em LL} =  O_{cc}\ln (\frac{O_{cc}}{E_{cc}} ) + O_{nc}\ln (\frac{O_{nc}}{E_{nc}} )
\label{LLR} 
\end{equation}
\noindent
where $O_{cc}$ ($O_{nc}$) is the observed frequence of the word in $cc$ ($nc$) and similarly $E_{cc}$ ($E_{nc}$) is its expected frequency. The expected frequency $E_{cc}$  is given by:

\begin{equation}
E_{cc} = \frac{N_{cc} \times (O_{cc} + O_{nc})}{N_{cc} + N_{nc}}
\label{modelFreqs} 
\end{equation}
where $N_{cc}$ denotes the total number of words in corpus $cc$ (i.e. the sum of the frequencies of all words drawn from corpus $cc$). The expected frequency $E_{nc}$ is defined in a way analogous to Equation \ref{modelFreqs}.

As computed above, the log-likelihood ratio measures the extent to which the distribution of a given word deviates from what might be expected if its distribution is not corpus dependent. The higher the log likelihood ratio score for a given word, the greater the deviation from what is expected. It should be noted however, that the statistic tells us only that  the observed distribution of a word in the two corpora is unexpected (and to what extent).  It does not  tell us whether the word is more or less frequent than expected in the creativity corpus. To identify words significantly associated with creativity therefore, it was necessary to select just those words with observed counts higher than that expected in the creativity corpus. It should perhaps be further noted that the resulting words may be either positively or negatively connoted with respect to creativity. In practice this is not a problem, as the significance of a given word lies in its semantic connection to creativity, not in its sentiment or affect. Affect is taken into account as part of the later manual examination of the data used to identify components of creativity.

The results of the calculations were filtered to remove any words with a log-likelihood score less than 10.83, representing a chi-squared significance value for p=0.001 (one degree of freedom). In this way, the filtering process reduced the set of candidate words to just those that appear to occur significantly more often than expected in the creativity corpus. To avoid extremely infrequent words disproportionately affecting the data, any word occurring fewer than five times was also removed from the data. Finally, the words were inspected to remove any `spurious' items such as proper nouns or misclassified or odd character sequences. This resulted in a total of 694 {\em creativity words\/}: a collection of 389 nouns, 205 adjectives, 72 verbs and 28 adverbs that occurred significantly more often than expected in the creativity corpus. Table 1 %\ref{S1_Table} 
gives the top 20 results of these calculations.

\subsection*{Identifying components of creativity}
\label{creat-comps}

It is important to note that our objective is to identify key themes in the lexical data, not to induce a comprehensive terminology of creativity. Despite the relatively small size of the corpora used, the resulting set of 694 creativity words is sufficiently rich for this purpose, but is still somewhat large to work with in its raw form. In previous, related work \cite{jordanous10a} an attempt was made to identify key components by manually clustering creativity words by inspection of the raw data. In practice, this proved laborious and made it impossible systematically to consider all of the identified words. It also raised issues of subjectivity and experimenter bias. These problems are addressed here, at least in part, by automatically clustering the words according to a statistical measure of {\em distributional similarity\/} \cite{lin98}.  The more manageable collection of clusters may then be examined to identify key components or dimensions of creativity.

The creativity words were clustered according  a statistical measure of distributional similarity due to Lin \cite{lin98}. The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}. This hypothesis  states that similarity of distribution correlates with similarity of meaning: two words that tend to appear in similar linguistic contexts will tend to have similar meanings. The notion of linguistic context here is not fixed and might plausibly be modelled in a variety of different ways. For example, two words might be considered to inhabit the same context if they appear in the same document or the same sentence or if they stand in the same grammatical relationship to some other word (e.g. both occur as {\em subject\/} of a particular verb or {\em modifier\/} of a given noun). In practice it has been shown that modelling distributiequationon in terms of grammatical relations leads to a tighter correlation between distributional similarity and closeness of meaning \cite{kilgarriff00}.

In the present work, grammatical relations are used to represent linguistic context  and distributional similarity is measured as a function of the number of  relations 
that two words share. To illustrate, evidence that the words {\em concept} and {\em idea} are similar in meaning might be provided by occurrences such as the following:

\begin{quote}
(1) the {\em concept/idea} involves \hfill (subject of verb `involve')\\
(2) applied the {\em concept/idea\/} \hfill (object of verb `apply') \\
(3) the basic {\em concept/idea\/} \hfill (modified by adjective `basic')
\end{quote}

\noindent
Grammatical relations were obtained from an analysis of the written portion of the British National Corpus \cite{leech92}, which had previously been processed using the RASP toolkit \cite{briscoe06} in order to extract them. Using this data, each word in the creativity corpus was associated with a list of all of the grammatical relations with which it occurred, together with their corresponding counts of occurrence.\footnote{Not all of the grammatical relation information output by RASP was used to calculate distributional similarity. In practice, just the subject, object and modifier relation types are used as these tend to give the best results \cite{weeds03}.} A potential difficulty with obtaining word similarity data based on the BNC (i.e. using data from sources of everyday usage of English, rather than from more specialist sources) would arise if the majority of the creativity words were used with distinctive or technical senses within the creativity corpus. From inspection and from knowledge of creativity literature, however, this situation was found to be unlikely. While some narrowly specialised usage may be present to some small degree in the set of creativity words, most words retain general senses as reflected in the wider BNC data set. An advantage of unsing the BNC is that its  size increases the chances of a comprehensive coverage of the general senses of each word of interest.

Distributional similarity of two words is measured in terms of the similarity of their associated lists of grammatical relations. A variety of different methods for calculating distributional similarity have been investigated in the literature, including standard techniques such as the cosine measure \cite[for example]{mannschu99}. The present work adopts an information-theoretic measure due to Lin \cite{lin98}, which has been widely used in language processing applications as a means of automatically discovering semantic relationships between words. In comparison to other similarity measures it has been shown to perform particularly well as a means of identifying near-synonyms \cite{weedsweir03,mccanavi09}.

Similarity scores were calculated between all pairs of creativity words of the same grammatical category. That is, scores were obtained separately for pairs of nouns, verbs, adjectives and adverbs. For a given set of words, word pair similarity data calculated in this way can be conveniently visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0), as in Fig. 2. % \ref{S2_Fig}.

Graphical representations of the similarity data like that shown in Fig. 2 % \ref{S2_Fig} 
provide a useful basis for analysing the creativity words and identifying recurring themes or components of creativity. Two complementary methods for identifying key components of the data were adopted:

\begin{description}

\item[Clustering:] The graph clustering software {\em Chinese Whispers} \cite{biemann06} was used to automatically identify word clusters (groups of closely interconnected words) in the dataset. This algorithm uses an iterative process to group together graph nodes that are located close to each other. By grouping words with similar meanings, the number of data items was effectively reduced and themes in the data could be recognised more readily from each distinct cluster. A sample of some of the resulting clusters can be seen in Fig. 3. %\ref{S3_Fig}. %To carry out Chinese Whispers, a preprocessing step was taken to categorise words according to their parts of speech, using the RASP software \cite{carrollRASP}.

\item[Inspection:] To focus on the words most closely related to creativity, the top twenty creativity words (i.e. the twenty  words with the highest log likelihood scores) were selected. Each word was then visualised as the root node of its own individual subgraph using the graph drawing software {\em GraphViz} \cite{graphviz}. In order to reduce the amount of data to be examined, similarity scores were discarded if they fell below a threshold value (adjusted manually for each graph to highlight the most strongly connected words). This made the size and complexity of the graphs smaller and therefore easier to inspect and analyse visually. Fig. 4 % \ref{S4_Fig}
illustrates, in diagram form, the process of using manual inspection to identify components.

\end{description}

As part of the manual inspection process, candidate components were further considered in terms of the {\em Four Ps} of creativity \cite{rhodes61,mooney63,mackinnon70,kaufman09} described earlier in this paper. This additional analysis provided a means of identifying alternative perspectives and revealing subtle (but still important) aspects of creativity.  For example, {\em novelty} is commonly associated with the results of creative behaviour ({\em product\/}): how novel is the artefact or idea that has been produced? However, we could similarly recognise as creative an approach to a task  ({\em process\/}) that does things in a novel and different way.  Also, if a product is new in a particular environment ({\em press\/}), then it may well be be regarded as creative to those in that environment. Viewing {\em novelty} from the perspectives of {\em product}, {\em process} and {\em press} uncovers these subtle and interlinked distinctions.

% Results and Discussion can be combined.
\section*{Results and Discussion}
\label{results}

\subsection*{Components of creativity}\label{componentsResults}

From the analysis steps described in the previous section it was possible to extract a set of fourteen key components of creativity. These components are summarised in Fig. 5 %\ref{S5_Fig} 
and are presented in more detail below. The components contribute collectively to the overall concept and may be regarded as providing an {\em ontology of creativity\/}.  It is important to note however that no claim is made here that the fourteen components constitutes a necessary and sufficient definition of creativity, in all its possible manifestations. There are two reasons for this. Firstly, 
some of the components we have identified appear to be logically inconsistent with others in the set. Consider for example the apparent need for autonomous, independent behaviour identified in {\em Independence and Freedom\/} and contrast this with the requirement for social interaction implied by {\em Social Interaction and Communication\/}. %\hidden{These factors may appear logically opposed.}
Secondly, of course, creativity %\hidden{does not lend itself to formal and precise definition and 
%I added this bit to clarify the point a bit [does not lend itself to formal and precise definition and]
also manifests itself in rather different ways across different domains \cite{plucker04} and components will vary in importance, according to the requirements of a particular domain. As an illustration of this second point, %Can we explicitly relate this illustration to one or more of the components that have been identified?
creative behaviour in mathematical reasoning has more focus on finding a correct solution to a problem than is the case for creative behaviour in, say,  musical improvisation \cite{colton08,jordanous12jims}.

The following set of fourteen components is therefore presented as a collection of dimensions -- attributes, abilities and behaviours, etc. -- which contribute to our understanding of creativity. The analysis of creativity in terms of the dimensions should be informative for a human audience and provide a basis for machine-understanding of the concept. 
%This approach is informed by debates in cognitive linguistics, computational linguistics and through philosophical underpinnings (see Background section). 
The components should be treated as {\em building blocks} for creativity that may be arranged in different ways and with different emphases to suit different definitional purposes. Each component is presented here with a brief explanation or gloss. These explanations will later be used for part of the semantic content in the creativity ontology.

%The current work illuminates the sorts of issues that arise in formal modelling of subjective or `soft' concepts such as creativity, which are unlikely to resolve to fixed, static meaning(s). For example,  some components appear  logically inconsistent with others in the set: e.g. the need for autonomous, independent behaviour ({\em Independence and Freedom\/}) versus the requirement for social interaction ({\em Social Interaction and Communication\/}). Also, creativity clearly manifests itself in different ways across different domains \cite{plucker04} and components will vary in importance, according to the requirements of a particular domain. For example, creative behaviour in mathematical reasoning has more focus on finding a correct solution to a problem than is the case for creative behaviour in, say,  musical improvisation \cite{colton08}. The set of creativity components are therefore presented as a collection of dimensions -- attributes, abilities and behaviours, etc. -- which contribute to an overall improvement in the understanding of creativity that provides greater clarity and information both to a human audience and in machine-readable form for future Linked Data links and applications on the Semantic Web.  This approach is informed by debates in cognitive linguistics, computational linguistics and through philosophical underpinnings (section \ref{cogPhil}).

\begin{description}

\item[Active Involvement and Persistence:] \mbox{}\\
{\em Being actively involved; reacting to and having a deliberate effect on the creative process.\/}\\
{\em The tenacity to persist with the creative process throughout, even during problematic points\/}.

\item[Dealing with Uncertainty:] \mbox{}\\{\em
Coping with incomplete, missing, inconsistent, contradictory, ambiguous and/or uncertain information. Element of risk and chance - no guarantee that information problems will be resolved.\\
Not relying on every step of the process to be specified in detail; perhaps even avoiding routine or pre-existing methods and solutions.
}

\item[Domain Competence:] \mbox{}\\{\em
Domain-specific intelligence, knowledge, talent, skills, experience and expertise.\\
Knowing a domain well enough to be equipped to recognise gaps, needs or problems that need solving and to generate, validate, develop and promote new ideas in that domain.
}

\item[General Intellectual Ability:] \mbox{}\\{\em
General intelligence and IQ.\\
Good mental capacity.
}

\item[Generation of Results:] \mbox{}\\
{\em Working towards some end target, goal, or result.\/}\\
{\em Producing something (tangible or intangible) that previously did not exist.\/}

\item[Independence and Freedom:] \mbox{}\\{\em 
Working independently with autonomy over actions and decisions.\\
Freedom to work without being bound to pre-existing solutions, processes or biases; perhaps challenging cultural or domain norms.
}

\item[Intention and Emotional Involvement:] \mbox{}\\{\em
Personal and emotional investment, immersion, self-expression and involvement in the creative process.\\
The intention and desire to be creative: creativity is its own reward, a positive process giving fulfilment and enjoyment.
}

\item[Originality:] \mbox{}\\{\em
Novelty and originality; a new product, or doing something in a new way; seeing new links and relations between previously unassociated concepts.\\
Results that are unpredictable, unexpected, surprising, unusual, out of the ordinary.
}

\item[Progression and Development:] \mbox{}\\{\em
Movement, advancement, evolution and development during a process.\\
Whilst progress may or may not be linear, and an actual end goal may be only loosely specified (if at all), the entire process should represent some progress in a particular domain or task. }

\item[Social Interaction and Communication:] \mbox{}\\{\em
Communicating and promoting work to others in a persuasive and positive manner.\\
Mutual influence, feedback, sharing and collaboration between society and individual.
}

\item[Spontaneity/Subconscious Processing:] \mbox{}\\{\em 
No need to be in control of the whole process; thoughts and activities may inform the process subconsciously without being inaccessible for conscious analysis, or may receive less attention than others. \\
Being able to react quickly and spontaneously when appropriate, without needing to spend too much time thinking about the options.
}

\item[Thinking and Evaluation:] \mbox{}\\{\em 
Consciously evaluating several options to recognise potential value in each and identify the best option, using reasoning and good judgement.\\
Proactively selecting a decided choice from possible options, without allowing the process to stagnate under indecision.
}

\item[Value:] \mbox{}\\{\em 
Making a useful contribution that is valued by others and recognised as an achievement and influential advancement; perceived as special, `not just something anybody would have done'.\\
The end product is relevant and appropriate to the domain being worked in.
}

\item[Variety, Divergence and Experimentation:] \mbox{}\\{\em 
Generating a variety of different ideas to compare and choose from, with the flexibility to be open to several perspectives and to experiment and try different options out without bias.\\
Multi-tasking during the creative process.
}
\end{description}

\subsection*{Implementing a machine-readable ontology of creativity}\label{creativityOntology}

The fourteen components provide a fuller and clearer account of the constituent parts of the concept of creativity. An important aim of the current work is to make the components available as a resource for other researchers in computational creativity and to provide a basis for the automated evaluation of creative systems. As a step in this direction, the components have been expressed in an open, machine-readable form within the Semantic Web. In this way, the definition of the components benefits from and are enriched by concepts that are already defined within the Semantic Web. %To achieve this, SKOS (Simple Knowledge Organisation System) \cite{skos} was used as a basis for constructing an OWL ontology representation of creativity and its components,

In particular, the components are linked to the data in WordNet \cite{fellbaum98}, a large lexical database of English that has recently been made available as a Semantic Web ontology \cite{wordnetRKB}. In WordNet, words are grouped by sense and interlinked by lexical and conceptual relations. Note that, although the WordNet definition of the word such as `creativity' is brief (`the ability to create'), its utility lies in how it is linked to various concepts, such as its sense, hyponyms, type, `gloss' (brief definition) and other related concepts. Each creativity component relates to a cluster of keywords from the original set of 694 creativity words. Following Linked Data principles, each can therefore be linked across the Semantic Web to an appropriate set of concepts from WordNet. In this way,  associated semantic information is provided for each component. 
%The SKOS ontology incorporates three main classes:  {\em skos:Concept}  (anything we may want to record information about), {\em skos:ConceptScheme} (a set that collectively defines a skos:Concept) and  {\em skos:Collection} (a collection of semantically-related information). An instance of {\em skos:ConceptScheme\/} was created as {\em CreativityComponents}, to represent the set of components that defines the {\em skos:Concept\/} of {\em Creativity}. Each component is represented as an individual {\em skos:Concept\/}.

The resulting encoding can be visualised as a graph, as shown in Fig. 6. %\ref{S6_Fig}. 
The data has also been published under an Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} at:
%as an OWL/XML file at:
\begin{quote}
\texttt{\scriptsize http://purl.org/creativity/ontology}
\end{quote}
%under a Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} .
%The {\em skos:Concept\/}  
The concept labelled {\em Creativity} has the unique URI: 
\begin{quote}
\texttt{\scriptsize http://purl.org/creativity/ontology\#Creativity}
\end{quote}%
Any Linked Data that needs to refer to the concept can use this identifier.

%\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
%\caption{
%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
%\begin{tabular}{|l|l|l|l|l|l|l|l|}
%\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
%\end{tabular}
%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
%\end{flushleft}
%\label{table1}
%\end{adjustwidth}
%\end{table}

% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.

%\section*{Discussion}
%\label{implications}

%As already noted above, the need for a clearer, multi-perspective and broadly applicable account of creativity is evident: this point has been repeatedly underlined by creativity researchers \cite[for example]{rhodes61,torrance67,plucker04defn,kaufman09,hennessey10}.  As Hennessey and Amabile point out \cite{hennessey10}, an accurate and comprehensive account assists our understanding of creativity and further research. It also helps smooth out individual differences of interpretation,   highlighting common ground and transcending discipline or domain bias \cite{plucker04}. The novel, language-driven approach to definition adopted in the present work draws together multiple perspectives across disciplinary divides and a confluence approach yields a broader understanding of the concept in the form of an ontology of creativity.

%There are a number of ways to evaluate Semantic Web ontologies \cite{brank05}. For the purposes of the creativity ontology presented in this paper, evaluation based on matching any `golden standards' \cite{brank05} is not so appropriate given the lack of any such standards or baselines to adopt, as discussed above in the Introduction of this paper and elsewhere \cite{rhodes61,taylor88,sternberg99a,plucker04defn,kaufman09,jordanousphd,jordanous12cc}. It is hoped that publication of the creativity ontology can now facilitate future applications in description and evaluation of creativity, for application-based evaluation of the ontology, perhaps incorporating other data sources to enable data-driven evaluation. In areas of knowledge representation such as that tackled in this paper, it is not appropriate to test the ontology definitions against `a set of predefined criteria, standards, requirements, etc.' \cite{brank05} as these sets do not necessarily exist,  but the spirit of such recommendations can be followed by seeing how the ontology matches against human interpretations of the same concepts. One can also evaluate how the ontology data can be linked to other data sources \cite{bizer09}. Hence, as a reflection of the cross-disciplinary nature of this work, evaluation of the creativity ontology is two-fold, concerning both the cognitive accuracy of this representation of creativity and evaluation of the creativity data publication as an output of Semantic Web research.

\section*{Evaluation}

From a practical stand-point, the current work is part of an overarching project engaged with the question of the evaluation of creativity, particularly computational creativity \cite{jordanous12cc}. It is clear that a rigorous and comparative evaluation process needs clear standards to use as guidelines or benchmarks \cite{torrance88,kaufman09}.

The components of creativity in this paper have been employed in two case studies to evaluate the creativity of computational systems \cite{jordanousphd,jordanous12jims,jordanous16aisb}. In these case studies, evaluation was carried out using the three step approach of the Standardised Procedure for Evaluating Creative Systems (SPECS) \cite{jordanous12cc}:

\begin{quote}
\begin{enumerate}
\item Identify a definition of creativity that your system should satisfy to be considered creative:
	\begin{enumerate}
	\item What does it mean to be creative in a general context, independent of any domain specifics?
	\item What aspects of creativity are particularly important in the domain your system works in (and what aspects of creativity are less important in that domain)?
	\end{enumerate}
\item Using Step 1, clearly state what standards you use to evaluate the creativity of your system.
\item Test your creative system against the standards stated in Step 2 and report the results.
\end{enumerate}    
\end{quote}

In both case studies, the components of creativity were chosen as the way of defining creativity for step 1a of SPECS, and were weighted according to their importance and relevance for creativity in the creative domains under study for each case study (step 1b of SPECS). Each component was treated as one standard to be used to evaluate the creativity of the creative systems in the case studies (step 2 of SPECS). Each case study system was then tested against each component using feedback provided by judges (step 3 of SPECS), resulting in a detailed set of evaluative feedback on the creativity of each system in the case studies.

Case Study 1 \cite{jordanousphd,jordanous12cc} evaluated the creativity of three different computational musical improvisation systems \cite{jordanous12cc}. 
Case Study 2 used the components of creativity in an evaluation scenario where information and time was limited for evaluation, to simulate the forming of first impressions and snapshot judgements of the creativeness of a given computational creativity system \cite{jordanousphd,jordanous16aisb}.

The resulting component-based evaluation yielded detailed information about creative strengths and weaknesses of the systems under investigation, highlighting those components where a system performs strongly. Crucially, the evaluation feedback also highlighted areas where a given system performed poorly. For example, in the musical improvisation study, Case Study 1, we found that all systems' creativity could be improved most by improving performance in {\em Social Interaction and Communication}, {\em Intention and Emotional Involvement} and {\em Domain Competence} (the three components found to be most important for creativity in musical improvisation). Similarly, it is useful to be able to quickly obtain formative feedback on strengths and weaknesses in time-limited scenarios such as that replicated in Case Study 2 during the development of creative systems (when ongoing evaluation of progress ideally needs to be both timely and time-efficient). Insight can then be obtained on where future development effort is best spent.

The results obtained above were compared with those from applying other evaluation models and with surveys of people's opinions, where people were asked how creative they thought each system was. There was general agreement between evaluation approaches on the most and least creative systems. The approaches differed in the formative feedback they provided, particularly for identifying strengths of the system at being creative, and weaknesses of the system to be improved. The model of creativity offered in this paper gave the most detailed feedback, but required most information to be collected.

To support the usefulness of having the components as a tangible characterisation of creativity, an interesting finding was made as part of the first case study, in a separate evaluation carried out: asking for people's opinions on how creative the musical improvisation systems were. A striking observation was that a number of participants called for the word ``creativity'' to be defined before they felt comfortable with the task and confident in evaluating creativity in this setting, even though participants reported feeling generally positive or at least neutral towards the concept of computational creativity. This challenges the generally held view that people have a  common-sense working definition of creativity, at least in the context of judgement and evaluation. A representation of creativity is useful to:

\begin{enumerate}
\item establish what it means for something to be deemed creative; and
\item identify appropriate evaluation standards that replicate typical human opinion on how creative something is or in comparing two or more creative systems.
\end{enumerate}

\subsection*{Conclusions and directions for future work}
\label{conclusions}

This paper has described the methods used to identify a set of {\em components of creativity} using corpus-based, statistical language processing techniques. The motivation for the work is the need for a shared, comprehensive, multi-perspective account of creativity. Such an account should be of great value to researchers investigating the nature of creativity and in particular those concerned with the evaluation of creative practice. More broadly, the inter-disciplinary approach described here exemplifies a general approach to the investigation and representation of semantically fuzzy and essentially-contested concepts. For this reason, we expect that it will interest other researchers investigating computational methods for analysing and representing such concepts.

Rather than attempting to provide a unitary definition of creativity, our approach extracts common, underlying themes that transcend discipline or domain bias. Our point of departure is the observation that the vocabulary used in discussions of the nature of creativity may be analysed in order to throw light on our understanding of the concept and its key attributes. Using techniques from corpus linguistics and natural language processing (as described in the Methods section), key components of creativity have been identified. The results of this novel, empirical analysis (presented in the Results section) inform the development of an {\em ontology of creativity\/} comprising a set of fourteen distinct components (see Fig. 5). %\ref{S5_Fig}).
It is noted that each component makes a separate contribution to the overall meaning of the concept. At the same time, because creativity manifests itself in different ways across different domains \cite{plucker04}, the individual components vary in importance and influence according to the requirements of a given domain. The components can be therefore be usefully thought of as 'building blocks' for the concept in its different manifestations. Taken together, the components make creativity more tractable to study and to evaluate.

The fourteen components provide a multi-perspective characterisation of creativity that has been successfully applied in a comparative analysis and evaluation of computational creativity systems \cite{jordanous12cc,jordanousphd,jordanous16aisb} (see the Discussions section). The outcome of the evaluation process provides relatively fine-grained information about the creative strengths of a given system. This information in turn evidences ways in which a system could be considered creative. In addition, evaluation based on the components is able to highlight areas of weakness. These can be used to inform future work aimed at further developing a system's creative potential.

The components have been published in an open, machine-readable format, making them freely available to the research community. This has a number of implications. First, the set of components may be readily elaborated, extended or amended by other researchers investigating the concept of creativity. Second, the machine-readable format facilitates the development of creativity-aware applications, based on the components. Such applications might be developed to support manual evaluation of creative practice or as a significant step towards the development of methods for automated evaluation.

The problem of developing automated evaluation has elsewhere been described as `the Achilles' heel of AI research on creativity' \cite{boden99}.  An intriguing possibility that we are currently exploring is to further exploit language processing techniques to perform evaluation based on textual reviews, descriptions of system performance, or social media interactions \cite{jordanous15vem}. Such an approach would be analogous to the way sentiment analysis techniques are now used to evaluate attitude and opinion based on reviews of products or services \cite{panglee08}. This is a fascinating direction for future work, with great potential for real progress towards tackling computational creativity's `Achilles' heel'.

\section*{Supporting Information}

% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
%\subsection*{S1 Video}
%\label{S1_Video}
%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

%\subsection*{S1 Text}
%\label{S1_Text}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Fig}\label{S1_Fig}
{\bf The 30 papers that make up the Creativity Corpus} 
%\begin{figure}
%\caption{The 30 papers that make up the Creativity Corpus}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\includegraphics[width=\textwidth]{images/papersImage}
%\label{S1_Fig}
%\end{figure}

\subsection*{S2 Fig}
\label{S2_Fig}
{\bf Graph representation of the similarity of the nouns {\em concept} and {\em idea} and closely semantically related words. Each word is drawn as a node in the graph, linked together by a weighted edge representing the similarity of the two words (maximum similarity strength is 1.0).} 
%\begin{figure}[!ht]
% \begin{center}
%\includegraphics[scale=0.5]{images/conceptIdea}
% \end{center}
% \caption{Graph representation of the similarity of the nouns {\em concept} and {\em idea} and closely semantically related words. Each word is drawn as a node in the graph, linked together by a weighted edge representing the similarity of the two words (maximum similarity strength is 1.0).}
% \label{S2_Fig}
%\end{figure}

\subsection*{S3 Fig}
\label{S3_Fig}
{\bf Sample of clusters produced by the Chinese Whispers clustering step.}
%\begin{figure}
% \caption{Sample of clusters produced by the Chinese Whispers clustering step.}
%\includegraphics[width=\textwidth]{images/clustersZoom}
% \label{S3_Fig}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\end{figure}

\subsection*{S4 Fig}
\label{S4_Fig}
{\bf Illustration of the process of using manual inspection for further clustering.}
%\begin{figure}
% \caption{Illustration of the process of using manual inspection for further clustering.}
%\includegraphics[width=\textwidth]{images/clusterToComponents}
% \label{S4_Fig}
% REMOVE IMAGES FROM SUBMITTED VERSION
%\end{figure}

\subsection*{S5 Fig}
\label{S5_Fig}
{\bf The fourteen key components of creativity identified through an analysis of the word clusters}
%\begin{figure} 
%\caption{The fourteen key components of creativity identified through an analysis of the word clusters}
%\includegraphics[width=\textwidth]{images/factorsOnly}
%\label{S5_Fig}
%\end{figure}

\subsection*{S6 Fig}
\label{S6_Fig}
{\bf The ontology of Creativity, in graph form.}
%\begin{figure}
%\caption{The ontology of Creativity, in graph form.}
%\includegraphics[scale=0.5]{images/ontGraph}
%\label{S6_Fig}
%\end{figure}

\subsection*{S1 Table}
\label{S1_Table}
{\bf The top 20 results of the log-likelihood ratio (LLR) calculations. A significant LLR score at p=0.001 is 10.83. N.B. POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.} 
%\begin{table}[!ht]%dp]
%\begin{center}
%\begin{tabular}{c c | c c}
%Word (\& POS tag) & LLR & Word (\& POS tag) & LLR \\
%\hline
%thinking (N) & 834.55 & process (N) & 612.05 \\
%innovation (N) & 546.20 & idea (N) & 475.74 \\
%program (N) & 474.41 & domain (N) & 436.58 \\
%cognitive (J) & 393.79 & divergent (J) & 355.11 \\
%openness (N) & 328.57 & discovery (N) & 327.38 \\
%primary (J) & 326.65 & originality (N) & 315.60 \\
%criterion (N) & 312.61 & intelligence (N) & 309.31 \\
%ability (N) & 299.27 & knowledge (N) & 290.48 \\
%create (V) & 280.06 & experiment (N) & 253.32 \\
%plan (N) & 246.29 & agent (N) & 246.24 \\
%\end{tabular}
%\end{center}
%\caption{The top 20 results of the log-likelihood ratio (LLR) calculations. A significant LLR score at p=0.001 is 10.83. N.B. POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
%\label{S1_Table}
%\end{table}%

\section*{Acknowledgments}
We would like to acknowledge Nick Collins and Chris Thornton for their helpful comments during this work.

\nolinenumbers

%\section*{References}
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% OR
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here.
%

\bibliography{references}

%\begin{thebibliography}{10}
%\bibitem{bib1}
%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS. Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes. Mol Immunol. 2014 Nov 22. pii: S0161-5890(14)00313-7. doi: 10.1016/j.molimm.2014.11.005
%
%\bibitem{bib2}
%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
%
%\end{thebibliography}

\end{document}

### 2016-05-05 plosOneJordanousKeller/PlosONE2/instruction to authors/PLoS ONE instructions to authors_files/asset_EX4VNEIQU5IB46JRJI3Y5OFMEADZPYJK.js

@@ -1,0 +1,71 @@
+/*!
+ * jQuery JavaScript Library v1.11.0
+ * http://jquery.com/
+ *
+ * Includes Sizzle.js
+ * http://sizzlejs.com/
+ *
+ * Copyright 2005, 2014 jQuery Foundation, Inc. and other contributors
+ * Released under the MIT license
+ * http://jquery.org/license
+ *
+ * Date: 2014-01-23T21:02Z
+ */
+(function(b,a){if(typeof module==="object"&&typeof module.exports==="object"){module.exports=b.document?a(b,true):function(c){if(!c.document){throw new Error("jQuery requires a window with a document");}return a(c);};}else{a(b);}}(typeof window!=="undefined"?window:this,function(a5,av){var aP=[];var O=aP.slice;var az=aP.concat;var w=aP.push;var bU=aP.indexOf;var ac={};var x=ac.toString;var J=ac.hasOwnProperty;var Z="".trim;var C={};var ai="1.11.0",bI=function(e,i){return new bI.fn.init(e,i);},D=/^[\s\uFEFF\xA0]+|[\s\uFEFF\xA0]+$/g,bS=/^-ms-/,aW=/-([\da-z])/gi,N=function(e,i){return i.toUpperCase();};bI.fn=bI.prototype={jquery:ai,constructor:bI,selector:"",length:0,toArray:function(){return O.call(this);},get:function(e){return e!=null?(e<0?this[e+this.length]:this[e]):O.call(this);},pushStack:function(e){var i=bI.merge(this.constructor(),e);i.prevObject=this;i.context=this.context;return i;},each:function(i,e){return bI.each(this,i,e);},map:function(e){return this.pushStack(bI.map(this,function(b7,b6){return e.call(b7,b6,b7);}));},slice:function(){return this.pushStack(O.apply(this,arguments));},first:function(){return this.eq(0);},last:function(){return this.eq(-1);},eq:function(b7){var e=this.length,b6=+b7+(b7<0?e:0);return this.pushStack(b6>=0&&b6<e?[this[b6]]:[]);},end:function(){return this.prevObject||this.constructor(null);},pu
[…]

### 2016-05-05 plosOneJordanousKeller/rebuttal.txt
initial commit and re-organising

PONE-D-16-09839
Creativity is what we say it is: identifying key components of creativity
PLOS ONE

We invite you to submit a revised version of the manuscript that addresses all concerns of the Reviewers. When doing this please indicate in your accompanying letter the exact places of the manuscript, which were changed as the response of the Reviewers’ remark. Please insert a change to the manuscript as a response of each concern. Please insert a section to the Discussion part of the revised manuscript even in case you disagree with any comment of the Reviewers noting the alternative view and the detailed reasons of your disagreement.

 ***** IF THERE ARE ANY POINTS WE WANT TO DISAGREE WITH, WE NEED TO PUT COMMENTARY ON THIS IN THE DISCUSSION OF THE PAPER  *****

We encourage you to submit your revision within forty-five days of the date of this decision. Please note that any manuscripts that require a revision period greater than 6 months should be resubmitted as a new submission to PLOS ONE. Any manuscripts remaining in Editorial Manager after 6 months will be withdrawn.

 ***** DATE OF DECISION 7 APRIL

When your files are ready, please submit your revision by logging on to http://pone.edmgr.com/ and following the Submissions Needing Revision link. Do not submit a revised manuscript as a new submission. Before uploading, you should proofread your manuscript very closely for mistakes and grammatical errors. Should your manuscript be accepted for publication, you may not have another chance to make corrections as we do not offer pre-publication proofs.

 ***** SEE ABOVE!!!  *****

In addition, when submitting your revision please include the following items:

* A rebuttal letter that responds to each point brought up by the academic editor and reviewer(s). This letter should be uploaded as a 'Response to Reviewers' file.
* A clean revised manuscript as your 'Manuscript' file.
* A marked-up copy of the changes made from the previous article file as a 'Revised Manuscript with Track Changes' file. This can be done using 'track changes' in programs such as MS Word and/or highlighting any changes in the new document.
***** WE'VE AGREED TO USE LATEX STRIKETHROUGH FOR REMOVED TEXT, AND BOLD FONT FOR ADDED TEXT *****

While revising your submission, we encourage you to use PACE (the Preflight* Analysis and Conversion Engine, http://pace.apexcovantage.com/), a digital diagnostic and conversion tool for figure files. PACE helps users ensure that their figures meet PLOS requirements and that the quality of published figures will be as high as possible.

***** ANNA TO LOOK AT THIS *****

To use PACE, you must first register as a user. Then, login and navigate to the UPLOAD tab, where you will find detailed instructions on how to use the tool. If you encounter any issues or have any questions when using PACE, please email us at figures@plos.org.

For more information on how to upload your revised submission, see our video: http://blogs.plos.org/everyone/2011/05/10/how-to-submit-your-revised-manuscript/

When submitting your revision, we need you to address these additional requirements.

Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at

http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf

***** For some reason, we've fallen foul of some of these, so I'll check that *****

1.  We request that you please report additional details in your Methods:
i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
ii) The specific methods for selecting papers, including inclusion and exclusion criteria
In addition, please include a figure of a flow diagram describing your search strategy (see http://prisma-statement.org/PRISMAStatement/FlowDiagram.aspx for examples)
We appreciate your attention to these requests."

***** ANNA TO DO THIS *****

JW (Assoc Ed) 9 Mar 2016: **EO** At PRTC, please go back for crosscheck, do not ping with follow up. For crosscheck, please go back with "Thank you for submitting the above manuscript to PLOS ONE. During our internal evaluation of the manuscript, we found significant text overlap between your submission and the following previously published works, on which you are an author:

http://www.creativitypost.com/technology/technology/evaluating_computational_creativity
The re-use of text from a previous publication may have implications for the copyright or license that applies to the published article. To avoid any concerns in this respect, we would recommend that you revise the manuscript to either remove any text overlap where possible/appropriate, or to clearly indicate that the text reproduces information already reported in detail elsewhere (e.g. “As described in detail previously [ref],…”) citing the relevant sources.

  ***** BILL TO CHECK THIS OVERLAP WITH THE MENTIONED BLOG POST *****

2.

We note that you stated “data are available upon request” at submission. Could you please upload the minimal data set underlying the findings in your study in the manuscript, supplemental files, or in a stable public repository? If this is not the case, and your data are available upon request because of an ethical or legal restriction, or because you obtained data from a third party, please include the following in your revised cover letter:

 ***** BILL TO UPLOAD WORKING DATA SET TO SUSSEX REPOSITORY AND ADD LINK TO DataAvailabilityStatement.rtf FILE  *****

3. Please upload a copy of Figure1-6, to which you refer ithroughtout your manuscript. If the figure is no longer to be included as part of the submission please remove all reference to it within the text.

4. Please include a copy of Table 1 which you refer to in your text on page 11.

***** THESE WERE INCLUDED BUT NEEDED TO BE HIGHER RESOLUTION (SEE REVIEWER 2 COMMENTS) - ANNA TO REVISE FIGURES/TABLES  *****

Reviewer #1: This is interesting paper that could have some value in the literature on creativity and innovation. The conceptual framing of the paper did not work for me, but I see a path forward for the authors that would help clarify what they’re trying to do – and the implications that can be drawn from their results.

My major concerns about the paper are (a) the implied reification in the title, abstract, and introduction; and (b) that the authors aren’t really attempting to come up with a definition at all.

Implied reification. To say that creativity is subjective and difficult if not impossible to define would have been understandable 20 years ago, but this was a major weakness of the field and many scholars have tackled the issue. Several highly cited papers have focused the field on a general definition – interestingly, this paper cites most of them – and most creativity scholars consider this to be a minor issue in the field today. To frame a paper such as this one around the idea that the definition of creativity is subjective and still needs to be found is a bit odd, as it implies that creativity is a real thing that we have yet to discover adequately. But creativity doesn’t really exist; rather, it’s a label we made up to describe certain behaviors and outcomes. So “discovering” the definition feels weird to me. The authors can disagree with the definitions at hand, or revise them, or argue that we’ve been defining it incorrectly all this time – those would all be fair perspectives (e.g., Dean Keith Simonton makes these arguments regularly, and his analyses are moving the field forward). But to argue that we haven’t hit on the right definition yet? I’m not sure that’s a workable approach.

Is the point really a definition? I suspect it’s not. The resulting “definition” (Figures S5 and S6) doesn’t strike me as a definition at all. It’s a clever, unique approach to a model (or maybe even the beginnings of a theory) of creativity, essentially a meta-model along the lines of what Vartanian (2014) called for recently. But I know of no one – not a scholar, not a practitioner – who would provide such a “definition” when asked what creativity is. But if asked for a model on how creativity emerges, I think the authors’ proposed model is something they would share.

 ***** BILL TO DEAL WITH ABOVE POINTS AND REFRAMING  *****

In general, I found the methods to be well-explained and carefully done, but I have some experience using these methods (albeit limited), and other reviewers without such experience may request greater detail, which I would understand. But for me, they felt appropriate and offered a unique way to get at the components of creativity.

 ***** ANNA TO ADD MORE DETAIL ON METHODOLOGY FOR IDENTIFYING PAPERS AS REQUESTED BY EDITOR. 
       BILL TO CHECK TECHNICAL DETAIL OF METHODS AND SEE IF THEY ARE REPORTED IN AN APPROPRIATE LEVEL OF DETAIL  *****

I recommend reframing the paper as a meta-model or meta-theory employing previously unused methods. That gets to the heart of the matter much more directly (and accurately), and it speaks to the type of work Vartanian and others have been calling for as the field of creativity matures.

 ***** THIS FITS INTO THE WORK BILL IS DOING FOR THE ABOVE POINT  *****

Reference
Vartanian, O. (2014). Toward a cumulative psychological science of aesthetics, creativity, and the arts. Psychology of Aesthetics , Creativity , and the Arts, 8(1), 15-17.

 ***** LET'S BOTH READ THIS! BILL TO ADD SOME CONTENT RELATIVE TO THIS WHILE DEALING WITH REVIEWER 1's FIRST POINT *****

Reviewer #2: Review of “Creativity is what we say it is: identifying key components of creativity” for PLoS ONE

This paper proposes that creativity be defined in terms of themes emerging as a result of word clusters analysis of scholarly papers on creativity. I am not convinced that this approach captures the essence of what creativity is (any more than doing this kind of word cluster analysis of your own name on the internet would capture the essence of who you are).

***** BILL I'M SURE WE COULD ADD REFERENCES TO SUPPORT OUR APPROACH AGAINST THIS CRITICISM? ****

I am sympathetic with Gabora, O’Connor, & Ranjan’s (2012) conviction of that creativity needs to be defined in terms of internal change to the creator’s network of understandings. I am not altogether convinced by the authors’ that this kind of analysis makes creativity easier to evaluate. However, the approach is new and interesting and at the very least could provoke fruitful discussion of what is meant by creativity. Therefore I believe it could make a valuable contribution to the literature.

Literature Cited
Gabora, L., O’Connor, B., & Ranjan, A. (2012). The recognizability of individual creative styles within and across domains. Psychology of Aesthetics, Creativity, and the Arts, 6(4), 351-360.

 ***** ANNA TO CHECK HOW THE GABORA ET AL PAPER FITS INTO THIS
       (UNLESS THIS COMES UP IN THE WORK BILL IS DOING FOR REVIEWER 1'S MAIN POINT??) *****

A concern I have about the methodology concerns the set of papers used in the analysis, provided in Figure 1. (Note: this figure is rather hazy; in the final paper a higher resolution version should be used.) Despite the authors’ intention to capture how is creativity is understood from a broad range of vantage points and disciplines, almost all of these papers are in psychology journals. In my view they should have included papers from other scholarly journals that discuss creativity and innovation, e.g. design, architecture, art, theatre, film, multimedia, creative writing, electronic arts, and engineering journals.

 ***** ANNA TO ADD DIAGRAM REPRESENTING JOURNAL MAKE UP AND COMMENT ON THIS IN REBUTTAL/DISCUSSION OF PAPER  *****

I would suggest that the authors exaggerate the extent to which scholars differ in their view of what constitutes creativity (see p. 5). Completely unanimous agreement on anything in psychology is rare but it seems to me there is pretty unanimous agreement that creativity be defined in terms of (1) new/original and (2) useful/aesthetically appealing, or some variant of these. The authors’ approach still makes an interesting and provocative contribution even if there is widespread agreement on what creativity is.

 ***** ANNA TO ADD CONTENT ON HOW novelty/usefulness ARE NECESSARY BUT NOT SUFFICIENT, USING COMPUTATIONAL CREATIVITY SOFTWARE AND EXTRA COMMENTARY ON CREATIVITY = NOVELTY+USEFULNESS+???  *****

The paper is well-written overall, though there are some minor spelling / grammatical errors, e.g., “which” instead of “that on the first line of the abstract, and missed commas, e.g., after the word ‘sciences’ in the second paragraph.

 ***** WE'LL BOTH CATCH SOME OF THESE DURING PROOFREADING/EDITING/FINAL SPELL CHECK. BILL WOULD YOU MIND CHECKING THESE PARTICULAR TYPOS? *****

### 2016-05-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
Changes from papeeria
Edits on method

--- 2016-05-05 plosOneJordanousKeller/PlosONE2/plos_JordanousKeller.tex
@@
 \usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
+%\DisableLigatures[f]{encoding = *, family = * }
 
@@
 \usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+
+% Use strikethrough for track changes 
+\usepackage[normalem]{ulem}
+% command is \sout{text text text etc}
 
@@
 The 30 papers selected for the creativity corpus are listed in Fig. 1. %\ref{S1_Fig}.
-The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines.
+
+i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
+ii) The specific methods for selecting papers, including inclusion and exclusion criteria
+
+\textbf{Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines: }
+\begin{itemize}
+\item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
+\item \textbf{The primary inclusion criterion was to choose particularly influential papers, as measured by the number of times it had been cited by other academic authors.
+For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
+\item \textbf{Cross section of years [the corpus was compiled in 2010] over the range of years 1950-2009.
+1950 was chosen as a starting point in recognition of the effect of J.
+P.
+Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof).
+His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.}
+\end{itemize}
+\sout{The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines.
 A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors.
-For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.
+For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
 

### 2016-05-19 plosOneJordanousKeller/rebuttal.txt
Changes from papeeria - additions to response/rebuttals document

@@
 
-***** ANNA TO DO THIS *****
+*****
+* We have added, as requested, the detailed overview of our search strategy and the methods/criteria for selecting papers.
+This is reported in text added in the Methods section.
+Thank you for the link to the flow diagram examples.
+***** PRISMA - ANNA TO DO THIS *****
 
@@
 
- ***** ANNA TO ADD DIAGRAM REPRESENTING JOURNAL MAKE UP AND COMMENT ON THIS IN REBUTTAL/DISCUSSION OF PAPER  *****
+ ***** 
+ * We have edited the figure accordingly, thank you for this feedback.
+Regarding the raised concern: we have added a diagram representing the disciplinary makeup of the corpus, as categorised by the journal disciplinary classification in Scopus.
+Additionally, we have commented on the disciplinary coverage as part of the added text in the Methods section, which give a detailed report and discussion of our search strategy and methods for compiling the corpus.
+ *****
 

### 2016-05-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
edits to add specific detail on search strategy and inclusion/exclusion criteria.

@@
 
-A sample of academic papers discussing the nature of creativity was assembled.
-This {\em creativity corpus\/} consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.
+A sample of academic papers discussing the nature of creativity was assembled as a {\em creativity corpus\/} in 2010.
+This creativity corpus consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.
 
@@
 
-The 30 papers selected for the creativity corpus are listed in Fig. 1. %\ref{S1_Fig}.
-
-i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
-ii) The specific methods for selecting papers, including inclusion and exclusion criteria
-
-\textbf{Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines: }
+The 30 papers selected for the creativity corpus are listed in Fig. 1a. %\ref{S1a_Fig}.
+
+%**** i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus ****
+%**** ii) The specific methods for selecting papers, including inclusion and exclusion criteria ****
+
+\textbf{The search strategy for identifying papers for the corpus was based around a literature search for the term `creativity' on the academic database {\em Scopus}.
+Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
+The inclusion criteria are as follows, listed in descending order of precedence: }
 \begin{itemize}
 \item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
-\item \textbf{The primary inclusion criterion was to choose particularly influential papers, as measured by the number of times it had been cited by other academic authors.
-For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
-\item \textbf{Cross section of years [the corpus was compiled in 2010] over the range of years 1950-2009.
-1950 was chosen as a starting point in recognition of the effect of J.
+\item \textbf{Papers should be considered particularly influential, as measured by the number of times it had been cited by other academic authors.
+For papers published in recent years and which have consequently not yet accrued many citations, selection was based on our subjective judgement of influence.}
+\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009.
+[The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J.
 P.
 Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof).
-His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.}
+His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.
+}
+\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of what creativity is.
+Fig.
+1b.
+illustrates the disciplinary distribution of the corpus as it changes over the time period included in the corpus, according to journal disciplinary classification in the academic database {\em Scopus}, which classifies journals under their main subject area(s) covered.
+We should acknowledge here though that while many disciplines include work that applies information about creativity, often the focus is on application rather than in depth discussion of what creativity entails.
+Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the key focus of our corpus as a representation of key discussions about the nature of creativity.}
 \end{itemize}
@@
 For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
+
+\textbf{Exclusion criteria for this search were: }
+\begin{itemize}
+\item \textbf{Authors were only represented more than one in the corpus if the relevant papers were written from different perspectives.
+For example, Mark Runco's work is represented twice in the corpus, but covering two different topics relating to the nature of creativity (psychoeconomic approach to creativity; cognition and creativity).
+If the search process highlighted two or more papers with a shared author, on the same or highly similar perspectives on creativity, then the more highly cited paper was chosen.
+}
+\item \textbf{Papers had to be written in English, as the language processing tools we were working with were for English language texts.}
+\item \textbf{Papers had to be available in a format that plain text could be extracted from (this excluded books or book chapters).}
+\end{itemize}
 
@@
 Our objective is to identify what is distinctive in the language used to discuss creativity, in contrast to the language used to discuss other topics.
-As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled.
+As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled \textbf{alongside the creativity corpus, in 2010}.
 
@@
 {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).
+\textbf{In other words, inclusion for this second corpus was based on the criteria of if a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus (as determined by {\em Scopus}), and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.}
 
@@
 \noindent
+
+\textbf{Some pre-processing was undertaken for each paper in both the creativity corpus and non-creativity corpus prior to analysis.
+A plain text file was generated for each paper, containing the full text of that paper.
+All journal headers and copyright notices were removed from each paper, as were the author names and affiliations, list of references and acknowledgements.
+All files were also checked for any non-ascii characters and anomalies that may have arisen during the creation of the text file.}
 

### 2016-05-19 plosOneJordanousKeller/rebuttal.txt
Edits to rebuttal.txt to better reframe answer to reviewers on methodology update.

@@
 
-***** For some reason, we've fallen foul of some of these, so I'll check that *****
+***** ANNA TO DO For some reason, we've fallen foul of some of these, so I'll check that *****
 
@@
 * We have added, as requested, the detailed overview of our search strategy and the methods/criteria for selecting papers.
+In particular we found that it was particularly helpful, for clarity, to frame our paper selection strategy in terms of inclusion/exclusion criteria.
 This is reported in text added in the Methods section.
-Thank you for the link to the flow diagram examples.
+* Thank you for the link to the flow diagram examples.
 ***** PRISMA - ANNA TO DO THIS *****

### 2016-05-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
edit to methods section on search for papers

@@
 \textbf{The search strategy for identifying papers for the corpus was based around a literature search for the term `creativity' on the academic database {\em Scopus}.
+This literature search was supplemented with other influential papers which may have not appeared in a Scopus search, such as a computational conference paper on cognitive models of creativity.
+(N.B.
+In Computer Science, a number of conferences carry as much or more publication weight as some journals).
 Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
@@
 
+\subsection*{S1a Fig}\label{S1a_Fig}
+{\bf The 30 papers that make up the Creativity Corpus} 
+%\begin{figure}
+%\caption{The 30 papers that make up the Creativity Corpus}
+% REMOVE IMAGES FROM SUBMITTED VERSION
+%\includegraphics[width=\textwidth]{images/papersImage}
+%\label{S1_Fig}
+%\end{figure}
+
 \subsection*{S1 Fig}\label{S1_Fig}
@@
 
-\subsection*{S2 Fig}
-\label{S2_Fig}
-{\bf Graph representation of the similarity of the nouns {\em concept} and {\em idea} and closely semantically related words.
-Each word is drawn as a node in the graph, linked together by a weighted edge representing the similarity of the two words (maximum similarity strength is 1.0).}
+\subsection*{S1b Fig}
+\label{S1b_Fig}
+{\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period.
+Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}.
+Note that Scopus may classify a journal under more than one discipline.}
 %\begin{figure}[!ht]
 % \begin{center}
-%\includegraphics[scale=0.5]{images/conceptIdea}
+%\includegraphics[scale=0.5]{images/disciplines}
 % \end{center}
-% \caption{Graph representation of the similarity of the nouns {\em concept} and {\em idea} and closely semantically related words.
-Each word is drawn as a node in the graph, linked together by a weighted edge representing the similarity of the two words (maximum similarity strength is 1.0).}
-% \label{S2_Fig}
+% \caption{Representation of the disciplinary breakdown of the Creativity Corpus by time period.
+Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}.
+Note that Scopus may classify a journal under more than one discipline.}
+% \label{S1b_Fig}
 %\end{figure}

### 2016-05-27 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
Model not definition
Edits towards re-framing paper as building a model of creativity,
rather than providing a definition

@@
 {\Large
-\textbf\newline{Creativity is what we say it is: identifying key components of creativity}
+\textbf\newline{NEW TITLE? {\em Creativity is what we say it is: identifying key components of creativity}}
 }
@@
 
+NEED TO RE-WRITE THIS EVENTUALLY:
+{\em
 Creativity is a complex multi-dimensional concept which resists definition; it is accessible to us at a subjective, multi-faceted and dynamic level rather than being fixed and clearly defined.
@@
 Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerged, which collectively contribute to a comprehensive and multi-perspective definition of creativity.
-The components provide an ontology of creativity: a set of building blocks which, in evaluation, have proven useful for making the concept easier to understand and more tractable to study and evaluate.
+The components provide an ontology of creativity: a set of building blocks which, in evaluation, have proven useful for making the concept easier to understand and more tractable to study and evaluate.}
 
@@
 Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling \cite[provide examples]{colton08,widmerAIM09,leon10MM,perezyperez99}.
-The evaluation of computational {\emph creative systems} that have been developed by researchers in the field has proven non-trivial.
-Creativity evaluation, a recurring topic for discussion, has been described as one of the `Grand Challenges' of computational creativity research \cite{cardoso09}.
+
+The evaluation of creative systems developed by researchers in the field of computational creativity has proven non-trivial.
+Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}.
 Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what is meant when we talk about creativity and what does it constitute?
 
-Creativity is a complex, multi-faceted concept encompassing many related aspects, abilities, properties and behaviours.
-There have been many attempts to capture the nature of creativity in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in Fig.
+Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
+There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in Fig.
 1).
 %\ref{S1_Fig}).
-Yet despite many efforts to provide a workable and comprehensive definition of the concept, no real consensus has yet been reached.
-In the academic literature on creativity, many repeated themes have emerged.
+In the academic literature on creativity, many common themes have emerged. 
 However, multiple viewpoints exist, prioritising different aspects of the concept according to what are traditionally considered to be the primary factors for a particular discipline. 
-The need for a more comprehensive, inclusive, multi-dimensional  account has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}.
+The need for a more over-arching, inclusive, multi-dimensional account of creativity has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}.
 Such an account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
@@
 There are many challenges to modelling a concept like creativity in a computational setting.
-As a concept, creativity seems inherently fuzzy or vague, with a meaning that shifts depending on the domain of application.
-Tackling these challenges affords two key advantages.
+Conceptually, creativity seems inherently fuzzy or vague, with a meaning that shifts depending on the domain of application.
+Tackling these challenges affords two key advantages, both of which motivate the current paper.
 First, we can take advantage of computing and artificial intelligence to perform and/or enhance creative activities using computational power and research expertise.
 Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept.
-Both these advantages motivate this current paper.
 
 The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components representing key dimensions, as recognised across a combination of different viewpoints.
-The paper presents a novel, empirical approach focusing on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
-Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive account of creativity \cite{lakoff87,wittgenstein58}.
-The current work is intended as a significant, practical methodological contribution towards addressing this Grand Challenge of computational creativity and should provide researchers with a first foundation for evaluating exactly how creative so-called {\emph creative systems} actually are.
+The paper presents a novel, empirical approach to this problem that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
+Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}.
+The current work is intended as a significant, methodological contribution towards addressing the Grand Challenge of evaluation in computational creativity research.
+It should provide researchers with a firm foundation for evaluating exactly how creative so-called {\emph creative systems} actually are.
 
@@
 
-The remainder of this section considers the problem of providing a definition of creativity and reviews previous attempts to do so.
+The rest of this section considers the problem of providing a definition of creativity and reviews previous attempts to do so.
 The representation of subjective, ambiguous, loosely structured concepts is also considered.
 %, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
-Details are provided of the methodology used to identify components of creativity from an analysis of language data and the results of this analysis are presented in terms of fourteen key components or dimensions of creativity.
-The derived set of components is evaluated in terms of how well it satisies the need for a shared, inclusive and comprehensive acount of creativity and provides a vocabulary of creativity that is acessible to both people and machines.
+In the remaining sections, details are provided of the methodology used to identify components of creativity from an analysis of language data.
+The results of this analysis are then presented in terms of a model that encompasses fourteen key components or dimensions of creativity.
+The derived set of components is evaluated in terms of how well it satisfies the need for a shared, inclusive and comprehensive account of creativity and provides a vocabulary of creativity that is accessible to both people and machines.
 Finally, conclusions are drawn and some directions for further work are outlined.
 
-\subsection*{Background: A question of definition} \label{background}
-
-We begin by considering the problem of definition. As Torrance observes:
+\subsection*{RE-FRAME THIS? Background: {\em A question of definition}} \label{background}
+
+As Torrance observes:
 
@@
 Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. 
-Currently, no one definition has been adopted as standard, either in everyday use (as evidenced by the dictionary definitions considered below), for research purposes \cite{rhodes61,taylor88,plucker04defn} or even in legal practice \cite{clifford04,mandel11}, where one would expect a term critical to legal judgements  -- as creativity surely is \cite{feist91,karjala08,schafer15} -- to be precisely and unambiguously defined.
-
-The difficulty of formulating an adequate definition of creativity in words should not discourage us from the attempt, however  \cite{rhodes61,plucker04defn,kaufman09}.
+% Currently, no one definition has been adopted as standard, either in everyday use (as evidenced by the dictionary definitions considered below), for research % purposes \cite{rhodes61,taylor88,plucker04defn} or even in legal practice \cite{clifford04,mandel11}, where one would expect a term critical to legal
+% judgements  -- as creativity surely is \cite{feist91,karjala08,schafer15} -- to be precisely and unambiguously defined. 
+%
+%The difficulty of formulating an adequate definition of creativity in words should not discourage us from the attempt, however  \cite{rhodes61,plucker04defn,kaufman09}.
 Even if other researchers have been swayed away from this task \cite[for example]{sternberg99a,veale06preface},  care must be taken that we `do not throw out the baby with the bath water just because the water is cloudy' \cite[p.

### 2016-07-06 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
Model not definition
Another read through — most changes to orient the paper towards
modelling rather than definition.

@@
 {\Large
-\textbf\newline{NEW TITLE? {\em Creativity is what we say it is: identifying key components of creativity}}
+\textbf\newline{Towards a model of creativity: a corpus based approach to identifying key components}
+% \textbf\newline{NEW TITLE? {\em Creativity is what we say it is: identifying key components of creativity}}
 }
@@
 Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}.
-Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what is meant when we talk about creativity and what does it constitute?
+Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about 'creativity' and what does it constitute?
 
@@
 The need for a more over-arching, inclusive, multi-dimensional account of creativity has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}.
-Such an account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
+Such a meta-level account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
 
@@
 
-The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components representing key dimensions, as recognised across a combination of different viewpoints.
-The paper presents a novel, empirical approach to this problem that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
+The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components, representing key dimensions, that are recognised across a combination of different viewpoints.
+We present a novel, empirical approach to this problem that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
 Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}.
@@
 
-The rest of this section considers the problem of providing a definition of creativity and reviews previous attempts to do so.
-The representation of subjective, ambiguous, loosely structured concepts is also considered.
+In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is also considered.
 %, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
@@
 
-\subsection*{RE-FRAME THIS? Background: {\em A question of definition}} \label{background}
+\subsection*{Background:  {\em The nature of creativity}} \label{background}
 
@@
 
-\paragraph{The need for a more tangible understanding of creativity}
-
-Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research.
+\paragraph{A question of definition?}
+
+{\bf \em The next paragraph needs some thought, as it is is still talking about the need for definition.
+I think Plucker's comments on the original submission might suggest that he feels that this debate has now concluded (and that definition(s) of creativity have been provided.
+If so, then we need to modify this, at least.)}
+{\em Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research.
 He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited' \cite[p.87]{plucker04defn} and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding' \cite[p.92]{plucker04defn}.
@@
 \cite[p. 310]{rhodes61}.
+}
 
@@
 
-\paragraph{Existing definitions}
+\paragraph{Definitions of creativity.}
 \label{existing_defs}
@@
 172]{gallie56}, rather than to argue for a single interpretation.
-Thus, different types of creativity manifest themselves in different ways while sharing certain characteristics (not necessarily the same across all creative instances): what Wittgenstein refers to as `family resemblances' \cite{wittgenstein58}:
+Thus, different types of creativity manifest themselves in different ways while sharing certain characteristics (not necessarily the same across all creative instances).
+This is what Wittgenstein refers to as `family resemblances' \cite{wittgenstein58}:
 
@@
 
-Similarly, with creativity, different manifestations of creativity are not all necessarily required to share the same common, core elements in order to be identified as part of the creativity `family', but relationships between different manifestations reveal various shared characteristics emerging similar to Wittgenstein's `family resemblances' in language.
-We need to identify what those family resemblances are.
-So to understand creativity, we can investigate what resemblances exist across different instantiations of creativity.
+Similarly, with creativity, different manifestations of creativity are not all necessarily required to share the same common, core elements in order to be identified as part of the creativity `family'.
+Rather, relationships between different manifestations reveal various shared characteristics that emerge in a similar way to Wittgenstein's `family resemblances' in language.
+We need to identify what those family resemblances are in the case of creativity.
+To understand creativity, we can investigate what resemblances exist across different instantiations of the concept.
 
@@
 
-\subsection*{Towards a clearer understanding of creativity}\label{progressingForwards}
-
-Returning to the concept under investigation, the need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed.
-There is a large quantity of material contributory to a satisfactory definition of creativity and a number of key contributions have been discussed during this section.
+\subsection*{Towards a model of creativity}\label{progressingForwards}
+
+The need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed.
+There is a large quantity of material contributory to a satisfactory model of creativity and a number of key contributions have been discussed during this section.
 What must be done now is to marshal this assortment of material and to unify different perspectives where possible, in order to avoid the disciplinary `blinkers' or compartmentalisation that is often seen in creativity research \cite{hennessey10}.
@@
 
-The proposed approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
+Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
 In addition, following from the observations above, a {\em  confluence approach\/} to creativity is adopted \cite{sternberg99a,mayer99,ivcevic09}.
@@
 Tools from natural language processing and statistical analysis are used to identify words that appear to be highly associated with dimensions of creativity, as represented in a sample of academic papers on the topic.
-A key innovation is the use of a statistical measure of lexical similarity, which allows the words to be clustered into semantically-related groups.
+A key innovation is the use of a statistical measure of lexical similarity, which allows the words to be clustered into coherent and semantically-related groups.
 Clustering reveals a number of common themes or factors of creativity, allowing the identification of a set of fourteen components that serve as building blocks for creativity.
@@
 \textbf{The search strategy for identifying papers for the corpus was based around a literature search for the term `creativity' on the academic database {\em Scopus}.
-This literature search was supplemented with other influential papers which may have not appeared in a Scopus search, such as a computational conference paper on cognitive models of creativity.
-(N.B.
-In Computer Science, a number of conferences carry as much or more publication weight as some journals).
+This literature search was supplemented with other influential papers which may have not appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field}.
 Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
@@
 \item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
-\item \textbf{Papers should be considered particularly influential, as measured by the number of times it had been cited by other academic authors.
-For papers published in recent years and which have consequently not yet accrued many citations, selection was based on our subjective judgement of influence.}
+\item \textbf{Papers should be considered particularly influential.
+Influence was generally measured objectively, in terms of the number of times a paper had been cited by other academic authors.
+However, for papers published in recent years and which had consequently had little time to accrue citations, selection was based instead on a subjective judgement of influence grounded in a knowledge of the field.}
 \item \textbf{Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009.
@@
 }
-\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of what creativity is.
+\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of creativity.
 Fig.
 1b.
-illustrates the disciplinary distribution of the corpus as it changes over the time period included in the corpus, according to journal disciplinary classification in the academic database {\em Scopus}, which classifies journals under their main subject area(s) covered.
-We should acknowledge here though that while many disciplines include work that applies information about creativity, often the focus is on application rather than in depth discussion of what creativity entails.
-Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the key focus of our corpus as a representation of key discussions about the nature of creativity.}
+illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers.
+This distribution is based on the {\em Scopus} database, which classifies journals under their main subject area(s) covered.
+We should acknowledge here though that while many disciplines include work that {\sc applies information??} about creativity, often the focus is on application rather than in depth discussion of what creativity entails.
+Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the focus of our corpus as a representation of key discussions about the nature of creativity.}
 \end{itemize}
@@
 
-\textbf{Exclusion criteria for this search were: }
+\textbf{Exclusion criteria for this search were as follows: }
 \begin{itemize}
-\item \textbf{Authors were only represented more than one in the corpus if the relevant papers were written from different perspectives.
+\item \textbf{Authors were only represented more than once in the corpus if the relevant papers were written from different perspectives.
 For example, Mark Runco's work is represented twice in the corpus, but covering two different topics relating to the nature of creativity (psychoeconomic approach to creativity; cognition and creativity).
-If the search process highlighted two or more papers with a shared author, on the same or highly similar perspectives on creativity, then the more highly cited paper was chosen.
+If the search process highlighted two or more papers with a shared author on the same or highly similar perspectives on creativity, then the more highly cited paper was chosen.
 }
 \item \textbf{Papers had to be written in English, as the language processing tools we were working with were for English language texts.}
-\item \textbf{Papers had to be available in a format that plain text could be extracted from (this excluded books or book chapters).}
+\item \textbf{Papers had to be available in a format that enabled us easily to extract plain text (this excluded books or book chapters).}
 \end{itemize}
@@
 
-The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline\footnote{As categorised by the literature database {\em Scopus} \texttt{http://www.scopus.com/})} published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e.
+The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline (as categorised by  {\em Scopus}) and published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e.
 {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).
-\textbf{In other words, inclusion for this second corpus was based on the criteria of if a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus (as determined by {\em Scopus}), and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.}
+\textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.}
+
+%\texttt{http://www.scopus.com/})}
 
@@
 As a further refinement, each lemma was also mapped to lower case to ensure that capitalised word forms (e.g.
-{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).
+{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).\footnote{While this can result in confusion between proper names and common nouns (e.g.
+{\em Apple\/} v.
+{\em apple\/}), it is not considered that the resulting level of 'noise'  in the data is likely to adversely affect the results of the analysis.}
 
@@
 This in turn can be regarded as providing evidence of which words are salient to the definition of creativity.
-Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic).
-The log-likelihood ratio is a measure of how well observed data fits a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.
+Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fits a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.
 It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}.
@@
 
-The creativity words were clustered according  a statistical measure of distributional similarity due to Lin \cite{lin98}.
+The creativity words were clustered according a statistical measure of {\em distributional similarity\/}.
 The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}.
@@
 both occur as {\em subject\/} of a particular verb or {\em modifier\/} of a given noun).
-In practice it has been shown that modelling distributiequationon in terms of grammatical relations leads to a tighter correlation between distributional similarity and closeness of meaning \cite{kilgarriff00}.
+In practice it has been shown that modelling distribution in terms of grammatical relations leads to a tighter correlation between distributional similarity and closeness of meaning \cite{kilgarriff00}.
 
@@
 The components contribute collectively to the overall concept and may be regarded as providing an {\em ontology of creativity\/}.
-It is important to note however that no claim is made here that the fourteen components constitutes a necessary and sufficient definition of creativity, in all its possible manifestations.
+It is important to note, however that the fourteen components do not constitute a necessary and sufficient definition of creativity, in all its possible manifestations.
 There are two reasons for this.
-Firstly,
-some of the components we have identified appear to be logically inconsistent with others in the set.
+Firstly, some of the components we have identified appear to be logically inconsistent with others in the set.
 Consider for example the apparent need for autonomous, independent behaviour identified in {\em Independence and Freedom\/} and contrast this with the requirement for social interaction implied by {\em Social Interaction and Communication\/}.
@@
 -- which contribute to our understanding of creativity.
+The components should be treated as {\em building blocks} for creativity that may be arranged in different ways and with different emphases to suit different modelling purposes.
 The analysis of creativity in terms of the dimensions should be informative for a human audience and provide a basis for machine-understanding of the concept.
 %This approach is informed by debates in cognitive linguistics, computational linguistics and through philosophical underpinnings (see Background section).
-The components should be treated as {\em building blocks} for creativity that may be arranged in different ways and with different emphases to suit different definitional purposes.
-Each component is presented here with a brief explanation or gloss.
-These explanations will later be used for part of the semantic content in the creativity ontology.
+ Each component is presented here with a brief explanation or gloss. These explanations will later be used for part of the semantic content in the creativity ontology.
 
@@
 This paper has described the methods used to identify a set of {\em components of creativity} using corpus-based, statistical language processing techniques.
-The motivation for the work is the need for a shared, comprehensive, multi-perspective account of creativity.
-Such an account should be of great value to researchers investigating the nature of creativity and in particular those concerned with the evaluation of creative practice.
+The motivation for the work is the need for a shared, comprehensive and multi-perspective model of creativity.
+Such a model should be of great value to researchers investigating the nature of creativity and in particular those concerned with the evaluation of creative practice.
 More broadly, the inter-disciplinary approach described here exemplifies a general approach to the investigation and representation of semantically fuzzy and essentially-contested concepts.
-For this reason, we expect that it will interest other researchers investigating computational methods for analysing and representing such concepts.
+For this reason, we expect that it will interest researchers investigating computational methods for analysing and representing other such concepts.
 
@@
 
-The fourteen components provide a multi-perspective characterisation of creativity that has been successfully applied in a comparative analysis and evaluation of computational creativity systems \cite{jordanous12cc,jordanousphd,jordanous16aisb} (see the Discussions section).
+The fourteen components provide a multi-perspective model of creativity that has been successfully applied in a comparative analysis and evaluation of computational creativity systems \cite{jordanous12cc,jordanousphd,jordanous16aisb} (see the Discussions section).
 The outcome of the evaluation process provides relatively fine-grained information about the creative strengths of a given system.
@@
 An intriguing possibility that we are currently exploring is to further exploit language processing techniques to perform evaluation based on textual reviews, descriptions of system performance, or social media interactions \cite{jordanous15vem}.
-Such an approach would be analogous to the way sentiment analysis techniques are now used to evaluate attitude and opinion based on reviews of products or services \cite{panglee08}.
+Such an approach would be analogous to the way sentiment analysis techniques are now in common use to evaluate attitude and opinion based on reviews of products or services \cite{panglee08}.
 This is a fascinating direction for future work, with great potential for real progress towards tackling computational creativity's `Achilles' heel'.

### 2016-07-14 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
strikeout

@@
 
-\paragraph{A question of definition?}
-
-{\bf \em The next paragraph needs some thought, as it is is still talking about the need for definition.
+\paragraph{\sout{A question of definition?}}
+
+%{\bf \em The next paragraph needs some thought, as it is is still talking about the need for definition.
 I think Plucker's comments on the original submission might suggest that he feels that this debate has now concluded (and that definition(s) of creativity have been provided.
 If so, then we need to modify this, at least.)}
-{\em Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research.
+\sout{Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research.
 He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited' \cite[p.87]{plucker04defn} and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding' \cite[p.92]{plucker04defn}.
@@
 93]{plucker04defn}.
-Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear'
-\cite[p. 310]{rhodes61}.
-}
-
-In their review of research into human creativity, Hennessey and Amabile ask a significant question: 
+Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear' \cite[p.
+310]{rhodes61}.}
+
+In their review of research into human creativity, Hennessey and Amabile ask a significant follow-on question: 
 \begin{quote}
@@
 This distribution is based on the {\em Scopus} database, which classifies journals under their main subject area(s) covered.
-We should acknowledge here though that while many disciplines include work that {\sc applies information??} about creativity, often the focus is on application rather than in depth discussion of what creativity entails.
+We should acknowledge here though that while many disciplines include creative practice, often the focus is on application rather than in depth discussion of what creativity entails.
 Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the focus of our corpus as a representation of key discussions about the nature of creativity.}

### 2016-07-14 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
strikeout fixed

@@
 Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}.
-Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about 'creativity' and what does it constitute?
+Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about `creativity' and what does it constitute?
 
@@
 The following sections consider the need for an explicit and comprehensive definition of creativity and the difficulties researchers encounter in providing one.
-
 \paragraph{\sout{A question of definition?}}
-
 %{\bf \em The next paragraph needs some thought, as it is is still talking about the need for definition.
@@
 \sout{Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research.
-He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited' \cite[p.87]{plucker04defn} and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding' \cite[p.92]{plucker04defn}.
-In fact, `Rather than being a strength of the field, as many believe, the lack of a common definition is a major, debilitating weakness.
+He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited'} \cite[\sout{p.87}]{\sout{plucker04defn}} \sout{and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding'} \cite[\sout{p.92}]{\sout{plucker04defn}}.
+\sout{In fact, `Rather than being a strength of the field, as many believe, the lack of a common definition is a major, debilitating weakness.
 ...
@@
 ...
-This change in the focus and direction of creativity research is needed if the field is to move from a shadowy past into the forefront of constructive approaches' \cite[p.
-93]{plucker04defn}.
-Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear' \cite[p.
-310]{rhodes61}.}
+This change in the focus and direction of creativity research is needed if the field is to move from a shadowy past into the forefront of constructive approaches' }\cite[\sout{p.
+93}]{\sout{plucker04defn}}.
+\sout{Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear' }\cite[\sout{p.
+310}]{\sout{rhodes61}}.
 

### 2016-07-14 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
novelty and value comments

@@
 \sout{Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research.
-He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited'} \cite[\sout{p.87}]{\sout{plucker04defn}} \sout{and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding'} \cite[\sout{p.92}]{\sout{plucker04defn}}.
+He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited'} \cite[\sout{p.87}]{plucker04defn} \sout{and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding'} \cite[\sout{p.92}]{plucker04defn}.
 \sout{In fact, `Rather than being a strength of the field, as many believe, the lack of a common definition is a major, debilitating weakness.
@@
 This change in the focus and direction of creativity research is needed if the field is to move from a shadowy past into the forefront of constructive approaches' }\cite[\sout{p.
-93}]{\sout{plucker04defn}}.
+93}]{plucker04defn}.
 \sout{Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear' }\cite[\sout{p.
-310}]{\sout{rhodes61}}.
+310}]{rhodes61}.
 
@@
 For example, psychometric tests for creativity such as \cite{guilford50,torrance74} focus on {\em problem solving} and {\em divergent thinking} as key attributes of a creative person.
-In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} places emphasis on the {\em novelty} and {\em value} of creative products.
-Whilst there is some consensus across academic fields, the differing emphases contribute to variations in the interpretation of creativity.
+In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} has historially placed emphasis on the {\em novelty} and {\em value} of creative products.
+Whilst there is some consensus across academic fields, for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99}, the differing emphases contribute to variations in the interpretation of creativity.
 These variations affect consistency across creativity research in different disciplines and potentially hinder interdisciplinary collaborations and cross-application of findings.

### 2016-07-14 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
Title edited

@@
 {\Large
-\textbf\newline{Towards a model of creativity: a corpus based approach to identifying key components}
+\textbf\newline{Modelling creativity: identifying key components through a corpus based approach}
 % \textbf\newline{NEW TITLE? {\em Creativity is what we say it is: identifying key components of creativity}}
@@
 In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} has historially placed emphasis on the {\em novelty} and {\em value} of creative products.
-Whilst there is some consensus across academic fields, for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99}, the differing emphases contribute to variations in the interpretation of creativity.
+Whilst there is some consensus across academic fields, \textbf{for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99},} the differing emphases contribute to variations in the interpretation of creativity.
 These variations affect consistency across creativity research in different disciplines and potentially hinder interdisciplinary collaborations and cross-application of findings.

### 2016-07-18 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex

@@
 
-NEED TO RE-WRITE THIS EVENTUALLY:
-{\em
+\sout{
 Creativity is a complex multi-dimensional concept which resists definition; it is accessible to us at a subjective, multi-faceted and dynamic level rather than being fixed and clearly defined.
@@
 The components provide an ontology of creativity: a set of building blocks which, in evaluation, have proven useful for making the concept easier to understand and more tractable to study and evaluate.}
+
+Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
+If we wish to study creativity scientifically, then a tractable and well-articulated model of how creativity behaviour emerges is required.
+Such a model would be of great value to researchers investigating the nature of creativity and in particular, those concerned with the evaluation of creative practice.
+This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people used to describe the concept.
+Using techniques from the field of statistical natural language processing, we identify a collection of fourteen key components of creativity through an analysis of a corpus of academic papers on the topic.
+Words are identified which appear significantly often in connection with discussions of the concept.
+Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerge, which collectively contribute to a comprehensive and multi-perspective model of creativity.
+The components provide an ontology of creativity: a set of building blocks which can be used to model creative practice in a variety of domains.
+The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating the strengths and weaknesses of computational creativity systems.
 
@@
 The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components, representing key dimensions, that are recognised across a combination of different viewpoints.
-We present a novel, empirical approach to this problem that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
+We present a novel, empirical approach to the problem of modelling how creative behaviour emerges, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
 Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}.
@@
 
-In our approach, statistical language processing techniques are used to identify words significantly associated with creativity in a corpus of academic papers on the subject.
+On our approach, statistical language processing techniques are used to identify words significantly associated with creativity in a corpus of academic papers on the subject.
 A corpus spanning some 60 years of research into the nature of creativity was collected together.
@@
 A measure of lexical similarity provided a basis for clustering the creativity words into groups of words with similar or shared aspects of meaning.
-Through inspection of these clusters, a total of fourteen {\em key components of creativity\/} was identified, where each represents a key theme or aspect of creativity.
+Through inspection of these clusters, a total of fourteen {\em key components of creativity\/} was identified, where each represents a key theme or attribute of creativity.
 The set of components yields information about the nature of creativity, based on what is collectively emphasised in discussions about the concept.
@@
 
-In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is also considered.
+In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is considered.
 %, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
 In the remaining sections, details are provided of the methodology used to identify components of creativity from an analysis of language data.
-The results of this analysis are then presented in terms of a model that encompasses fourteen key components or dimensions of creativity.
+The results of this analysis are then presented in terms of a model that encompasses fourteen key components.
 The derived set of components is evaluated in terms of how well it satisfies the need for a shared, inclusive and comprehensive account of creativity and provides a vocabulary of creativity that is accessible to both people and machines.
@@
 \noindent In short, we need to specify and justify the standards that we use to judge creativity.
-A more objective and well-articulated definition of creativity enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.
+A more objective and well-articulated account of how creativity is manifested enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.
 
@@
 
-\subsection*{Towards a model of creativity}\label{progressingForwards}
+%\subsection*{Towards a model of creativity}\label{progressingForwards}
 
@@
 
+% You may title this section "Methods" or "Models". 
+% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
+% authors may use "Analysis" 
+\section*{Methods}
+\label{methodology}
+
 Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
@@
 This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.
-
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Methods}
-\label{methodology}
 
@@
 {\em many\/}, {\em more\/}).
-Such words have little independent semantic content so are of limited interest for the present study and may be removed from the data.
+Because such words have little independent semantic content, they are of limited interest for the present study and may be removed from the data.
 
@@
 This in turn can be regarded as providing evidence of which words are salient to the definition of creativity.
-Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fits a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.
+Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.
 It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}.
@@
 
-The creativity words were clustered according a statistical measure of {\em distributional similarity\/}.
-The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}.
+\sout{The creativity words were clustered according a statistical measure of {\em distributional similarity\/}.
+}The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}.
 This hypothesis  states that similarity of distribution correlates with similarity of meaning: two words that tend to appear in similar linguistic contexts will tend to have similar meanings.
@@
 While some narrowly specialised usage may be present to some small degree in the set of creativity words, most words retain general senses as reflected in the wider BNC data set.
-An advantage of unsing the BNC is that its  size increases the chances of a comprehensive coverage of the general senses of each word of interest.
+An advantage of using the BNC is that its  size increases the chances of a comprehensive coverage of the general senses of each word of interest.
 
@@
 However, we could similarly recognise as creative an approach to a task  ({\em process\/}) that does things in a novel and different way.
-Also, if a product is new in a particular environment ({\em press\/}), then it may well be be regarded as creative to those in that environment.
+Also, if a product is new in a particular environment ({\em press\/}), then it may well be regarded as creative to those in that environment.
 Viewing {\em novelty} from the perspectives of {\em product}, {\em process} and {\em press} uncovers these subtle and interlinked distinctions.
@@
 The components contribute collectively to the overall concept and may be regarded as providing an {\em ontology of creativity\/}.
-It is important to note, however that the fourteen components do not constitute a necessary and sufficient definition of creativity, in all its possible manifestations.
+It is important to note, however that the fourteen components do not constitute a set of necessary and sufficient conditions for creativity, in all its possible manifestations.
 There are two reasons for this.
@@
 As a step in this direction, the components have been expressed in an open, machine-readable form within the Semantic Web.
-In this way, the definition of the components benefits from and are enriched by concepts that are already defined within the Semantic Web.
+In this way, the characterization of the components benefits from and is enriched by concepts that are already represented within the Semantic Web.
 %To achieve this, SKOS (Simple Knowledge Organisation System) \cite{skos} was used as a basis for constructing an OWL ontology representation of creativity and its components,
@@
 
-In both case studies, the components of creativity were chosen as the way of defining creativity for step 1a of SPECS, and were weighted according to their importance and relevance for creativity in the creative domains under study for each case study (step 1b of SPECS).
+In both case studies, the components of creativity were chosen as the way of characterising creativity for step 1a of SPECS, and were weighted according to their importance and relevance for creativity in the creative domains under study for each case study (step 1b of SPECS).
 Each component was treated as one standard to be used to evaluate the creativity of the creative systems in the case studies (step 2 of SPECS).
@@
 Crucially, the evaluation feedback also highlighted areas where a given system performed poorly.
-For example, in the musical improvisation study, Case Study 1, we found that all systems' creativity could be improved most by improving performance in {\em Social Interaction and Communication}, {\em Intention and Emotional Involvement} and {\em Domain Competence} (the three components found to be most important for creativity in musical improvisation).
+For example, in the musical improvisation study, Case Study 1, we found that, in general, creativity could be improved most by improving performance in {\em Social Interaction and Communication}, {\em Intention and Emotional Involvement} and {\em Domain Competence} (the three components found to be most important for creativity in musical improvisation).
 Similarly, it is useful to be able to quickly obtain formative feedback on strengths and weaknesses in time-limited scenarios such as that replicated in Case Study 2 during the development of creative systems (when ongoing evaluation of progress ideally needs to be both timely and time-efficient).

### 2016-07-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
adding Vartanian ref and fixing some references
abstract edits

@@
 Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
-If we wish to study creativity scientifically, then a tractable and well-articulated model of how creativity behaviour emerges is required.
+If we wish to study creativity scientifically, then a tractable and well-articulated model of creativity is required.
 Such a model would be of great value to researchers investigating the nature of creativity and in particular, those concerned with the evaluation of creative practice.
@@
 The components provide an ontology of creativity: a set of building blocks which can be used to model creative practice in a variety of domains.
-The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating the strengths and weaknesses of computational creativity systems.
+The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating achievements of this work and directions for further research.
 
@@
 A more objective and well-articulated account of how creativity is manifested enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.
+\textbf{Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite[p.
+15]{vartanian14}, based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.}
 

### 2016-07-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
abstract edits

@@
 
-Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
+\textbf{Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
 If we wish to study creativity scientifically, then a tractable and well-articulated model of creativity is required.
@@
 The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating achievements of this work and directions for further research.
+}
 
@@
 The non-creativity corpus is twice the size of the creativity corpus ($\approx$ 700,000 words and $\approx$ 300,000 words respectively), in acknowledgement of the fact that in general the set of academic papers on creativity is only a small subset of all academic papers.
-Both corpora are very small in comparison to corpora such as the British National Corpus, a large  ($\approx$ 100M words) corpus of written and spoken English in general usage across a number of different contexts, and tiny in comparison to more recent web-derived text collections containing billions of words.
+Both corpora are very small in comparison to corpora such as the British National Corpus, a \textbf{relatively} large  ($\approx$ 100M words) corpus of written and spoken English in general usage across a number of different contexts, and tiny in comparison to more recent web-derived text collections containing billions of words.
 There are, however, several benefits associated with using a corpus derived from specialist academic literature:

### 2016-07-19 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
reference added for PRISMA
added figures and edited references

@@
 
-\subsection*{Background:  {\em The nature of creativity}} \label{background}
+\subsection*{Background:  The nature of creativity} \label{background}
 
@@
 The 30 papers selected for the creativity corpus are listed in Fig. 1a. %\ref{S1a_Fig}. 
+\textbf{The search strategy used to select papers for this corpus is illustrated in a PRISMA \cite{prisma09} flow diagram, in Fig. 0a.} %\ref{S0a_Fig}.
 
@@
 {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).
-\textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.}
+\textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.
+The search strategy used to select papers for this non-creativity corpus is illustrated in a second PRISMA \cite{prisma09} flow diagram, in Fig.
+0b.
+%\ref{S0b_Fig}.
+}
 
@@
 
+\subsection*{S0a Fig}\label{S0a_Fig}
+{\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus} 
+%\begin{figure}
+%\caption{ A flow diagram describing the search strategy used to identify papers for the creativity corpus}
+% REMOVE IMAGES FROM SUBMITTED VERSION
+%\includegraphics[width=\textwidth]{images/PRISMAcc}
+%\label{S0a_Fig}
+%\end{figure}
+
+\subsection*{S0b Fig}\label{S0b_Fig}
+{\bf A flow diagram describing the search strategy used to identify papers for the non-creativity corpus} 
+%\begin{figure}
+%\caption{ A flow diagram describing the search strategy used to identify papers for the non-creativity corpus}
+% REMOVE IMAGES FROM SUBMITTED VERSION
+%\includegraphics[width=\textwidth]{images/PRISMAncc}
+%\label{S0b_Fig}
+%\end{figure}
+
 \subsection*{S1a Fig}\label{S1a_Fig}
-{\bf The 30 papers that make up the Creativity Corpus} 
-%\begin{figure}
-%\caption{The 30 papers that make up the Creativity Corpus}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/papersImage}
-%\label{S1_Fig}
-%\end{figure}
-
-\subsection*{S1 Fig}\label{S1_Fig}
 {\bf The 30 papers that make up the Creativity Corpus} 
@@
 % \label{S1b_Fig}
+%\end{figure}
+
+\subsection*{S2 Fig}\label{S2_Fig}
+{\bf Word pairwise similarity data visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). } 
+%\begin{figure}
+%\caption{Word pairwise similarity data visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). }
+% REMOVE IMAGES FROM SUBMITTED VERSION
+%\includegraphics[width=\textwidth]{images/conceptIdea}
+%\label{S2_Fig}
 %\end{figure}

### 2016-07-22 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
data availability statement updated and small text changes to main paper
adding reference

@@
 
-\sout{
-Creativity is a complex multi-dimensional concept which resists definition; it is accessible to us at a subjective, multi-faceted and dynamic level rather than being fixed and clearly defined.
-If we wish to study creativity scientifically using computational models, or simulate it computationally, then a tractable and accurate interpretation of creativity is needed.
-Creativity encompasses many related aspects, abilities, properties and behaviours.
-This paper uses techniques from the field of statistical natural language processing to identify a collection of fourteen key components of creativity through an analysis of what is considered to be important in talking about creativity.
-Words were identified which appeared significantly often in connection with discussions of the concept.
-Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerged, which collectively contribute to a comprehensive and multi-perspective definition of creativity.
-The components provide an ontology of creativity: a set of building blocks which, in evaluation, have proven useful for making the concept easier to understand and more tractable to study and evaluate.}
-
 \textbf{Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
@@
 }
+
+\sout{
+Creativity is a complex multi-dimensional concept which resists definition; it is accessible to us at a subjective, multi-faceted and dynamic level rather than being fixed and clearly defined.
+If we wish to study creativity scientifically using computational models, or simulate it computationally, then a tractable and accurate interpretation of creativity is needed.
+Creativity encompasses many related aspects, abilities, properties and behaviours.
+This paper uses techniques from the field of statistical natural language processing to identify a collection of fourteen key components of creativity through an analysis of what is considered to be important in talking about creativity.
+Words were identified which appeared significantly often in connection with discussions of the concept.
+Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerged, which collectively contribute to a comprehensive and multi-perspective definition of creativity.
+The components provide an ontology of creativity: a set of building blocks which, in evaluation, have proven useful for making the concept easier to understand and more tractable to study and evaluate.}
 
@@
 Sometimes these differences of opinion do not need to be directly resolved but can be included alongside each other.
-Examples include whether creativity is centred around mental processes \cite{boden04,dietrich10} or embodied and situated in an interactive environment \cite{mccormack07,sosa09}.
+Examples include whether creativity is centred around mental processes \cite{boden04,dietrich10,gabora12} or embodied and situated in an interactive environment \cite{mccormack07,sosa09}.
 Another example is whether creativity is domain-independent \cite{plucker98}, or dependent on domain-specific context \cite{baer98}, or (as both Plucker and Baer have concluded) a combination of both \cite{plucker04,baer10}.

### 2016-08-01 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
Marking up
Just going back and marking up more significant changes with bf and shut

@@
 {\Large
-\textbf\newline{Modelling creativity: identifying key components through a corpus based approach}
-% \textbf\newline{NEW TITLE? {\em Creativity is what we say it is: identifying key components of creativity}}
+\textbf\newline{\bf Modelling creativity: identifying key components through a corpus based approach}
+\textbf\newline{\sout{Creativity is what we say it is: identifying key components of creativity}}
 }
@@
 The need for a more over-arching, inclusive, multi-dimensional account of creativity has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}.
-Such a meta-level account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
+Such a {\bf meta-level} account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
 
@@
 Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept.
+\sout{Both these advantages motivate this current paper.}
 
@@
 
-In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is considered.
+\sout{The rest of this section considers the problem of providing a definition of creativity and reviews previous attempts to do so.}
+{\bf In the rest of this section we begin by noting a variety of attempts to define creativity.} The representation of subjective, ambiguous, loosely structured concepts is considered.
 %, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
@@
 
-\paragraph{Definitions of creativity.}
+\paragraph{\sout{Existing definitions.}{\bf Definitions of creativity.}}
 \label{existing_defs}
@@
 
-%\subsection*{Towards a model of creativity}\label{progressingForwards}
-
+\subsection*{\sout{Towards a clearer understanding of creativity}}\label{progressingForwards}
+
+\sout{Returning to the concept under discussion } 
 The need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed.
@@
 In approaching the semantic representation of subjective and multi-faceted concepts, some useful guidance is offered through philosophical reflections on the meaning of such concepts.
+
+\sout{The proposed approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
+In addition, following from the observations above, a   confluence approach to creativity is adopted [refs]
+%\cite{sternberg99a,mayer99,ivcevic09}. 
+This works on the principle that creativity results from several components converging and goes on to examine what these components are.
+Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted.
+This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.}
+
 %Further, cognitive science methodologies, {\bf IS THIS NEXT BIT TO GO?} as well as approaches to ontology learning from texts \cite{gomezperez04} {\bf END} can be harnessed to enable the representation of more semantically ambiguous concepts such as creativity
@@
 
-Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
+{\bf Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
 In addition, following from the observations above, a {\em  confluence approach\/} to creativity is adopted \cite{sternberg99a,mayer99,ivcevic09}.
@@
 Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted.
-This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.
+This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.}
 
@@
 As a further refinement, each lemma was also mapped to lower case to ensure that capitalised word forms (e.g.
-{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).\footnote{While this can result in confusion between proper names and common nouns (e.g.
+{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).\footnote{\bf While this can result in confusion between proper names and common nouns (e.g.
 {\em Apple\/} v.

### 2016-08-03 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
All references fixed

--- 2016-07-22 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
@@
 The focus in Semantic Web research has generally been on reducing ambiguity in representations of these more structured domains and concepts, rather than directly tackling the representation and machine-readable representation of subjective, unstructured concepts in an ontology.
-However, cognitive science research and work on lexical resources such as WordNet \cite{fellbaum98,wordnetRKB} have laid foundations for more definitionally troublesome concepts to be considered in detail.
+However, cognitive science research and work on lexical resources such as WordNet \cite[$http://wordnet.rkbexplorer.com$]{fellbaum98} have laid foundations for more definitionally troublesome concepts to be considered in detail.
 The time is ripe for developing ontologies of subjective concepts such as creativity.
@@
 the twenty  words with the highest log likelihood scores) were selected.
-Each word was then visualised as the root node of its own individual subgraph using the graph drawing software {\em GraphViz} \cite{graphviz}.
+Each word was then visualised as the root node of its own individual subgraph using the graph drawing software {\em GraphViz}\footnote{$http://www.graphviz.org/$, last accessed August 2016}.
 In order to reduce the amount of data to be examined, similarity scores were discarded if they fell below a threshold value (adjusted manually for each graph to highlight the most strongly connected words).
@@
 
-In particular, the components are linked to the data in WordNet \cite{fellbaum98}, a large lexical database of English that has recently been made available as a Semantic Web ontology \cite{wordnetRKB}.
+In particular, the components are linked to the data in WordNet \cite{fellbaum98}, a large lexical database of English that has recently been made available as a Semantic Web ontology \footnote{$http://wordnet.rkbexplorer.com/$, last accessed August 2016}.
 In WordNet, words are grouped by sense and interlinked by lexical and conceptual relations.

### 2016-08-03 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
small rephrasing of words

@@
 {\Large
-\textbf\newline{\bf Modelling creativity: identifying key components through a corpus based approach}
+\textbf\newline{\bf Modelling creativity: identifying key components through a corpus-based approach}
 \textbf\newline{\sout{Creativity is what we say it is: identifying key components of creativity}}
@@
 The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus.
-This in turn can be regarded as providing evidence of which words are salient to the definition of creativity.
+This in turn can be regarded as providing evidence of which words are salient to the concept of creativity.
 Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.

### 2016-08-03 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
edits while doing response doc

@@
 
-\textbf{The search strategy for identifying papers for the corpus was based around a literature search for the term `creativity' on the academic database {\em Scopus}.
-This literature search was supplemented with other influential papers which may have not appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field}.
-Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
+\textbf{The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers.
+This literature search was supplemented with additional influential papers which may have not appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.} The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.}
+
+\textbf{Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
 The inclusion criteria are as follows, listed in descending order of precedence: }

### 2016-08-03 plosOneJordanousKeller/rebuttal.txt
Changes from papeeria to rebuttal.txt

@@
 
-We invite you to submit a revised version of the manuscript that addresses all concerns of the Reviewers.
-When doing this please indicate in your accompanying letter the exact places of the manuscript, which were changed as the response of the Reviewers’ remark.
-Please insert a change to the manuscript as a response of each concern.
-Please insert a section to the Discussion part of the revised manuscript even in case you disagree with any comment of the Reviewers noting the alternative view and the detailed reasons of your disagreement.
+Please find our revised version of the manuscript, where we have addressed all concerns of the Reviewers.
+We have indicated in this accompanying letter the places of the manuscript which were changed as the response of each Reviewers’ remark.
 
- ***** IF THERE ARE ANY POINTS WE WANT TO DISAGREE WITH, WE NEED TO PUT COMMENTARY ON THIS IN THE DISCUSSION OF THE PAPER  *****
+In our submission, we include a clean revised manuscript, this response letter, and a marked-up copy of the changes made from the previous article file as a 'Revised Manuscript with Track Changes' file.
+We have highlighted changes in the new document using LaTeX strikethrough for removed text and bold font for added text.
 
-We encourage you to submit your revision within forty-five days of the date of this decision.
-Please note that any manuscripts that require a revision period greater than 6 months should be resubmitted as a new submission to PLOS ONE.
-Any manuscripts remaining in Editorial Manager after 6 months will be withdrawn.
-
- ***** DATE OF DECISION 7 APRIL
-
-When your files are ready, please submit your revision by logging on to http://pone.edmgr.com/ and following the Submissions Needing Revision link.
-Do not submit a revised manuscript as a new submission.
-Before uploading, you should proofread your manuscript very closely for mistakes and grammatical errors.
-Should your manuscript be accepted for publication, you may not have another chance to make corrections as we do not offer pre-publication proofs.
-
- ***** SEE ABOVE!!!  *****
-
-In addition, when submitting your revision please include the following items:
-
-* A rebuttal letter that responds to each point brought up by the academic editor and reviewer(s). This letter should be uploaded as a 'Response to Reviewers' file.
-* A clean revised manuscript as your 'Manuscript' file.
-* A marked-up copy of the changes made from the previous article file as a 'Revised Manuscript with Track Changes' file.
-This can be done using 'track changes' in programs such as MS Word and/or highlighting any changes in the new document.
-***** WE'VE AGREED TO USE LATEX STRIKETHROUGH FOR REMOVED TEXT, AND BOLD FONT FOR ADDED TEXT *****
-
-While revising your submission, we encourage you to use PACE (the Preflight* Analysis and Conversion Engine, http://pace.apexcovantage.com/), a digital diagnostic and conversion tool for figure files.
+***** While revising your submission, we encourage you to use PACE (the Preflight* Analysis and Conversion Engine, http://pace.apexcovantage.com/), a digital diagnostic and conversion tool for figure files.
 PACE helps users ensure that their figures meet PLOS requirements and that the quality of published figures will be as high as possible.
@@
 
-To use PACE, you must first register as a user.
-Then, login and navigate to the UPLOAD tab, where you will find detailed instructions on how to use the tool.
-If you encounter any issues or have any questions when using PACE, please email us at figures@plos.org.
+***** Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at
 
-For more information on how to upload your revised submission, see our video: http://blogs.plos.org/everyone/2011/05/10/how-to-submit-your-revised-manuscript/
+***** http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf
 
-When submitting your revision, we need you to address these additional requirements.
+>> 1.  We request that you please report additional details in your Methods:
+>> i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
+>> ii) The specific methods for selecting papers, including inclusion and exclusion criteria
 
-Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at
+We have added, as requested, the detailed overview of our search strategy and the methods/criteria for selecting papers.
+In particular we found that it was particularly helpful, for clarity, to frame our paper selection strategy in terms of inclusion/exclusion criteria.
+This text has been added to the Corpus data section in Methods.
 
-http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf
+>> In addition, please include a figure of a flow diagram describing your search strategy (see http://prisma-statement.org/PRISMAStatement/FlowDiagram.aspx for examples)
 
-***** ANNA TO DO For some reason, we've fallen foul of some of these, so I'll check that *****
+A flow diagram has been added as Figure XX for the creativity corpus and Figure XX for the non-creativity corpus.
+These diagrams were inspired by the PRISMA format (thank you for the link to the flow diagram examples).
 
-1.  We request that you please report additional details in your Methods:
-i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus
-ii) The specific methods for selecting papers, including inclusion and exclusion criteria
-In addition, please include a figure of a flow diagram describing your search strategy (see http://prisma-statement.org/PRISMAStatement/FlowDiagram.aspx for examples)
-We appreciate your attention to these requests."
-
-*****
-* We have added, as requested, the detailed overview of our search strategy and the methods/criteria for selecting papers.
-In particular we found that it was particularly helpful, for clarity, to frame our paper selection strategy in terms of inclusion/exclusion criteria.
-This is reported in text added in the Methods section.
-* Thank you for the link to the flow diagram examples.
-***** PRISMA - ANNA TO DO THIS *****
-
-JW (Assoc Ed) 9 Mar 2016: **EO** At PRTC, please go back for crosscheck, do not ping with follow up.
+>> JW (Assoc Ed) 9 Mar 2016: **EO** At PRTC, please go back for crosscheck, do not ping with follow up.
 For crosscheck, please go back with "Thank you for submitting the above manuscript to PLOS ONE.
@@
 
-http://www.creativitypost.com/technology/technology/evaluating_computational_creativity
-The re-use of text from a previous publication may have implications for the copyright or license that applies to the published article.
+>> http://www.creativitypost.com/technology/technology/evaluating_computational_creativity
+
+>> The re-use of text from a previous publication may have implications for the copyright or license that applies to the published article.
 To avoid any concerns in this respect, we would recommend that you revise the manuscript to either remove any text overlap where possible/appropriate, or to clearly indicate that the text reproduces information already reported in detail elsewhere (e.g.
@@
 
-  ***** BILL TO CHECK THIS OVERLAP WITH THE MENTIONED BLOG POST *****
+The article being questioned is a short non-peer-reviewed 'pop-science' blog article aimed for a non-scientific audience.
+It discusses, at a superficial and non-technical level, the problems involved in understanding what creativity is (with a focus on computational creativity rather than the more general view on creativity that this submission takes).
+The blog post very briefly mentions the results of this work in passing, with no detail at all of the methods, underlying theories or analysis of results.
 
-2.
+The only text which is common to both articles is a quotation of the SPECS methodology, which is also included in this submitted article as a quotation.
+We have carefully examined the text of this blog post with cross-reference to this submitted article, and are satisfied that there is no overlap.
+We do not believe there is any issue of infringement of copyright between the two pieces.
 
-We note that you stated “data are available upon request” at submission.
+>> We note that you stated “data are available upon request” at submission.
 Could you please upload the minimal data set underlying the findings in your study in the manuscript, supplemental files, or in a stable public repository?
@@
 
- ***** BILL TO UPLOAD WORKING DATA SET TO SUSSEX REPOSITORY AND ADD LINK TO DataAvailabilityStatement.rtf FILE  *****
+We have uploaded all data generated during this study to one of the author's repository at http://users.sussex.ac.uk/~billk/bill_keller/downloads/index.html and we have added details and a link to the submitted DataAvailabilityStatement.rtf.
 
-3.
-Please upload a copy of Figure1-6, to which you refer ithroughtout your manuscript.
-If the figure is no longer to be included as part of the submission please remove all reference to it within the text.
+>> Reviewer #1:
 
-4. Please include a copy of Table 1 which you refer to in your text on page 11.
-
-***** THESE WERE INCLUDED BUT NEEDED TO BE HIGHER RESOLUTION (SEE REVIEWER 2 COMMENTS) - ANNA TO REVISE FIGURES/TABLES  *****
-
-Reviewer #1: This is interesting paper that could have some value in the literature on creativity and innovation.
+>> This is interesting paper that could have some value in the literature on creativity and innovation.
 The conceptual framing of the paper did not work for me, but I see a path forward for the authors that would help clarify what they’re trying to do – and the implications that can be drawn from their results.
-
-My major concerns about the paper are (a) the implied reification in the title, abstract, and introduction; and (b) that the authors aren’t really attempting to come up with a definition at all.
-
-Implied reification.
+>> My major concerns about the paper are (a) the implied reification in the title, abstract, and introduction; and (b) that the authors aren’t really attempting to come up with a definition at all.
+>> Implied reification.
 To say that creativity is subjective and difficult if not impossible to define would have been understandable 20 years ago, but this was a major weakness of the field and many scholars have tackled the issue.
@@
 I’m not sure that’s a workable approach.
-
-Is the point really a definition?
+>> Is the point really a definition?
 I suspect it’s not.
@@
 
- ***** BILL TO DEAL WITH ABOVE POINTS AND REFRAMING  *****
+We are very grateful for the feedback from the first reviewer.
+We agree that the point of the work is not to provide a definition at all, but to present an approach to a model of creativity.
+We are particularly pleased that the reviewer feels that there is merit in the general approach and that the proposed model is something that other scholars and practitioners would share.
+This was a very helpful and informative comment and has helped us to reframe the paper in terms of developing a model of creativity.
 
-In general, I found the methods to be well-explained and carefully done, but I have some experience using these methods (albeit limited), and other reviewers without such experience may request greater detail, which I would understand.
+Thank you to the reviewer also for pointing us at Vartanian (2014) which is very relevant to the current work: we have added a citation in the Background section (line no.: ??).
+The title has been amended to reflect the reframing and we have carefully edited the text throughout to ensure that the emphasis on modelling rather than definition is clear.
+The abstract and introductory sections have been reframed accordingly, in particular the Background section.
+The resulting changes mean that the paper provides a clearer account of the work, and a contribution towards understanding what processes and concepts relevant to creativity are 'sufficiently important to warrant study' based on 'an accumulation of the body of work on creativity to date' (Vartanian 2014).
+
+>> In general, I found the methods to be well-explained and carefully done, but I have some experience using these methods (albeit limited), and other reviewers without such experience may request greater detail, which I would understand.
 But for me, they felt appropriate and offered a unique way to get at the components of creativity.
 
- ***** ANNA TO ADD MORE DETAIL ON METHODOLOGY FOR IDENTIFYING PAPERS AS REQUESTED BY EDITOR. 
-       BILL TO CHECK TECHNICAL DETAIL OF METHODS AND SEE IF THEY ARE REPORTED IN AN APPROPRIATE LEVEL OF DETAIL  *****
+We have added more detail on the methodology for identifying papers, as requested by the editor, in the Methods section.
+We have also reviewed our reporting of the technical details of the methods, and feel that they are sufficiently clear, after some small edits to the Corpus Data section of Methods, regarding pre-processing.
+The other reviewer has not raised any questions about methods, so we hope that we have been successful in our attempts to make the methods accessible to an audience without NLP or statistical analysis experience.
 
-I recommend reframing the paper as a meta-model or meta-theory employing previously unused methods.
+>> I recommend reframing the paper as a meta-model or meta-theory employing previously unused methods.
 That gets to the heart of the matter much more directly (and accurately), and it speaks to the type of work Vartanian and others have been calling for as the field of creativity matures.
 
- ***** THIS FITS INTO THE WORK BILL IS DOING FOR THE ABOVE POINT  *****
+This reframing has been done (as noted in the earlier comment).
 
-Reference
-Vartanian, O. (2014). Toward a cumulative psychological science of aesthetics, creativity, and the arts. Psychology of Aesthetics , Creativity , and the Arts, 8(1), 15-17.
+>> Reviewer #2: Review of “Creativity is what we say it is: identifying key components of creativity” for PLoS ONE
 
- ***** LET'S BOTH READ THIS! BILL TO ADD SOME CONTENT RELATIVE TO THIS WHILE DEALING WITH REVIEWER 1's FIRST POINT *****
-
-Reviewer #2: Review of “Creativity is what we say it is: identifying key components of creativity” for PLoS ONE
-
-This paper proposes that creativity be defined in terms of themes emerging as a result of word clusters analysis of scholarly papers on creativity.
+>> This paper proposes that creativity be defined in terms of themes emerging as a result of word clusters analysis of scholarly papers on creativity.
 I am not convinced that this approach captures the essence of what creativity is (any more than doing this kind of word cluster analysis of your own name on the internet would capture the essence of who you are).
-
-***** BILL I'M SURE WE COULD ADD REFERENCES TO SUPPORT OUR APPROACH AGAINST THIS CRITICISM? ****
-
 I am sympathetic with Gabora, O’Connor, & Ranjan’s (2012) conviction of that creativity needs to be defined in terms of internal change to the creator’s network of understandings.
@@
 
-Literature Cited
-Gabora, L., O’Connor, B., & Ranjan, A. (2012). The recognizability of individual creative styles within and across domains. Psychology of Aesthetics, Creativity, and the Arts, 6(4), 351-360.
+We are glad that the reviewer finds this work novel and interesting, and that the results of this approach can make a valuable contribution to existing discussions of what is meant by creativity.
+We are grateful for the reviewer pointing us to the paper by Gabora et al, which presents an interesting perspective.
+We have added a citation to this paper to make sure we include this perspective in discussion about different takes on how creativity may be theorised.
 
- ***** ANNA TO CHECK HOW THE GABORA ET AL PAPER FITS INTO THIS
-       (UNLESS THIS COMES UP IN THE WORK BILL IS DOING FOR REVIEWER 1'S MAIN POINT??) *****
+>> A concern I have about the methodology concerns the set of papers used in the analysis, provided in Figure 1.
+(Note: this figure is rather hazy; in the final paper a higher resolution version should be used.)
 
-A concern I have about the methodology concerns the set of papers used in the analysis, provided in Figure 1.
-(Note: this figure is rather hazy; in the final paper a higher resolution version should be used.) Despite the authors’ intention to capture how is creativity is understood from a broad range of vantage points and disciplines, almost all of these papers are in psychology journals.
+This image and several others have been edited for clarity.
+
+>> Despite the authors’ intention to capture how is creativity is understood from a broad range of vantage points and disciplines, almost all of these papers are in psychology journals.
 In my view they should have included papers from other scholarly journals that discuss creativity and innovation, e.g.
@@
 
- ***** 
- * We have edited the figure accordingly, thank you for this feedback.
+We have edited the figure accordingly, thank you for this feedback.
 Regarding the raised concern: we have added a diagram representing the disciplinary makeup of the corpus, as categorised by the journal disciplinary classification in Scopus.
 Additionally, we have commented on the disciplinary coverage as part of the added text in the Methods section, which give a detailed report and discussion of our search strategy and methods for compiling the corpus.
- *****
 
-I would suggest that the authors exaggerate the extent to which scholars differ in their view of what constitutes creativity (see p.
+>> I would suggest that the authors exaggerate the extent to which scholars differ in their view of what constitutes creativity (see p.
 5).
@@
 
- ***** ANNA TO ADD CONTENT ON HOW novelty/usefulness ARE NECESSARY BUT NOT SUFFICIENT, USING COMPUTATIONAL CREATIVITY SOFTWARE AND EXTRA COMMENTARY ON CREATIVITY = NOVELTY+USEFULNESS+???  *****
+We have substantially edited the review of scholarly opinions on what constitutes creativity, in response to both reviewers' comments on this point.
+In particular, we have made several edits to the Background section, as indicated by the markup.
 
-The paper is well-written overall, though there are some minor spelling / grammatical errors, e.g., “which” instead of “that on the first line of the abstract, and missed commas, e.g., after the word ‘sciences’ in the second paragraph.
+We note in line ??209 that although originality and usefulness are indeed widely agreed to be two necessary components of creativity, there are many other components which have arisen in previous analyses which contribute to the understanding of creativity, such as Gabora et al's identification of internal cognitive changes.
 
- ***** WE'LL BOTH CATCH SOME OF THESE DURING PROOFREADING/EDITING/FINAL SPELL CHECK. BILL WOULD YOU MIND CHECKING THESE PARTICULAR TYPOS? *****
+In particular, in our experience, computational modelling of creativity has shown that it is not sufficient to incorporate only novelty and usefulness in software that is designed to be creative; this overlooks the more subtle aspects of creativity that creativity researchers and practicioners have been aware of for some time.
+
+ >> The paper is well-written overall, though there are some minor spelling / grammatical errors, e.g., “which” instead of “that on the first line of the abstract, and missed commas, e.g., after the word ‘sciences’ in the second paragraph.
+
+ The paper has been carefully proof-read post-editing for typos and grammatical errors, including correction of the two specific issues raised by the reviewer.

### 2016-08-03 plosOneJordanousKeller/responseToReviewers.txt
renaming response doc

--- 2016-05-19 plosOneJordanousKeller/rebuttal.txt
@@
 
- ***** BILL TO UPLOAD WORKING DATA SET TO SUSSEX REPOSITORY AND ADD LINK TO DataAvailabilityStatement.rtf FILE  *****
+We have uploaded all data generated during this study to one of the author's repository at http://users.sussex.ac.uk/~billk/bill_keller/downloads/index.html and we have added details and a link to the submitted DataAvailabilityStatement.rtf.
 

### 2016-08-03 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex
renaming tex file

--- 2016-08-03 plosOneJordanousKeller/PAPER/plos_JordanousKeller.tex
@@
 
-Computational creativity research follows both theoretical and practical directions and crosses several disciplinary boundaries between the arts, sciences and engineering.
+Computational creativity research follows both theoretical and practical directions and crosses several disciplinary boundaries between the arts, sciences, and engineering.
 Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling \cite[provide examples]{colton08,widmerAIM09,leon10MM,perezyperez99}.
@@
 The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus.
-This in turn can be regarded as providing evidence of which words are salient to the concept of creativity.
+This in turn can be regarded as providing evidence of which words are salient to the \sout{definition} \textbf{concept} of creativity.
 Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.

### 2016-08-03 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex
renumbering figures and tables

@@
 Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
-There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in Fig.
-1).
-%\ref{S1_Fig}).
+There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in Table \nameref{S1_Table}).
 In the academic literature on creativity, many common themes have emerged. 
@@
 
-The 30 papers selected for the creativity corpus are listed in Fig. 1a. %\ref{S1a_Fig}. 
-\textbf{The search strategy used to select papers for this corpus is illustrated in a PRISMA \cite{prisma09} flow diagram, in Fig. 0a.} %\ref{S0a_Fig}.
+The 30 papers selected for the creativity corpus are listed in Table \nameref{S1_Table}. 
+\textbf{The search strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \nameref{S1_Fig}. }
 
@@
 Fig.
-1b.
-illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers.
+\nameref{S3_Fig} illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers.
 This distribution is based on the {\em Scopus} database, which classifies journals under their main subject area(s) covered.
@@
 \textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.
-The search strategy used to select papers for this non-creativity corpus is illustrated in a second PRISMA \cite{prisma09} flow diagram, in Fig.
-0b.
-%\ref{S0b_Fig}.
+The 60 papers selected for the creativity corpus are listed in Table \nameref{S2_Table}.
+The search strategy used to select papers for this non-creativity corpus is illustrated in a second flow diagram, in Fig.
+\nameref{S2_Fig}.
 }
@@
 It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}.
-This is a particular issue when analysing smaller corpora, such as those used in the present work (see Fig.
-1).
-%\ref{S1_Fig}).
+This is a particular issue when analysing smaller corpora, such as those used in the present work.
 The log likelihood ratio statistic is more accurate in its treatment of infrequent words in the data,  which often hold useful information.
@@
 This resulted in a total of 694 {\em creativity words\/}: a collection of 389 nouns, 205 adjectives, 72 verbs and 28 adverbs that occurred significantly more often than expected in the creativity corpus.
-Table 1 %\ref{S1_Table}
-gives the top 20 results of these calculations.
+Table \nameref{S3_Table} gives the top 20 results of these calculations.
 
@@
 For a given set of words, word pair similarity data calculated in this way can be conveniently visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0), as in Fig.
-2.
-% \ref{S2_Fig}.
-
-Graphical representations of the similarity data like that shown in Fig. 2 % \ref{S2_Fig} 
-provide a useful basis for analysing the creativity words and identifying recurring themes or components of creativity.
+\nameref{S4_Fig}.
+
+Graphical representations of the similarity data like that shown in Fig.
+\nameref{S4_Fig} provide a useful basis for analysing the creativity words and identifying recurring themes or components of creativity.
 Two complementary methods for identifying key components of the data were adopted:
@@
 A sample of some of the resulting clusters can be seen in Fig.
-3.
-%\ref{S3_Fig}.
+\nameref{S5_Fig}.
 %To carry out Chinese Whispers, a preprocessing step was taken to categorise words according to their parts of speech, using the RASP software \cite{carrollRASP}.
@@
 Fig.
-4 % \ref{S4_Fig}
-illustrates, in diagram form, the process of using manual inspection to identify components.
+\nameref{S6_Fig} illustrates, in diagram form, the process of using manual inspection to identify components.
 
@@
 
-From the analysis steps described in the previous section it was possible to extract a set of fourteen key components of creativity. These components are summarised in Fig. 5 %\ref{S5_Fig} 
+From the analysis steps described in the previous section it was possible to extract a set of fourteen key components of creativity. These components are summarised in Fig. \nameref{S7_Fig} 
 and are presented in more detail below.
@@
 
-The resulting encoding can be visualised as a graph, as shown in Fig. 6. %\ref{S6_Fig}. 
+The resulting encoding can be visualised as a graph, as shown in Fig. \nameref{S8_Fig}. 
 The data has also been published under an Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} at:
@@
 The results of this novel, empirical analysis (presented in the Results section) inform the development of an {\em ontology of creativity\/} comprising a set of fourteen distinct components (see Fig.
-5).
-%\ref{S5_Fig}).
+\nameref{S7_Fig}).
 It is noted that each component makes a separate contribution to the overall meaning of the concept.
@@
 % Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
+
 %\subsection*{S1 Video}
@@
 
-\subsection*{S0a Fig}\label{S0a_Fig}
+%%%%%%
+% FIGURES
+%%%%%%
+
+\subsection*{S1 Fig}\label{S1_Fig} 
 {\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus} 
@@
 %\includegraphics[width=\textwidth]{images/PRISMAcc}
-%\label{S0a_Fig}
+%\label{S1_Fig}
 %\end{figure}
 
-\subsection*{S0b Fig}\label{S0b_Fig}
+\subsection*{S2 Fig}\label{S2_Fig}
 {\bf A flow diagram describing the search strategy used to identify papers for the non-creativity corpus} 
@@
 %\includegraphics[width=\textwidth]{images/PRISMAncc}
-%\label{S0b_Fig}
+%\label{S2_Fig}
 %\end{figure}
 
-\subsection*{S1a Fig}\label{S1a_Fig}
-{\bf The 30 papers that make up the Creativity Corpus} 
-%\begin{figure}
-%\caption{The 30 papers that make up the Creativity Corpus}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/papersImage}
-%\label{S1_Fig}
-%\end{figure}
-
-\subsection*{S1b Fig}
-\label{S1b_Fig}
+\subsection*{S3 Fig}
+\label{S3_Fig}
 {\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period.
@@
 Note that Scopus may classify a journal under more than one discipline.}
-% \label{S1b_Fig}
+% \label{S3_Fig}
 %\end{figure}
 
-\subsection*{S2 Fig}\label{S2_Fig}
+\subsection*{S4 Fig}\label{S4_Fig}
 {\bf Word pairwise similarity data visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). } 
@@
 %\includegraphics[width=\textwidth]{images/conceptIdea}
-%\label{S2_Fig}
+%\label{S4_Fig}
 %\end{figure}
 
-\subsection*{S3 Fig}
-\label{S3_Fig}
+\subsection*{S5 Fig}
+\label{S5_Fig}
 {\bf Sample of clusters produced by the Chinese Whispers clustering step.}
@@
 %\includegraphics[width=\textwidth]{images/clustersZoom}
-% \label{S3_Fig}
+% \label{S5_Fig}
 % REMOVE IMAGES FROM SUBMITTED VERSION
@@
 
-\subsection*{S4 Fig}
-\label{S4_Fig}
+\subsection*{S6 Fig}
+\label{S6_Fig}
 {\bf Illustration of the process of using manual inspection for further clustering.}
@@
 %\includegraphics[width=\textwidth]{images/clusterToComponents}
-% \label{S4_Fig}
+% \label{S6_Fig}
 % REMOVE IMAGES FROM SUBMITTED VERSION
@@
 
-\subsection*{S5 Fig}
-\label{S5_Fig}
+\subsection*{S7 Fig}
+\label{S7_Fig}
 {\bf The fourteen key components of creativity identified through an analysis of the word clusters}
@@
 %\includegraphics[width=\textwidth]{images/factorsOnly}
-%\label{S5_Fig}
+%\label{S7_Fig}
 %\end{figure}
 
-\subsection*{S6 Fig}
-\label{S6_Fig}
+\subsection*{S8 Fig}
+\label{S8_Fig}
 {\bf The ontology of Creativity, in graph form.}
@@
 %\includegraphics[scale=0.5]{images/ontGraph}
-%\label{S6_Fig}
+%\label{S8_Fig}
 %\end{figure}
 
-\subsection*{S1 Table}
-\label{S1_Table}
-{\bf The top 20 results of the log-likelihood ratio (LLR) calculations. A significant LLR score at p=0.001 is 10.83. N.B. POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.} 
-%\begin{table}[!ht]%dp]
-%\begin{center}
-%\begin{tabular}{c c | c c}
-%Word (\& POS tag) & LLR & Word (\& POS tag) & LLR \\
-%\hline
-%thinking (N) & 834.55 & process (N) & 612.05 \\
-%innovation (N) & 546.20 & idea (N) & 475.74 \\
-%program (N) & 474.41 & domain (N) & 436.58 \\
-%cognitive (J) & 393.79 & divergent (J) & 355.11 \\
-%openness (N) & 328.57 & discovery (N) & 327.38 \\
-%primary (J) & 326.65 & originality (N) & 315.60 \\
-%criterion (N) & 312.61 & intelligence (N) & 309.31 \\
-%ability (N) & 299.27 & knowledge (N) & 290.48 \\
-%create (V) & 280.06 & experiment (N) & 253.32 \\
-%plan (N) & 246.29 & agent (N) & 246.24 \\
-%\end{tabular}
-%\end{center}
-%\caption{The top 20 results of the log-likelihood ratio (LLR) calculations. A significant LLR score at p=0.001 is 10.83. N.B. POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
-%\label{S1_Table}
-%\end{table}%
+%%%%%%
+% TABLES
+%%%%%%
+\subsection*{S1 Table}\label{S1_Table}
+{\bf The 30 papers that make up the Creativity Corpus} 
+\begin{table}[!h]%dp]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\footnotesize
+\begin{center}
+\begin{tabular}{l}
+Paper \\
+\hline
+T. M. Amabile. The social psychology of creativity: A componential conceptualization. \\ 	
+	\hspace{10mm} Journal of Personality and Social Psychology, 45(2):357-376, 1983. \\
+M. A. Boden. Precis of The Creative Mind: Myths and mechanisms.  \\ 	
+	\hspace{10mm} Behavioural and Brain Sciences, 17(3):519-570, 1994. \\
+D. T. Campbell. Blind variation and selective retentions in creative thought as in other knowledge processes.  \\ 	
+	\hspace{10mm} Psychological Review, 67(7):380-400, 1960. \\
+S. Colton, A. Pease \& G. Ritchie. The effect of input knowledge on creativity.  \\ 	
+	\hspace{10mm} In Proceedings of Workshop Program of ICCBR-Creative Systems, 2001. \\
+M. Csikszentmihalyi. Motivation and creativity: Toward a synthesis of structural and energistic approaches to cognition.  \\ 	
+	\hspace{10mm} New Ideas in Psychology, 6(2):159-176, 1988. \\
+M. Dellas \&  E. L. Gaier. Identification of creativity: The individual.  \\ 	
+	\hspace{10mm} Psychological Bulletin, 73(1):55- 73, 1970. \\
+A. Dietrich. The cognitive neuroscience of creativity.  \\ 	
+	\hspace{10mm} Psychonomic Bulletin \& Review, 11(6):1011-1026, 2004. \\
+G. Domino. Identification of potentially creative persons from the adjective check list.  \\ 	
+	\hspace{10mm} Journal of Consulting and Clinical Psychology, 35(1):48-51, 1970. \\
+W. Duch. Intuition, insight, imagination and creativity.  \\ 	
+	\hspace{10mm} IEEE Computational Intelligence Magazine, 2(3):40-52, 2007. \\
+C. S. Findlay \&  C. J. Lumsden. The creative mind: Toward an evolutionary theory of discovery and innovation.  \\ 	
+	\hspace{10mm} Journal of Social and Biological Systems, 11(1):3-55, 1988. \\
+C. M. Ford. A theory of individual creative action in multiple social domains.  \\ 	
+	\hspace{10mm} The Academy of Management Review, 21(4):1112-1142, 1996. \\
+J. Gero. Creativity, emergence and evolution in design.  \\ 	
+	\hspace{10mm} Knowledge-Based Systems, 9(7):435-448, 1996.  \\
+H. G. Gough. A creative personality scale for the adjective checklist.  \\ 	
+	\hspace{10mm} Journal of Personality and Social Psychology, 37(8):1398-1405, 1979. \\
+J. P. Guilford. Creativity.  \\ 	
+	\hspace{10mm} American Psychologist, 5:444-454, 1950. \\
+Z. Ivcevic. Creativity map: Toward the next generation of theories of creativity.  \\ 	
+	\hspace{10mm} Psychology of Aesthetics, Creativity, and the Arts, 3(1):17-21, 2009. \\
+K. H. Kim. Can we trust creativity tests? A review of the Torrance tests of creative thinking (TTCT).  \\ 	
+	\hspace{10mm} Creativity Research Journal, 18(1):3-14, 2006. \\
+L. A. King, L. McKee Walker \&  S. J. Broyles. Creativity and the five-factor model.  \\ 	
+	\hspace{10mm} Journal of Research in Personality, 30(2):189-203, 1996. \\
+R. R. McCrae. Creativity, divergent thinking, and openness to experience.  \\ 	
+	\hspace{10mm} Journal of Personality and Social Psychology, 52(6):1258-1265, 1987. \\
+S. A. Mednick. The associative basis of the creative process.  \\ 	
+	\hspace{10mm} Psychological Review, 69(3):220-232, 1962.  \\
+M. D. Mumford \&  S. B. Gustafson. Creativity syndrome: Integration, application, and innovation.  \\ 	
+	\hspace{10mm} Psychological Bulletin, 103(1):27-43, 1988.  \\
+M. T. Pearce, D. Meredith \&  G. A. Wiggins. Motivations and methodologies for automation of the compositional process.  \\ 	
+	\hspace{10mm} Musicae Scientae, 6(2):119-147, 2002. \\
+J. A. Plucker, R. A. Beghetto \&  G. T. Dow. Why isn't creativity more important to educational psychologists? \\ 	
+	\hspace{10mm}  Potentials, pitfalls, and future directions in creativity research. \\ 	
+	\hspace{10mm}  Educational Psychologist, 39(2):83-96, 2004. \\
+R. Richards, D. K. Kinney, M. Benet \& A. P. C. Merzel. Assessing everyday creativity: \\ 	
+	\hspace{10mm}  Characteristics of the lifetime creativity scales and validation with three large samples.  \\ 	
+	\hspace{10mm} Journal of Personality and Social Psychology, 54(3):476-485, 1988. \\
+G. Ritchie. The transformational creativity hypothesis.  \\ 	
+	\hspace{10mm} New Generation Computing, 24(3):241-266, 2006. \\
+G. Ritchie. Some empirical criteria for attributing creativity to a computer program.  \\ 	
+	\hspace{10mm} Minds and Machines, 17:67-99, 2007. \\
+D. L. Rubenson \&  M. A. Runco. The psychoeconomic approach to creativity.  \\ 	
+	\hspace{10mm} New Ideas in Psychology, 10(2):131-147, 1992. \\
+M. A. Runco \&  I. Chand. Cognition and creativity.  \\ 	
+	\hspace{10mm} Educational Psychology Review, 7(3):243-267, 1995. \\
+D. K. Simonton. Creativity: Cognitive, personal, developmental, and social aspects.  \\ 	
+	\hspace{10mm} American Psychologist, 55(1):151-158, 2000. \\
+J. R. Suler. Primary process thinking and creativity.  \\ 	
+	\hspace{10mm} Psychological Bulletin, 88(1):144-165, 1980. \\
+G. A. Wiggins. A preliminary framework for description, analysis and comparison of creative systems. \\ 	
+	\hspace{10mm}  Knowledge-Based Systems, 19(7):449-458, 2006.
+\end{tabular}
+\end{center}
+\normalsize
+\caption{The 30 papers that make up the Creativity Corpus}
+\end{adjustwidth}
+\end{table}%
+
+\subsection*{S2 Table}\label{S2_Table}
+{\bf The 60 papers that make up the Non-Creativity Corpus} 
+\begin{table}[!h]%dp]
+\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+\footnotesize
+\begin{center}
+\begin{tabular}{l}
+Paper \\
+\hline 
+C. Ames \& J. Archer. Achievement goals in the classroom: Students' learning strategies and motivation processes. \\ 	
+	\hspace{10mm} Journal of Educational Psychology, 80(3):260-267, 1988. \\ % Cited by:  (since 1996) 639. \\
+J. Anderson \& D. Gerbing. Structural equation modeling in practice: A review and recommended two-step approach. \\ 	
+	\hspace{10mm} Psychological Bulletin, 103(3):411-423, 1988. \\ % Cited by:  (since 1996) 3884. \\
+J. Arnett. Emerging adulthood: A theory of development from the late teens through the twenties. \\ 	
+	\hspace{10mm} American Psychologist, 55(5):469-480, 2000. \\ % Cited by:  (since 1996) 800. \\
+M. Arulampalam, S. Maskell, N. Gordon \& T. Clapp. A tutorial on particle filters for online nonlinear/non-gaussian bayesian tracking. \\ 	
+	\hspace{10mm} IEEE Transactions on Signal Processing, 50(2):174-188, 2002. \\ % Cited by:  (since 1996) 1984. \\
+A. Baddeley. Exploring the central executive. \\ 	
+	\hspace{10mm} Quarterly Journal of Experimental Psychology Section A: Human Experimental Psychology, 49(1):5-28, 1996. \\ % Cited by:  (since 1996) 672. \\
+T. Baker, M. Piper, D. McCarthy, M. Majeskie \& M. Fiore. Addiction motivation reformulated: An affective processing model of negative reinforcement. \\ 	
+	\hspace{10mm} Psychological Review, 111(1):33-51, 2004. \\ % Cited by:  (since 1996) 177. \\
+P. Barnett \& I. Gotlib. Psychosocial functioning and depression: Distinguishing among antecedents, concomitants \& consequences. \\ 	
+	\hspace{10mm} Psychological Bulletin, 104(1):97-126, 1988. \\ % Cited by:  (since 1996) 366. \\
+J. Baron. Nonconsequentialist decisions. \\ 	
+	\hspace{10mm} Behavioral \& Brain Sciences, 17(1):1-42, 1994. \\ % Cited by:  (since 1996) 68. \\
+F. Beach. The snark was a boojum. \\ 	
+	\hspace{10mm} American Psychologist, 5(4):115-124, 1950. \\ % Cited by:  (since 1996) 32. \\
+M. Belkin, P. Niyogi \& V. Sindhwani. \\ 	
+	\hspace{10mm} Manifold regularization: A geometric framework for learning from labeled and unlabeled examples.
+Journal of Machine Learning Research, 7:2399-2434, 2006.
+\\ % Cited by:  (since 1996) 145.
+\\
+G. Bonanno. Loss, trauma \& human resilience: Have we underestimated the human capacity to thrive after extremely aversive events? \\ 
+	\hspace{10mm} American Psychologist, 59(1):20-28, 2004. \\ % Cited by:  (since 1996) 352. \\
+T. Chan \& L. Vese. Active contours without edges. \\ 	
+	\hspace{10mm} IEEE Transactions on Image Processing, 10(2):266-277, 2001. \\ % Cited by:  (since 1996) 1520. \\
+H. Cheng \& J. Schweitzer. Cultural values reflected in Chinese and U.S. television commercials. \\ 	
+	\hspace{10mm} Journal of Advertising Research, 36(3):27-45, 1996. \\ % Cited by:  (since 1996) 88. \\
+C. Coello Coello. Evolutionary multi-objective optimization: A historical view of the field. \\ 	
+	\hspace{10mm} IEEE Computational Intelligence Magazine, 1(1):28-36, 2006. \\ % Cited by:  (since 1996) 109. \\
+D. Comaniciu \& P. Meer. Mean shift: A robust approach toward feature space analysis. \\ 	
+	\hspace{10mm} IEEE Transactions on Pattern Analysis \& Machine Intelligence, 24(5):603-619, 2002.  \\ % Cited by:  (since 1996) 1613 \\
+L. Cronbach \& L. Furby. How we should measure `change': Or should we? \\ 	
+	\hspace{10mm} Psychological Bulletin, 74(1):68-80, 1970. \\ % Cited by: (since 1996) 526. \\
+M. Davis. Measuring individual differences in empathy: Evidence for a multidimensional approach. \\ 	
+	\hspace{10mm} Journal of Personality \& Social Psychology, 44(1):113-126, 1983. \\ % Cited by:  (since 1996) 631. \\
+J. Dem\~{s}ar. Statistical comparisons of classifiers over multiple data sets. \\ 	
+	\hspace{10mm} Journal of Machine Learning Research, 7:1-30, 2006. \\ % Cited by:  (since 1996) 389. \\
+M. Dorigo, M. Birattari \& T. St\"{u}tzle. Ant colony optimization artificial ants as a computational intelligence technique. \\ 	
+	\hspace{10mm} IEEE Computational Intelligence Magazine, 1(4):28-39, 2006. \\ % Cited by:  (since 1996) 134. \\
+E. Fischer \& J. Turner. Orientations to seeking professional help: Development and research utility of an attitude scale. \\ 	
+	\hspace{10mm} Journal of Consulting \& Clinical Psychology, 35(1 PART 1):79-90, 1970. \\ % Cited by:  (since 1996) 189. \\
+J. Gibson. Observations on active touch. \\ 	
+	\hspace{10mm} Psychological Review, 69(6):477-491, 1962. \\ % Cited by:  (since 1996) 179. \\
+A. Gopnik \& J. Astington. Children's understanding of representational change and its relation to the understanding of false belief and the appearance-reality distinction. \\ 	
+	\hspace{10mm} Child development, 59(1):26-37, 1988. \\ % Cited by:  (since 1996) 314. \\
+S. Gosling, S. Vazire, S. Srivastava \& O. John. Should we trust web-based studies? A comparative analysis of six preconceptions about internet questionnaires. \\ 	
+	\hspace{10mm} American Psychologist, 59(2):93-104, 2004. \\ % Cited by:  (since 1996) 313. \\
+J. Gray. The psychophysiological basis of introversion-extraversion. \\ 	
+	\hspace{10mm} Behaviour Research \& Therapy, 8(3):249-266, 1970. \\ % Cited by:  (since 1996) 225. \\
+B. Grosz \& S. Kraus. Collaborative plans for complex group action. \\ 	
+	\hspace{10mm} Artificial Intelligence, 86(2):269- 357, 1996. \\ % Cited by:  (since 1996) 275. \\
+P. Groves \& R. Thompson. Habituation: A dual-process theory. \\ 	
+	\hspace{10mm} Psychological Review, 77(5):419-450, 1970. \\ % Cited by:  (since 1996) 375. \\
+M. Hall, J. Anderson, S. Amarasinghe, B. Murphy, S.-W. Liao, E. Bugnion \& M. Lam. Maximizing multiprocessor performance with the SUIF compiler. \\ 	
+	\hspace{10mm} Computer, 29(12):84-89, 1996. \\ % Cited by:  (since 1996) 161. \\
+F. Happ\'{e}. The role of age and verbal ability in the theory of mind task performance of subjects with autism. Child development, 66(3):843-855, 1995. \\ % Cited by:  (since 1996) 285. \\
+C. Harland. Supply chain management: Relationships, chains and networks. \\ 	
+	\hspace{10mm} British Journal of Management, 7(SPEC. ISS.):S63-S80, 1996. \\ % Cited by:  (since 1996) 172. \\
+S.
+Hayes, K.
+Strosahl, K.
+Wilson, R.
+Bissett, J.
+Pistorello, D.
+Toarmino, M.
+Polusny, T.
+Dykstra, S.
+Batten, J.
+Bergan, S.
+Stewart, M.
+Zvolensky, G.
+Eifert, F.
+Bond, J.
+Forsyth, M.
+Karekla \& S.
+McCurry.
+Measuring experiential avoidance: A preliminary test of a working model.
+\\
+	\hspace{10mm} Psychological Record, 54(4):553-578, 2004. \\ % Cited by:  (since 1996) 168. \\
+J.
+Hirsch \& K.
+L\"{u}cke.
+Overview no.
+76.
+mechanism of deformation and development of rolling textures in polycrystalline f.c.c.
+metals-i.
+description of rolling texture development in homogeneous cuzn alloys.
+\\
+	\hspace{10mm} Acta Metallurgica, 36(11):2863-2882, 1988. \\ % Cited by:  (since 1996) 243. \\
+P. Killeen. Mathematical principles of reinforcement. \\ 	
+	\hspace{10mm} Behavioral \& Brain Sciences, 17(1):105-172, 1994. \\ % Cited by:  (since 1996) 86. \\
+P.
+Kirschner, J.
+Sweller \& R.
+Clark.
+Why minimal guidance during instruction does not work: An analysis of the failure of constructivist, discovery, problem-based, experiential \& inquiry-based teaching.
+\\
+	\hspace{10mm} Educational Psychologist, 41(2):75-86, 2006. \\ % Cited by:  (since 1996) 139. \\
+S. Liao. Notes on the homotopy analysis method: Some definitions and theorems. \\ 	
+	\hspace{10mm} Communications in Nonlinear Science \& Numerical Simulation, 14(4):983-997, 2009. \\ % Cited by:  (since 1996) 56. \\
+C. Lord, L. Ross \& M. Lepper. Biased assimilation and attitude polarization: The effects of prior theories on subsequently considered evidence. \\ 	
+	\hspace{10mm} Journal of Personality \& Social Psychology, 37(11):2098- 2109, 1979. \\ % Cited by:  (since 1996) 523. \\
+S. Luthar, D. Cicchetti \& B. Becker. The construct of resilience: A critical evaluation and guidelines for future work. \\ 	
+	\hspace{10mm} Child Development, 71(3):543-562, 2000. \\ % Cited by:  (since 1996) 566. \\
+G. Mandler. Recognizing: The judgment of previous occurrence. \\ 	
+	\hspace{10mm} Psychological Review, 87(3):252-271, 1980. \\ % Cited by:  (since 1996) 877. \\
+G. Miller \& J. Selfridge. Verbal context and the recall of meaningful material. \\ 	
+	\hspace{10mm} The American journal of psychology, 63(2):176-185, 1950. \\ % Cited by:  (since 1996) 57. \\
+S. Miller. Monitoring and blunting: Validation of a questionnaire to assess styles of information seeking under threat. \\ 	
+	\hspace{10mm} Journal of Personality \& Social Psychology, 52(2):345-353, 1987. \\ % Cited by:  (since 1996) 385. \\
+G. Navarro \& V. M\"{a}kinen. Compressed full-text indexes. \\ 	
+	\hspace{10mm} ACM Computing Surveys, 39(1), 2007. \\ % Cited by:  (since 1996) 62. \\
+M. Nissen \& P. Bullemer. Attentional requirements of learning: Evidence from performance measures. \\ 	
+	\hspace{10mm} Cognitive Psychology, 19(1):1-32, 1987. \\ % Cited by:  (since 1996) 729. \\
+J. Payne, J. Bettman \& E. Johnson. Adaptive strategy selection in decision making. \\ 	
+	\hspace{10mm} Journal of Experimental Psychology: Learning, Memory \& Cognition, 14(3):534-552, 1988. \\ % Cited by:  (since 1996) 300. \\
+J. Prochaska, C. DiClemente \& J. Norcross. In search of how people change: Applications to addictive behaviors. \\ 	
+	\hspace{10mm} American Psychologist, 47(9):1102-1114, 1992. \\ % Cited by:  (since 1996) 2742. \\
+T. Richardson, M. Shokrollahi \& R. Urbanke. Design of capacity-approaching irregular low-density parity-check codes. \\ 	
+	\hspace{10mm} IEEE Transactions on Information Theory, 47(2):619-637, 2001. \\ % Cited by:  (since 1996) 1162. \\
+W. Rozeboom. The fallacy of the null-hypothesis significance test. \\ 	
+	\hspace{10mm} Psychological Bulletin, 57(5):416-428, 1960. \\ % Cited by:  (since 1996) 133. \\
+C. Rusbult. A longitudinal test of the investment model: The development (and deterioration) of satisfaction and commitment in heterosexual involvements. \\ 	
+	\hspace{10mm} Journal of Personality \& Social Psychology, 45(1):101-117, 1983. \\ % Cited by:  (since 1996) 301. \\
+T. Ryan. Significance tests for multiple comparison of proportion, variance, and other statistics. \\ 	
+	\hspace{10mm} Psychological Bulletin, 57(4):318-328, 1960. \\ % Cited by:  (since 1996) 154. \\
+W. Schultz. Behavioral theories and the neurophysiology of reward. \\ 	
+	\hspace{10mm} Annual Review of Psychology, 57:87-115, 2006. \\ % Cited by:  (since 1996) 226. \\
+E. Sirin, B. Parsia, B. Grau, A. Kalyanpur \& Y. Katz. Pellet: A practical OWL-DL reasoner. \\ 	
+	\hspace{10mm} Web Semantics, 5(2):51-53, 2007. \\ % Cited by:  (since 1996) 125. \\
+T. Srull \& R. Wyer. The role of category accessibility in the interpretation of information about persons: Some determinants and implications. \\ 	
+	\hspace{10mm} Journal of Personality \& Social Psychology, 37(10):1660- 1672, 1979. \\ % Cited by:  (since 1996) 374. \\
+J. Steiger. Tests for comparing elements of a correlation matrix. \\ 	
+	\hspace{10mm} Psychological Bulletin, 87(2):245-251, 1980. \\ % Cited by:  (since 1996) 705. \\
+L. Steinberg, S. Lamborn, S. Dornbusch \& N. Darling. Impact of parenting practices on adolescent achievement: authoritative parenting, school involvement, and encouragement to succeed. \\ 	
+	\hspace{10mm} Child development, 63(5):1266-1281, 1992. \\ % Cited by:  (since 1996) 435. \\
+D. Tao, X. Li, X. Wu, W. Hu \& S. Maybank. Supervised tensor learning. \\ 	
+	\hspace{10mm} Knowledge \& Information Systems, 13(1):1-42, 2007. \\ % Cited by:  (since 1996) 54. \\
+A. Tellegen, D. Lykken, T. Bouchard Jr., K. Wilcox, N. Segal \& S. Rich. Personality similarity in twins reared apart and together. \\ 	
+	\hspace{10mm} Journal of Personality \& Social Psychology, 54(6):1031-1039, 1988. \\ % Cited by:  (since 1996) 398. \\
+L. Thomas \& D. Ganster. Impact of family-supportive work variables on work-family conflict and strain: A control perspective. \\ 	
+	\hspace{10mm} Journal of Applied Psychology, 80(1):6-15, 1995. \\ % Cited by:  (since 1996) 339. \\
+I. Thompson. Coupled reaction channels calculations in nuclear physics. \\ 	
+	\hspace{10mm} Computer Physics Reports, 7(4):167-212, 1988. \\ % Cited by:  (since 1996) 360. \\
+E. Tulving. Subjective organization in free recall of ``unrelated'' words. \\ 	
+	\hspace{10mm} Psychological Review, 69(4):344- 354, 1962. \\ % Cited by:  (since 1996) 121. \\
+U. Von Luxburg. A tutorial on spectral clustering. \\ 	
+	\hspace{10mm} Statistics \& Computing, 17(4):395-416, 2007. \\ % Cited by:  (since 1996) 107. \\
+J. Williams, A. Mathews \& C. MacLeod. The emotional Stroop task and psychopathology. \\ 	
+	\hspace{10mm} Psychological Bulletin, 122(1):3-24, 1996. \\ % Cited by:  (since 1996) 716. \\
+J. Wright, A. Yang, A. Ganesh, S. Sastry \& Y. Ma. Robust face recognition via sparse representation. \\ 	
+	\hspace{10mm} IEEE Transactions on Pattern Analysis \& Machine Intelligence, 31(2):210-227, 2009. \\ % Cited by:  (since 1996) 46.
+\end{tabular}
+\end{center}
+\normalsize
+\caption{The 60 papers that make up the Non-Creativity Corpus}
+\end{adjustwidth}
+\end{table}%
+
+\subsection*{S3 Table}\label{S3_Table}
+{\bf The top 20 results (in descending order) of the log-likelihood ratio (LLR) calculations.
+A significant LLR score at p=0.001 is 10.83.
+N.B.
+POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
+\begin{table}[!h]%dp]
+\begin{center}
+\begin{tabular}{c c | c c}
+\# & Word (\& POS tag) & LLR \\
+\hline
+\#1 & thinking (N) & 834.55  \\
+\#2 & process (N) & 612.05 \\
+\#3 & innovation (N) & 546.20 \\
+\#4 & idea (N) & 475.74  \\
+\#5 & program (N) & 474.41  \\
+\#6 & domain (N) & 436.58 \\
+\#7 & cognitive (J) & 393.79  \\
+\#8 & divergent (J) & 355.11 \\
+\#9 & openness (N) & 328.57  \\
+\#10 & discovery (N) & 327.38 \\
+\#11 & primary (J) & 326.65 \\
+\#12 & originality (N) & 315.60  \\
+\#13 & criterion (N) & 312.61  \\
+\#14 & intelligence (N) & 309.31 \\
+\#15 & ability (N) & 299.27 \\
+\#16 & knowledge (N) & 290.48  \\
+\#17 & create (V) & 280.06 \\
+\#18 & experiment (N) & 253.32 \\
+\#19 & plan (N) & 246.29 \\
+\#20 & agent (N) & 246.24  \\
+\end{tabular}
+\end{center}
+\caption{The top 20 results (in descending order) of the log-likelihood ratio (LLR) calculations.
+A significant LLR score at p=0.001 is 10.83.
+N.B.
+POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
+\end{table}%
 
@@
 We would like to acknowledge Nick Collins and Chris Thornton for their helpful comments during this work. 
+\pagebreak
 

### 2016-08-03 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex
oops did the figures and tables wrong... fixed

--- 2016-08-03 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex
@@
 Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
-There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in Fig.
-1).
-%\ref{S1_Fig}).
+There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in \nameref{S1_Appendix}).
 In the academic literature on creativity, many common themes have emerged. 
@@
 
-The 30 papers selected for the creativity corpus are listed in Fig. 1a. %\ref{S1a_Fig}. 
-\textbf{The search strategy used to select papers for this corpus is illustrated in a PRISMA \cite{prisma09} flow diagram, in Fig. 0a.} %\ref{S0a_Fig}.
-
-%**** i) A detailed overview of the search strategy used to identify papers for the creativity corpus and non-creativity corpus ****
-%**** ii) The specific methods for selecting papers, including inclusion and exclusion criteria ****
+The 30 papers selected for the creativity corpus are listed in \nameref{S1_Appendix}. 
+\textbf{The search strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}. }
+
+\begin{figure}[!b]
+\caption{{\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus.}}
+% REMOVE IMAGES FROM SUBMITTED VERSION
+%\includegraphics[width=\textwidth]{images/Fig1}
+\label{searchCC}
+\end{figure}
 
@@
 Fig.
-1b.
-illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers.
+\ref{disciplinaryDistribution} illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers.
 This distribution is based on the {\em Scopus} database, which classifies journals under their main subject area(s) covered.
@@
 
+\begin{figure}[!b]
+% REMOVE IMAGES FROM SUBMITTED VERSION
+%%\includegraphics[scale=0.5]{images/Fig2}
+\caption{{\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period.} \\Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}.
+Note that Scopus may classify a journal under more than one discipline.}
+\label{disciplinaryDistribution}
+\end{figure}
+
 \textbf{Exclusion criteria for this search were as follows: }
@@
 \textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.
-The search strategy used to select papers for this non-creativity corpus is illustrated in a second PRISMA \cite{prisma09} flow diagram, in Fig.
-0b.
-%\ref{S0b_Fig}.
-}
-
-%\texttt{http://www.scopus.com/})}
+The 60 papers selected for the creativity corpus are listed in \nameref{S2_Appendix}.
+The search strategy used to select papers for this non-creativity corpus is illustrated in a second flow diagram, in Fig.
+\ref{searchNonCC}.
+}
+
+\begin{figure}
+\caption{ A flow diagram describing the search strategy used to identify papers for the non-creativity corpus.}
+% REMOVE IMAGES FROM SUBMITTED VERSION
+%\includegraphics[width=\textwidth]{images/Fig3}
+\label{searchNonCC}
+\end{figure}
 
@@
 This resulted in a total of 694 {\em creativity words\/}: a collection of 389 nouns, 205 adjectives, 72 verbs and 28 adverbs that occurred significantly more often than expected in the creativity corpus.
-Table 1 %\ref{S1_Table}
-gives the top 20 results of these calculations.
+Table \ref{creativityTop20} gives the top 20 results of these calculations.
+
+\begin{table}[!b]
+\begin{center}
+\begin{tabular}{c c | c c}
+\# & Word (\& POS tag) & LLR \\
+\hline
+\#1 & thinking (N) & 834.55  \\
+\#2 & process (N) & 612.05 \\
+\#3 & innovation (N) & 546.20 \\
+\#4 & idea (N) & 475.74  \\
+\#5 & program (N) & 474.41  \\
+\#6 & domain (N) & 436.58 \\
+\#7 & cognitive (J) & 393.79  \\
+\#8 & divergent (J) & 355.11 \\
+\#9 & openness (N) & 328.57  \\
+\#10 & discovery (N) & 327.38 \\
+\#11 & primary (J) & 326.65 \\
+\#12 & originality (N) & 315.60  \\
+\#13 & criterion (N) & 312.61  \\
+\#14 & intelligence (N) & 309.31 \\
+\#15 & ability (N) & 299.27 \\
+\#16 & knowledge (N) & 290.48  \\
+\#17 & create (V) & 280.06 \\
+\#18 & experiment (N) & 253.32 \\
+\#19 & plan (N) & 246.29 \\
+\#20 & agent (N) & 246.24  \\
+\end{tabular}
+\end{center}
+\caption{{\bf The top 20 results (in descending order) of the log-likelihood ratio (LLR) calculations.}\\ A significant LLR score at p=0.001 is 10.83.
+N.B.
+POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
+\label{creativityTop20}
+\end{table}%
 
@@
 For a given set of words, word pair similarity data calculated in this way can be conveniently visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0), as in Fig.
-2.
-% \ref{S2_Fig}.
-
-Graphical representations of the similarity data like that shown in Fig. 2 % \ref{S2_Fig} 
-provide a useful basis for analysing the creativity words and identifying recurring themes or components of creativity.
+\ref{conceptIdea}.
+
+\begin{figure}
+\caption{{\bf Word pairwise similarity data visualised as an edge-weighted graph.} \\Nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). }
+%% REMOVE IMAGES FROM SUBMITTED VERSION
+%%\includegraphics[width=\textwidth]{images/Fig4}
+\label{conceptIdea}
+\end{figure}
+
+Graphical representations of the similarity data like that shown in Fig.
+\ref{conceptIdea} provide a useful basis for analysing the creativity words and identifying recurring themes or components of creativity.
 Two complementary methods for identifying key components of the data were adopted:
@@
 A sample of some of the resulting clusters can be seen in Fig.
-3.
-%\ref{S3_Fig}.
+\ref{clustersZoom}.
 %To carry out Chinese Whispers, a preprocessing step was taken to categorise words according to their parts of speech, using the RASP software \cite{carrollRASP}.
@@
 Fig.
-4 % \ref{S4_Fig}
-illustrates, in diagram form, the process of using manual inspection to identify components.
+\ref{clusterToComponents} illustrates, in diagram form, the process of using manual inspection to identify components.
 
 \end{description}
+
+\begin{figure}
+\caption{{\bf Sample of clusters produced by the Chinese Whispers clustering step.}}
+%% REMOVE IMAGES FROM SUBMITTED VERSION
+%%\includegraphics[width=\textwidth]{images/Fig5}
+\label{clustersZoom}
+\end{figure}
+
+\begin{figure}
+\caption{{\bf Illustration of the process of using manual inspection for further clustering.}}
+%% REMOVE IMAGES FROM SUBMITTED VERSION
+%%\includegraphics[width=\textwidth]{images/Fig6}
+\label{clusterToComponents}
+\end{figure}
 
@@
 
-From the analysis steps described in the previous section it was possible to extract a set of fourteen key components of creativity. These components are summarised in Fig. 5 %\ref{S5_Fig} 
+From the analysis steps described in the previous section it was possible to extract a set of fourteen key components of creativity. These components are summarised in Fig. \ref{components} 
 and are presented in more detail below.
@@
 
+\begin{figure} 
+%% REMOVE IMAGES FROM SUBMITTED VERSION
+\caption{{\bf The fourteen key components of creativity identified through an analysis of the word clusters.}}
+%%\includegraphics[width=\textwidth]{images/Fig7}
+\label{components}
+\end{figure}
+
 The following set of fourteen components is therefore presented as a collection of dimensions -- attributes, abilities and behaviours, etc.
@@
 
-The resulting encoding can be visualised as a graph, as shown in Fig. 6. %\ref{S6_Fig}. 
+The resulting encoding can be visualised as a graph, as shown in Fig. \ref{ontologyGraph}. 
 The data has also been published under an Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} at:
@@
 Any Linked Data that needs to refer to the concept can use this identifier.
+
+\begin{figure}
+\caption{{\bf The ontology of creativity generated from this work's results, in graph form.}}
+%% REMOVE IMAGES FROM SUBMITTED VERSION
+%%\includegraphics[scale=0.5]{images/Fig8}
+\label{ontologyGraph}
+\end{figure}
 
@@
 The results of this novel, empirical analysis (presented in the Results section) inform the development of an {\em ontology of creativity\/} comprising a set of fourteen distinct components (see Fig.
-5).
-%\ref{S5_Fig}).
+\ref{components}).
 It is noted that each component makes a separate contribution to the overall meaning of the concept.
@@
 % Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S0a Fig}\label{S0a_Fig}
-{\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus} 
-%\begin{figure}
-%\caption{ A flow diagram describing the search strategy used to identify papers for the creativity corpus}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/PRISMAcc}
-%\label{S0a_Fig}
-%\end{figure}
-
-\subsection*{S0b Fig}\label{S0b_Fig}
-{\bf A flow diagram describing the search strategy used to identify papers for the non-creativity corpus} 
-%\begin{figure}
-%\caption{ A flow diagram describing the search strategy used to identify papers for the non-creativity corpus}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/PRISMAncc}
-%\label{S0b_Fig}
-%\end{figure}
-
-\subsection*{S1a Fig}\label{S1a_Fig}
-{\bf The 30 papers that make up the Creativity Corpus} 
-%\begin{figure}
-%\caption{The 30 papers that make up the Creativity Corpus}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/papersImage}
-%\label{S1_Fig}
-%\end{figure}
-
-\subsection*{S1b Fig}
-\label{S1b_Fig}
-{\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period.
-Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}.
-Note that Scopus may classify a journal under more than one discipline.}
-%\begin{figure}[!ht]
-% \begin{center}
-%\includegraphics[scale=0.5]{images/disciplines}
-% \end{center}
-% \caption{Representation of the disciplinary breakdown of the Creativity Corpus by time period.
-Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}.
-Note that Scopus may classify a journal under more than one discipline.}
-% \label{S1b_Fig}
-%\end{figure}
-
-\subsection*{S2 Fig}\label{S2_Fig}
-{\bf Word pairwise similarity data visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). } 
-%\begin{figure}
-%\caption{Word pairwise similarity data visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). }
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/conceptIdea}
-%\label{S2_Fig}
-%\end{figure}
-
-\subsection*{S3 Fig}
-\label{S3_Fig}
-{\bf Sample of clusters produced by the Chinese Whispers clustering step.}
-%\begin{figure}
-% \caption{Sample of clusters produced by the Chinese Whispers clustering step.}
-%\includegraphics[width=\textwidth]{images/clustersZoom}
-% \label{S3_Fig}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\end{figure}
-
-\subsection*{S4 Fig}
-\label{S4_Fig}
-{\bf Illustration of the process of using manual inspection for further clustering.}
-%\begin{figure}
-% \caption{Illustration of the process of using manual inspection for further clustering.}
-%\includegraphics[width=\textwidth]{images/clusterToComponents}
-% \label{S4_Fig}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\end{figure}
-
-\subsection*{S5 Fig}
-\label{S5_Fig}
-{\bf The fourteen key components of creativity identified through an analysis of the word clusters}
-%\begin{figure} 
-%\caption{The fourteen key components of creativity identified through an analysis of the word clusters}
-%\includegraphics[width=\textwidth]{images/factorsOnly}
-%\label{S5_Fig}
-%\end{figure}
-
-\subsection*{S6 Fig}
-\label{S6_Fig}
-{\bf The ontology of Creativity, in graph form.}
-%\begin{figure}
-%\caption{The ontology of Creativity, in graph form.}
-%\includegraphics[scale=0.5]{images/ontGraph}
-%\label{S6_Fig}
-%\end{figure}
-
-\subsection*{S1 Table}
-\label{S1_Table}
-{\bf The top 20 results of the log-likelihood ratio (LLR) calculations. A significant LLR score at p=0.001 is 10.83. N.B. POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.} 
-%\begin{table}[!ht]%dp]
-%\begin{center}
-%\begin{tabular}{c c | c c}
-%Word (\& POS tag) & LLR & Word (\& POS tag) & LLR \\
-%\hline
-%thinking (N) & 834.55 & process (N) & 612.05 \\
-%innovation (N) & 546.20 & idea (N) & 475.74 \\
-%program (N) & 474.41 & domain (N) & 436.58 \\
-%cognitive (J) & 393.79 & divergent (J) & 355.11 \\
-%openness (N) & 328.57 & discovery (N) & 327.38 \\
-%primary (J) & 326.65 & originality (N) & 315.60 \\
-%criterion (N) & 312.61 & intelligence (N) & 309.31 \\
-%ability (N) & 299.27 & knowledge (N) & 290.48 \\
-%create (V) & 280.06 & experiment (N) & 253.32 \\
-%plan (N) & 246.29 & agent (N) & 246.24 \\
-%\end{tabular}
-%\end{center}
-%\caption{The top 20 results of the log-likelihood ratio (LLR) calculations. A significant LLR score at p=0.001 is 10.83. N.B. POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
-%\label{S1_Table}
-%\end{table}%
+
+\subsection*{S1 Appendix}\label{S1_Appendix}
+{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
+
+\begin{itemize}
+\item T. M. Amabile. The social psychology of creativity: A componential conceptualization. Journal of Personality and Social Psychology, 45(2):357-376, 1983.
+\item M. A. Boden. Precis of The Creative Mind: Myths and mechanisms. Behavioural and Brain Sciences, 17(3):519-570, 1994.
+\item D. T. Campbell. Blind variation and selective retentions in creative thought as in other knowledge processes. Psychological Review, 67(7):380-400, 1960.
+\item S.
+Colton, A.
+Pease, and G.
+Ritchie.
+The effect of input knowledge on creativity.
+In Proceedings of Workshop Program of ICCBR-Creative Systems: Approaches to Creativity in AI and Cognitive Science, 2001.
+\item M. Csikszentmihalyi. Motivation and creativity: Toward a synthesis of structural and energistic approaches to cognition. New Ideas in Psychology, 6(2):159-176, 1988.
+\item M. Dellas and E. L. Gaier. Identification of creativity: The individual. Psychological Bulletin, 73(1):55- 73, 1970.
+\item A. Dietrich. The cognitive neuroscience of creativity. Psychonomic Bulletin \& Review, 11(6):1011-1026, 2004.
+\item G. Domino. Identification of potentially creative persons from the adjective check list. Journal of Consulting and Clinical Psychology, 35(1):48-51, 1970.
+\item W. Duch. Intuition, insight, imagination and creativity. IEEE Computational Intelligence Magazine, 2(3):40-52, 2007.
+\item C. S. Findlay and C. J. Lumsden. The creative mind: Toward an evolutionary theory of discovery and innovation. Journal of Social and Biological Systems, 11(1):3-55, 1988.
+\item C. M. Ford. A theory of individual creative action in multiple social domains. The Academy of Management Review, 21(4):1112-1142, 1996.
+\item J. Gero. Creativity, emergence and evolution in design. Knowledge-Based Systems, 9(7):435-448, 1996. 
+\item H. G. Gough. A creative personality scale for the adjective checklist. Journal of Personality and Social Psychology, 37(8):1398-1405, 1979.
+\item J. P. Guilford. Creativity. American Psychologist, 5:444-454, 1950.
+\item Z. Ivcevic. Creativity map: Toward the next generation of theories of creativity. Psychology of Aesthetics, Creativity, and the Arts, 3(1):17-21, 2009.
+\item K. H. Kim. Can we trust creativity tests? A review of the Torrance tests of creative thinking (TTCT). Creativity Research Journal, 18(1):3-14, 2006.
+\item L. A. King, L. McKee Walker, and S. J. Broyles. Creativity and the five-factor model. Journal of Research in Personality, 30(2):189-203, 1996.
+\item R. R. McCrae. Creativity, divergent thinking, and openness to experience. Journal of Personality and Social Psychology, 52(6):1258-1265, 1987.
+\item S. A. Mednick. The associative basis of the creative process. Psychological Review, 69(3):220-232, 1962. 
+\item M. D. Mumford and S. B. Gustafson. Creativity syndrome: Integration, application, and innovation. Psychological Bulletin, 103(1):27-43, 1988. 
+\item M. T. Pearce, D. Meredith, and G. A. Wiggins. Motivations and methodologies for automation of the compositional process. Musicae Scientae, 6(2):119-147, 2002.
+\item J.
+A.
+Plucker, R.
+A.
+Beghetto, and G.
+T.
+Dow.
+Why isn't creativity more important to educational psychologists?
+Potentials, pitfalls, and future directions in creativity research.
+Educational Psychologist, 39(2):83-96, 2004.
+\item R.
+Richards, D.
+K.
+Kinney, M.
+Benet, and A.
+P.
+C.
+Merzel.
+Assessing everyday creativity: Characteristics of the lifetime creativity scales and validation with three large samples.
+Journal of Personality and Social Psychology, 54(3):476-485, 1988.
+\item G. Ritchie. The transformational creativity hypothesis. New Generation Computing, 24(3):241-266, 2006.
+\item G. Ritchie. Some empirical criteria for attributing creativity to a computer program. Minds and Machines, 17:67-99, 2007.
+\item D. L. Rubenson and M. A. Runco. The psychoeconomic approach to creativity. New Ideas in Psychology, 10(2):131-147, 1992.
+\item M. A. Runco and I. Chand. Cognition and creativity. Educational Psychology Review, 7(3):243-267, 1995.
+\item D. K. Simonton. Creativity: Cognitive, personal, developmental, and social aspects. American Psychologist, 55(1):151-158, 2000.
+\item J. R. Suler. Primary process thinking and creativity. Psychological Bulletin, 88(1):144-165, 1980.
+\item G. A. Wiggins. A preliminary framework for description, analysis and comparison of creative systems. Knowledge-Based Systems, 19(7):449-458, 2006.
+\end{itemize}
+
+\subsection*{S2 Appendix}\label{S2_Appendix}
+\bf{Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
+
+\begin{itemize}
+\item C.
+Ames and J.
+Archer.
+Achievement goals in the classroom: Students' learning strategies and motivation processes.
+Journal of Educational Psychology, 80(3):260-267, 1988.
+% Cited by:  (since 1996) 639.
+\item J. Anderson and D. Gerbing. Structural equation modeling in practice: A review and recommended two-step approach. Psychological Bulletin, 103(3):411-423, 1988. % Cited by:  (since 1996) 3884.
+\item J. Arnett. Emerging adulthood: A theory of development from the late teens through the twenties. American Psychologist, 55(5):469-480, 2000. % Cited by:  (since 1996) 800.
+\item M.
+Arulampalam, S.
+Maskell, N.
+Gordon, and T.
+Clapp.
+A tutorial on particle filters for online nonlinear/non-gaussian bayesian tracking.
+IEEE Transactions on Signal Processing, 50(2):174-188, 2002.
+% Cited by:  (since 1996) 1984.
+\item A. Baddeley. Exploring the central executive. Quarterly Journal of Experimental Psychology Section A: Human Experimental Psychology, 49(1):5-28, 1996. % Cited by:  (since 1996) 672.
+\item T.
+Baker, M.
+Piper, D.
+McCarthy, M.
+Majeskie, and M.
+Fiore.
+Addiction motivation reformulated: An affective processing model of negative reinforcement.
+Psychological Review, 111(1):33-51, 2004.
+% Cited by:  (since 1996) 177.
+\item P.
+Barnett and I.
+Gotlib.
+Psychosocial functioning and depression: Distinguishing among antecedents, concomitants, and consequences.
+Psychological Bulletin, 104(1):97-126, 1988.
+% Cited by:  (since 1996) 366.
+\item J. Baron. Nonconsequentialist decisions. Behavioral and Brain Sciences, 17(1):1-42, 1994. % Cited by:  (since 1996) 68.
+\item F. Beach. The snark was a boojum. American Psychologist, 5(4):115-124, 1950. % Cited by:  (since 1996) 32.
+\item M.
+Belkin, P.
+Niyogi, and V.
+Sindhwani.
+Manifold regularization: A geometric framework for learning from labeled and unlabeled examples.
+Journal of Machine Learning Research, 7:2399-2434, 2006.
+% Cited by:  (since 1996) 145.
+\item G.
+Bonanno.
+Loss, trauma, and human resilience: Have we underestimated the human capacity to thrive after extremely aversive events?
+American Psychologist, 59(1):20-28, 2004.
+% Cited by:  (since 1996) 352.
+\item T. Chan and L. Vese. Active contours without edges. IEEE Transactions on Image Processing, 10(2):266-277, 2001. % Cited by:  (since 1996) 1520.
+\item H. Cheng and J. Schweitzer. Cultural values reflected in Chinese and U.S. television commercials. Journal of Advertising Research, 36(3):27-45, 1996. % Cited by:  (since 1996) 88.
+\item C. Coello Coello. Evolutionary multi-objective optimization: A historical view of the field. IEEE Computational Intelligence Magazine, 1(1):28-36, 2006. % Cited by:  (since 1996) 109.
+\item D.
+Comaniciu and P.
+Meer.
+Mean shift: A robust approach toward feature space analysis.
+IEEE Transactions on Pattern Analysis and Machine Intelligence, 24(5):603-619, 2002.
+% Cited by:  (since 1996) 1613
+\item L. Cronbach and L. Furby. How we should measure `change': Or should we? Psychological Bulletin, 74(1):68-80, 1970. % Cited by: (since 1996) 526.
+\item M. Davis. Measuring individual differences in empathy: Evidence for a multidimensional approach. Journal of Personality and Social Psychology, 44(1):113-126, 1983. % Cited by:  (since 1996) 631.
+\item J. Dem\~{s}ar. Statistical comparisons of classifiers over multiple data sets. Journal of Machine Learning Research, 7:1-30, 2006. % Cited by:  (since 1996) 389.
+\item M.
+Dorigo, M.
+Birattari, and T.
+St\"{u}tzle.
+Ant colony optimization artificial ants as a computational intelligence technique.
+IEEE Computational Intelligence Magazine, 1(4):28-39, 2006.
+% Cited by:  (since 1996) 134.
+\item E.
+Fischer and J.
+Turner.
+Orientations to seeking professional help: Development and research utility of an attitude scale.
+Journal of Consulting and Clinical Psychology, 35(1 PART 1):79-90, 1970.
+% Cited by:  (since 1996) 189.
+\item J. Gibson. Observations on active touch. Psychological Review, 69(6):477-491, 1962. % Cited by:  (since 1996) 179.
+\item A.
+Gopnik and J.
+Astington.
+Children's understanding of representational change and its relation to the understanding of false belief and the appearance-reality distinction.
+Child development, 59(1):26-37, 1988.
+% Cited by:  (since 1996) 314.
+\item S.
+Gosling, S.
+Vazire, S.
+Srivastava, and O.
+John.
+Should we trust web-based studies?
+A comparative analysis of six preconceptions about internet questionnaires.
+American Psychologist, 59(2):93-104, 2004.
+% Cited by:  (since 1996) 313.
+\item J. Gray. The psychophysiological basis of introversion-extraversion. Behaviour Research and Therapy, 8(3):249-266, 1970. % Cited by:  (since 1996) 225.
+\item B. Grosz and S. Kraus. Collaborative plans for complex group action. Artificial Intelligence, 86(2):269- 357, 1996. % Cited by:  (since 1996) 275.
+\item P. Groves and R. Thompson. Habituation: A dual-process theory. Psychological Review, 77(5):419-450, 1970. % Cited by:  (since 1996) 375.
+\item M.
+Hall, J.
+Anderson, S.
+Amarasinghe, B.
+Murphy, S.-W.
+Liao, E.
+Bugnion, and M.
+Lam.
+Maximizing multiprocessor performance with the SUIF compiler.
+Computer, 29(12):84-89, 1996.
+% Cited by:  (since 1996) 161.
+\item F. Happ\'{e}. The role of age and verbal ability in the theory of mind task performance of subjects with autism. Child development, 66(3):843-855, 1995. % Cited by:  (since 1996) 285.
+\item C. Harland. Supply chain management: Relationships, chains and networks. British Journal of Management, 7(SPEC. ISS.):S63-S80, 1996. % Cited by:  (since 1996) 172.
+\item S.
+Hayes, K.
+Strosahl, K.
+Wilson, R.
+Bissett, J.
+Pistorello, D.
+Toarmino, M.
+Polusny, T.
+Dykstra, S.
+Batten, J.
+Bergan, S.
+Stewart, M.
+Zvolensky, G.
+Eifert, F.
+Bond, J.
+Forsyth, M.
+Karekla, and S.
+McCurry.
+Measuring experiential avoidance: A preliminary test of a working model.
+Psychological Record, 54(4):553-578, 2004.
+% Cited by:  (since 1996) 168.
+\item J.
+Hirsch and K.
+L\"{u}cke.
+Overview no.
+76.
+mechanism of deformation and development of rolling textures in polycrystalline f.c.c.
+metals-i.
+description of rolling texture development in homogeneous cuzn alloys.
+Acta Metallurgica, 36(11):2863-2882, 1988.
+% Cited by:  (since 1996) 243.
+\item P. Killeen. Mathematical principles of reinforcement. Behavioral and Brain Sciences, 17(1):105-172, 1994. % Cited by:  (since 1996) 86.
+\item P.
+Kirschner, J.
+Sweller, and R.
+Clark.
+Why minimal guidance during instruction does not work: An analysis of the failure of constructivist, discovery, problem-based, experiential, and inquiry-based teaching.
+Educational Psychologist, 41(2):75-86, 2006.
+% Cited by:  (since 1996) 139.
+\item S. Liao. Notes on the homotopy analysis method: Some definitions and theorems. Communications in Nonlinear Science and Numerical Simulation, 14(4):983-997, 2009. % Cited by:  (since 1996) 56.
+\item C.
+Lord, L.
+Ross, and M.
+Lepper.
+Biased assimilation and attitude polarization: The effects of prior theories on subsequently considered evidence.
+Journal of Personality and Social Psychology, 37(11):2098- 2109, 1979.
+% Cited by:  (since 1996) 523.
+\item S. Luthar, D. Cicchetti, and B. Becker. The construct of resilience: A critical evaluation and guidelines for future work. Child Development, 71(3):543-562, 2000. % Cited by:  (since 1996) 566.
+\item G. Mandler. Recognizing: The judgment of previous occurrence. Psychological Review, 87(3):252-271, 1980. % Cited by:  (since 1996) 877.
+\item G. Miller and J. Selfridge. Verbal context and the recall of meaningful material. The American journal of psychology, 63(2):176-185, 1950. % Cited by:  (since 1996) 57.
+\item S.
+Miller.
+Monitoring and blunting: Validation of a questionnaire to assess styles of information seeking under threat.
+Journal of Personality and Social Psychology, 52(2):345-353, 1987.
+% Cited by:  (since 1996) 385.
+\item G. Navarro and V. M\"{a}kinen. Compressed full-text indexes. ACM Computing Surveys, 39(1), 2007. % Cited by:  (since 1996) 62.
+\item M. Nissen and P. Bullemer. Attentional requirements of learning: Evidence from performance measures. Cognitive Psychology, 19(1):1-32, 1987. % Cited by:  (since 1996) 729.
+\item J.
+Payne, J.
+Bettman, and E.
+Johnson.
+Adaptive strategy selection in decision making.
+Journal of Experimental Psychology: Learning, Memory, and Cognition, 14(3):534-552, 1988.
+% Cited by:  (since 1996) 300.
+\item J. Prochaska, C. DiClemente, and J. Norcross. In search of how people change: Applications to addictive behaviors. American Psychologist, 47(9):1102-1114, 1992. % Cited by:  (since 1996) 2742.
+\item T.
+Richardson, M.
+Shokrollahi, and R.
+Urbanke.
+Design of capacity-approaching irregular low-density parity-check codes.
+IEEE Transactions on Information Theory, 47(2):619-637, 2001.
+% Cited by:  (since 1996) 1162.
+\item W. Rozeboom. The fallacy of the null-hypothesis significance test. Psychological Bulletin, 57(5):416-428, 1960. % Cited by:  (since 1996) 133.
+\item C.
+Rusbult.
+A longitudinal test of the investment model: The development (and deterioration) of satisfaction and commitment in heterosexual involvements.
+Journal of Personality and Social Psychology, 45(1):101-117, 1983.
+% Cited by:  (since 1996) 301.
+\item T. Ryan. Significance tests for multiple comparison of proportion, variance, and other statistics. Psychological Bulletin, 57(4):318-328, 1960. % Cited by:  (since 1996) 154.
+\item W. Schultz. Behavioral theories and the neurophysiology of reward. Annual Review of Psychology, 57:87-115, 2006. % Cited by:  (since 1996) 226.
+\item E. Sirin, B. Parsia, B. Grau, A. Kalyanpur, and Y. Katz. Pellet: A practical OWL-DL reasoner. Web Semantics, 5(2):51-53, 2007. % Cited by:  (since 1996) 125.
+\item T.
+Srull and R.
+Wyer.
+The role of category accessibility in the interpretation of information about persons: Some determinants and implications.
+Journal of Personality and Social Psychology, 37(10):1660- 1672, 1979.
+% Cited by:  (since 1996) 374.
+\item J. Steiger. Tests for comparing elements of a correlation matrix. Psychological Bulletin, 87(2):245-251, 1980. % Cited by:  (since 1996) 705.
+\item L.
+Steinberg, S.
+Lamborn, S.
+Dornbusch, and N.
+Darling.
+Impact of parenting practices on adolescent achievement: authoritative parenting, school involvement, and encouragement to succeed.
+Child development, 63(5):1266-1281, 1992.
+% Cited by:  (since 1996) 435.
+\item D. Tao, X. Li, X. Wu, W. Hu, and S. Maybank. Supervised tensor learning. Knowledge and Information Systems, 13(1):1-42, 2007. % Cited by:  (since 1996) 54.
+\item A.
+Tellegen, D.
+Lykken, T.
+Bouchard Jr., K.
+Wilcox, N.
+Segal, and S.
+Rich.
+Personality similarity in twins reared apart and together.
+Journal of Personality and Social Psychology, 54(6):1031-1039, 1988.
+% Cited by:  (since 1996) 398.
+\item L.
+Thomas and D.
+Ganster.
+Impact of family-supportive work variables on work-family conflict and strain: A control perspective.
+Journal of Applied Psychology, 80(1):6-15, 1995.
+% Cited by:  (since 1996) 339.
+\item I. Thompson. Coupled reaction channels calculations in nuclear physics. Computer Physics Reports, 7(4):167-212, 1988. % Cited by:  (since 1996) 360.
+\item E. Tulving. Subjective organization in free recall of ``unrelated'' words. Psychological Review, 69(4):344- 354, 1962. % Cited by:  (since 1996) 121.
+\item U. Von Luxburg. A tutorial on spectral clustering. Statistics and Computing, 17(4):395-416, 2007. % Cited by:  (since 1996) 107.
+\item J. Williams, A. Mathews, and C. MacLeod. The emotional stroop task and psychopathology. Psychological Bulletin, 122(1):3-24, 1996. % Cited by:  (since 1996) 716.
+\item J.
+Wright, A.
+Yang, A.
+Ganesh, S.
+Sastry, and Y.
+Ma.
+Robust face recognition via sparse representation.
+IEEE Transactions on Pattern Analysis and Machine Intelligence, 31(2):210-227, 2009.
+% Cited by:  (since 1996) 46.
+\end{itemize}
 

### 2016-08-04 plosOneJordanousKeller/PAPER/RevisedManuscript.tex

--- 2016-08-03 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex
@@
 {\Large
-\textbf\newline{\bf Modelling creativity: identifying key components through a corpus-based approach}
-\textbf\newline{\sout{Creativity is what we say it is: identifying key components of creativity}}
+\textbf\newline{Modelling Creativity: Identifying Key Components through a Corpus-Based Approach}
 }
@@
 
-\textbf{Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
+Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
 If we wish to study creativity scientifically, then a tractable and well-articulated model of creativity is required.
 Such a model would be of great value to researchers investigating the nature of creativity and in particular, those concerned with the evaluation of creative practice.
-This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people used to describe the concept.
+This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people use to describe the concept.
 Using techniques from the field of statistical natural language processing, we identify a collection of fourteen key components of creativity through an analysis of a corpus of academic papers on the topic.
@@
 The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating achievements of this work and directions for further research.
-}
-
-\sout{
-Creativity is a complex multi-dimensional concept which resists definition; it is accessible to us at a subjective, multi-faceted and dynamic level rather than being fixed and clearly defined.
-If we wish to study creativity scientifically using computational models, or simulate it computationally, then a tractable and accurate interpretation of creativity is needed.
-Creativity encompasses many related aspects, abilities, properties and behaviours.
-This paper uses techniques from the field of statistical natural language processing to identify a collection of fourteen key components of creativity through an analysis of what is considered to be important in talking about creativity.
-Words were identified which appeared significantly often in connection with discussions of the concept.
-Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerged, which collectively contribute to a comprehensive and multi-perspective definition of creativity.
-The components provide an ontology of creativity: a set of building blocks which, in evaluation, have proven useful for making the concept easier to understand and more tractable to study and evaluate.}
 
@@
 The need for a more over-arching, inclusive, multi-dimensional account of creativity has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}.
-Such a {\bf meta-level} account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
+Such a meta-level account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
 
@@
 Tackling these challenges affords two key advantages, both of which motivate the current paper.
-First, we can take advantage of computing and artificial intelligence to perform and/or enhance creative activities using computational power and research expertise.
+First, we can take advantage of computing and artificial intelligence to perform or enhance creative activities using computational power and research expertise.
 Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept.
-\sout{Both these advantages motivate this current paper.}
 
 The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components, representing key dimensions, that are recognised across a combination of different viewpoints.
-We present a novel, empirical approach to the problem of modelling how creative behaviour emerges, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
+We present a novel, empirical approach to the problem of modelling how creative behaviour is manifested, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
 Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}.
@@
 
-\sout{The rest of this section considers the problem of providing a definition of creativity and reviews previous attempts to do so.}
-{\bf In the rest of this section we begin by noting a variety of attempts to define creativity.} The representation of subjective, ambiguous, loosely structured concepts is considered.
+In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is considered.
 %, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
@@
 Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. 
-% Currently, no one definition has been adopted as standard, either in everyday use (as evidenced by the dictionary definitions considered below), for research % purposes \cite{rhodes61,taylor88,plucker04defn} or even in legal practice \cite{clifford04,mandel11}, where one would expect a term critical to legal
-% judgements  -- as creativity surely is \cite{feist91,karjala08,schafer15} -- to be precisely and unambiguously defined. 
-%
-%The difficulty of formulating an adequate definition of creativity in words should not discourage us from the attempt, however  \cite{rhodes61,plucker04defn,kaufman09}.
-Even if other researchers have been swayed away from this task \cite[for example]{sternberg99a,veale06preface},  care must be taken that we `do not throw out the baby with the bath water just because the water is cloudy' \cite[p.
-310]{rhodes61}.
-Some of the issues concerning the problem of defining creativity have been debated for decades.
-The following sections consider the need for an explicit and comprehensive definition of creativity and the difficulties researchers encounter in providing one.
-\paragraph{\sout{A question of definition?}}
-%{\bf \em The next paragraph needs some thought, as it is is still talking about the need for definition.
-I think Plucker's comments on the original submission might suggest that he feels that this debate has now concluded (and that definition(s) of creativity have been provided.
-If so, then we need to modify this, at least.)}
-\sout{Plucker makes the case that the lack of a common understanding for creativity research weakens the `legitimacy' and validity of that research.
-He notes that `Without an agreed-on definition of the construct, creativity's potential contributions to psychology and education will remain limited'} \cite[\sout{p.87}]{plucker04defn} \sout{and further that  `unless the definitional problem is addressed, creativity research will continue to be impeded by lack of direction, damaging mythologies, and general misunderstanding'} \cite[\sout{p.92}]{plucker04defn}.
-\sout{In fact, `Rather than being a strength of the field, as many believe, the lack of a common definition is a major, debilitating weakness.
-...
-we feel that an agreed-on definition is long overdue and has placed the field in a crisis of legitimacy.
-...
-This change in the focus and direction of creativity research is needed if the field is to move from a shadowy past into the forefront of constructive approaches' }\cite[\sout{p.
-93}]{plucker04defn}.
-\sout{Other researchers share these concerns: `I submit that the time has come for more precision in definition and usage [of the word creativity], that only when the field is analyzed and organized - when the listener can be sure he knows what the speaker is talking about - will the pseudo aspect of the subject of creativity disappear' }\cite[\sout{p.
-310}]{rhodes61}.
-
 In their review of research into human creativity, Hennessey and Amabile ask a significant follow-on question: 
@@
 A more objective and well-articulated account of how creativity is manifested enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.
-\textbf{Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite[p.
-15]{vartanian14}, based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.}
-
-\paragraph{\sout{Existing definitions.}{\bf Definitions of creativity.}}
+Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite[p.
+15]{vartanian14}, based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.
+
+\paragraph{Definitions of creativity.}
 \label{existing_defs}
@@
 To find out the meaning of a word, a natural first step might be to consult a dictionary.
-Dictionary definitions of `creativity' provide a brief introduction to  the meaning of the word.
+Dictionary definitions of creativity provide a brief introduction to  the meaning of the word.
 However, for the purposes of research, the utility of such definitions is severely restricted by their format and brevity, and they generally provide only cursory, shallow insights into the nature of creativity.
@@
 In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} has historially placed emphasis on the {\em novelty} and {\em value} of creative products.
-Whilst there is some consensus across academic fields, \textbf{for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99},} the differing emphases contribute to variations in the interpretation of creativity.
+Whilst there is some consensus across academic fields, for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99}, the differing emphases contribute to variations in the interpretation of creativity.
 These variations affect consistency across creativity research in different disciplines and potentially hinder interdisciplinary collaborations and cross-application of findings.
@@
 
-\subsection*{\sout{Towards a clearer understanding of creativity}}\label{progressingForwards}
-
-\sout{Returning to the concept under discussion } 
 The need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed.
@@
 In approaching the semantic representation of subjective and multi-faceted concepts, some useful guidance is offered through philosophical reflections on the meaning of such concepts.
-
-\sout{The proposed approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
-In addition, following from the observations above, a   confluence approach to creativity is adopted [refs]
-%\cite{sternberg99a,mayer99,ivcevic09}. 
-This works on the principle that creativity results from several components converging and goes on to examine what these components are.
-Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted.
-This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.}
 
@@
 
-{\bf Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
+Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
 In addition, following from the observations above, a {\em  confluence approach\/} to creativity is adopted \cite{sternberg99a,mayer99,ivcevic09}.
@@
 Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted.
-This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.}
+This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.
 
@@
 
-The 30 papers selected for the creativity corpus are listed in \nameref{S1_Appendix}. 
-\textbf{The search strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}. }
+The 30 papers selected for the creativity corpus are listed in \nameref{S1_Appendix}. The strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}.
 
@@
 
-\textbf{The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers.
-This literature search was supplemented with additional influential papers which may have not appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.} The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.}
-
-\textbf{Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
-The inclusion criteria are as follows, listed in descending order of precedence: }
+The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers.
+This literature search was supplemented with additional influential papers which may not have appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.} The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.
+
+Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
+The inclusion criteria are as follows, listed in descending order of precedence:
 \begin{itemize}
-\item \textbf{Papers must have, as their primary focus, discussion of the nature of creativity.}
-\item \textbf{Papers should be considered particularly influential.
+\item Papers must have, as their primary focus, discussion of the nature of creativity.
+\item Papers should be considered particularly influential.
 Influence was generally measured objectively, in terms of the number of times a paper had been cited by other academic authors.
-However, for papers published in recent years and which had consequently had little time to accrue citations, selection was based instead on a subjective judgement of influence grounded in a knowledge of the field.}
-\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009.
+However, for papers published in recent years and which had consequently had little time to accrue citations, selection was based instead on a subjective judgement of influence grounded in a knowledge of the field.
+\item Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009.
 [The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J.
@@
 His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.
-}
-\item \textbf{Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of creativity.
+\item Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of creativity.
 Fig.
@@
 We should acknowledge here though that while many disciplines include creative practice, often the focus is on application rather than in depth discussion of what creativity entails.
-Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the focus of our corpus as a representation of key discussions about the nature of creativity.}
+Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the focus of our corpus as a representation of key discussions about the nature of creativity.
 \end{itemize}
-\sout{The papers were carefully chosen so as to cover a wide range of years (1950-2009) and academic disciplines.
-A paper was included if it was considered particularly influential, as measured by the number of times it had been cited by other academic authors.
-For papers published in recent years and which have consequently not yet accrued many citations, selection was based on subjective judgement of influence.}
 
@@
 
-\textbf{Exclusion criteria for this search were as follows: }
+Exclusion criteria for this search were as follows: 
 \begin{itemize}
-\item \textbf{Authors were only represented more than once in the corpus if the relevant papers were written from different perspectives.
+\item Authors were only represented more than once in the corpus if the relevant papers were written from different perspectives.
 For example, Mark Runco's work is represented twice in the corpus, but covering two different topics relating to the nature of creativity (psychoeconomic approach to creativity; cognition and creativity).
 If the search process highlighted two or more papers with a shared author on the same or highly similar perspectives on creativity, then the more highly cited paper was chosen.
-}
-\item \textbf{Papers had to be written in English, as the language processing tools we were working with were for English language texts.}
-\item \textbf{Papers had to be available in a format that enabled us easily to extract plain text (this excluded books or book chapters).}
+\item Papers had to be written in English, as the language processing tools we were working with were for English language texts.
+\item Papers had to be available in a format that enabled us easily to extract plain text (this excluded books or book chapters).
 \end{itemize}
@@
 Our objective is to identify what is distinctive in the language used to discuss creativity, in contrast to the language used to discuss other topics.
-As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled \textbf{alongside the creativity corpus, in 2010}.
+As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled alongside the creativity corpus, in 2010.
 
@@
 {\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).
-\textbf{In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.
+In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.
 The 60 papers selected for the creativity corpus are listed in \nameref{S2_Appendix}.
@@
 \ref{searchNonCC}.
-}
 
@@
 The non-creativity corpus is twice the size of the creativity corpus ($\approx$ 700,000 words and $\approx$ 300,000 words respectively), in acknowledgement of the fact that in general the set of academic papers on creativity is only a small subset of all academic papers.
-Both corpora are very small in comparison to corpora such as the British National Corpus, a \textbf{relatively} large  ($\approx$ 100M words) corpus of written and spoken English in general usage across a number of different contexts, and tiny in comparison to more recent web-derived text collections containing billions of words.
+Both corpora are very small in comparison to corpora such as the British National Corpus, a relatively large  ($\approx$ 100M words) corpus of written and spoken English in general usage across a number of different contexts, and tiny in comparison to more recent web-derived text collections containing billions of words.
 There are, however, several benefits associated with using a corpus derived from specialist academic literature:
@@
 
-\textbf{Some pre-processing was undertaken for each paper in both the creativity corpus and non-creativity corpus prior to analysis.
+Some pre-processing was undertaken for each paper in both the creativity corpus and non-creativity corpus prior to analysis.
 A plain text file was generated for each paper, containing the full text of that paper.
 All journal headers and copyright notices were removed from each paper, as were the author names and affiliations, list of references and acknowledgements.
-All files were also checked for any non-ascii characters and anomalies that may have arisen during the creation of the text file.}
+All files were also checked for any non-ASCII characters and anomalies that may have arisen during the creation of the text file.
 
@@
 As a further refinement, each lemma was also mapped to lower case to ensure that capitalised word forms (e.g.
-{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).\footnote{\bf While this can result in confusion between proper names and common nouns (e.g.
+{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).\footnote{While this can result in confusion between proper names and common nouns (e.g.
 {\em Apple\/} v.
@@
 The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus.
-This in turn can be regarded as providing evidence of which words are salient to the \sout{definition} \textbf{concept} of creativity.
+This in turn can be regarded as providing evidence of which words are salient to the concept of creativity.
 Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.
@@
 
-\sout{The creativity words were clustered according a statistical measure of {\em distributional similarity\/}.
-}The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}.
+The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}.
 This hypothesis  states that similarity of distribution correlates with similarity of meaning: two words that tend to appear in similar linguistic contexts will tend to have similar meanings.
@@
 This additional analysis provided a means of identifying alternative perspectives and revealing subtle (but still important) aspects of creativity.
-For example, {\em novelty} is commonly associated with the results of creative behaviour ({\em product\/}): how novel is the artefact or idea that has been produced?
-However, we could similarly recognise as creative an approach to a task  ({\em process\/}) that does things in a novel and different way.
-Also, if a product is new in a particular environment ({\em press\/}), then it may well be regarded as creative to those in that environment.
-Viewing {\em novelty} from the perspectives of {\em product}, {\em process} and {\em press} uncovers these subtle and interlinked distinctions.
+For example, {\em novelty} is commonly associated with the results of creative behaviour (Product): how novel is the artefact or idea that has been produced?
+However, we could similarly recognise as creative an approach to a task  (Process) that does things in a novel and different way.
+Also, if a product is new in a particular environment (Press), then it may well be regarded as creative to those in that environment.
+Viewing {\em novelty} from the perspectives of Product, Process and Press uncovers these subtle and interlinked distinctions.
 
@@
 
-The results obtained above were compared with those from applying other evaluation models and with surveys of people's opinions, where people were asked how creative they thought each system was.
+The results described above were compared with those obtained from applying other evaluation models and with surveys of people's opinions, where people were asked how creative they thought each system was.
 There was general agreement between evaluation approaches on the most and least creative systems.
@@
 
-Rather than attempting to provide a unitary definition of creativity, our approach extracts common, underlying themes that transcend discipline or domain bias.
+Rather than attempting to provide a unitary account of creativity, our approach extracts common, underlying themes that transcend discipline or domain bias.
 Our point of departure is the observation that the vocabulary used in discussions of the nature of creativity may be analysed in order to throw light on our understanding of the concept and its key attributes.

### 2016-08-04 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
Gallie cite
added cite after ‘Gallie’ in section “The challenges of modelling
creativity”

@@
 167]{gallie56}.
-Gallie defines an essentially contested concept through several features: being internally complex in nature, but amenable to being broken down into identifiable constituent elements of varying relative importance, and dependent on a number of factors such as context and individual preference.
+Gallie \cite{gallie56} defines an essentially contested concept through several features: being internally complex in nature, but amenable to being broken down into identifiable constituent elements of varying relative importance, and dependent on a number of factors such as context and individual preference.
 Although there may be consensus on the meaning of such concepts in very general terms, they may defy precise interpretation.

### 2016-08-04 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex

@@
 Such a model would be of great value to researchers investigating the nature of creativity and in particular, those concerned with the evaluation of creative practice.
-This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people used to describe the concept.
+This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people use to describe the concept.
 Using techniques from the field of statistical natural language processing, we identify a collection of fourteen key components of creativity through an analysis of a corpus of academic papers on the topic.
@@
 Tackling these challenges affords two key advantages, both of which motivate the current paper.
-First, we can take advantage of computing and artificial intelligence to perform and/or enhance creative activities using computational power and research expertise.
+First, we can take advantage of computing and artificial intelligence to perform or enhance creative activities using computational power and research expertise.
 Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept.
@@
 The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components, representing key dimensions, that are recognised across a combination of different viewpoints.
-We present a novel, empirical approach to the problem of modelling how creative behaviour emerges, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
+We present a novel, empirical approach to the problem of modelling how creative behaviour is manifested, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
 Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}.
@@
 The 30 papers selected for the creativity corpus are listed in \nameref{S1_Appendix}. 
-\textbf{The search strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}. }
+\textbf{The strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}. }
 
@@
 \textbf{The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers.
-This literature search was supplemented with additional influential papers which may have not appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.} The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.}
+This literature search was supplemented with additional influential papers which may not have appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.} The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.}
 
@@
 All journal headers and copyright notices were removed from each paper, as were the author names and affiliations, list of references and acknowledgements.
-All files were also checked for any non-ascii characters and anomalies that may have arisen during the creation of the text file.}
+All files were also checked for any non-ASCII characters and anomalies that may have arisen during the creation of the text file.}
 

### 2016-08-04 plosOneJordanousKeller/responseToReviewers.txt
adding line numbers to response doc

--- 2016-08-03 plosOneJordanousKeller/rebuttal.txt
@@
 PLOS ONE
+
+We send our thanks to the reviewers and editor for their useful and constructive comments, and appreciate the time they have taken.
 
@@
 
-***** While revising your submission, we encourage you to use PACE (the Preflight* Analysis and Conversion Engine, http://pace.apexcovantage.com/), a digital diagnostic and conversion tool for figure files.
+>> While revising your submission, we encourage you to use PACE (the Preflight* Analysis and Conversion Engine, http://pace.apexcovantage.com/), a digital diagnostic and conversion tool for figure files.
 PACE helps users ensure that their figures meet PLOS requirements and that the quality of published figures will be as high as possible.
 
-***** ANNA TO LOOK AT THIS *****
-
-***** Please ensure that your manuscript meets PLOS ONE's style requirements, including those for file naming. The PLOS ONE style templates can be found at
-
-***** http://www.journals.plos.org/plosone/s/file?id=wjVg/PLOSOne_formatting_sample_main_body.pdf and http://www.journals.plos.org/plosone/s/file?id=ba62/PLOSOne_formatting_sample_title_authors_affiliations.pdf
+This has been done.
 
@@
 
-Thank you to the reviewer also for pointing us at Vartanian (2014) which is very relevant to the current work: we have added a citation in the Background section (line no.: ??).
+Thank you to the reviewer also for pointing us at Vartanian (2014) which is very relevant to the current work: we have added a citation in the Background section (lines no 123-126 in the Tracked Changes manuscript).
 The title has been amended to reflect the reframing and we have carefully edited the text throughout to ensure that the emphasis on modelling rather than definition is clear.
@@
 
-We note in line ??209 that although originality and usefulness are indeed widely agreed to be two necessary components of creativity, there are many other components which have arisen in previous analyses which contribute to the understanding of creativity, such as Gabora et al's identification of internal cognitive changes.
+We note in lines 208-213 of the Tracked Changes Manuscript that although originality and usefulness are indeed widely agreed to be two necessary components of creativity, there are many other components which have arisen in previous analyses which contribute to the understanding of creativity, such as Gabora et al's identification of internal cognitive changes.
 
-In particular, in our experience, computational modelling of creativity has shown that it is not sufficient to incorporate only novelty and usefulness in software that is designed to be creative; this overlooks the more subtle aspects of creativity that creativity researchers and practicioners have been aware of for some time.
+In particular, in our experience, computational modelling of creativity has shown that it is not sufficient to incorporate only novelty and usefulness in software that is designed to be creative; this overlooks the more subtle aspects of creativity that creativity researchers and practitioners have been aware of for some time.
 

### 2016-08-04 plosOneJordanousKeller/PAPER/RevisedManuscriptWithTrackChanges.tex
boldening the Appendices as they are a change to the manuscript

@@
 \subsection*{S1 Appendix}\label{S1_Appendix}
-{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
+\bf{Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
 
@@
 \subsection*{S2 Appendix}\label{S2_Appendix}
-\bf{Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
+{\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
 

### 2016-09-07 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
final small edits before submitting
incorporated bibliography
Copy-and-paste of generated bbl file into tex source as required by PLOS

@@
 
-\bibliography{references}
+\begin{thebibliography}{10}
+
+\bibitem{coltonwiggins12}
+Colton S, Wiggins GA.
+\newblock Computational Creativity: The Final Frontier?
+\newblock In: Proceedings of 20th European Conference on Artificial
+  Intelligence (ECAI). Montpellier, France; 2012. p. 21--26.
+
+\bibitem{colton08}
+Colton S.
+\newblock Creativity versus the Perception of Creativity in Computational
+  Systems.
+\newblock In: Proceedings of AAAI Symposium on Creative Systems; 2008. p.
+  14--20.
+
+\bibitem{widmerAIM09}
+Widmer G, Flossmann S, Grachten M.
+\newblock {YQX} Plays {Chopin}.
+\newblock AI Magazine. {2009};{30}({3}):35--48.
+
+\bibitem{leon10MM}
+Le\'on C, Gerv\'as P.
+\newblock The Role of Evaluation-Driven Rejection in the Successful Exploration
+  of a Conceptual Space of Stories.
+\newblock Minds and Machines. 2010;20(4):615--634.
+
+\bibitem{perezyperez99}
+P\'erez~y P\'erez R.
+\newblock MEXICA: A Computer Model of Creativity in Writing [PhD thesis].
+\newblock University of Sussex. Brighton, UK; 1999.
+
+\bibitem{cardoso09}
+Cardoso A, Veale T, Wiggins GA.
+\newblock Converging on the Divergent: The History (and Future) of the
+  International Joint Workshops in Computational Creativity.
+\newblock AI Magazine. 2009;30(3):15--22.
+
+\bibitem{rhodes61}
+Rhodes M.
+\newblock An analysis of creativity.
+\newblock Phi Delta Kappan. 1961;42(7):305--310.
+
+\bibitem{torrance67}
+Torrance EP.
+\newblock Scientific Views of Creativity and Factors Affecting its Growth.
+\newblock In: Kagan J, editor. Creativity and Learning. Boston: Beacon Press;
+  1967. p. 73--91.
+
+\bibitem{plucker04defn}
+Plucker JA, Beghetto RA, Dow GT.
+\newblock Why Isn't Creativity More Important to Educational Psychologists?
+  {Potentials}, Pitfalls, and Future Directions in Creativity Research.
+\newblock Educational Psychologist. 2004;39(2):83--96.
+
+\bibitem{kaufman09}
+Kaufman JC.
+\newblock Creativity 101.
+\newblock The Psych 101 series. New York: Springer; 2009.
+
+\bibitem{hennessey10}
+Hennessey BA, Amabile TM.
+\newblock Creativity.
+\newblock Annual Review of Psychology. 2010;61:569--598.
+
+\bibitem{plucker04}
+Plucker JA, Beghetto RA.
+\newblock Why Creativity is Domain General, Why it Looks Domain Specific, and
+  why the Distinction Doesn't Matter.
+\newblock In: Sternberg RJ, Grigorenko EL, Singer JL, editors. Creativity: From
+  Potential to Realization. Washington, DC: American Psychological Association;
+  2004. p. 153--167.
+
+\bibitem{lakoff87}
+Lakoff G.
+\newblock Women, Fire and Dangerous things: What Categories reveal about the
+  mind.
+\newblock Chicago, IL: University of Chicago Press; 1987.
+
+\bibitem{wittgenstein58}
+Wittgenstein L.
+\newblock {Philosophical Investigations, eds. Anscombe, G. E. M. and Rhees, R.
+  and {Von Wright}, G. H.}
+\newblock 2nd ed. Oxford, UK: Basil Blackwell; 1958.
+
+\bibitem{torrance88}
+Torrance EP.
+\newblock The Nature of Creativity as Manifest in its testing.
+\newblock In: Sternberg RJ, editor. The Nature of Creativity. Cambridge, UK:
+  Cambridge University Press; 1988. p. 43--75.
+
+\bibitem{sternberg99a}
+Sternberg RJ, Lubart TI.
+\newblock The Concept of Creativity: Prospects and Paradigms.
+\newblock In: Sternberg RJ, editor. Handbook of Creativity. Cambridge, UK:
+  Cambridge University Press; 1999. p. 3--15.
+
+\bibitem{vartanian14}
+Vartanian O.
+\newblock Toward a Cumulative Psychological Science of Aesthetics, Creativity,
+  and the Arts.
+\newblock Psychology of Aesthetics, Creativity, and the Arts. 2014;8(1):15--17.
+
+\bibitem{stein63}
+Stein MI.
+\newblock A Transactional Approach to Creativity.
+\newblock In: Taylor CW, Barron F, editors. Scientific Creativity: Its
+  Recognition and Development. New York: John Wiley \& Sons; 1963. p. 217--227.
+
+\bibitem{boden04}
+Boden MA.
+\newblock The creative mind: Myths and mechanisms.
+\newblock 2nd ed. London, UK: Routledge; 2004.
+
+\bibitem{guilford50}
+Guilford JP.
+\newblock Creativity.
+\newblock American Psychologist. 1950;5:444--454.
+
+\bibitem{torrance74}
+Torrance EP.
+\newblock Torrance Tests of Creative Thinking.
+\newblock Bensenville, IL: Scholastic Testing Service; 1974.
+
+\bibitem{pease01}
+Pease A, Winterstein D, Colton S.
+\newblock Evaluating Machine Creativity.
+\newblock In: Proceedings of Workshop Program of ICCBR-Creative Systems:
+  Approaches to Creativity in AI and Cognitive Science; 2001. p. 129--137.
+
+\bibitem{wiggins06ngc}
+Wiggins GA.
+\newblock Searching for computational creativity.
+\newblock New Generation Computing. 2006;24(3):209--222.
+
+\bibitem{peinado06ngc}
+Peinado F, Gervas P.
+\newblock {Evaluation of automatic generation of basic stories}.
+\newblock New Generation Computing. {2006};{24}({3}):{289--302}.
+
+\bibitem{ritchie07}
+Ritchie G.
+\newblock Some Empirical Criteria for Attributing Creativity to a Computer
+  Program.
+\newblock Minds and Machines. 2007;17:67--99.
+
+\bibitem{mayer99}
+Mayer RE.
+\newblock Fifty Years of Creativity Research.
+\newblock In: Sternberg RJ, editor. Handbook of Creativity. Cambridge, UK:
+  Cambridge University Press; 1999. p. 449--460.
+
+\bibitem{dietrich10}
+Dietrich A, Kanso R.
+\newblock A review of {EEG}, {ERP}, and Neuroimaging Studies of Creativity and
+  Insight.
+\newblock Psychological Bulletin. 2010;136(5):822--848.
+
+\bibitem{gabora12}
+Gabora L, O'Connor B, Ranjan A.
+\newblock The recognizability of individual creative styles within and across
+  domains.
+\newblock Psychology of Aesthetics, Creativity, and the Arts.
+  2012;6(4):351--360.
+
+\bibitem{mccormack07}
+McCormack J.
+\newblock Creative Ecosystems.
+\newblock In: Proceedings of the 4th International Joint Workshop on
+  Computational Creativity. London, UK; 2007. p. 129--136.
+
+\bibitem{sosa09}
+Sosa R, Gero J, Jennings K.
+\newblock Growing and Destroying the Worth of Ideas.
+\newblock In: Proceedings of the 7th ACM Creativity and Cognition conference.
+  Berkeley, California; 2009. p. 295--304.
+
+\bibitem{plucker98}
+Plucker JA.
+\newblock Beware of Simple Conclusions: The Case for Content Generality of
+  Creativity.
+\newblock Creativity Research Journal. 1998;11(2):179--182.
+
+\bibitem{baer98}
+Baer J.
+\newblock The Case for Domain Specificity of Creativity.
+\newblock Creativity Research Journal. 1998;11(2):173--177.
+
+\bibitem{baer10}
+Baer J.
+\newblock Is Creativity Domain-Specific?
+\newblock In: Kaufman JC, Sternberg RJ, editors. The Cambridge Handbook of
+  Creativity. New York, NY: Cambridge University Press; 2010. p. 321--341.
+
+\bibitem{poincare29}
+Poincar\'e H.
+\newblock Mathematical Creation.
+\newblock In: The Foundations of Science: Science and Hypothesis, The Value of
+  Science, Science and Method.. vol. Science and Method [Original French
+  version published 1908, Authorized translation by George Bruce Halsted]. New
+  York: The Science Press; 1929. p. 383--394.
+
+\bibitem{hadamard45}
+Hadamard J.
+\newblock An Essay on the Psychology of Invention in the Mathematical Field.
+\newblock Princeton, NJ: Princeton University Press; 1945.
+
+\bibitem{weisberg88}
+Weisberg RW.
+\newblock Problem Solving and Creativity.
+\newblock In: Sternberg RJ, editor. The Nature of Creativity. Cambridge, UK:
+  Cambridge University Press; 1988. p. 148--176.
+
+\bibitem{bryankinns09}
+Bryan-Kinns N.
+\newblock {Everyday Creativity}.
+\newblock In: Bryan-Kinns N, Gross MD, Johnson H, Ox J, Wakkary R, editors.
+  Proceedings of the 7th ACM conference on Creativity and Cognition. Berkeley,
+  California: ACM; 2009. p. iii--iv.
+
+\bibitem{mooney63}
+Mooney RL.
+\newblock A Conceptual Model for Integrating Four Approaches to the
+  Identification of Creative Talent.
+\newblock In: Taylor CW, Barron F, editors. Scientific Creativity: Its
+  Recognition and Development. New York: John Wiley \& Sons; 1963. p. 331--340.
+
+\bibitem{odena09}
+Odena O, Welch G.
+\newblock A Generative Model of Teachers' Thinking on Musical Creativity.
+\newblock Psychology of Music. 2009;37(4):416--442.
+
+\bibitem{jordanous16cs}
+Jordanous A.
+\newblock Four PPPPerspectives on Computational Creativity in theory and in
+  practice.
+\newblock Connection Science. 2016;tbc(tbc).
+
+\bibitem{wallas26}
+Wallas G.
+\newblock The Art of Thought.
+\newblock 1st ed. London, UK: Jonathan Cape; 1926.
+
+\bibitem{goldman64}
+Goldman RJ.
+\newblock The {M}innesota Tests of Creative Thinking.
+\newblock Educational Research. 1964;7(1):3--14.
+
+\bibitem{guilford67}
+Guilford JP.
+\newblock The nature of human intelligence.
+\newblock New York, NY: McGraw-Hill; 1967.
+
+\bibitem{amabile96}
+Amabile TM.
+\newblock Creativity in context.
+\newblock Boulder, Colorado: Westview Press; 1996.
+
+\bibitem{gallie56}
+Gallie WB.
+\newblock Essentially Contested Concepts.
+\newblock Proceedings of the Aristotelian Society. 1956;56:167--198.
+\newblock Available from: \url{http://www.jstor.org/stable/4544562}.
+
+\bibitem{firth57}
+Firth JR.
+\newblock A synopsis of linguistic theory, 1930-1955.
+\newblock Studies in Linguistic Analysis. 1957;p. 1--32.
+
+\bibitem{lakoff80}
+Lakoff G, Johnson M.
+\newblock Metaphors we live by.
+\newblock Chicago, IL: University of Chicago Press; 1980.
+
+\bibitem{oakes98}
+Oakes MP.
+\newblock Statistics for Corpus Linguistics.
+\newblock Edinburgh, UK: Edinburgh University Press; 1998.
+
+\bibitem{rayson00}
+Rayson P, Garside R.
+\newblock Comparing Corpora using Frequency Profiling.
+\newblock In: Kilgarriff A, Sardinha TB, editors. Proceedings of ACL Workshop
+  on Comparing Corpora. vol.~9. ACL. Hong Kong: ACM; 2000. p. 1--6.
+
+\bibitem{kilgarriff01}
+Kilgarriff A.
+\newblock Comparing Corpora.
+\newblock International Journal of Corpus Linguistics. 2001;6(1):97--133.
+
+\bibitem{kilgarriff06}
+Kilgarriff A.
+\newblock Where to go if you would like to find out more about a word than the
+  dictionary tells you.
+\newblock Macmillan English Dictionary Magazine. 2006;Issue 35 (Jan-Feb).
+
+\bibitem{ivcevic09}
+Ivcevic Z.
+\newblock Creativity Map: Toward the Next Generation of Theories of Creativity.
+\newblock Psychology of Aesthetics, Creativity, and the Arts. 2009;3(1):17--21.
+
+\bibitem{garfield72}
+Garfield E.
+\newblock Citation analysis as a tool in journal evaluation.
+\newblock Science. 1972;178(60):471--479.
+
+\bibitem{hirsch05}
+Hirsch JE.
+\newblock An index to quantify an individual's scientific research output.
+\newblock Proceedings of the National Academy of Sciences of the United States
+  of America. 2005;102(46):16569--16572.
+
+\bibitem{briscoe06}
+Briscoe T, Carroll J, Watson R.
+\newblock The Second Release of the {RASP} System.
+\newblock In: Curran J, editor. Proceedings of the COLING/ACL 2006 Interactive
+  Presentation Sessions. ACL. Sydney, Australia: ACM; 2006. p. 77--80.
+
+\bibitem{dunning93}
+Dunning T.
+\newblock Accurate Methods for the Statistics of Surprise and Coincidence.
+\newblock Computational Linguistics. 1993;19(1):61--74.
+
+\bibitem{jordanous10a}
+Jordanous A.
+\newblock Defining Creativity: Finding Keywords for Creativity Using Corpus
+  Linguistics Techniques.
+\newblock In: Proceedings of the International Conference on Computational
+  Creativity. Lisbon, Portugal; 2010. p. 278--287.
+
+\bibitem{lin98}
+Lin D.
+\newblock An information-theoretic definition of similarity.
+\newblock In: Proceedings of the 15th International Conference on Machine
+  Learning. Madison, WI; 1998. p. 296--304.
+
+\bibitem{harris68}
+Harris Z.
+\newblock Mathematical Structures of Language.
+\newblock New York: Wiley; 1968.
+
+\bibitem{kilgarriff00}
+Kilgarriff A, Yallop C.
+\newblock What's in a thesaurus.
+\newblock In: Proceedings of the Second Conference on Language Resources and
+  Evaluation (LREC-00). Athens; 2000. p. 1371--1379.
+
+\bibitem{leech92}
+Leech G.
+\newblock 100 million words of {English}: the {British National Corpus (BNC)}.
+\newblock Language Research. 1992;28(1):1--13.
+
+\bibitem{weeds03}
+Weeds JE.
+\newblock Measures and Applications of Lexical Distributional Similarity [PhD
+  thesis].
+\newblock Informatics, University of Sussex. Brighton, UK; 2003.
+
+\bibitem{mannschu99}
+Manning C, Sch{\"u}tze H.
+\newblock Foundations of Statistical Natural Language Processing.
+\newblock Cambridge, MA: MIT Press; 1999.
+
+\bibitem{weedsweir03}
+Weeds J, Weir D.
+\newblock Finding and evaluating nearest neighbours.
+\newblock In: Archer D, Rayson P, Wilson A, McEnery T, editors. Proceedings of
+  the 2nd International Conference of Corpus Linguistics. Lancaster, UK: UCREL;
+  2003. p. 879--888.
+
+\bibitem{mccanavi09}
+McCarthy D, Navigli R.
+\newblock The {English} lexical substitution task.
+\newblock Language Resources and Evaluation: Special Issue on Computational
+  Semantic Analysis of Language. 2009;43(3):139--159.
+
+\bibitem{biemann06}
+Biemann C.
+\newblock Chinese {Whispers}: an efficient graph clustering algorithm and its
+  application to natural language processing problems.
+\newblock In: Proceedings of TextGraphs: the First Workshop on Graph Based
+  Methods for Natural Language Processing. Morristown, NJ: Association for
+  Computational Linguistics; 2006. p. 73--80.
+
+\bibitem{mackinnon70}
+MacKinnon DW.
+\newblock Creativity: a Multi-Faceted Phenomenon.
+\newblock In: Roslansky JD, editor. Creativity: A Discussion at the Nobel
+  Conference. Amsterdam, The Netherlands: North-Holland Publishing Company;
+  1970. p. 17--32.
+
+\bibitem{jordanous12jims}
+Jordanous A, Keller B.
+\newblock What makes musical improvisation creative?
+\newblock Journal of Interdisciplinary Music Studies. 2012;6:151--175.
+
+\bibitem{fellbaum98}
+Fellbaum C, editor.
+\newblock WordNet: An electronic lexical database.
+\newblock Cambridge, MA: The MIT press; 1998.
+
+\bibitem{miller08}
+Miller P, Styles R, Heath T.
+\newblock Open data commons, a license for open data.
+\newblock In: Bizer C, Heath T, Idehen K, Berners-Lee T, editors. Proceedings
+  of the WWW2008 Workshop on Linked Data on the Web. vol. 369 of CEUR-WS.
+  Beijing, China: CEUR; 2008. p.~8.
+
+\bibitem{jordanous12cc}
+Jordanous A.
+\newblock A Standardised Procedure for Evaluating Creative Systems:
+  Computational Creativity Evaluation Based on What it is to be Creative.
+\newblock Cognitive Computation. 2012;4(3):246--279.
+
+\bibitem{jordanousphd}
+Jordanous A.
+\newblock Evaluating Computational Creativity: A Standardised Procedure for
+  Evaluating Creative Systems and its Application [PhD thesis].
+\newblock University of Sussex. Brighton, UK; 2012.
+
+\bibitem{jordanous16aisb}
+Jordanous A.
+\newblock The longer term value of creativity judgements in computational
+  creativity.
+\newblock In: al~Rifaie MM, McGregor S, editors. {AISB} Symposium on
+  Computational Creativity (CC2016). Sheffield, UK: AISB; 2016. p. 16--23.
+
+\bibitem{boden99}
+Boden MA.
+\newblock Introduction [summary of {B}oden's keynote address to {AISB}'99].
+\newblock In: AISB Quarterly - Special issue on AISB99: Creativity in the arts
+  and sciences. vol. 102; 1999. p.~11.
+
+\bibitem{jordanous15vem}
+Jordanous A, Allington D, Dueck B.
+\newblock Measuring cultural value using social network analysis: a case study
+  on valuing electronic musicians.
+\newblock In: Proceedings of the Sixth International Conference on
+  Computational Creativity June; 2015. p. 110.
+
+\bibitem{panglee08}
+Pang B, Lee L.
+\newblock Opinion mining and sentiment analysis.
+\newblock Foundation and Trends in Information Retrieval. 2008;2(1-2):1--135.
+
+\end{thebibliography}
+
+%\bibliography{references}
 

### 2016-09-07 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
footnotes removed
Footnotes removed and footnote text incorporated into main text, as
required by PLOS-ONE.

@@
 More problematic still, dictionary entries are often self-referential or circular,  defining creativity in terms of ``being creative'' or ``creative ability''.
-To illustrate these limitations, there follow several typical dictionary definitions of creativity and the related words creative and create:\footnote{For readability, some definitions are edited slightly to standardise formats and remove etymological/grammatical annotations.}
+To illustrate these limitations, there follow several typical dictionary definitions of creativity and the related words `creative' and `create'.
+For readability, some definitions are edited slightly to standardise formats and remove etymological/grammatical annotations:
 \begin{quotation}
@@
 The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers.
-This literature search was supplemented with additional influential papers which may not have appeared in a Scopus search; for example, a computer science conference paper on cognitive models of creativity.\footnote{It should be noted that in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.} The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.
+This literature search was supplemented with additional influential papers which may not have appeared in a Scopus search.
+For example, a Computer Science conference paper on cognitive models of creativity has been included, as in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.
+The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.
 
@@
 As a further refinement, each lemma was also mapped to lower case to ensure that capitalised word forms (e.g.
-{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).\footnote{While this can result in confusion between proper names and common nouns (e.g.
+{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).
+While this has the potential for occasional confusion between proper names and common nouns (e.g.
 {\em Apple\/} v.
-{\em apple\/}), it is not considered that the resulting level of 'noise'  in the data is likely to adversely affect the results of the analysis.}
+{\em apple\/}), it is not considered that the resulting level of `noise'  in the data is likely to adversely affect the results of the analysis.
 
@@
 Grammatical relations were obtained from an analysis of the written portion of the British National Corpus \cite{leech92}, which had previously been processed using the RASP toolkit \cite{briscoe06} in order to extract them.
-Using this data, each word in the creativity corpus was associated with a list of all of the grammatical relations with which it occurred, together with their corresponding counts of occurrence.\footnote{Not all of the grammatical relation information output by RASP was used to calculate distributional similarity.
-In practice, just the subject, object and modifier relation types are used as these tend to give the best results \cite{weeds03}.} A potential difficulty with obtaining word similarity data based on the BNC (i.e.
+Using this data, each word in the creativity corpus was associated with a list of grammatical relations in which it occurred, together with corresponding counts of occurrence.
+In practice, not all of the grammatical relation information output by RASP was used to calculate distributional similarity.
+Just the subject, object and modifier relation types are used as these tend to give the best results \cite{weeds03}.
+A potential difficulty with obtaining word similarity data based on the BNC (i.e.
 using data from sources of everyday usage of English, rather than from more specialist sources) would arise if the majority of the creativity words were used with distinctive or technical senses within the creativity corpus.
@@
 the twenty  words with the highest log likelihood scores) were selected.
-Each word was then visualised as the root node of its own individual subgraph using the graph drawing software {\em GraphViz}\footnote{$http://www.graphviz.org/$, last accessed August 2016}.
+Each word was then visualised as the root node of its own individual subgraph using the graph drawing software {\em GraphViz} (http://www.graphviz.org/, last accessed August 2016).
 In order to reduce the amount of data to be examined, similarity scores were discarded if they fell below a threshold value (adjusted manually for each graph to highlight the most strongly connected words).
@@
 
-In particular, the components are linked to the data in WordNet \cite{fellbaum98}, a large lexical database of English that has recently been made available as a Semantic Web ontology \footnote{$http://wordnet.rkbexplorer.com/$, last accessed August 2016}.
+In particular, the components are linked to the data in WordNet \cite{fellbaum98}, a large lexical database of English that has recently been made available as a Semantic Web ontology (http://wordnet.rkbexplorer.com/, last accessed August 2016).
 In WordNet, words are grouped by sense and interlinked by lexical and conceptual relations.

### 2016-09-07 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
citations
All citations changed so that only numbers appear in square brackets,
no text or page numbers. Have tried to preserve page numbers by putting
in round brackets after the citations. For e.g. ‘[34] (p.72)’ Not
great, but not sure how else to do that! Other text preserved more
easily: e.g. ‘(for examples see [27,34])’ etc.

@@
 \begin{quote}`The philosophy, science and engineering of computational systems which, by taking on particular responsibilities, exhibit behaviours that unbiased observers would deem to be creative.' 
-\cite[p. 21]{coltonwiggins12}
+\cite{coltonwiggins12} (p. 21).
 \end{quote}
@@
 Computational creativity research follows both theoretical and practical directions and crosses several disciplinary boundaries between the arts, sciences, and engineering.
-Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling \cite[provide examples]{colton08,widmerAIM09,leon10MM,perezyperez99}.
+Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling (for examples, see \cite{colton08,widmerAIM09,leon10MM,perezyperez99}).
 
@@
 \begin{quote}
-`[c]reativity defies precise definition ... even if we had a precise conception of creativity, I am certain we would have difficulty putting it into words' \cite[p. 43]{torrance88}. 
+`[c]reativity defies precise definition ... even if we had a precise conception of creativity, I am certain we would have difficulty putting it into words' \cite{torrance88} (p.43). 
 \end{quote}
@@
 `Even if this mysterious phenomenon can be isolated, quantified, and dissected, why bother? Wouldn't it make more sense to revel in the mystery and wonder of it all?' 
-\cite[p. 570]{hennessey10}
+\cite{hennessey10} (p.570).
 \end{quote}
@@
 \item discuss how the definition they are using is similar to or different from other definitions, and
-\item address the question of creativity for whom and in what context.' \cite[p.92]{plucker04defn}
+\item address the question of creativity for whom and in what context.' \cite{plucker04defn} (p.92).
 \end{enumerate}
@@
 A more objective and well-articulated account of how creativity is manifested enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.
-Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite[p.
-15]{vartanian14}, based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.
+Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite{vartanian14} (p.15), based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.
 
@@
  `creativity is that process which results in a novel work that is accepted as tenable or useful or satisfying by a group at some point in time' %By this definition we limit ourselves to the study of individuals who are regarded as creative by ``significant others'' in their environment.'
-\cite[p. 218]{stein63}
+\cite{stein63} (p.28)
 \end{quote}
@@
 `Creativity is the ability to produce work that is both novel (i.e., original, unexpected) and appropriate (i.e., useful, adaptive concerning task constraints)'
-\cite[p. 3]{sternberg99a}
+\cite{sternberg99a}(p.3)
 \end{quote}
@@
 `Creativity is the ability to come up with ideas or artefacts that are {\em new}, {\em surprising and valuable}'
-\cite[p. 1]{boden04}
+\cite{boden04}(p.1)
 \end{quote}
@@
 `Creativity is the interaction among \emph{aptitude, process, and environment} by which an individual or group produces a \emph{perceptible product} that is both \emph{novel and useful} as defined within a \emph{social context}'
-\cite[p. 90]{plucker04defn}
+\cite{plucker04defn}(p.90)
 \end{quote}
@@
 `Creativity: the generation of products or ideas that are both novel and appropriate' 
-\cite[p. 570]{hennessey10}
+\cite{hennessey10}(p.570)
 \end{quote}
@@
 Mental activity (or mental process) is implicit in this definition, and of course no one could conceive of a person living or operating in a vacuum, so the term \emph{press} is also implicit'
-\cite[p. 305]{rhodes61}
+\cite{rhodes61}(p.305)
 \end{quote}
@@
 For example, psychometric tests for creativity such as \cite{guilford50,torrance74} focus on {\em problem solving} and {\em divergent thinking} as key attributes of a creative person.
-In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} has historially placed emphasis on the {\em novelty} and {\em value} of creative products.
+In contrast, computational creativity research (for examples see \cite{pease01,wiggins06ngc,peinado06ngc,ritchie07}) has historially placed emphasis on the {\em novelty} and {\em value} of creative products.
 Whilst there is some consensus across academic fields, for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99}, the differing emphases contribute to variations in the interpretation of creativity.
@@
 To resolve the conflict, an inclusive, all-encompassing view of creativity should adopt the wider perspective and incorporate the narrower perspective.
-For example rather than focussing narrowly on creative {\em genius}, through the study of people with exceptional creative achievements \cite[for example]{poincare29,hadamard45} emphasis has shifted to encompass the broader study of {\em everyday} creativity, with genius as a special case: the notion that everyone can be creative to some degree \cite{weisberg88,bryankinns09}.
+For example rather than focussing narrowly on creative {\em genius}, through the study of people with exceptional creative achievements (see \cite{poincare29,hadamard45}) emphasis has shifted to encompass the broader study of {\em everyday} creativity, with genius as a special case: the notion that everyone can be creative to some degree \cite{weisberg88,bryankinns09}.
 
@@
 
-Creativity can be seen as an essentially contested concept \cite{gallie56}: it is subjective, abstract and can be interpreted in a variety of acceptable ways, such that a fixed `proper general use' is elusive \cite[p.
-167]{gallie56}.
+Creativity can be seen as an essentially contested concept \cite{gallie56}: it is subjective, abstract and can be interpreted in a variety of acceptable ways, such that a fixed `proper general use' is elusive \cite{gallie56} (p.167).
 Gallie \cite{gallie56} defines an essentially contested concept through several features: being internally complex in nature, but amenable to being broken down into identifiable constituent elements of varying relative importance, and dependent on a number of factors such as context and individual preference.
@@
 There is not a single agreed instantiation, but instead many reasonable possibilities, influenced by changing circumstances and contexts.
-It is more productive to acknowledge that these different interpretations exist and refer to `the respective contributions of its various parts or features' \cite[p.
-172]{gallie56}, rather than to argue for a single interpretation.
+It is more productive to acknowledge that these different interpretations exist and refer to `the respective contributions of its various parts or features' \cite{gallie56} (p.172), rather than to argue for a single interpretation.
 Thus, different types of creativity manifest themselves in different ways while sharing certain characteristics (not necessarily the same across all creative instances).
@@
 And I shall say: ``games'' form a family.'
-\cite[Part 1, Paragraphs 66-67]{wittgenstein58}
+\cite{wittgenstein58} (Part 1, Paragraphs 66-67).
 \end{quote}
@@
 
-Wittgenstein \cite{wittgenstein58} has argued that `a clear view of the aim and functioning of the words' helps us `dispers[e] the fog' that obscures a clear vision of the `working of language' \cite[Part 1, Paragraph 5]{wittgenstein58}.
+Wittgenstein \cite{wittgenstein58} has argued that `a clear view of the aim and functioning of the words' helps us `dispers[e] the fog' that obscures a clear vision of the `working of language' \cite{wittgenstein58} (Part 1, Paragraph 5).
 To understand the use of a word, one must have background information and context.
-Wittgenstein gives the example of a chess piece, which is introduced to someone as a `king' \cite[paragraph 31]{wittgenstein58}: to understand this usage the person must already know the rules of chess, or must at least know what it means to have a piece in a game.
+Wittgenstein gives the example of a chess piece, which is introduced to someone as a `king' (Paragraph 31): to understand this usage the person must already know the rules of chess, or must at least know what it means to have a piece in a game.
 To Wittgenstein, the semantics of words and statements are determined by how we use them, grounded in rules set by our habitual use of a word and our shared consensual practices, rather than being fixed by static, pre-assigned meanings.
@@
 Distributional similarity of two words is measured in terms of the similarity of their associated lists of grammatical relations.
-A variety of different methods for calculating distributional similarity have been investigated in the literature, including standard techniques such as the cosine measure \cite[for example]{mannschu99}.
+A variety of different methods for calculating distributional similarity have been investigated in the literature, including standard techniques such as the cosine measure (for example \cite{mannschu99}).
 The present work adopts an information-theoretic measure due to Lin \cite{lin98}, which has been widely used in language processing applications as a means of automatically discovering semantic relationships between words.

### 2016-09-12 plosOneJordanousKeller/PAPER/S1_appendix.tex
changes to image and appendices

--- 2016-09-07 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
@@
-% Template for PLoS
-% Version 3.1 February 2015
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
-% the final text of your manuscript.
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig." instead of "Figure".
-% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout or alignment
-% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
-% - colors, shading, or graphic objects
-% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
-%
-% Please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
 \documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% fixltx2e package for \textsubscript
-\usepackage{fixltx2e}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-%\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-\usepackage{rotating}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-
-% Use strikethrough for track changes 
-\usepackage[normalem]{ulem}
-% command is \sout{text text text etc}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
-
 \begin{document}
-\vspace*{0.35in}
-
-% Title must be 250 characters or less.
-% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
-\begin{flushleft}
-{\Large
-\textbf\newline{Modelling Creativity: Identifying Key Components through a Corpus-Based Approach}
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Anna Jordanous\textsuperscript{1,\Yinyang, *},
-Bill Keller\textsuperscript{2,\Yinyang}
-\\
-\bigskip
-\bf{1} School of Computing, University of Kent, Chatham Maritime, Kent, UK
-\\
-\bf{2} Department of Informatics, University of Sussex, Falmer, Brighton, UK
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-%\textcurrency a Insert current address of first author with an address update
-% \textcurrency b Insert current address of second author with an address update
-% \textcurrency c Insert current address of third author with an address update
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* a.k.jordanous@kent.ac.uk / billk@sussex.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-
-Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
-If we wish to study creativity scientifically, then a tractable and well-articulated model of creativity is required.
-Such a model would be of great value to researchers investigating the nature of creativity and in particular, those concerned with the evaluation of creative practice.
-This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people use to describe the concept.
-Using techniques from the field of statistical natural language processing, we identify a collection of fourteen key components of creativity through an analysis of a corpus of academic papers on the topic.
-Words are identified which appear significantly often in connection with discussions of the concept.
-Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerge, which collectively contribute to a comprehensive and multi-perspective model of creativity.
-The components provide an ontology of creativity: a set of building blocks which can be used to model creative practice in a variety of domains.
-The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating achievements of this work and directions for further research.
-
-\linenumbers
-
-\section*{Introduction}\label{intro}
-
-%Currently, most content on the Semantic Web is in the form of ontologies of `things': semantically structured collections of factual or objective data on topics as diverse as people \cite{foaf}, places \cite{geonames}, music \cite{musicOntology} or manuscripts \cite{sawsOntology}.
-The focus in Semantic Web research has generally been on reducing ambiguity in representations of these more structured domains and concepts, rather than directly tackling the representation and machine-readable representation of subjective, unstructured concepts in an ontology.
-However, cognitive science research and work on lexical resources such as WordNet \cite[$http://wordnet.rkbexplorer.com$]{fellbaum98} have laid foundations for more definitionally troublesome concepts to be considered in detail.
-The time is ripe for developing ontologies of subjective concepts such as creativity.
-
-What is creativity, and how can we better understand and learn about creativity using computational modelling?
-Computational creativity is a relatively youthful research area that has been growing with significant pace in recent years.
-Computational creativity is:
-\begin{quote}`The philosophy, science and engineering of computational systems which, by taking on particular responsibilities, exhibit behaviours that unbiased observers would deem to be creative.' 
-\cite[p. 21]{coltonwiggins12}
-\end{quote}
-
-Computational creativity research follows both theoretical and practical directions and crosses several disciplinary boundaries between the arts, sciences, and engineering.
-Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling \cite[provide examples]{colton08,widmerAIM09,leon10MM,perezyperez99}.
-
-The evaluation of creative systems developed by researchers in the field of computational creativity has proven non-trivial.
-Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}.
-Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about `creativity' and what does it constitute?
-
-Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
-There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in \nameref{S1_Appendix}).
-In the academic literature on creativity, many common themes have emerged. 
-However, multiple viewpoints exist, prioritising different aspects of the concept according to what are traditionally considered to be the primary factors for a particular discipline. 
-The need for a more over-arching, inclusive, multi-dimensional account of creativity has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}.
-Such a meta-level account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
-
-There are many challenges to modelling a concept like creativity in a computational setting.
-Conceptually, creativity seems inherently fuzzy or vague, with a meaning that shifts depending on the domain of application.
-Tackling these challenges affords two key advantages, both of which motivate the current paper.
-First, we can take advantage of computing and artificial intelligence to perform or enhance creative activities using computational power and research expertise.
-Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept.
-
-The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components, representing key dimensions, that are recognised across a combination of different viewpoints.
-We present a novel, empirical approach to the problem of modelling how creative behaviour is manifested, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
-Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}.
-The current work is intended as a significant, methodological contribution towards addressing the Grand Challenge of evaluation in computational creativity research.
-It should provide researchers with a firm foundation for evaluating exactly how creative so-called {\emph creative systems} actually are.
-
-On our approach, statistical language processing techniques are used to identify words significantly associated with creativity in a corpus of academic papers on the subject.
-A corpus spanning some 60 years of research into the nature of creativity was collected together.
-The papers were gathered from a wide variety of disciplines including psychology, educational testing and computational creativity, amongst others.
-The language data drawn from this collection was then analysed and contrasted with data from a corpus of matched papers on subjects unrelated to creativity.
-From this analysis, a set of 694 {\em creativity words\/} was identified, where each creativity word appeared significantly more often than expected in the corpus of creativity papers.
-A measure of lexical similarity provided a basis for clustering the creativity words into groups of words with similar or shared aspects of meaning.
-Through inspection of these clusters, a total of fourteen {\em key components of creativity\/} was identified, where each represents a key theme or attribute of creativity.
-The set of components yields information about the nature of creativity, based on what is collectively emphasised in discussions about the concept.
-
-% The Semantic Web has emerged as a way to address the troublesome but important issue \cite{boden99} of articulating values, concepts and information using an open and  {\em machine-understandable} vocabulary.
-Encoding the creativity components in an OWL ontology has enabled this {\em ontology of creativity} to be made publicly available to the wider research community as a resource in the Semantic Web, under the permanent URL:
-%\begin{quote}
-%{\small \texttt{http://purl.org/creativity/ontology}}
-%\end{quote}
-
-In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is considered.
-%, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
-In the remaining sections, details are provided of the methodology used to identify components of creativity from an analysis of language data.
-The results of this analysis are then presented in terms of a model that encompasses fourteen key components.
-The derived set of components is evaluated in terms of how well it satisfies the need for a shared, inclusive and comprehensive account of creativity and provides a vocabulary of creativity that is accessible to both people and machines.
-Finally, conclusions are drawn and some directions for further work are outlined.
-
-\subsection*{Background:  The nature of creativity} \label{background}
-
-As Torrance observes:
-
-\begin{quote}
-`[c]reativity defies precise definition ... even if we had a precise conception of creativity, I am certain we would have difficulty putting it into words' \cite[p. 43]{torrance88}. 
-\end{quote}
-
-Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. 
-In their review of research into human creativity, Hennessey and Amabile ask a significant follow-on question: 
-\begin{quote}
-`Even if this mysterious phenomenon can be isolated, quantified, and dissected, why bother? Wouldn't it make more sense to revel in the mystery and wonder of it all?' 
-\cite[p. 570]{hennessey10}
-\end{quote}
-
-\noindent Two answers to this question are offered by Hennessey and Amabile, both of which are identified as desirable: to gain a deeper understanding of creativity and to learn how to boost people's creativity.
-
-Creativity can and should be studied and measured scientifically, but the lack of a commonly-agreed understanding causes problems for measurement \cite{kaufman09}.
-Plucker et al.
-make recommendations about best practice based on their own survey of the creativity literature:
-\begin{quote}
-\noindent
-`we argue that creativity researchers must
-
-\begin{enumerate}
-\renewcommand{\labelenumi}{(\alph{enumi})}
-\item explicitly define what they mean by creativity,
-\item avoid using scores of creativity measures as the sole definition of creativity (e.g., creativity is what creativity tests measure and creativity tests measure creativity, therefore we will use a score on a creativity test as our outcome variable),
-\item discuss how the definition they are using is similar to or different from other definitions, and
-\item address the question of creativity for whom and in what context.' \cite[p.92]{plucker04defn}
-\end{enumerate}
-\end{quote}
-
-\noindent In short, we need to specify and justify the standards that we use to judge creativity.
-A more objective and well-articulated account of how creativity is manifested enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.
-Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite[p.
-15]{vartanian14}, based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.
-
-\paragraph{Definitions of creativity.}
-\label{existing_defs}
-
-To find out the meaning of a word, a natural first step might be to consult a dictionary.
-Dictionary definitions of creativity provide a brief introduction to  the meaning of the word.
-However, for the purposes of research, the utility of such definitions is severely restricted by their format and brevity, and they generally provide only cursory, shallow insights into the nature of creativity.
-More problematic still, dictionary entries are often self-referential or circular,  defining creativity in terms of ``being creative'' or ``creative ability''.
-To illustrate these limitations, there follow several typical dictionary definitions of creativity and the related words `creative' and `create'.
-For readability, some definitions are edited slightly to standardise formats and remove etymological/grammatical annotations:
-\begin{quotation}
-\begin{description}
-\item {\em Oxford English Dictionary} 2nd ed. (1989) pp. 1134-5:
-	\begin{enumerate}
-	\item[creativity:] creative power or faculty; ability to create
-	\item [creative:] Having the quality of creating, able to create; of or relating to creation; originative.
-b.
-Inventive, imaginative; of, relating to, displaying, using, or involving imagination or original ideas as well as routine skill or intellect, esp.
-in literature or art.
-c.
-Esp.
-of a financial or other strategy: ingenious, esp.
-in a misleading way.
-2.
-Providing the cause or occasion of, productive of.
-\item [create:] 1.a.
-Said of the divine agent: To bring into being, cause to exist; esp.
-to produce where nothing was before, 'to form out of nothing'.
-b.
-with complemental extension.
-2.
-To make, form, constitute, or bring into legal existence (an institution, condition, action, mental product, or form, not existing before).
-Sometimes of material works.
-3.
-To constitute (a personage of rank or dignity); to invest with rank, title, etc.
-4.
-To cause, occasion, produce, give rise to (a condition or set of circumstances).
-	\end{enumerate}
-\item {\em The Penguin English Dictionary} 2nd ed. (1969) p. 174:
-	\begin{enumerate}
-	\item[creativity:] creative power or faculty; ability to create
-	\item[creative:] having power to create; related to process of creation; constructive, original, producing an essentially new product; produced by original intellectual or artistic effort 
-	\item [create:] make out of nothing, bestow existence on; cause, bring about; produce or make something new or original; confer new rank etc on; (theat) be the first to act (a certain part); make a fuss
-	\end{enumerate}
-\item {\em Webster's 3rd New International Dictionary} (1961) p. 532:
-	\begin{enumerate}
-	\item[creativity:] the quality of being creative; ability to create 
-	\item[creative:] 1.
-having the power or quality of creating; given to creation 2: PRODUCTIVE - used with 3: having the quality of something created rather than imitated or assembled; expressive of the maker; IMAGINATIVE
-	\item[create:] 1: to bring into existence; make out of nothing and for the first time 2: to cause to be or to produce by fiat or by mental, moral, or legal action 3: to cause or occasion - used of natural or physical causes and esp.
-of social and evolutionary or emergent forces 4a: to produce (as a work of art or of dramatic interpretation) along new or unconventional lines) b: to design (as a costume or dress)
-	\end{enumerate}
-\end{description}
-\end{quotation}
-
-Given the problems inherent in dictionary definitions of creativity, it is not surprising that a number of creativity researchers have set out  to provide their own definitions of the concept.
-Some examples are:
-
-\begin{quotation}
-\begin{quote}
- `creativity is that process which results in a novel work that is accepted as tenable or useful or satisfying by a group at some point in time' %By this definition we limit ourselves to the study of individuals who are regarded as creative by ``significant others'' in their environment.'
-\cite[p. 218]{stein63}
-\end{quote}
-%\begin{quote}
-%`A product or response will be judged as creative to the extent that (a) it is both a novel and appropriate, useful, correct or valuable response to the task at hand, and (b) the task is heuristic rather than algorithmic.'
-%\cite[p. 35]{amabile96}
-%\end{quote}
-\begin{quote}
-`Creativity is the ability to produce work that is both novel (i.e., original, unexpected) and appropriate (i.e., useful, adaptive concerning task constraints)'
-\cite[p. 3]{sternberg99a}
-\end{quote}
-\begin{quote}
-`Creativity is the ability to come up with ideas or artefacts that are {\em new}, {\em surprising and valuable}'
-\cite[p. 1]{boden04}
-\end{quote}
-\begin{quote}
-`Creativity is the interaction among \emph{aptitude, process, and environment} by which an individual or group produces a \emph{perceptible product} that is both \emph{novel and useful} as defined within a \emph{social context}'
-\cite[p. 90]{plucker04defn}
-\end{quote}
-\begin{quote}
-`Creativity: the generation of products or ideas that are both novel and appropriate' 
-\cite[p. 570]{hennessey10}
-\end{quote}
-\begin{quote}
-`The word creativity is a noun naming the phenomenon in which a person communicates a new concept (which is the product).
-Mental activity (or mental process) is implicit in this definition, and of course no one could conceive of a person living or operating in a vacuum, so the term \emph{press} is also implicit'
-\cite[p. 305]{rhodes61}
-\end{quote}
-\end{quotation}
-
-These more research-oriented definitions avoid the problems of self-reference and circularity noted for the dictionary entries given previously.
-However, whilst the definitions may provide somewhat deeper insight into the nature of creativity, the brevity of the definitions means that they still only succeed in providing shallow, summary accounts of the concept.
-
-\paragraph{A multitude of different perspectives} \label{perspectives}
-
-The problem of identifying and quantifying creativity exists across many disciplines.
-How creative is this person?
-Does this person have the creative abilities to boost my business?
-Is this pupil's story creative?
-Is this computational system an example of computational creativity?
-As a consequence, when attempts are made to define creativity, it is often from the perspective of a particular domain or research discipline.
-For example, psychometric tests for creativity such as \cite{guilford50,torrance74} focus on {\em problem solving} and {\em divergent thinking} as key attributes of a creative person.
-In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} has historially placed emphasis on the {\em novelty} and {\em value} of creative products.
-Whilst there is some consensus across academic fields, for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99}, the differing emphases contribute to variations in the interpretation of creativity.
-These variations affect consistency across creativity research in different disciplines and potentially hinder interdisciplinary collaborations and cross-application of findings.
-
-Several competing interpretations of creativity exist in the literature.
-Sometimes these differences of opinion do not need to be directly resolved but can be included alongside each other.
-Examples include whether creativity is centred around mental processes \cite{boden04,dietrich10,gabora12} or embodied and situated in an interactive environment \cite{mccormack07,sosa09}.
-Another example is whether creativity is domain-independent \cite{plucker98}, or dependent on domain-specific context \cite{baer98}, or (as both Plucker and Baer have concluded) a combination of both \cite{plucker04,baer10}.
-
-Other conflicts arise where a previously narrow view of creativity has been widened in perspective.
-To resolve the conflict, an inclusive, all-encompassing view of creativity should adopt the wider perspective and incorporate the narrower perspective.
-For example rather than focussing narrowly on creative {\em genius}, through the study of people with exceptional creative achievements \cite[for example]{poincare29,hadamard45} emphasis has shifted to encompass the broader study of {\em everyday} creativity, with genius as a special case: the notion that everyone can be creative to some degree \cite{weisberg88,bryankinns09}.
-
-Similarly, researchers distinguish between {\em little-c} and {\em Big-C} creativity, or {\em psychological/P-creativity} and  {\em historical/H-creativity} \cite{boden04}, adjusting their focus accordingly to make their research more manageable.
-This is particularly the case in computational creativity, where endowing the computer with elements of general, human knowledge and experience is a major challenge.
-Little-c creative or p-creative work is perceived as creative by the creator personally but may replicate existing work (unknown to the creator) so is not necessarily creative in a wider social context.
-This encompasses the concept of Big-C creativity or h-creativity, where the work makes a creative contribution both to the creator and to society.
-To be Big-C creative/h-creative is to be little-c creative/p-creative in a way which has not been done before by anyone.
-
-The preceeding discussion indicates that creativity is a complex, multi-faceted concept that requires a broad and inclusive treatment.
-The {\em Four Ps} framework \cite{rhodes61,stein63,mooney63,odena09,jordanous16cs} ensures we pay attention to four key aspects of creativity:
-
-\begin{description}
-\setlength{\labelwidth}{1.5cm}
-\setlength{\itemindent}{1.5cm}
-\item[Person/Producer:] The individual that is creative
-\item[Process:] What the creative individual does to be creative
-\item[Product:] What is produced as a result of the creative process
-\item[Press:] The environment in which creative activity takes place
-\end{description}
-
-\noindent This framework presents creativity in a broader context, making our understanding of the concept more generally applicable and less specific to a domain or academic discipline.
-In contrast, models of the creative process \cite{wallas26,poincare29,hadamard45}, tests of people's creativity \cite{goldman64,guilford67,torrance74} or tests based on creative artefact generation \cite{amabile96,ritchie07} are useful only within a limited sphere.
-Jordanous \cite{jordanous16cs} has contextualised the Four Ps in a computational context, referring to the creative Producer (person or computational agent) carrying out Processes within the environmental context of a Press, to create computational Products.
-
-\subsection*{The challenges of modelling creativity} \label{cogPhil}
-
-% Was Reflections on the semantics of subjective concepts. Merge this together and make it more relevant to modelling creativity (specifically) rather than the general treatment it is now.
-
-Creativity can be seen as an essentially contested concept \cite{gallie56}: it is subjective, abstract and can be interpreted in a variety of acceptable ways, such that a fixed `proper general use' is elusive \cite[p.
-167]{gallie56}.
-Gallie \cite{gallie56} defines an essentially contested concept through several features: being internally complex in nature, but amenable to being broken down into identifiable constituent elements of varying relative importance, and dependent on a number of factors such as context and individual preference.
-Although there may be consensus on the meaning of such concepts in very general terms, they may defy precise interpretation.
-There is not a single agreed instantiation, but instead many reasonable possibilities, influenced by changing circumstances and contexts.
-It is more productive to acknowledge that these different interpretations exist and refer to `the respective contributions of its various parts or features' \cite[p.
-172]{gallie56}, rather than to argue for a single interpretation.
-Thus, different types of creativity manifest themselves in different ways while sharing certain characteristics (not necessarily the same across all creative instances).
-This is what Wittgenstein refers to as `family resemblances' \cite{wittgenstein58}:
-
-\begin{quote}
-[On discussing the example of what a `game' is] `we see a complicated network of similarities overlapping and criss-crossing: sometimes overall similarities, sometimes similarities of detail.
-...
-I can think of no better expression to characterize these similarities than ``family resemblances''; for the various resemblances between members of a family: build, features, colour of eyes, gait, temperament, etc.
-etc.
-overlap and criss-cross in the same way.
-And I shall say: ``games'' form a family.'
-\cite[Part 1, Paragraphs 66-67]{wittgenstein58}
-\end{quote}
-
-Similarly, with creativity, different manifestations of creativity are not all necessarily required to share the same common, core elements in order to be identified as part of the creativity `family'.
-Rather, relationships between different manifestations reveal various shared characteristics that emerge in a similar way to Wittgenstein's `family resemblances' in language.
-We need to identify what those family resemblances are in the case of creativity.
-To understand creativity, we can investigate what resemblances exist across different instantiations of the concept.
-
-Wittgenstein \cite{wittgenstein58} has argued that `a clear view of the aim and functioning of the words' helps us `dispers[e] the fog' that obscures a clear vision of the `working of language' \cite[Part 1, Paragraph 5]{wittgenstein58}.
-To understand the use of a word, one must have background information and context.
-Wittgenstein gives the example of a chess piece, which is introduced to someone as a `king' \cite[paragraph 31]{wittgenstein58}: to understand this usage the person must already know the rules of chess, or must at least know what it means to have a piece in a game.
-To Wittgenstein, the semantics of words and statements are determined by how we use them, grounded in rules set by our habitual use of a word and our shared consensual practices, rather than being fixed by static, pre-assigned meanings.
-
-%Waismann, a contemporary of Wittgenstein, has reflected on the impact of `open texture' on language, where certain words or phrases simply cannot be completely defined for all possible scenarios:
-
-%\begin{quote}
-%`Every description stretches, as it were, into a horizon of open possibilities: however far I go, I shall always carry this horizon with me.'
-%\cite[p. 122]{waismann68}
-%\end{quote}
-Linguistics research advocates that the meaning of a word is dependent on the context it is used in \cite{firth57}.
-In particular, Lakoff has argued that the study of language helps reveal how people think \cite{lakoff87,lakoff80}.
-Words used frequently in discussions of the nature of a concept provide the context for the commonly understood meaning of that concept, as has been shown in various corpus linguistics contributions \cite{oakes98,rayson00,kilgarriff01,kilgarriff06}.
-
-%We acknowledge that semantic ambiguity is unlikely to be resolved to a single agreed definition.
-Meanings can be dynamic, evolving over time and contextually dependent, rather than being fixed, with a static and unchanging prescribed definition.
-The key principle emerging across these present discussions is that the meaning of words like creativity can be modelled by identifying different aspects that collectively contribute to the meaning of the concept of creativity.
-
-%\subsection*{Subjectivity and ambiguity on the semantic web} \label{SWsubjectivity}
-
-%Ambiguity in semantic interpretation of terms is not an area that Semantic Web research shies away from.
-Ontologies are widely used to pinpoint and define what {\em things} mean in a machine-readable way, for greater clarity and precision in using various vocabularies and identifiers.
-Such research does not concentrate merely on those areas of interest which are simple to define and objectively clear to interpret; for example SKOS \cite{skos} provides vocabulary to organise and taxonomise knowledge, whether explicit or tacit, while FRBR-oo \cite{doerr07} defines various terms to do with bibliographical records and the works and ideas expressed within them, on various conceptual levels beyond merely the physical instantiation of a book or other written document.
-Upper ontologies such as Dolce \cite{gangemi02}, SUMO \cite{niles01} and Cyc \cite{reed02} have guided the objective, disambiguated expression of higher-level, cross-domain, general concepts and abstract knowledge.% An upper ontology defines higher-level vocabularies and concepts necessary to implement ontologies themselves, providing the meta-vocabulary to link specific ontologies to more general concepts.
-
-%What is not often tackled within Semantic Web research are the types of topic discussed above, where ambiguity is unlikely to be resolved to a single agreed definition and meanings are dynamic, changing over time and contextual interpretations, rather than being fixed to a static and unchanging prescribed definition.
-To date, there is a lack of suitable methodologies applied in Semantic Web research to enable or assist the building of ontological representations of such topics.
-Existing ontology construction methodologies tend to concentrate on how to extract and represent data objectively rather than retain subjectivity in the data \cite{fernandez97,noy01,haase08}; the focus is on how best to construct ontologies in an appropriate manner rather than how to tackle {\em moving-target} issues of dynamic, perhaps unresolvable, semantics.
-
-%There is of course much work still to be done in representing semantics on the Semantic Web; much information with fixed semantics is still to be represented in a machine readable form.
-With the growth of the Semantic Web, this ongoing collation and representation of knowledge is work-in-progress.
-As discussed above, advances in other research disciplines can assist progress in areas where there is less agreement generally over semantics.
-The representation of these areas and concepts on the Semantic Web is troublesome, particularly in a framework which is geared towards resolving semantic ambiguity to static, pre-assigned meanings.
-More established disciplines in cognitive science and related areas of research would not claim to have solved all such issues and challenges; however Semantic Web researchers can learn from advances that have been made in these disciplines.
-An approach informed by cross-disciplinary contributions helps Semantic Web research progress towards a broader and more complex coverage of data and their semantics.
-
-The need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed.
-There is a large quantity of material contributory to a satisfactory model of creativity and a number of key contributions have been discussed during this section.
-What must be done now is to marshal this assortment of material and to unify different perspectives where possible, in order to avoid the disciplinary `blinkers' or compartmentalisation that is often seen in creativity research \cite{hennessey10}.
-In approaching the semantic representation of subjective and multi-faceted concepts, some useful guidance is offered through philosophical reflections on the meaning of such concepts.
-
-%Further, cognitive science methodologies, {\bf IS THIS NEXT BIT TO GO?} as well as approaches to ontology learning from texts \cite{gomezperez04} {\bf END} can be harnessed to enable the representation of more semantically ambiguous concepts such as creativity
-
-%To date, however, the Semantic Web research community has largely focused on the representation of objective concepts and resources that are relatively clearly defined.
-
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Methods}
-\label{methodology}
-
-Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
-In addition, following from the observations above, a {\em  confluence approach\/} to creativity is adopted \cite{sternberg99a,mayer99,ivcevic09}.
-This works on the principle that creativity results from several components converging and goes on to examine what these components are.
-Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted.
-This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.
-
-Tools from natural language processing and statistical analysis are used to identify words that appear to be highly associated with dimensions of creativity, as represented in a sample of academic papers on the topic.
-A key innovation is the use of a statistical measure of lexical similarity, which allows the words to be clustered into coherent and semantically-related groups.
-Clustering reveals a number of common themes or factors of creativity, allowing the identification of a set of fourteen components that serve as building blocks for creativity.
-
-\subsection*{Corpus data}\label{corpusData}
-
-A sample of academic papers discussing the nature of creativity was assembled as a {\em creativity corpus\/} in 2010.
-This creativity corpus consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.
-
-\vspace{0.25cm}
-\begin{center}
-\fbox{
-\begin{minipage}{0.8\linewidth}
-\textbf{Creativity corpus}: \\ a collection of thirty academic papers which explicitly discuss the nature of creativity.
-\end{minipage}
-}
-\end{center}
-\vspace{0.25cm}
-
-The 30 papers selected for the creativity corpus are listed in \nameref{S1_Appendix}. The strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}.
-
-\begin{figure}[!b]
-\caption{{\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus.}}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/Fig1}
-\label{searchCC}
-\end{figure}
-
-The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers.
-This literature search was supplemented with additional influential papers which may not have appeared in a Scopus search.
-For example, a Computer Science conference paper on cognitive models of creativity has been included, as in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.
-The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.
-
-Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
-The inclusion criteria are as follows, listed in descending order of precedence:
-\begin{itemize}
-\item Papers must have, as their primary focus, discussion of the nature of creativity.
-\item Papers should be considered particularly influential.
-Influence was generally measured objectively, in terms of the number of times a paper had been cited by other academic authors.
-However, for papers published in recent years and which had consequently had little time to accrue citations, selection was based instead on a subjective judgement of influence grounded in a knowledge of the field.
-\item Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009.
-[The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J.
-P.
-Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof).
-His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.
-\item Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of creativity.
-Fig.
-\ref{disciplinaryDistribution} illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers.
-This distribution is based on the {\em Scopus} database, which classifies journals under their main subject area(s) covered.
-We should acknowledge here though that while many disciplines include creative practice, often the focus is on application rather than in depth discussion of what creativity entails.
-Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the focus of our corpus as a representation of key discussions about the nature of creativity.
-\end{itemize}
-
-\begin{figure}[!b]
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[scale=0.5]{images/Fig2}
-\caption{{\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period.} \\Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}.
-Note that Scopus may classify a journal under more than one discipline.}
-\label{disciplinaryDistribution}
-\end{figure}
-
-Exclusion criteria for this search were as follows: 
-\begin{itemize}
-\item Authors were only represented more than once in the corpus if the relevant papers were written from different perspectives.
-For example, Mark Runco's work is represented twice in the corpus, but covering two different topics relating to the nature of creativity (psychoeconomic approach to creativity; cognition and creativity).
-If the search process highlighted two or more papers with a shared author on the same or highly similar perspectives on creativity, then the more highly cited paper was chosen.
-\item Papers had to be written in English, as the language processing tools we were working with were for English language texts.
-\item Papers had to be available in a format that enabled us easily to extract plain text (this excluded books or book chapters).
-\end{itemize}
-
-The creativity corpus is relatively small and necessarily selective  in terms of the papers that are included.
-As such it constitutes just a small fraction of the many academic works on creativity that have been published in the last 60 or so years.
-Indeed, the 30 papers in the creativity corpus cannot be regarded as comprehensively representative of the wide range of academic positions on creativity that have been discussed in the literature over the decades.
-However, the goal of this work is not to present a fine-grained analysis of language use drawn from this complete literature, nor to provide a comprehensive lexicon or dictionary of creativity.
-Rather, the goal is to identify the broader ontological themes or factors that recur in our understanding of the concept of creativity.
-For this purpose, what is required is a sufficiently representative sample of the academic discourse on creativity.
-This sample can be used to identify the way in which word use reflects key themes or factors that persist across different perspectives.
-
-Our objective is to identify what is distinctive in the language used to discuss creativity, in contrast to the language used to discuss other topics.
-As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled alongside the creativity corpus, in 2010.
-
-\vspace{0.25cm}
-\begin{center}
-\fbox{
-\begin{minipage}{0.8\linewidth}
-\textbf{Non-creativity corpus}: \\ 60 academic papers on topics unrelated to creativity, from the  same range of academic disciplines and publication years as  the creativity corpus papers.
-\end{minipage}
-}
-\end{center}
-\vspace{0.25cm}
-
-The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline (as categorised by  {\em Scopus}) and published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e.
-{\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).
-In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.
-The 60 papers selected for the creativity corpus are listed in \nameref{S2_Appendix}.
-The search strategy used to select papers for this non-creativity corpus is illustrated in a second flow diagram, in Fig.
-\ref{searchNonCC}.
-
-\begin{figure}
-\caption{ A flow diagram describing the search strategy used to identify papers for the non-creativity corpus.}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/Fig3}
-\label{searchNonCC}
-\end{figure}
-
-The non-creativity corpus is twice the size of the creativity corpus ($\approx$ 700,000 words and $\approx$ 300,000 words respectively), in acknowledgement of the fact that in general the set of academic papers on creativity is only a small subset of all academic papers.
-Both corpora are very small in comparison to corpora such as the British National Corpus, a relatively large  ($\approx$ 100M words) corpus of written and spoken English in general usage across a number of different contexts, and tiny in comparison to more recent web-derived text collections containing billions of words.
-There are, however, several benefits associated with using a corpus derived from specialist academic literature:
-
-\begin{itemize}
-\item Ease of locating relevant and appropriate papers: e.g.
-availability of tools to perform targeted literature searches, electronic publication of papers for download, tagging of paper content by keywords, citations in papers to other related papers.
-\item Ability to access timestamped textual materials over a range of decades.
-\item Publication of academic papers in an appropriate format for computational analysis: most papers that are available electronically are in formats such as PDF or HTML, which can be converted to text fairly easily.
-\item Availability of citation data as a measure of how influential a paper is on others: whilst not a perfect reflection of a paper's influence, citation data is often used for measuring the impact of a journal \cite{garfield72} or an individual researcher's output \cite{hirsch05}.
-\item Availability of provenance data, such as who wrote the paper and for what audience (from the disciplinary classification of the journal).
-\end{itemize}
-\noindent
-
-Some pre-processing was undertaken for each paper in both the creativity corpus and non-creativity corpus prior to analysis.
-A plain text file was generated for each paper, containing the full text of that paper.
-All journal headers and copyright notices were removed from each paper, as were the author names and affiliations, list of references and acknowledgements.
-All files were also checked for any non-ASCII characters and anomalies that may have arisen during the creation of the text file.
-
-\subsection*{Natural language processing}
-
-The corpus data was first pre-processed using the RASP natural language processing toolkit \cite{briscoe06} in order to perform {\em lemmatisation} and {\em part-of-speech} tagging.
-Lemmatisation permits inflectional variants of a given word to be identified with a common `dictonary headword' form or `lemma'.
-For example,  {\em performs\/}, {\em performed\/}  and {\em performing\/} all occur in the creativity corpus as distinct morphological variants of  the  verb, {\em perform\/}.
-Intuitively, we would like to count each of these inflectional variants as an instance of the same word, rather than as separate and distinct lexical tokens.
-Lemmatisation software enables us to do this by mapping such variants to a cannonical lemma form.
-As a further refinement, each lemma was also mapped to lower case to ensure that capitalised word forms (e.g.
-{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).
-While this has the potential for occasional confusion between proper names and common nouns (e.g.
-{\em Apple\/} v.
-{\em apple\/}), it is not considered that the resulting level of `noise'  in the data is likely to adversely affect the results of the analysis.
-
-Each word was assigned a part-of-speech tag identifying its grammatical category (i.e.
-whether the word was a noun, verb, preposition, etc.).
-Such tagging is useful because it allows us to distinguish between different grammatical uses of a common orthographic form.
-For example, the use of {\em novel\/} as a noun in {\em a good novel\/} can be properly differentiated from its use as an adjective in {\em a novel idea\/}.
-The data was further simplified and filtered so that only words of the four `major' categories (i.e.
-noun, verb, adjective and adverb) were represented.
-Note that the major categories bear the semantic content of the papers making up the creativity corpus.
-They may be distinguished from minor categories or `function words', such as pronouns ({\em something\/}, {\em itself\/}) prepositions (e.g.
-{\em upon\/}, {\em by\/}) conjunctions ({\em but\/}, {\em or\/}) and quantifiers (e.g.
-{\em many\/}, {\em more\/}).
-Because such words have little independent semantic content, they are of limited interest for the present study and may be removed from the data.
-
-Following processing with RASP, a list of words found in the creativity corpus, together with their frequency counts was generated.
-The non-creativity corpus was pre-processed in the same way and a corresponding list of words and frequencies also generated.
-
-\subsection*{Identifying words associated with creativity}
-
-The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus.
-This in turn can be regarded as providing evidence of which words are salient to the concept of creativity.
-Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.
-It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}.
-This is a particular issue when analysing smaller corpora, such as those used in the present work.
-The log likelihood ratio statistic is more accurate in its treatment of infrequent words in the data,  which often hold useful information.
-By contrast, the $\chi^2$ statistic tends to under-emphasise such outliers at the expense of very frequently occurring data points.
-
-Our use of the log-likelihood ratio follows that of Rayson and Garside \cite{rayson00}.
-Given two corpora (in our case, the creativity corpus $cc$ and the non-creativity corpus $nc$) the log-likelihood score for a given word is calculated as shown in equation~(\ref{LLR}) below:
-
-\begin{equation}
-\mbox{\em LL} =  O_{cc}\ln (\frac{O_{cc}}{E_{cc}} ) + O_{nc}\ln (\frac{O_{nc}}{E_{nc}} )
-\label{LLR} 
-\end{equation}
-\noindent
-where $O_{cc}$ ($O_{nc}$) is the observed frequence of the word in $cc$ ($nc$) and similarly $E_{cc}$ ($E_{nc}$) is its expected frequency. The expected frequency $E_{cc}$  is given by:
-
-\begin{equation}
-E_{cc} = \frac{N_{cc} \times (O_{cc} + O_{nc})}{N_{cc} + N_{nc}}
-\label{modelFreqs} 
-\end{equation}
-where $N_{cc}$ denotes the total number of words in corpus $cc$ (i.e.
-the sum of the frequencies of all words drawn from corpus $cc$).
-The expected frequency $E_{nc}$ is defined in a way analogous to Equation \ref{modelFreqs}.
-
-As computed above, the log-likelihood ratio measures the extent to which the distribution of a given word deviates from what might be expected if its distribution is not corpus dependent.
-The higher the log likelihood ratio score for a given word, the greater the deviation from what is expected.
-It should be noted however, that the statistic tells us only that  the observed distribution of a word in the two corpora is unexpected (and to what extent).
-It does not  tell us whether the word is more or less frequent than expected in the creativity corpus.
-To identify words significantly associated with creativity therefore, it was necessary to select just those words with observed counts higher than that expected in the creativity corpus.
-It should perhaps be further noted that the resulting words may be either positively or negatively connoted with respect to creativity.
-In practice this is not a problem, as the significance of a given word lies in its semantic connection to creativity, not in its sentiment or affect.
-Affect is taken into account as part of the later manual examination of the data used to identify components of creativity.
-
-The results of the calculations were filtered to remove any words with a log-likelihood score less than 10.83, representing a chi-squared significance value for p=0.001 (one degree of freedom).
-In this way, the filtering process reduced the set of candidate words to just those that appear to occur significantly more often than expected in the creativity corpus.
-To avoid extremely infrequent words disproportionately affecting the data, any word occurring fewer than five times was also removed from the data.
-Finally, the words were inspected to remove any `spurious' items such as proper nouns or misclassified or odd character sequences.
-This resulted in a total of 694 {\em creativity words\/}: a collection of 389 nouns, 205 adjectives, 72 verbs and 28 adverbs that occurred significantly more often than expected in the creativity corpus.
-Table \ref{creativityTop20} gives the top 20 results of these calculations.
-
-\begin{table}[!b]
-\begin{center}
-\begin{tabular}{c c | c c}
-\# & Word (\& POS tag) & LLR \\
-\hline
-\#1 & thinking (N) & 834.55  \\
-\#2 & process (N) & 612.05 \\
-\#3 & innovation (N) & 546.20 \\
-\#4 & idea (N) & 475.74  \\
-\#5 & program (N) & 474.41  \\
-\#6 & domain (N) & 436.58 \\
-\#7 & cognitive (J) & 393.79  \\
-\#8 & divergent (J) & 355.11 \\
-\#9 & openness (N) & 328.57  \\
-\#10 & discovery (N) & 327.38 \\
-\#11 & primary (J) & 326.65 \\
-\#12 & originality (N) & 315.60  \\
-\#13 & criterion (N) & 312.61  \\
-\#14 & intelligence (N) & 309.31 \\
-\#15 & ability (N) & 299.27 \\
-\#16 & knowledge (N) & 290.48  \\
-\#17 & create (V) & 280.06 \\
-\#18 & experiment (N) & 253.32 \\
-\#19 & plan (N) & 246.29 \\
-\#20 & agent (N) & 246.24  \\
-\end{tabular}
-\end{center}
-\caption{{\bf The top 20 results (in descending order) of the log-likelihood ratio (LLR) calculations.}\\ A significant LLR score at p=0.001 is 10.83.
-N.B.
-POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
-\label{creativityTop20}
-\end{table}%
-
-\subsection*{Identifying components of creativity}
-\label{creat-comps}
-
-It is important to note that our objective is to identify key themes in the lexical data, not to induce a comprehensive terminology of creativity.
-Despite the relatively small size of the corpora used, the resulting set of 694 creativity words is sufficiently rich for this purpose, but is still somewhat large to work with in its raw form.
-In previous, related work \cite{jordanous10a} an attempt was made to identify key components by manually clustering creativity words by inspection of the raw data.
-In practice, this proved laborious and made it impossible systematically to consider all of the identified words.
-It also raised issues of subjectivity and experimenter bias.
-These problems are addressed here, at least in part, by automatically clustering the words according to a statistical measure of {\em distributional similarity\/} \cite{lin98}.
-The more manageable collection of clusters may then be examined to identify key components or dimensions of creativity.
-
-The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}.
-This hypothesis  states that similarity of distribution correlates with similarity of meaning: two words that tend to appear in similar linguistic contexts will tend to have similar meanings.
-The notion of linguistic context here is not fixed and might plausibly be modelled in a variety of different ways.
-For example, two words might be considered to inhabit the same context if they appear in the same document or the same sentence or if they stand in the same grammatical relationship to some other word (e.g.
-both occur as {\em subject\/} of a particular verb or {\em modifier\/} of a given noun).
-In practice it has been shown that modelling distribution in terms of grammatical relations leads to a tighter correlation between distributional similarity and closeness of meaning \cite{kilgarriff00}.
-
-In the present work, grammatical relations are used to represent linguistic context  and distributional similarity is measured as a function of the number of  relations 
-that two words share. To illustrate, evidence that the words {\em concept} and {\em idea} are similar in meaning might be provided by occurrences such as the following:
-
-\begin{quote}
-(1) the {\em concept/idea} involves \hfill (subject of verb `involve')\\
-(2) applied the {\em concept/idea\/} \hfill (object of verb `apply') \\
-(3) the basic {\em concept/idea\/} \hfill (modified by adjective `basic')
-\end{quote}
-
-\noindent
-Grammatical relations were obtained from an analysis of the written portion of the British National Corpus \cite{leech92}, which had previously been processed using the RASP toolkit \cite{briscoe06} in order to extract them.
-Using this data, each word in the creativity corpus was associated with a list of grammatical relations in which it occurred, together with corresponding counts of occurrence.
-In practice, not all of the grammatical relation information output by RASP was used to calculate distributional similarity.
-Just the subject, object and modifier relation types are used as these tend to give the best results \cite{weeds03}.
-A potential difficulty with obtaining word similarity data based on the BNC (i.e.
-using data from sources of everyday usage of English, rather than from more specialist sources) would arise if the majority of the creativity words were used with distinctive or technical senses within the creativity corpus.
-From inspection and from knowledge of creativity literature, however, this situation was found to be unlikely.
-While some narrowly specialised usage may be present to some small degree in the set of creativity words, most words retain general senses as reflected in the wider BNC data set.
-An advantage of using the BNC is that its  size increases the chances of a comprehensive coverage of the general senses of each word of interest.
-
-Distributional similarity of two words is measured in terms of the similarity of their associated lists of grammatical relations.
-A variety of different methods for calculating distributional similarity have been investigated in the literature, including standard techniques such as the cosine measure \cite[for example]{mannschu99}.
-The present work adopts an information-theoretic measure due to Lin \cite{lin98}, which has been widely used in language processing applications as a means of automatically discovering semantic relationships between words.
-In comparison to other similarity measures it has been shown to perform particularly well as a means of identifying near-synonyms \cite{weedsweir03,mccanavi09}.
-
-Similarity scores were calculated between all pairs of creativity words of the same grammatical category.
-That is, scores were obtained separately for pairs of nouns, verbs, adjectives and adverbs.
-For a given set of words, word pair similarity data calculated in this way can be conveniently visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0), as in Fig.
-\ref{conceptIdea}.
-
-\begin{figure}
-\caption{{\bf Word pairwise similarity data visualised as an edge-weighted graph.} \\Nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). }
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[width=\textwidth]{images/Fig4}
-\label{conceptIdea}
-\end{figure}
-
-Graphical representations of the similarity data like that shown in Fig.
-\ref{conceptIdea} provide a useful basis for analysing the creativity words and identifying recurring themes or components of creativity.
-Two complementary methods for identifying key components of the data were adopted:
-
-\begin{description}
-
-\item[Clustering:] The graph clustering software {\em Chinese Whispers} \cite{biemann06} was used to automatically identify word clusters (groups of closely interconnected words) in the dataset.
-This algorithm uses an iterative process to group together graph nodes that are located close to each other.
-By grouping words with similar meanings, the number of data items was effectively reduced and themes in the data could be recognised more readily from each distinct cluster.
-A sample of some of the resulting clusters can be seen in Fig.
-\ref{clustersZoom}.
-%To carry out Chinese Whispers, a preprocessing step was taken to categorise words according to their parts of speech, using the RASP software \cite{carrollRASP}.
-
-\item[Inspection:] To focus on the words most closely related to creativity, the top twenty creativity words (i.e.
-the twenty  words with the highest log likelihood scores) were selected.
-Each word was then visualised as the root node of its own individual subgraph using the graph drawing software {\em GraphViz} (http://www.graphviz.org/, last accessed August 2016).
-In order to reduce the amount of data to be examined, similarity scores were discarded if they fell below a threshold value (adjusted manually for each graph to highlight the most strongly connected words).
-This made the size and complexity of the graphs smaller and therefore easier to inspect and analyse visually.
-Fig.
-\ref{clusterToComponents} illustrates, in diagram form, the process of using manual inspection to identify components.
-
-\end{description}
-
-\begin{figure}
-\caption{{\bf Sample of clusters produced by the Chinese Whispers clustering step.}}
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[width=\textwidth]{images/Fig5}
-\label{clustersZoom}
-\end{figure}
-
-\begin{figure}
-\caption{{\bf Illustration of the process of using manual inspection for further clustering.}}
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[width=\textwidth]{images/Fig6}
-\label{clusterToComponents}
-\end{figure}
-
-As part of the manual inspection process, candidate components were further considered in terms of the {\em Four Ps} of creativity \cite{rhodes61,mooney63,mackinnon70,kaufman09} described earlier in this paper.
-This additional analysis provided a means of identifying alternative perspectives and revealing subtle (but still important) aspects of creativity.
-For example, {\em novelty} is commonly associated with the results of creative behaviour (Product): how novel is the artefact or idea that has been produced?
-However, we could similarly recognise as creative an approach to a task  (Process) that does things in a novel and different way.
-Also, if a product is new in a particular environment (Press), then it may well be regarded as creative to those in that environment.
-Viewing {\em novelty} from the perspectives of Product, Process and Press uncovers these subtle and interlinked distinctions.
-
-% Results and Discussion can be combined.
-\section*{Results and Discussion}
-\label{results}
-
-\subsection*{Components of creativity}\label{componentsResults}
-
-From the analysis steps described in the previous section it was possible to extract a set of fourteen key components of creativity. These components are summarised in Fig. \ref{components} 
-and are presented in more detail below.
-The components contribute collectively to the overall concept and may be regarded as providing an {\em ontology of creativity\/}.
-It is important to note, however that the fourteen components do not constitute a set of necessary and sufficient conditions for creativity, in all its possible manifestations.
-There are two reasons for this.
-Firstly, some of the components we have identified appear to be logically inconsistent with others in the set.
-Consider for example the apparent need for autonomous, independent behaviour identified in {\em Independence and Freedom\/} and contrast this with the requirement for social interaction implied by {\em Social Interaction and Communication\/}.
-%\hidden{These factors may appear logically opposed.}
-Secondly, of course, creativity %\hidden{does not lend itself to formal and precise definition and 
-%I added this bit to clarify the point a bit [does not lend itself to formal and precise definition and]
-also manifests itself in rather different ways across different domains \cite{plucker04} and components will vary in importance, according to the requirements of a particular domain.
-As an illustration of this second point, %Can we explicitly relate this illustration to one or more of the components that have been identified?
-creative behaviour in mathematical reasoning has more focus on finding a correct solution to a problem than is the case for creative behaviour in, say,  musical improvisation \cite{colton08,jordanous12jims}.
-
-\begin{figure} 
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-\caption{{\bf The fourteen key components of creativity identified through an analysis of the word clusters.}}
-%%\includegraphics[width=\textwidth]{images/Fig7}
-\label{components}
-\end{figure}
-
-The following set of fourteen components is therefore presented as a collection of dimensions -- attributes, abilities and behaviours, etc.
--- which contribute to our understanding of creativity.
-The components should be treated as {\em building blocks} for creativity that may be arranged in different ways and with different emphases to suit different modelling purposes.
-The analysis of creativity in terms of the dimensions should be informative for a human audience and provide a basis for machine-understanding of the concept.
-%This approach is informed by debates in cognitive linguistics, computational linguistics and through philosophical underpinnings (see Background section).
- Each component is presented here with a brief explanation or gloss. These explanations will later be used for part of the semantic content in the creativity ontology.
-
-%The current work illuminates the sorts of issues that arise in formal modelling of subjective or `soft' concepts such as creativity, which are unlikely to resolve to fixed, static meaning(s).
-For example,  some components appear  logically inconsistent with others in the set: e.g.
-the need for autonomous, independent behaviour ({\em Independence and Freedom\/}) versus the requirement for social interaction ({\em Social Interaction and Communication\/}).
-Also, creativity clearly manifests itself in different ways across different domains \cite{plucker04} and components will vary in importance, according to the requirements of a particular domain.
-For example, creative behaviour in mathematical reasoning has more focus on finding a correct solution to a problem than is the case for creative behaviour in, say,  musical improvisation \cite{colton08}.
-The set of creativity components are therefore presented as a collection of dimensions -- attributes, abilities and behaviours, etc.
--- which contribute to an overall improvement in the understanding of creativity that provides greater clarity and information both to a human audience and in machine-readable form for future Linked Data links and applications on the Semantic Web.
-This approach is informed by debates in cognitive linguistics, computational linguistics and through philosophical underpinnings (section \ref{cogPhil}).
-
-\begin{description}
-
-\item[Active Involvement and Persistence:] \mbox{}\\
-{\em Being actively involved; reacting to and having a deliberate effect on the creative process.\/}\\
-{\em The tenacity to persist with the creative process throughout, even during problematic points\/}.
-
-\item[Dealing with Uncertainty:] \mbox{}\\{\em
-Coping with incomplete, missing, inconsistent, contradictory, ambiguous and/or uncertain information. Element of risk and chance - no guarantee that information problems will be resolved.\\
-Not relying on every step of the process to be specified in detail; perhaps even avoiding routine or pre-existing methods and solutions.
-}
-
-\item[Domain Competence:] \mbox{}\\{\em
-Domain-specific intelligence, knowledge, talent, skills, experience and expertise.\\
-Knowing a domain well enough to be equipped to recognise gaps, needs or problems that need solving and to generate, validate, develop and promote new ideas in that domain.
-}
-
-\item[General Intellectual Ability:] \mbox{}\\{\em
-General intelligence and IQ.\\
-Good mental capacity.
-}
-
-\item[Generation of Results:] \mbox{}\\
-{\em Working towards some end target, goal, or result.\/}\\
-{\em Producing something (tangible or intangible) that previously did not exist.\/}
-
-\item[Independence and Freedom:] \mbox{}\\{\em 
-Working independently with autonomy over actions and decisions.\\
-Freedom to work without being bound to pre-existing solutions, processes or biases; perhaps challenging cultural or domain norms.
-}
-
-\item[Intention and Emotional Involvement:] \mbox{}\\{\em
-Personal and emotional investment, immersion, self-expression and involvement in the creative process.\\
-The intention and desire to be creative: creativity is its own reward, a positive process giving fulfilment and enjoyment.
-}
-
-\item[Originality:] \mbox{}\\{\em
-Novelty and originality; a new product, or doing something in a new way; seeing new links and relations between previously unassociated concepts.\\
-Results that are unpredictable, unexpected, surprising, unusual, out of the ordinary.
-}
-
-\item[Progression and Development:] \mbox{}\\{\em
-Movement, advancement, evolution and development during a process.\\
-Whilst progress may or may not be linear, and an actual end goal may be only loosely specified (if at all), the entire process should represent some progress in a particular domain or task. }
-
-\item[Social Interaction and Communication:] \mbox{}\\{\em
-Communicating and promoting work to others in a persuasive and positive manner.\\
-Mutual influence, feedback, sharing and collaboration between society and individual.
-}
-
-\item[Spontaneity/Subconscious Processing:] \mbox{}\\{\em 
-No need to be in control of the whole process; thoughts and activities may inform the process subconsciously without being inaccessible for conscious analysis, or may receive less attention than others.
-\\
-Being able to react quickly and spontaneously when appropriate, without needing to spend too much time thinking about the options.
-}
-
-\item[Thinking and Evaluation:] \mbox{}\\{\em 
-Consciously evaluating several options to recognise potential value in each and identify the best option, using reasoning and good judgement.\\
-Proactively selecting a decided choice from possible options, without allowing the process to stagnate under indecision.
-}
-
-\item[Value:] \mbox{}\\{\em 
-Making a useful contribution that is valued by others and recognised as an achievement and influential advancement; perceived as special, `not just something anybody would have done'.\\
-The end product is relevant and appropriate to the domain being worked in.
-}
-
-\item[Variety, Divergence and Experimentation:] \mbox{}\\{\em 
-Generating a variety of different ideas to compare and choose from, with the flexibility to be open to several perspectives and to experiment and try different options out without bias.\\
-Multi-tasking during the creative process.
-}
-\end{description}
-
-\subsection*{Implementing a machine-readable ontology of creativity}\label{creativityOntology}
-
-The fourteen components provide a fuller and clearer account of the constituent parts of the concept of creativity.
-An important aim of the current work is to make the components available as a resource for other researchers in computational creativity and to provide a basis for the automated evaluation of creative systems.
-As a step in this direction, the components have been expressed in an open, machine-readable form within the Semantic Web.
-In this way, the characterization of the components benefits from and is enriched by concepts that are already represented within the Semantic Web.
-%To achieve this, SKOS (Simple Knowledge Organisation System) \cite{skos} was used as a basis for constructing an OWL ontology representation of creativity and its components,
-
-In particular, the components are linked to the data in WordNet \cite{fellbaum98}, a large lexical database of English that has recently been made available as a Semantic Web ontology (http://wordnet.rkbexplorer.com/, last accessed August 2016).
-In WordNet, words are grouped by sense and interlinked by lexical and conceptual relations.
-Note that, although the WordNet definition of the word such as `creativity' is brief (`the ability to create'), its utility lies in how it is linked to various concepts, such as its sense, hyponyms, type, `gloss' (brief definition) and other related concepts.
-Each creativity component relates to a cluster of keywords from the original set of 694 creativity words.
-Following Linked Data principles, each can therefore be linked across the Semantic Web to an appropriate set of concepts from WordNet.
-In this way,  associated semantic information is provided for each component.
-%The SKOS ontology incorporates three main classes:  {\em skos:Concept}  (anything we may want to record information about), {\em skos:ConceptScheme} (a set that collectively defines a skos:Concept) and  {\em skos:Collection} (a collection of semantically-related information).
-An instance of {\em skos:ConceptScheme\/} was created as {\em CreativityComponents}, to represent the set of components that defines the {\em skos:Concept\/} of {\em Creativity}.
-Each component is represented as an individual {\em skos:Concept\/}.
-
-The resulting encoding can be visualised as a graph, as shown in Fig. \ref{ontologyGraph}. 
-The data has also been published under an Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} at:
-%as an OWL/XML file at:
-\begin{quote}
-\texttt{\scriptsize http://purl.org/creativity/ontology}
-\end{quote}
-%under a Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} .
-%The {\em skos:Concept\/}  
-The concept labelled {\em Creativity} has the unique URI: 
-\begin{quote}
-\texttt{\scriptsize http://purl.org/creativity/ontology\#Creativity}
-\end{quote}%
-Any Linked Data that needs to refer to the concept can use this identifier.
-
-\begin{figure}
-\caption{{\bf The ontology of creativity generated from this work's results, in graph form.}}
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[scale=0.5]{images/Fig8}
-\label{ontologyGraph}
-\end{figure}
-
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-
-%\section*{Discussion}
-%\label{implications}
-
-%As already noted above, the need for a clearer, multi-perspective and broadly applicable account of creativity is evident: this point has been repeatedly underlined by creativity researchers \cite[for example]{rhodes61,torrance67,plucker04defn,kaufman09,hennessey10}.
-As Hennessey and Amabile point out \cite{hennessey10}, an accurate and comprehensive account assists our understanding of creativity and further research.
-It also helps smooth out individual differences of interpretation,   highlighting common ground and transcending discipline or domain bias \cite{plucker04}.
-The novel, language-driven approach to definition adopted in the present work draws together multiple perspectives across disciplinary divides and a confluence approach yields a broader understanding of the concept in the form of an ontology of creativity.
-
-%There are a number of ways to evaluate Semantic Web ontologies \cite{brank05}.
-For the purposes of the creativity ontology presented in this paper, evaluation based on matching any `golden standards' \cite{brank05} is not so appropriate given the lack of any such standards or baselines to adopt, as discussed above in the Introduction of this paper and elsewhere \cite{rhodes61,taylor88,sternberg99a,plucker04defn,kaufman09,jordanousphd,jordanous12cc}.
-It is hoped that publication of the creativity ontology can now facilitate future applications in description and evaluation of creativity, for application-based evaluation of the ontology, perhaps incorporating other data sources to enable data-driven evaluation.
-In areas of knowledge representation such as that tackled in this paper, it is not appropriate to test the ontology definitions against `a set of predefined criteria, standards, requirements, etc.' \cite{brank05} as these sets do not necessarily exist,  but the spirit of such recommendations can be followed by seeing how the ontology matches against human interpretations of the same concepts.
-One can also evaluate how the ontology data can be linked to other data sources \cite{bizer09}.
-Hence, as a reflection of the cross-disciplinary nature of this work, evaluation of the creativity ontology is two-fold, concerning both the cognitive accuracy of this representation of creativity and evaluation of the creativity data publication as an output of Semantic Web research.
-
-\section*{Evaluation}
-
-From a practical stand-point, the current work is part of an overarching project engaged with the question of the evaluation of creativity, particularly computational creativity \cite{jordanous12cc}.
-It is clear that a rigorous and comparative evaluation process needs clear standards to use as guidelines or benchmarks \cite{torrance88,kaufman09}.
-
-The components of creativity in this paper have been employed in two case studies to evaluate the creativity of computational systems \cite{jordanousphd,jordanous12jims,jordanous16aisb}.
-In these case studies, evaluation was carried out using the three step approach of the Standardised Procedure for Evaluating Creative Systems (SPECS) \cite{jordanous12cc}:
-
-\begin{quote}
-\begin{enumerate}
-\item Identify a definition of creativity that your system should satisfy to be considered creative:
-	\begin{enumerate}
-	\item What does it mean to be creative in a general context, independent of any domain specifics?
-	\item What aspects of creativity are particularly important in the domain your system works in (and what aspects of creativity are less important in that domain)?
-	\end{enumerate}
-\item Using Step 1, clearly state what standards you use to evaluate the creativity of your system.
-\item Test your creative system against the standards stated in Step 2 and report the results.
-\end{enumerate}    
-\end{quote}
-
-In both case studies, the components of creativity were chosen as the way of characterising creativity for step 1a of SPECS, and were weighted according to their importance and relevance for creativity in the creative domains under study for each case study (step 1b of SPECS).
-Each component was treated as one standard to be used to evaluate the creativity of the creative systems in the case studies (step 2 of SPECS).
-Each case study system was then tested against each component using feedback provided by judges (step 3 of SPECS), resulting in a detailed set of evaluative feedback on the creativity of each system in the case studies.
-
-Case Study 1 \cite{jordanousphd,jordanous12cc} evaluated the creativity of three different computational musical improvisation systems \cite{jordanous12cc}. 
-Case Study 2 used the components of creativity in an evaluation scenario where information and time was limited for evaluation, to simulate the forming of first impressions and snapshot judgements of the creativeness of a given computational creativity system \cite{jordanousphd,jordanous16aisb}.
-
-The resulting component-based evaluation yielded detailed information about creative strengths and weaknesses of the systems under investigation, highlighting those components where a system performs strongly.
-Crucially, the evaluation feedback also highlighted areas where a given system performed poorly.
-For example, in the musical improvisation study, Case Study 1, we found that, in general, creativity could be improved most by improving performance in {\em Social Interaction and Communication}, {\em Intention and Emotional Involvement} and {\em Domain Competence} (the three components found to be most important for creativity in musical improvisation).
-Similarly, it is useful to be able to quickly obtain formative feedback on strengths and weaknesses in time-limited scenarios such as that replicated in Case Study 2 during the development of creative systems (when ongoing evaluation of progress ideally needs to be both timely and time-efficient).
-Insight can then be obtained on where future development effort is best spent.
-
-The results described above were compared with those obtained from applying other evaluation models and with surveys of people's opinions, where people were asked how creative they thought each system was.
-There was general agreement between evaluation approaches on the most and least creative systems.
-The approaches differed in the formative feedback they provided, particularly for identifying strengths of the system at being creative, and weaknesses of the system to be improved.
-The model of creativity offered in this paper gave the most detailed feedback, but required most information to be collected.
-
-To support the usefulness of having the components as a tangible characterisation of creativity, an interesting finding was made as part of the first case study, in a separate evaluation carried out: asking for people's opinions on how creative the musical improvisation systems were.
-A striking observation was that a number of participants called for the word ``creativity'' to be defined before they felt comfortable with the task and confident in evaluating creativity in this setting, even though participants reported feeling generally positive or at least neutral towards the concept of computational creativity.
-This challenges the generally held view that people have a  common-sense working definition of creativity, at least in the context of judgement and evaluation.
-A representation of creativity is useful to:
-
-\begin{enumerate}
-\item establish what it means for something to be deemed creative; and
-\item identify appropriate evaluation standards that replicate typical human opinion on how creative something is or in comparing two or more creative systems.
-\end{enumerate}
-
-\subsection*{Conclusions and directions for future work}
-\label{conclusions}
-
-This paper has described the methods used to identify a set of {\em components of creativity} using corpus-based, statistical language processing techniques.
-The motivation for the work is the need for a shared, comprehensive and multi-perspective model of creativity.
-Such a model should be of great value to researchers investigating the nature of creativity and in particular those concerned with the evaluation of creative practice.
-More broadly, the inter-disciplinary approach described here exemplifies a general approach to the investigation and representation of semantically fuzzy and essentially-contested concepts.
-For this reason, we expect that it will interest researchers investigating computational methods for analysing and representing other such concepts.
-
-Rather than attempting to provide a unitary account of creativity, our approach extracts common, underlying themes that transcend discipline or domain bias.
-Our point of departure is the observation that the vocabulary used in discussions of the nature of creativity may be analysed in order to throw light on our understanding of the concept and its key attributes.
-Using techniques from corpus linguistics and natural language processing (as described in the Methods section), key components of creativity have been identified.
-The results of this novel, empirical analysis (presented in the Results section) inform the development of an {\em ontology of creativity\/} comprising a set of fourteen distinct components (see Fig.
-\ref{components}).
-It is noted that each component makes a separate contribution to the overall meaning of the concept.
-At the same time, because creativity manifests itself in different ways across different domains \cite{plucker04}, the individual components vary in importance and influence according to the requirements of a given domain.
-The components can be therefore be usefully thought of as 'building blocks' for the concept in its different manifestations.
-Taken together, the components make creativity more tractable to study and to evaluate.
-
-The fourteen components provide a multi-perspective model of creativity that has been successfully applied in a comparative analysis and evaluation of computational creativity systems \cite{jordanous12cc,jordanousphd,jordanous16aisb} (see the Discussions section).
-The outcome of the evaluation process provides relatively fine-grained information about the creative strengths of a given system.
-This information in turn evidences ways in which a system could be considered creative.
-In addition, evaluation based on the components is able to highlight areas of weakness.
-These can be used to inform future work aimed at further developing a system's creative potential.
-
-The components have been published in an open, machine-readable format, making them freely available to the research community.
-This has a number of implications.
-First, the set of components may be readily elaborated, extended or amended by other researchers investigating the concept of creativity.
-Second, the machine-readable format facilitates the development of creativity-aware applications, based on the components.
-Such applications might be developed to support manual evaluation of creative practice or as a significant step towards the development of methods for automated evaluation.
-
-The problem of developing automated evaluation has elsewhere been described as `the Achilles' heel of AI research on creativity' \cite{boden99}.
-An intriguing possibility that we are currently exploring is to further exploit language processing techniques to perform evaluation based on textual reviews, descriptions of system performance, or social media interactions \cite{jordanous15vem}.
-Such an approach would be analogous to the way sentiment analysis techniques are now in common use to evaluate attitude and opinion based on reviews of products or services \cite{panglee08}.
-This is a fascinating direction for future work, with great potential for real progress towards tackling computational creativity's `Achilles' heel'.
-
-\section*{Supporting Information}
-
 % Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
 
-\subsection*{S1 Appendix}\label{S1_Appendix}
+\section*{S1 Appendix}\label{S1_Appendix}
 {\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
@@
 
-\subsection*{S2 Appendix}\label{S2_Appendix}
+\section*{S2 Appendix}\label{S2_Appendix}
 {\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
@@
 
-\section*{Acknowledgments}
-We would like to acknowledge Nick Collins and Chris Thornton for their helpful comments during this work. 
-\pagebreak
-
-\nolinenumbers
-
-%\section*{References}
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% OR
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here.
-%
-
-\begin{thebibliography}{10}
-
-\bibitem{coltonwiggins12}
-Colton S, Wiggins GA.
-\newblock Computational Creativity: The Final Frontier?
-\newblock In: Proceedings of 20th European Conference on Artificial
-  Intelligence (ECAI). Montpellier, France; 2012. p. 21--26.
-
-\bibitem{colton08}
-Colton S.
-\newblock Creativity versus the Perception of Creativity in Computational
-  Systems.
-\newblock In: Proceedings of AAAI Symposium on Creative Systems; 2008. p.
-  14--20.
-
-\bibitem{widmerAIM09}
-Widmer G, Flossmann S, Grachten M.
-\newblock {YQX} Plays {Chopin}.
-\newblock AI Magazine. {2009};{30}({3}):35--48.
-
-\bibitem{leon10MM}
-Le\'on C, Gerv\'as P.
-\newblock The Role of Evaluation-Driven Rejection in the Successful Exploration
-  of a Conceptual Space of Stories.
-\newblock Minds and Machines. 2010;20(4):615--634.
-
-\bibitem{perezyperez99}
-P\'erez~y P\'erez R.
-\newblock MEXICA: A Computer Model of Creativity in Writing [PhD thesis].
-\newblock University of Sussex. Brighton, UK; 1999.
-
-\bibitem{cardoso09}
-Cardoso A, Veale T, Wiggins GA.
-\newblock Converging on the Divergent: The History (and Future) of the
-  International Joint Workshops in Computational Creativity.
-\newblock AI Magazine. 2009;30(3):15--22.
-
-\bibitem{rhodes61}
-Rhodes M.
-\newblock An analysis of creativity.
-\newblock Phi Delta Kappan. 1961;42(7):305--310.
-
-\bibitem{torrance67}
-Torrance EP.
-\newblock Scientific Views of Creativity and Factors Affecting its Growth.
-\newblock In: Kagan J, editor. Creativity and Learning. Boston: Beacon Press;
-  1967. p. 73--91.
-
-\bibitem{plucker04defn}
-Plucker JA, Beghetto RA, Dow GT.
-\newblock Why Isn't Creativity More Important to Educational Psychologists?
-  {Potentials}, Pitfalls, and Future Directions in Creativity Research.
-\newblock Educational Psychologist. 2004;39(2):83--96.
-
-\bibitem{kaufman09}
-Kaufman JC.
-\newblock Creativity 101.
-\newblock The Psych 101 series. New York: Springer; 2009.
-
-\bibitem{hennessey10}
-Hennessey BA, Amabile TM.
-\newblock Creativity.
-\newblock Annual Review of Psychology. 2010;61:569--598.
-
-\bibitem{plucker04}
-Plucker JA, Beghetto RA.
-\newblock Why Creativity is Domain General, Why it Looks Domain Specific, and
-  why the Distinction Doesn't Matter.
-\newblock In: Sternberg RJ, Grigorenko EL, Singer JL, editors. Creativity: From
-  Potential to Realization. Washington, DC: American Psychological Association;
-  2004. p. 153--167.
-
-\bibitem{lakoff87}
-Lakoff G.
-\newblock Women, Fire and Dangerous things: What Categories reveal about the
-  mind.
-\newblock Chicago, IL: University of Chicago Press; 1987.
-
-\bibitem{wittgenstein58}
-Wittgenstein L.
-\newblock {Philosophical Investigations, eds. Anscombe, G. E. M. and Rhees, R.
-  and {Von Wright}, G. H.}
-\newblock 2nd ed. Oxford, UK: Basil Blackwell; 1958.
-
-\bibitem{torrance88}
-Torrance EP.
-\newblock The Nature of Creativity as Manifest in its testing.
-\newblock In: Sternberg RJ, editor. The Nature of Creativity. Cambridge, UK:
-  Cambridge University Press; 1988. p. 43--75.
-
-\bibitem{sternberg99a}
-Sternberg RJ, Lubart TI.
-\newblock The Concept of Creativity: Prospects and Paradigms.
-\newblock In: Sternberg RJ, editor. Handbook of Creativity. Cambridge, UK:
-  Cambridge University Press; 1999. p. 3--15.
-
-\bibitem{vartanian14}
-Vartanian O.
-\newblock Toward a Cumulative Psychological Science of Aesthetics, Creativity,
-  and the Arts.
-\newblock Psychology of Aesthetics, Creativity, and the Arts. 2014;8(1):15--17.
-
-\bibitem{stein63}
-Stein MI.
-\newblock A Transactional Approach to Creativity.
-\newblock In: Taylor CW, Barron F, editors. Scientific Creativity: Its
-  Recognition and Development. New York: John Wiley \& Sons; 1963. p. 217--227.
-
-\bibitem{boden04}
-Boden MA.
-\newblock The creative mind: Myths and mechanisms.
-\newblock 2nd ed. London, UK: Routledge; 2004.
-
-\bibitem{guilford50}
-Guilford JP.
-\newblock Creativity.
-\newblock American Psychologist. 1950;5:444--454.
-
-\bibitem{torrance74}
-Torrance EP.
-\newblock Torrance Tests of Creative Thinking.
-\newblock Bensenville, IL: Scholastic Testing Service; 1974.
-
-\bibitem{pease01}
-Pease A, Winterstein D, Colton S.
-\newblock Evaluating Machine Creativity.
-\newblock In: Proceedings of Workshop Program of ICCBR-Creative Systems:
-  Approaches to Creativity in AI and Cognitive Science; 2001. p. 129--137.
-
-\bibitem{wiggins06ngc}
-Wiggins GA.
-\newblock Searching for computational creativity.
-\newblock New Generation Computing. 2006;24(3):209--222.
-
-\bibitem{peinado06ngc}
-Peinado F, Gervas P.
-\newblock {Evaluation of automatic generation of basic stories}.
-\newblock New Generation Computing. {2006};{24}({3}):{289--302}.
-
-\bibitem{ritchie07}
-Ritchie G.
-\newblock Some Empirical Criteria for Attributing Creativity to a Computer
-  Program.
-\newblock Minds and Machines. 2007;17:67--99.
-
-\bibitem{mayer99}
-Mayer RE.
-\newblock Fifty Years of Creativity Research.
-\newblock In: Sternberg RJ, editor. Handbook of Creativity. Cambridge, UK:
-  Cambridge University Press; 1999. p. 449--460.
-
-\bibitem{dietrich10}
-Dietrich A, Kanso R.
-\newblock A review of {EEG}, {ERP}, and Neuroimaging Studies of Creativity and
-  Insight.
-\newblock Psychological Bulletin. 2010;136(5):822--848.
-
-\bibitem{gabora12}
-Gabora L, O'Connor B, Ranjan A.
-\newblock The recognizability of individual creative styles within and across
-  domains.
-\newblock Psychology of Aesthetics, Creativity, and the Arts.
-  2012;6(4):351--360.
-
-\bibitem{mccormack07}
-McCormack J.
-\newblock Creative Ecosystems.
-\newblock In: Proceedings of the 4th International Joint Workshop on
-  Computational Creativity. London, UK; 2007. p. 129--136.
-
-\bibitem{sosa09}
-Sosa R, Gero J, Jennings K.
-\newblock Growing and Destroying the Worth of Ideas.
-\newblock In: Proceedings of the 7th ACM Creativity and Cognition conference.
-  Berkeley, California; 2009. p. 295--304.
-
-\bibitem{plucker98}
-Plucker JA.
-\newblock Beware of Simple Conclusions: The Case for Content Generality of
-  Creativity.
-\newblock Creativity Research Journal. 1998;11(2):179--182.
-
-\bibitem{baer98}
-Baer J.
-\newblock The Case for Domain Specificity of Creativity.
-\newblock Creativity Research Journal. 1998;11(2):173--177.
-
-\bibitem{baer10}
-Baer J.
-\newblock Is Creativity Domain-Specific?
-\newblock In: Kaufman JC, Sternberg RJ, editors. The Cambridge Handbook of
-  Creativity. New York, NY: Cambridge University Press; 2010. p. 321--341.
-
-\bibitem{poincare29}
-Poincar\'e H.
-\newblock Mathematical Creation.
-\newblock In: The Foundations of Science: Science and Hypothesis, The Value of
-  Science, Science and Method.. vol. Science and Method [Original French
-  version published 1908, Authorized translation by George Bruce Halsted]. New
-  York: The Science Press; 1929. p. 383--394.
-
-\bibitem{hadamard45}
-Hadamard J.
-\newblock An Essay on the Psychology of Invention in the Mathematical Field.
-\newblock Princeton, NJ: Princeton University Press; 1945.
-
-\bibitem{weisberg88}
-Weisberg RW.
-\newblock Problem Solving and Creativity.
-\newblock In: Sternberg RJ, editor. The Nature of Creativity. Cambridge, UK:
-  Cambridge University Press; 1988. p. 148--176.
-
-\bibitem{bryankinns09}
-Bryan-Kinns N.
-\newblock {Everyday Creativity}.
-\newblock In: Bryan-Kinns N, Gross MD, Johnson H, Ox J, Wakkary R, editors.
-  Proceedings of the 7th ACM conference on Creativity and Cognition. Berkeley,
-  California: ACM; 2009. p. iii--iv.
-
-\bibitem{mooney63}
-Mooney RL.
-\newblock A Conceptual Model for Integrating Four Approaches to the
-  Identification of Creative Talent.
-\newblock In: Taylor CW, Barron F, editors. Scientific Creativity: Its
-  Recognition and Development. New York: John Wiley \& Sons; 1963. p. 331--340.
-
-\bibitem{odena09}
-Odena O, Welch G.
-\newblock A Generative Model of Teachers' Thinking on Musical Creativity.
-\newblock Psychology of Music. 2009;37(4):416--442.
-
-\bibitem{jordanous16cs}
-Jordanous A.
-\newblock Four PPPPerspectives on Computational Creativity in theory and in
-  practice.
-\newblock Connection Science. 2016;tbc(tbc).
-
-\bibitem{wallas26}
-Wallas G.
-\newblock The Art of Thought.
-\newblock 1st ed. London, UK: Jonathan Cape; 1926.
-
-\bibitem{goldman64}
-Goldman RJ.
-\newblock The {M}innesota Tests of Creative Thinking.
-\newblock Educational Research. 1964;7(1):3--14.
-
-\bibitem{guilford67}
-Guilford JP.
-\newblock The nature of human intelligence.
-\newblock New York, NY: McGraw-Hill; 1967.
-
-\bibitem{amabile96}
-Amabile TM.
-\newblock Creativity in context.
-\newblock Boulder, Colorado: Westview Press; 1996.
-
-\bibitem{gallie56}
-Gallie WB.
-\newblock Essentially Contested Concepts.
-\newblock Proceedings of the Aristotelian Society. 1956;56:167--198.
-\newblock Available from: \url{http://www.jstor.org/stable/4544562}.
-
-\bibitem{firth57}
-Firth JR.
-\newblock A synopsis of linguistic theory, 1930-1955.
-\newblock Studies in Linguistic Analysis. 1957;p. 1--32.
-
-\bibitem{lakoff80}
-Lakoff G, Johnson M.
-\newblock Metaphors we live by.
-\newblock Chicago, IL: University of Chicago Press; 1980.
-
-\bibitem{oakes98}
-Oakes MP.
-\newblock Statistics for Corpus Linguistics.
-\newblock Edinburgh, UK: Edinburgh University Press; 1998.
-
-\bibitem{rayson00}
-Rayson P, Garside R.
-\newblock Comparing Corpora using Frequency Profiling.
-\newblock In: Kilgarriff A, Sardinha TB, editors. Proceedings of ACL Workshop
-  on Comparing Corpora. vol.~9. ACL. Hong Kong: ACM; 2000. p. 1--6.
-
-\bibitem{kilgarriff01}
-Kilgarriff A.
-\newblock Comparing Corpora.
-\newblock International Journal of Corpus Linguistics. 2001;6(1):97--133.
-
-\bibitem{kilgarriff06}
-Kilgarriff A.
-\newblock Where to go if you would like to find out more about a word than the
-  dictionary tells you.
-\newblock Macmillan English Dictionary Magazine. 2006;Issue 35 (Jan-Feb).
-
-\bibitem{ivcevic09}
-Ivcevic Z.
-\newblock Creativity Map: Toward the Next Generation of Theories of Creativity.
-\newblock Psychology of Aesthetics, Creativity, and the Arts. 2009;3(1):17--21.
-
-\bibitem{garfield72}
-Garfield E.
-\newblock Citation analysis as a tool in journal evaluation.
-\newblock Science. 1972;178(60):471--479.
-
-\bibitem{hirsch05}
-Hirsch JE.
-\newblock An index to quantify an individual's scientific research output.
-\newblock Proceedings of the National Academy of Sciences of the United States
-  of America. 2005;102(46):16569--16572.
-
-\bibitem{briscoe06}
-Briscoe T, Carroll J, Watson R.
-\newblock The Second Release of the {RASP} System.
-\newblock In: Curran J, editor. Proceedings of the COLING/ACL 2006 Interactive
-  Presentation Sessions. ACL. Sydney, Australia: ACM; 2006. p. 77--80.
-
-\bibitem{dunning93}
-Dunning T.
-\newblock Accurate Methods for the Statistics of Surprise and Coincidence.
-\newblock Computational Linguistics. 1993;19(1):61--74.
-
-\bibitem{jordanous10a}
-Jordanous A.
-\newblock Defining Creativity: Finding Keywords for Creativity Using Corpus
-  Linguistics Techniques.
-\newblock In: Proceedings of the International Conference on Computational
-  Creativity. Lisbon, Portugal; 2010. p. 278--287.
-
-\bibitem{lin98}
-Lin D.
-\newblock An information-theoretic definition of similarity.
-\newblock In: Proceedings of the 15th International Conference on Machine
-  Learning. Madison, WI; 1998. p. 296--304.
-
-\bibitem{harris68}
-Harris Z.
-\newblock Mathematical Structures of Language.
-\newblock New York: Wiley; 1968.
-
-\bibitem{kilgarriff00}
-Kilgarriff A, Yallop C.
-\newblock What's in a thesaurus.
-\newblock In: Proceedings of the Second Conference on Language Resources and
-  Evaluation (LREC-00). Athens; 2000. p. 1371--1379.
-
-\bibitem{leech92}
-Leech G.
-\newblock 100 million words of {English}: the {British National Corpus (BNC)}.
-\newblock Language Research. 1992;28(1):1--13.
-
-\bibitem{weeds03}
-Weeds JE.
-\newblock Measures and Applications of Lexical Distributional Similarity [PhD
-  thesis].
-\newblock Informatics, University of Sussex. Brighton, UK; 2003.
-
-\bibitem{mannschu99}
-Manning C, Sch{\"u}tze H.
-\newblock Foundations of Statistical Natural Language Processing.
-\newblock Cambridge, MA: MIT Press; 1999.
-
-\bibitem{weedsweir03}
-Weeds J, Weir D.
-\newblock Finding and evaluating nearest neighbours.
-\newblock In: Archer D, Rayson P, Wilson A, McEnery T, editors. Proceedings of
-  the 2nd International Conference of Corpus Linguistics. Lancaster, UK: UCREL;
-  2003. p. 879--888.
-
-\bibitem{mccanavi09}
-McCarthy D, Navigli R.
-\newblock The {English} lexical substitution task.
-\newblock Language Resources and Evaluation: Special Issue on Computational
-  Semantic Analysis of Language. 2009;43(3):139--159.
-
-\bibitem{biemann06}
-Biemann C.
-\newblock Chinese {Whispers}: an efficient graph clustering algorithm and its
-  application to natural language processing problems.
-\newblock In: Proceedings of TextGraphs: the First Workshop on Graph Based
-  Methods for Natural Language Processing. Morristown, NJ: Association for
-  Computational Linguistics; 2006. p. 73--80.
-
-\bibitem{mackinnon70}
-MacKinnon DW.
-\newblock Creativity: a Multi-Faceted Phenomenon.
-\newblock In: Roslansky JD, editor. Creativity: A Discussion at the Nobel
-  Conference. Amsterdam, The Netherlands: North-Holland Publishing Company;
-  1970. p. 17--32.
-
-\bibitem{jordanous12jims}
-Jordanous A, Keller B.
-\newblock What makes musical improvisation creative?
-\newblock Journal of Interdisciplinary Music Studies. 2012;6:151--175.
-
-\bibitem{fellbaum98}
-Fellbaum C, editor.
-\newblock WordNet: An electronic lexical database.
-\newblock Cambridge, MA: The MIT press; 1998.
-
-\bibitem{miller08}
-Miller P, Styles R, Heath T.
-\newblock Open data commons, a license for open data.
-\newblock In: Bizer C, Heath T, Idehen K, Berners-Lee T, editors. Proceedings
-  of the WWW2008 Workshop on Linked Data on the Web. vol. 369 of CEUR-WS.
-  Beijing, China: CEUR; 2008. p.~8.
-
-\bibitem{jordanous12cc}
-Jordanous A.
-\newblock A Standardised Procedure for Evaluating Creative Systems:
-  Computational Creativity Evaluation Based on What it is to be Creative.
-\newblock Cognitive Computation. 2012;4(3):246--279.
-
-\bibitem{jordanousphd}
-Jordanous A.
-\newblock Evaluating Computational Creativity: A Standardised Procedure for
-  Evaluating Creative Systems and its Application [PhD thesis].
-\newblock University of Sussex. Brighton, UK; 2012.
-
-\bibitem{jordanous16aisb}
-Jordanous A.
-\newblock The longer term value of creativity judgements in computational
-  creativity.
-\newblock In: al~Rifaie MM, McGregor S, editors. {AISB} Symposium on
-  Computational Creativity (CC2016). Sheffield, UK: AISB; 2016. p. 16--23.
-
-\bibitem{boden99}
-Boden MA.
-\newblock Introduction [summary of {B}oden's keynote address to {AISB}'99].
-\newblock In: AISB Quarterly - Special issue on AISB99: Creativity in the arts
-  and sciences. vol. 102; 1999. p.~11.
-
-\bibitem{jordanous15vem}
-Jordanous A, Allington D, Dueck B.
-\newblock Measuring cultural value using social network analysis: a case study
-  on valuing electronic musicians.
-\newblock In: Proceedings of the Sixth International Conference on
-  Computational Creativity June; 2015. p. 110.
-
-\bibitem{panglee08}
-Pang B, Lee L.
-\newblock Opinion mining and sentiment analysis.
-\newblock Foundation and Trends in Information Retrieval. 2008;2(1-2):1--135.
-
-\end{thebibliography}
-
-%\bibliography{references}
-
-%\begin{thebibliography}{10}
-%\bibitem{bib1}
-%Devaraju P, Gulati R, Antony PT, Mithun CB, Negi VS.
-Susceptibility to SLE in South Indian Tamils may be influenced by genetic selection pressure on TLR2 and TLR9 genes.
-Mol Immunol.
-2014 Nov 22.
-pii: S0161-5890(14)00313-7.
-doi: 10.1016/j.molimm.2014.11.005
-%
-%\bibitem{bib2}
-%Huynen MMTE, Martens P, Hilderlink HBM. The health impacts of globalisation: a conceptual framework. Global Health. 2005;1: 14. Available: http://www.globalizationandhealth.com/content/1/1/14.
-%
-%\end{thebibliography}
-
 \end{document}

### 2016-09-12 plosOneJordanousKeller/PAPER/S1_appendix.tex
making two appendixes file

@@
 
-\section*{S2 Appendix}\label{S2_Appendix}
-{\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
-
-\begin{itemize}
-\item C.
+%
+%\section*{S2 Appendix}\label{S2_Appendix}
+%{\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
+%
+%\begin{itemize}
+%\item C.
 Ames and J.
@@
 % Cited by:  (since 1996) 639.
-\item J. Anderson and D. Gerbing. Structural equation modeling in practice: A review and recommended two-step approach. Psychological Bulletin, 103(3):411-423, 1988. % Cited by:  (since 1996) 3884.
-\item J. Arnett. Emerging adulthood: A theory of development from the late teens through the twenties. American Psychologist, 55(5):469-480, 2000. % Cited by:  (since 1996) 800.
-\item M.
+%\item J. Anderson and D. Gerbing. Structural equation modeling in practice: A review and recommended two-step approach. Psychological Bulletin, 103(3):411-423, 1988. % Cited by:  (since 1996) 3884.
+%\item J. Arnett. Emerging adulthood: A theory of development from the late teens through the twenties. American Psychologist, 55(5):469-480, 2000. % Cited by:  (since 1996) 800.
+%\item M.
 Arulampalam, S.
@@
 % Cited by:  (since 1996) 1984.
-\item A. Baddeley. Exploring the central executive. Quarterly Journal of Experimental Psychology Section A: Human Experimental Psychology, 49(1):5-28, 1996. % Cited by:  (since 1996) 672.
-\item T.
+%\item A. Baddeley. Exploring the central executive. Quarterly Journal of Experimental Psychology Section A: Human Experimental Psychology, 49(1):5-28, 1996. % Cited by:  (since 1996) 672.
+%\item T.
 Baker, M.
@@
 % Cited by:  (since 1996) 177.
-\item P.
+%\item P.
 Barnett and I.
@@
 % Cited by:  (since 1996) 366.
-\item J. Baron. Nonconsequentialist decisions. Behavioral and Brain Sciences, 17(1):1-42, 1994. % Cited by:  (since 1996) 68.
-\item F. Beach. The snark was a boojum. American Psychologist, 5(4):115-124, 1950. % Cited by:  (since 1996) 32.
-\item M.
+%\item J. Baron. Nonconsequentialist decisions. Behavioral and Brain Sciences, 17(1):1-42, 1994. % Cited by:  (since 1996) 68.
+%\item F. Beach. The snark was a boojum. American Psychologist, 5(4):115-124, 1950. % Cited by:  (since 1996) 32.
+%\item M.
 Belkin, P.
@@
 % Cited by:  (since 1996) 145.
-\item G.
+%\item G.
 Bonanno.
@@
 % Cited by:  (since 1996) 352.
-\item T. Chan and L. Vese. Active contours without edges. IEEE Transactions on Image Processing, 10(2):266-277, 2001. % Cited by:  (since 1996) 1520.
-\item H. Cheng and J. Schweitzer. Cultural values reflected in Chinese and U.S. television commercials. Journal of Advertising Research, 36(3):27-45, 1996. % Cited by:  (since 1996) 88.
-\item C. Coello Coello. Evolutionary multi-objective optimization: A historical view of the field. IEEE Computational Intelligence Magazine, 1(1):28-36, 2006. % Cited by:  (since 1996) 109.
-\item D.
+%\item T. Chan and L. Vese. Active contours without edges. IEEE Transactions on Image Processing, 10(2):266-277, 2001. % Cited by:  (since 1996) 1520.
+%\item H. Cheng and J. Schweitzer. Cultural values reflected in Chinese and U.S. television commercials. Journal of Advertising Research, 36(3):27-45, 1996. % Cited by:  (since 1996) 88.
+%\item C. Coello Coello. Evolutionary multi-objective optimization: A historical view of the field. IEEE Computational Intelligence Magazine, 1(1):28-36, 2006. % Cited by:  (since 1996) 109.
+%\item D.
 Comaniciu and P.
@@
 % Cited by:  (since 1996) 1613
-\item L. Cronbach and L. Furby. How we should measure `change': Or should we? Psychological Bulletin, 74(1):68-80, 1970. % Cited by: (since 1996) 526.
-\item M. Davis. Measuring individual differences in empathy: Evidence for a multidimensional approach. Journal of Personality and Social Psychology, 44(1):113-126, 1983. % Cited by:  (since 1996) 631.
-\item J. Dem\~{s}ar. Statistical comparisons of classifiers over multiple data sets. Journal of Machine Learning Research, 7:1-30, 2006. % Cited by:  (since 1996) 389.
-\item M.
+%\item L. Cronbach and L. Furby. How we should measure `change': Or should we? Psychological Bulletin, 74(1):68-80, 1970. % Cited by: (since 1996) 526.
+%\item M.
+Davis.
+Measuring individual differences in empathy: Evidence for a multidimensional approach.
+Journal of Personality and Social Psychology, 44(1):113-126, 1983.
+% Cited by:  (since 1996) 631.
+%\item J. Dem\~{s}ar. Statistical comparisons of classifiers over multiple data sets. Journal of Machine Learning Research, 7:1-30, 2006. % Cited by:  (since 1996) 389.
+%\item M.
 Dorigo, M.
@@
 % Cited by:  (since 1996) 134.
-\item E.
+%\item E.
 Fischer and J.
@@
 % Cited by:  (since 1996) 189.
-\item J. Gibson. Observations on active touch. Psychological Review, 69(6):477-491, 1962. % Cited by:  (since 1996) 179.
-\item A.
+%\item J. Gibson. Observations on active touch. Psychological Review, 69(6):477-491, 1962. % Cited by:  (since 1996) 179.
+%\item A.
 Gopnik and J.
@@
 % Cited by:  (since 1996) 314.
-\item S.
+%\item S.
 Gosling, S.
@@
 % Cited by:  (since 1996) 313.
-\item J. Gray. The psychophysiological basis of introversion-extraversion. Behaviour Research and Therapy, 8(3):249-266, 1970. % Cited by:  (since 1996) 225.
-\item B. Grosz and S. Kraus. Collaborative plans for complex group action. Artificial Intelligence, 86(2):269- 357, 1996. % Cited by:  (since 1996) 275.
-\item P. Groves and R. Thompson. Habituation: A dual-process theory. Psychological Review, 77(5):419-450, 1970. % Cited by:  (since 1996) 375.
-\item M.
+%\item J. Gray. The psychophysiological basis of introversion-extraversion. Behaviour Research and Therapy, 8(3):249-266, 1970. % Cited by:  (since 1996) 225.
+%\item B. Grosz and S. Kraus. Collaborative plans for complex group action. Artificial Intelligence, 86(2):269- 357, 1996. % Cited by:  (since 1996) 275.
+%\item P. Groves and R. Thompson. Habituation: A dual-process theory. Psychological Review, 77(5):419-450, 1970. % Cited by:  (since 1996) 375.
+%\item M.
 Hall, J.
@@
 % Cited by:  (since 1996) 161.
-\item F. Happ\'{e}. The role of age and verbal ability in the theory of mind task performance of subjects with autism. Child development, 66(3):843-855, 1995. % Cited by:  (since 1996) 285.
-\item C. Harland. Supply chain management: Relationships, chains and networks. British Journal of Management, 7(SPEC. ISS.):S63-S80, 1996. % Cited by:  (since 1996) 172.
-\item S.
+%\item F. Happ\'{e}. The role of age and verbal ability in the theory of mind task performance of subjects with autism. Child development, 66(3):843-855, 1995. % Cited by:  (since 1996) 285.
+%\item C. Harland. Supply chain management: Relationships, chains and networks. British Journal of Management, 7(SPEC. ISS.):S63-S80, 1996. % Cited by:  (since 1996) 172.
+%\item S.
 Hayes, K.
@@
 % Cited by:  (since 1996) 168.
-\item J.
+%\item J.
 Hirsch and K.
@@
 % Cited by:  (since 1996) 243.
-\item P. Killeen. Mathematical principles of reinforcement. Behavioral and Brain Sciences, 17(1):105-172, 1994. % Cited by:  (since 1996) 86.
-\item P.
+%\item P. Killeen. Mathematical principles of reinforcement. Behavioral and Brain Sciences, 17(1):105-172, 1994. % Cited by:  (since 1996) 86.
+%\item P.
 Kirschner, J.
@@
 % Cited by:  (since 1996) 139.
-\item S. Liao. Notes on the homotopy analysis method: Some definitions and theorems. Communications in Nonlinear Science and Numerical Simulation, 14(4):983-997, 2009. % Cited by:  (since 1996) 56.
-\item C.
+%\item S. Liao. Notes on the homotopy analysis method: Some definitions and theorems. Communications in Nonlinear Science and Numerical Simulation, 14(4):983-997, 2009. % Cited by:  (since 1996) 56.
+%\item C.
 Lord, L.
@@
 % Cited by:  (since 1996) 523.
-\item S. Luthar, D. Cicchetti, and B. Becker. The construct of resilience: A critical evaluation and guidelines for future work. Child Development, 71(3):543-562, 2000. % Cited by:  (since 1996) 566.
-\item G. Mandler. Recognizing: The judgment of previous occurrence. Psychological Review, 87(3):252-271, 1980. % Cited by:  (since 1996) 877.
-\item G. Miller and J. Selfridge. Verbal context and the recall of meaningful material. The American journal of psychology, 63(2):176-185, 1950. % Cited by:  (since 1996) 57.
-\item S.
+%\item S. Luthar, D. Cicchetti, and B. Becker. The construct of resilience: A critical evaluation and guidelines for future work. Child Development, 71(3):543-562, 2000. % Cited by:  (since 1996) 566.
+%\item G. Mandler. Recognizing: The judgment of previous occurrence. Psychological Review, 87(3):252-271, 1980. % Cited by:  (since 1996) 877.
+%\item G. Miller and J. Selfridge. Verbal context and the recall of meaningful material. The American journal of psychology, 63(2):176-185, 1950. % Cited by:  (since 1996) 57.
+%\item S.
 Miller.
@@
 % Cited by:  (since 1996) 385.
-\item G. Navarro and V. M\"{a}kinen. Compressed full-text indexes. ACM Computing Surveys, 39(1), 2007. % Cited by:  (since 1996) 62.
-\item M. Nissen and P. Bullemer. Attentional requirements of learning: Evidence from performance measures. Cognitive Psychology, 19(1):1-32, 1987. % Cited by:  (since 1996) 729.
-\item J.
+%\item G. Navarro and V. M\"{a}kinen. Compressed full-text indexes. ACM Computing Surveys, 39(1), 2007. % Cited by:  (since 1996) 62.
+%\item M. Nissen and P. Bullemer. Attentional requirements of learning: Evidence from performance measures. Cognitive Psychology, 19(1):1-32, 1987. % Cited by:  (since 1996) 729.
+%\item J.
 Payne, J.
@@
 % Cited by:  (since 1996) 300.
-\item J. Prochaska, C. DiClemente, and J. Norcross. In search of how people change: Applications to addictive behaviors. American Psychologist, 47(9):1102-1114, 1992. % Cited by:  (since 1996) 2742.
-\item T.
+%\item J. Prochaska, C. DiClemente, and J. Norcross. In search of how people change: Applications to addictive behaviors. American Psychologist, 47(9):1102-1114, 1992. % Cited by:  (since 1996) 2742.
+%\item T.
 Richardson, M.
@@
 % Cited by:  (since 1996) 1162.
-\item W. Rozeboom. The fallacy of the null-hypothesis significance test. Psychological Bulletin, 57(5):416-428, 1960. % Cited by:  (since 1996) 133.
-\item C.
+%\item W. Rozeboom. The fallacy of the null-hypothesis significance test. Psychological Bulletin, 57(5):416-428, 1960. % Cited by:  (since 1996) 133.
+%\item C.
 Rusbult.
@@
 % Cited by:  (since 1996) 301.
-\item T. Ryan. Significance tests for multiple comparison of proportion, variance, and other statistics. Psychological Bulletin, 57(4):318-328, 1960. % Cited by:  (since 1996) 154.
-\item W. Schultz. Behavioral theories and the neurophysiology of reward. Annual Review of Psychology, 57:87-115, 2006. % Cited by:  (since 1996) 226.
-\item E. Sirin, B. Parsia, B. Grau, A. Kalyanpur, and Y. Katz. Pellet: A practical OWL-DL reasoner. Web Semantics, 5(2):51-53, 2007. % Cited by:  (since 1996) 125.
-\item T.
+%\item T. Ryan. Significance tests for multiple comparison of proportion, variance, and other statistics. Psychological Bulletin, 57(4):318-328, 1960. % Cited by:  (since 1996) 154.
+%\item W. Schultz. Behavioral theories and the neurophysiology of reward. Annual Review of Psychology, 57:87-115, 2006. % Cited by:  (since 1996) 226.
+%\item E. Sirin, B. Parsia, B. Grau, A. Kalyanpur, and Y. Katz. Pellet: A practical OWL-DL reasoner. Web Semantics, 5(2):51-53, 2007. % Cited by:  (since 1996) 125.
+%\item T.
 Srull and R.
@@
 % Cited by:  (since 1996) 374.
-\item J. Steiger. Tests for comparing elements of a correlation matrix. Psychological Bulletin, 87(2):245-251, 1980. % Cited by:  (since 1996) 705.
-\item L.
+%\item J. Steiger. Tests for comparing elements of a correlation matrix. Psychological Bulletin, 87(2):245-251, 1980. % Cited by:  (since 1996) 705.
+%\item L.
 Steinberg, S.
@@
 % Cited by:  (since 1996) 435.
-\item D. Tao, X. Li, X. Wu, W. Hu, and S. Maybank. Supervised tensor learning. Knowledge and Information Systems, 13(1):1-42, 2007. % Cited by:  (since 1996) 54.
-\item A.
+%\item D. Tao, X. Li, X. Wu, W. Hu, and S. Maybank. Supervised tensor learning. Knowledge and Information Systems, 13(1):1-42, 2007. % Cited by:  (since 1996) 54.
+%\item A.
 Tellegen, D.
@@
 % Cited by:  (since 1996) 398.
-\item L.
+%\item L.
 Thomas and D.
@@
 % Cited by:  (since 1996) 339.
-\item I. Thompson. Coupled reaction channels calculations in nuclear physics. Computer Physics Reports, 7(4):167-212, 1988. % Cited by:  (since 1996) 360.
-\item E. Tulving. Subjective organization in free recall of ``unrelated'' words. Psychological Review, 69(4):344- 354, 1962. % Cited by:  (since 1996) 121.
-\item U. Von Luxburg. A tutorial on spectral clustering. Statistics and Computing, 17(4):395-416, 2007. % Cited by:  (since 1996) 107.
-\item J. Williams, A. Mathews, and C. MacLeod. The emotional stroop task and psychopathology. Psychological Bulletin, 122(1):3-24, 1996. % Cited by:  (since 1996) 716.
-\item J.
+%\item I. Thompson. Coupled reaction channels calculations in nuclear physics. Computer Physics Reports, 7(4):167-212, 1988. % Cited by:  (since 1996) 360.
+%\item E. Tulving. Subjective organization in free recall of ``unrelated'' words. Psychological Review, 69(4):344- 354, 1962. % Cited by:  (since 1996) 121.
+%\item U. Von Luxburg. A tutorial on spectral clustering. Statistics and Computing, 17(4):395-416, 2007. % Cited by:  (since 1996) 107.
+%\item J. Williams, A. Mathews, and C. MacLeod. The emotional stroop task and psychopathology. Psychological Bulletin, 122(1):3-24, 1996. % Cited by:  (since 1996) 716.
+%\item J.
 Wright, A.
@@
 % Cited by:  (since 1996) 46.
-\end{itemize}
+%\end{itemize}
 

### 2016-09-12 plosOneJordanousKeller/PAPER/S2_appendix.tex
making two appendixes file

--- 2016-09-07 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
@@
-% Template for PLoS
-% Version 3.1 February 2015
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
-% the final text of your manuscript.
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig." instead of "Figure".
-% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout or alignment
-% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
-% - colors, shading, or graphic objects
-% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
-%
-% Please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
 \documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% fixltx2e package for \textsubscript
-\usepackage{fixltx2e}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-%\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-\usepackage{rotating}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-
-% Use strikethrough for track changes 
-\usepackage[normalem]{ulem}
-% command is \sout{text text text etc}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
-
 \begin{document}
-\vspace*{0.35in}
-
-% Title must be 250 characters or less.
-% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
-\begin{flushleft}
-{\Large
-\textbf\newline{Modelling Creativity: Identifying Key Components through a Corpus-Based Approach}
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Anna Jordanous\textsuperscript{1,\Yinyang, *},
-Bill Keller\textsuperscript{2,\Yinyang}
-\\
-\bigskip
-\bf{1} School of Computing, University of Kent, Chatham Maritime, Kent, UK
-\\
-\bf{2} Department of Informatics, University of Sussex, Falmer, Brighton, UK
-\\
-\bigskip
-
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
-
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-%\ddag These authors also contributed equally to this work.
-
-% Current address notes
-%\textcurrency a Insert current address of first author with an address update
-% \textcurrency b Insert current address of second author with an address update
-% \textcurrency c Insert current address of third author with an address update
-
-% Deceased author note
-%\dag Deceased
-
-% Group/Consortium Author Note
-%\textpilcrow Membership list can be found in the Acknowledgments section.
-
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* a.k.jordanous@kent.ac.uk / billk@sussex.ac.uk
-
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-
-Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
-If we wish to study creativity scientifically, then a tractable and well-articulated model of creativity is required.
-Such a model would be of great value to researchers investigating the nature of creativity and in particular, those concerned with the evaluation of creative practice.
-This paper describes a unique approach to developing a suitable model of how creative behaviour emerges that is based on the words people use to describe the concept.
-Using techniques from the field of statistical natural language processing, we identify a collection of fourteen key components of creativity through an analysis of a corpus of academic papers on the topic.
-Words are identified which appear significantly often in connection with discussions of the concept.
-Using a measure of lexical similarity to help cluster these words, a number of distinct themes emerge, which collectively contribute to a comprehensive and multi-perspective model of creativity.
-The components provide an ontology of creativity: a set of building blocks which can be used to model creative practice in a variety of domains.
-The components have been employed in two case studies to evaluate the creativity of computational systems and have proven useful in articulating achievements of this work and directions for further research.
-
-\linenumbers
-
-\section*{Introduction}\label{intro}
-
-%Currently, most content on the Semantic Web is in the form of ontologies of `things': semantically structured collections of factual or objective data on topics as diverse as people \cite{foaf}, places \cite{geonames}, music \cite{musicOntology} or manuscripts \cite{sawsOntology}.
-The focus in Semantic Web research has generally been on reducing ambiguity in representations of these more structured domains and concepts, rather than directly tackling the representation and machine-readable representation of subjective, unstructured concepts in an ontology.
-However, cognitive science research and work on lexical resources such as WordNet \cite[$http://wordnet.rkbexplorer.com$]{fellbaum98} have laid foundations for more definitionally troublesome concepts to be considered in detail.
-The time is ripe for developing ontologies of subjective concepts such as creativity.
-
-What is creativity, and how can we better understand and learn about creativity using computational modelling?
-Computational creativity is a relatively youthful research area that has been growing with significant pace in recent years.
-Computational creativity is:
-\begin{quote}`The philosophy, science and engineering of computational systems which, by taking on particular responsibilities, exhibit behaviours that unbiased observers would deem to be creative.' 
-\cite[p. 21]{coltonwiggins12}
-\end{quote}
-
-Computational creativity research follows both theoretical and practical directions and crosses several disciplinary boundaries between the arts, sciences, and engineering.
-Research within the field is influenced by artificial intelligence, computer science, psychology and specific creative domains that have received attention from computational creativity researchers to date, such as art, music, reasoning and narrative/story telling \cite[provide examples]{colton08,widmerAIM09,leon10MM,perezyperez99}.
-
-The evaluation of creative systems developed by researchers in the field of computational creativity has proven non-trivial.
-Creativity evaluation, a recurring topic for discussion, has been described as a `Grand Challenge' for computational creativity research \cite{cardoso09}.
-Difficulties are inherently linked to a question that both motivates and complicates the computational modelling of creativity: what  do we mean when we talk about `creativity' and what does it constitute?
-
-Creativity is a complex, multi-faceted concept encompassing a variety of related aspects, abilities, properties and behaviours.
-There have been many attempts to capture this concept in words; indeed the work described in this paper is based on thirty such attempts (see the Methods section and the papers listed in \nameref{S1_Appendix}).
-In the academic literature on creativity, many common themes have emerged. 
-However, multiple viewpoints exist, prioritising different aspects of the concept according to what are traditionally considered to be the primary factors for a particular discipline. 
-The need for a more over-arching, inclusive, multi-dimensional account of creativity has been widely recognised \cite{rhodes61,torrance67,plucker04defn,kaufman09}.
-Such a meta-level account would assist our understanding of creativity, highlighting areas of common ground and avoiding the pitfalls of disciplinary bias \cite{hennessey10,plucker04}.
-
-There are many challenges to modelling a concept like creativity in a computational setting.
-Conceptually, creativity seems inherently fuzzy or vague, with a meaning that shifts depending on the domain of application.
-Tackling these challenges affords two key advantages, both of which motivate the current paper.
-First, we can take advantage of computing and artificial intelligence to perform or enhance creative activities using computational power and research expertise.
-Secondly, the act of modelling creativity requires us to more carefully identify what informs our intuitive notions about creativity and this can guide us towards a more rigorous and comprehensive understanding of the concept.
-
-The aim of the work reported in this paper is to examine the nature of creativity and to identify within it a set of components, representing key dimensions, that are recognised across a combination of different viewpoints.
-We present a novel, empirical approach to the problem of modelling how creative behaviour is manifested, that focuses on what is revealed about our understanding of creativity and its attributes by the words we use to discuss and debate the nature of the concept.
-Analysis of this language provides a sound basis for constructing a sufficiently detailed and comprehensive model of creativity \cite{lakoff87,wittgenstein58}.
-The current work is intended as a significant, methodological contribution towards addressing the Grand Challenge of evaluation in computational creativity research.
-It should provide researchers with a firm foundation for evaluating exactly how creative so-called {\emph creative systems} actually are.
-
-On our approach, statistical language processing techniques are used to identify words significantly associated with creativity in a corpus of academic papers on the subject.
-A corpus spanning some 60 years of research into the nature of creativity was collected together.
-The papers were gathered from a wide variety of disciplines including psychology, educational testing and computational creativity, amongst others.
-The language data drawn from this collection was then analysed and contrasted with data from a corpus of matched papers on subjects unrelated to creativity.
-From this analysis, a set of 694 {\em creativity words\/} was identified, where each creativity word appeared significantly more often than expected in the corpus of creativity papers.
-A measure of lexical similarity provided a basis for clustering the creativity words into groups of words with similar or shared aspects of meaning.
-Through inspection of these clusters, a total of fourteen {\em key components of creativity\/} was identified, where each represents a key theme or attribute of creativity.
-The set of components yields information about the nature of creativity, based on what is collectively emphasised in discussions about the concept.
-
-% The Semantic Web has emerged as a way to address the troublesome but important issue \cite{boden99} of articulating values, concepts and information using an open and  {\em machine-understandable} vocabulary.
-Encoding the creativity components in an OWL ontology has enabled this {\em ontology of creativity} to be made publicly available to the wider research community as a resource in the Semantic Web, under the permanent URL:
-%\begin{quote}
-%{\small \texttt{http://purl.org/creativity/ontology}}
-%\end{quote}
-
-In the rest of this section we begin by noting a variety of attempts to define creativity. The representation of subjective, ambiguous, loosely structured concepts is considered.
-%, both from the perspective of current Semantic Web research and from a broader conceptual perspective. 
-In the remaining sections, details are provided of the methodology used to identify components of creativity from an analysis of language data.
-The results of this analysis are then presented in terms of a model that encompasses fourteen key components.
-The derived set of components is evaluated in terms of how well it satisfies the need for a shared, inclusive and comprehensive account of creativity and provides a vocabulary of creativity that is accessible to both people and machines.
-Finally, conclusions are drawn and some directions for further work are outlined.
-
-\subsection*{Background:  The nature of creativity} \label{background}
-
-As Torrance observes:
-
-\begin{quote}
-`[c]reativity defies precise definition ... even if we had a precise conception of creativity, I am certain we would have difficulty putting it into words' \cite[p. 43]{torrance88}. 
-\end{quote}
-
-Many other authors have expressed similar difficulties \cite{rhodes61,sternberg99a,kaufman09}. 
-In their review of research into human creativity, Hennessey and Amabile ask a significant follow-on question: 
-\begin{quote}
-`Even if this mysterious phenomenon can be isolated, quantified, and dissected, why bother? Wouldn't it make more sense to revel in the mystery and wonder of it all?' 
-\cite[p. 570]{hennessey10}
-\end{quote}
-
-\noindent Two answers to this question are offered by Hennessey and Amabile, both of which are identified as desirable: to gain a deeper understanding of creativity and to learn how to boost people's creativity.
-
-Creativity can and should be studied and measured scientifically, but the lack of a commonly-agreed understanding causes problems for measurement \cite{kaufman09}.
-Plucker et al.
-make recommendations about best practice based on their own survey of the creativity literature:
-\begin{quote}
-\noindent
-`we argue that creativity researchers must
-
-\begin{enumerate}
-\renewcommand{\labelenumi}{(\alph{enumi})}
-\item explicitly define what they mean by creativity,
-\item avoid using scores of creativity measures as the sole definition of creativity (e.g., creativity is what creativity tests measure and creativity tests measure creativity, therefore we will use a score on a creativity test as our outcome variable),
-\item discuss how the definition they are using is similar to or different from other definitions, and
-\item address the question of creativity for whom and in what context.' \cite[p.92]{plucker04defn}
-\end{enumerate}
-\end{quote}
-
-\noindent In short, we need to specify and justify the standards that we use to judge creativity.
-A more objective and well-articulated account of how creativity is manifested enables researchers to make a worthwhile contribution \cite{torrance67,plucker04defn,kaufman09}.
-Particularly, in research we would like to focus on what processes and concepts relevant to creativity are `sufficiently important to warrant study' \cite[p.
-15]{vartanian14}, based on an {\em accumulation} of the body of work on creativity to date \cite{vartanian14}.
-
-\paragraph{Definitions of creativity.}
-\label{existing_defs}
-
-To find out the meaning of a word, a natural first step might be to consult a dictionary.
-Dictionary definitions of creativity provide a brief introduction to  the meaning of the word.
-However, for the purposes of research, the utility of such definitions is severely restricted by their format and brevity, and they generally provide only cursory, shallow insights into the nature of creativity.
-More problematic still, dictionary entries are often self-referential or circular,  defining creativity in terms of ``being creative'' or ``creative ability''.
-To illustrate these limitations, there follow several typical dictionary definitions of creativity and the related words `creative' and `create'.
-For readability, some definitions are edited slightly to standardise formats and remove etymological/grammatical annotations:
-\begin{quotation}
-\begin{description}
-\item {\em Oxford English Dictionary} 2nd ed. (1989) pp. 1134-5:
-	\begin{enumerate}
-	\item[creativity:] creative power or faculty; ability to create
-	\item [creative:] Having the quality of creating, able to create; of or relating to creation; originative.
-b.
-Inventive, imaginative; of, relating to, displaying, using, or involving imagination or original ideas as well as routine skill or intellect, esp.
-in literature or art.
-c.
-Esp.
-of a financial or other strategy: ingenious, esp.
-in a misleading way.
-2.
-Providing the cause or occasion of, productive of.
-\item [create:] 1.a.
-Said of the divine agent: To bring into being, cause to exist; esp.
-to produce where nothing was before, 'to form out of nothing'.
-b.
-with complemental extension.
-2.
-To make, form, constitute, or bring into legal existence (an institution, condition, action, mental product, or form, not existing before).
-Sometimes of material works.
-3.
-To constitute (a personage of rank or dignity); to invest with rank, title, etc.
-4.
-To cause, occasion, produce, give rise to (a condition or set of circumstances).
-	\end{enumerate}
-\item {\em The Penguin English Dictionary} 2nd ed. (1969) p. 174:
-	\begin{enumerate}
-	\item[creativity:] creative power or faculty; ability to create
-	\item[creative:] having power to create; related to process of creation; constructive, original, producing an essentially new product; produced by original intellectual or artistic effort 
-	\item [create:] make out of nothing, bestow existence on; cause, bring about; produce or make something new or original; confer new rank etc on; (theat) be the first to act (a certain part); make a fuss
-	\end{enumerate}
-\item {\em Webster's 3rd New International Dictionary} (1961) p. 532:
-	\begin{enumerate}
-	\item[creativity:] the quality of being creative; ability to create 
-	\item[creative:] 1.
-having the power or quality of creating; given to creation 2: PRODUCTIVE - used with 3: having the quality of something created rather than imitated or assembled; expressive of the maker; IMAGINATIVE
-	\item[create:] 1: to bring into existence; make out of nothing and for the first time 2: to cause to be or to produce by fiat or by mental, moral, or legal action 3: to cause or occasion - used of natural or physical causes and esp.
-of social and evolutionary or emergent forces 4a: to produce (as a work of art or of dramatic interpretation) along new or unconventional lines) b: to design (as a costume or dress)
-	\end{enumerate}
-\end{description}
-\end{quotation}
-
-Given the problems inherent in dictionary definitions of creativity, it is not surprising that a number of creativity researchers have set out  to provide their own definitions of the concept.
-Some examples are:
-
-\begin{quotation}
-\begin{quote}
- `creativity is that process which results in a novel work that is accepted as tenable or useful or satisfying by a group at some point in time' %By this definition we limit ourselves to the study of individuals who are regarded as creative by ``significant others'' in their environment.'
-\cite[p. 218]{stein63}
-\end{quote}
-%\begin{quote}
-%`A product or response will be judged as creative to the extent that (a) it is both a novel and appropriate, useful, correct or valuable response to the task at hand, and (b) the task is heuristic rather than algorithmic.'
-%\cite[p. 35]{amabile96}
-%\end{quote}
-\begin{quote}
-`Creativity is the ability to produce work that is both novel (i.e., original, unexpected) and appropriate (i.e., useful, adaptive concerning task constraints)'
-\cite[p. 3]{sternberg99a}
-\end{quote}
-\begin{quote}
-`Creativity is the ability to come up with ideas or artefacts that are {\em new}, {\em surprising and valuable}'
-\cite[p. 1]{boden04}
-\end{quote}
-\begin{quote}
-`Creativity is the interaction among \emph{aptitude, process, and environment} by which an individual or group produces a \emph{perceptible product} that is both \emph{novel and useful} as defined within a \emph{social context}'
-\cite[p. 90]{plucker04defn}
-\end{quote}
-\begin{quote}
-`Creativity: the generation of products or ideas that are both novel and appropriate' 
-\cite[p. 570]{hennessey10}
-\end{quote}
-\begin{quote}
-`The word creativity is a noun naming the phenomenon in which a person communicates a new concept (which is the product).
-Mental activity (or mental process) is implicit in this definition, and of course no one could conceive of a person living or operating in a vacuum, so the term \emph{press} is also implicit'
-\cite[p. 305]{rhodes61}
-\end{quote}
-\end{quotation}
-
-These more research-oriented definitions avoid the problems of self-reference and circularity noted for the dictionary entries given previously.
-However, whilst the definitions may provide somewhat deeper insight into the nature of creativity, the brevity of the definitions means that they still only succeed in providing shallow, summary accounts of the concept.
-
-\paragraph{A multitude of different perspectives} \label{perspectives}
-
-The problem of identifying and quantifying creativity exists across many disciplines.
-How creative is this person?
-Does this person have the creative abilities to boost my business?
-Is this pupil's story creative?
-Is this computational system an example of computational creativity?
-As a consequence, when attempts are made to define creativity, it is often from the perspective of a particular domain or research discipline.
-For example, psychometric tests for creativity such as \cite{guilford50,torrance74} focus on {\em problem solving} and {\em divergent thinking} as key attributes of a creative person.
-In contrast, computational creativity research \cite[for example]{pease01,wiggins06ngc,peinado06ngc,ritchie07} has historially placed emphasis on the {\em novelty} and {\em value} of creative products.
-Whilst there is some consensus across academic fields, for example novelty and value are typically recognised as necessary (but arguably not sufficient) components of creativity \cite{mayer99}, the differing emphases contribute to variations in the interpretation of creativity.
-These variations affect consistency across creativity research in different disciplines and potentially hinder interdisciplinary collaborations and cross-application of findings.
-
-Several competing interpretations of creativity exist in the literature.
-Sometimes these differences of opinion do not need to be directly resolved but can be included alongside each other.
-Examples include whether creativity is centred around mental processes \cite{boden04,dietrich10,gabora12} or embodied and situated in an interactive environment \cite{mccormack07,sosa09}.
-Another example is whether creativity is domain-independent \cite{plucker98}, or dependent on domain-specific context \cite{baer98}, or (as both Plucker and Baer have concluded) a combination of both \cite{plucker04,baer10}.
-
-Other conflicts arise where a previously narrow view of creativity has been widened in perspective.
-To resolve the conflict, an inclusive, all-encompassing view of creativity should adopt the wider perspective and incorporate the narrower perspective.
-For example rather than focussing narrowly on creative {\em genius}, through the study of people with exceptional creative achievements \cite[for example]{poincare29,hadamard45} emphasis has shifted to encompass the broader study of {\em everyday} creativity, with genius as a special case: the notion that everyone can be creative to some degree \cite{weisberg88,bryankinns09}.
-
-Similarly, researchers distinguish between {\em little-c} and {\em Big-C} creativity, or {\em psychological/P-creativity} and  {\em historical/H-creativity} \cite{boden04}, adjusting their focus accordingly to make their research more manageable.
-This is particularly the case in computational creativity, where endowing the computer with elements of general, human knowledge and experience is a major challenge.
-Little-c creative or p-creative work is perceived as creative by the creator personally but may replicate existing work (unknown to the creator) so is not necessarily creative in a wider social context.
-This encompasses the concept of Big-C creativity or h-creativity, where the work makes a creative contribution both to the creator and to society.
-To be Big-C creative/h-creative is to be little-c creative/p-creative in a way which has not been done before by anyone.
-
-The preceeding discussion indicates that creativity is a complex, multi-faceted concept that requires a broad and inclusive treatment.
-The {\em Four Ps} framework \cite{rhodes61,stein63,mooney63,odena09,jordanous16cs} ensures we pay attention to four key aspects of creativity:
-
-\begin{description}
-\setlength{\labelwidth}{1.5cm}
-\setlength{\itemindent}{1.5cm}
-\item[Person/Producer:] The individual that is creative
-\item[Process:] What the creative individual does to be creative
-\item[Product:] What is produced as a result of the creative process
-\item[Press:] The environment in which creative activity takes place
-\end{description}
-
-\noindent This framework presents creativity in a broader context, making our understanding of the concept more generally applicable and less specific to a domain or academic discipline.
-In contrast, models of the creative process \cite{wallas26,poincare29,hadamard45}, tests of people's creativity \cite{goldman64,guilford67,torrance74} or tests based on creative artefact generation \cite{amabile96,ritchie07} are useful only within a limited sphere.
-Jordanous \cite{jordanous16cs} has contextualised the Four Ps in a computational context, referring to the creative Producer (person or computational agent) carrying out Processes within the environmental context of a Press, to create computational Products.
-
-\subsection*{The challenges of modelling creativity} \label{cogPhil}
-
-% Was Reflections on the semantics of subjective concepts. Merge this together and make it more relevant to modelling creativity (specifically) rather than the general treatment it is now.
-
-Creativity can be seen as an essentially contested concept \cite{gallie56}: it is subjective, abstract and can be interpreted in a variety of acceptable ways, such that a fixed `proper general use' is elusive \cite[p.
-167]{gallie56}.
-Gallie \cite{gallie56} defines an essentially contested concept through several features: being internally complex in nature, but amenable to being broken down into identifiable constituent elements of varying relative importance, and dependent on a number of factors such as context and individual preference.
-Although there may be consensus on the meaning of such concepts in very general terms, they may defy precise interpretation.
-There is not a single agreed instantiation, but instead many reasonable possibilities, influenced by changing circumstances and contexts.
-It is more productive to acknowledge that these different interpretations exist and refer to `the respective contributions of its various parts or features' \cite[p.
-172]{gallie56}, rather than to argue for a single interpretation.
-Thus, different types of creativity manifest themselves in different ways while sharing certain characteristics (not necessarily the same across all creative instances).
-This is what Wittgenstein refers to as `family resemblances' \cite{wittgenstein58}:
-
-\begin{quote}
-[On discussing the example of what a `game' is] `we see a complicated network of similarities overlapping and criss-crossing: sometimes overall similarities, sometimes similarities of detail.
-...
-I can think of no better expression to characterize these similarities than ``family resemblances''; for the various resemblances between members of a family: build, features, colour of eyes, gait, temperament, etc.
-etc.
-overlap and criss-cross in the same way.
-And I shall say: ``games'' form a family.'
-\cite[Part 1, Paragraphs 66-67]{wittgenstein58}
-\end{quote}
-
-Similarly, with creativity, different manifestations of creativity are not all necessarily required to share the same common, core elements in order to be identified as part of the creativity `family'.
-Rather, relationships between different manifestations reveal various shared characteristics that emerge in a similar way to Wittgenstein's `family resemblances' in language.
-We need to identify what those family resemblances are in the case of creativity.
-To understand creativity, we can investigate what resemblances exist across different instantiations of the concept.
-
-Wittgenstein \cite{wittgenstein58} has argued that `a clear view of the aim and functioning of the words' helps us `dispers[e] the fog' that obscures a clear vision of the `working of language' \cite[Part 1, Paragraph 5]{wittgenstein58}.
-To understand the use of a word, one must have background information and context.
-Wittgenstein gives the example of a chess piece, which is introduced to someone as a `king' \cite[paragraph 31]{wittgenstein58}: to understand this usage the person must already know the rules of chess, or must at least know what it means to have a piece in a game.
-To Wittgenstein, the semantics of words and statements are determined by how we use them, grounded in rules set by our habitual use of a word and our shared consensual practices, rather than being fixed by static, pre-assigned meanings.
-
-%Waismann, a contemporary of Wittgenstein, has reflected on the impact of `open texture' on language, where certain words or phrases simply cannot be completely defined for all possible scenarios:
-
-%\begin{quote}
-%`Every description stretches, as it were, into a horizon of open possibilities: however far I go, I shall always carry this horizon with me.'
-%\cite[p. 122]{waismann68}
-%\end{quote}
-Linguistics research advocates that the meaning of a word is dependent on the context it is used in \cite{firth57}.
-In particular, Lakoff has argued that the study of language helps reveal how people think \cite{lakoff87,lakoff80}.
-Words used frequently in discussions of the nature of a concept provide the context for the commonly understood meaning of that concept, as has been shown in various corpus linguistics contributions \cite{oakes98,rayson00,kilgarriff01,kilgarriff06}.
-
-%We acknowledge that semantic ambiguity is unlikely to be resolved to a single agreed definition.
-Meanings can be dynamic, evolving over time and contextually dependent, rather than being fixed, with a static and unchanging prescribed definition.
-The key principle emerging across these present discussions is that the meaning of words like creativity can be modelled by identifying different aspects that collectively contribute to the meaning of the concept of creativity.
-
-%\subsection*{Subjectivity and ambiguity on the semantic web} \label{SWsubjectivity}
-
-%Ambiguity in semantic interpretation of terms is not an area that Semantic Web research shies away from.
-Ontologies are widely used to pinpoint and define what {\em things} mean in a machine-readable way, for greater clarity and precision in using various vocabularies and identifiers.
-Such research does not concentrate merely on those areas of interest which are simple to define and objectively clear to interpret; for example SKOS \cite{skos} provides vocabulary to organise and taxonomise knowledge, whether explicit or tacit, while FRBR-oo \cite{doerr07} defines various terms to do with bibliographical records and the works and ideas expressed within them, on various conceptual levels beyond merely the physical instantiation of a book or other written document.
-Upper ontologies such as Dolce \cite{gangemi02}, SUMO \cite{niles01} and Cyc \cite{reed02} have guided the objective, disambiguated expression of higher-level, cross-domain, general concepts and abstract knowledge.% An upper ontology defines higher-level vocabularies and concepts necessary to implement ontologies themselves, providing the meta-vocabulary to link specific ontologies to more general concepts.
-
-%What is not often tackled within Semantic Web research are the types of topic discussed above, where ambiguity is unlikely to be resolved to a single agreed definition and meanings are dynamic, changing over time and contextual interpretations, rather than being fixed to a static and unchanging prescribed definition.
-To date, there is a lack of suitable methodologies applied in Semantic Web research to enable or assist the building of ontological representations of such topics.
-Existing ontology construction methodologies tend to concentrate on how to extract and represent data objectively rather than retain subjectivity in the data \cite{fernandez97,noy01,haase08}; the focus is on how best to construct ontologies in an appropriate manner rather than how to tackle {\em moving-target} issues of dynamic, perhaps unresolvable, semantics.
-
-%There is of course much work still to be done in representing semantics on the Semantic Web; much information with fixed semantics is still to be represented in a machine readable form.
-With the growth of the Semantic Web, this ongoing collation and representation of knowledge is work-in-progress.
-As discussed above, advances in other research disciplines can assist progress in areas where there is less agreement generally over semantics.
-The representation of these areas and concepts on the Semantic Web is troublesome, particularly in a framework which is geared towards resolving semantic ambiguity to static, pre-assigned meanings.
-More established disciplines in cognitive science and related areas of research would not claim to have solved all such issues and challenges; however Semantic Web researchers can learn from advances that have been made in these disciplines.
-An approach informed by cross-disciplinary contributions helps Semantic Web research progress towards a broader and more complex coverage of data and their semantics.
-
-The need for a clearer, multi-perspective understanding of creativity is evident, but remains to be addressed.
-There is a large quantity of material contributory to a satisfactory model of creativity and a number of key contributions have been discussed during this section.
-What must be done now is to marshal this assortment of material and to unify different perspectives where possible, in order to avoid the disciplinary `blinkers' or compartmentalisation that is often seen in creativity research \cite{hennessey10}.
-In approaching the semantic representation of subjective and multi-faceted concepts, some useful guidance is offered through philosophical reflections on the meaning of such concepts.
-
-%Further, cognitive science methodologies, {\bf IS THIS NEXT BIT TO GO?} as well as approaches to ontology learning from texts \cite{gomezperez04} {\bf END} can be harnessed to enable the representation of more semantically ambiguous concepts such as creativity
-
-%To date, however, the Semantic Web research community has largely focused on the representation of objective concepts and resources that are relatively clearly defined.
-
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Methods}
-\label{methodology}
-
-Our approach makes use of an empirical study and analysis of the language used to talk about creativity in order to gather and collate knowledge about the concept.
-In addition, following from the observations above, a {\em  confluence approach\/} to creativity is adopted \cite{sternberg99a,mayer99,ivcevic09}.
-This works on the principle that creativity results from several components converging and goes on to examine what these components are.
-Taking this approach in conjunction with the application of tools from computational linguistics and statistical analysis allows a wider disciplinary spectrum of perspectives on creativity to be captured than has previously been attempted.
-This is achieved by breaking down the whole into smaller and more tractable constituent parts identified through a broad cross-disciplinary examination of creativity research.
-
-Tools from natural language processing and statistical analysis are used to identify words that appear to be highly associated with dimensions of creativity, as represented in a sample of academic papers on the topic.
-A key innovation is the use of a statistical measure of lexical similarity, which allows the words to be clustered into coherent and semantically-related groups.
-Clustering reveals a number of common themes or factors of creativity, allowing the identification of a set of fourteen components that serve as building blocks for creativity.
-
-\subsection*{Corpus data}\label{corpusData}
-
-A sample of academic papers discussing the nature of creativity was assembled as a {\em creativity corpus\/} in 2010.
-This creativity corpus consisted of 30 papers examining creativity from various academic stand-points ranging from psychological studies to computational models.
-
-\vspace{0.25cm}
-\begin{center}
-\fbox{
-\begin{minipage}{0.8\linewidth}
-\textbf{Creativity corpus}: \\ a collection of thirty academic papers which explicitly discuss the nature of creativity.
-\end{minipage}
-}
-\end{center}
-\vspace{0.25cm}
-
-The 30 papers selected for the creativity corpus are listed in \nameref{S1_Appendix}. The strategy used to select papers for this corpus is illustrated in a flow diagram, in Fig. \ref{searchCC}.
-
-\begin{figure}[!b]
-\caption{{\bf A flow diagram describing the search strategy used to identify papers for the creativity corpus.}}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/Fig1}
-\label{searchCC}
-\end{figure}
-
-The search strategy for identifying papers for the corpus involved a literature search for the term `creativity' on the academic database {\em Scopus} to identify suitable papers.
-This literature search was supplemented with additional influential papers which may not have appeared in a Scopus search.
-For example, a Computer Science conference paper on cognitive models of creativity has been included, as in Computer Science, a number of conferences carry as much or more publication weight as some journals in the field.
-The eligibility of each identified article was verified for inclusion in the corpus via careful manual inspection.
-
-Paper selection for the creativity corpus was governed by inclusion criteria based on measuring the influence of a paper and coverage of a wide range of years and academic disciplines.
-The inclusion criteria are as follows, listed in descending order of precedence:
-\begin{itemize}
-\item Papers must have, as their primary focus, discussion of the nature of creativity.
-\item Papers should be considered particularly influential.
-Influence was generally measured objectively, in terms of the number of times a paper had been cited by other academic authors.
-However, for papers published in recent years and which had consequently had little time to accrue citations, selection was based instead on a subjective judgement of influence grounded in a knowledge of the field.
-\item Papers selected should, as far as reasonable, represent a cross-section of years over the range 1950-2009.
-[The corpus was compiled in 2010.] 1950 was chosen as a starting point in recognition of the effect of J.
-P.
-Guilford's presidential address to the American Psychological Association \cite{guilford50}, which examined contemporary creativity research (or more specifically, the lack of thereof).
-His talk was highly influential in encouraging more creativity research activity \cite{kaufman09}.
-\item Papers selected should, as far as reasonable, represent a cross-section of disciplines relevant to discussions of creativity.
-Fig.
-\ref{disciplinaryDistribution} illustrates the disciplinary distribution of the corpus as it changes over the time period covered by the selected papers.
-This distribution is based on the {\em Scopus} database, which classifies journals under their main subject area(s) covered.
-We should acknowledge here though that while many disciplines include creative practice, often the focus is on application rather than in depth discussion of what creativity entails.
-Hence, while we sought to cover creativity from a broad range of perspectives, we also felt it was important not to compromise the focus of our corpus as a representation of key discussions about the nature of creativity.
-\end{itemize}
-
-\begin{figure}[!b]
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[scale=0.5]{images/Fig2}
-\caption{{\bf Representation of the disciplinary breakdown of the Creativity Corpus by time period.} \\Disciplines are as specified for the paper's journal, by the academic database {\em Scopus}.
-Note that Scopus may classify a journal under more than one discipline.}
-\label{disciplinaryDistribution}
-\end{figure}
-
-Exclusion criteria for this search were as follows: 
-\begin{itemize}
-\item Authors were only represented more than once in the corpus if the relevant papers were written from different perspectives.
-For example, Mark Runco's work is represented twice in the corpus, but covering two different topics relating to the nature of creativity (psychoeconomic approach to creativity; cognition and creativity).
-If the search process highlighted two or more papers with a shared author on the same or highly similar perspectives on creativity, then the more highly cited paper was chosen.
-\item Papers had to be written in English, as the language processing tools we were working with were for English language texts.
-\item Papers had to be available in a format that enabled us easily to extract plain text (this excluded books or book chapters).
-\end{itemize}
-
-The creativity corpus is relatively small and necessarily selective  in terms of the papers that are included.
-As such it constitutes just a small fraction of the many academic works on creativity that have been published in the last 60 or so years.
-Indeed, the 30 papers in the creativity corpus cannot be regarded as comprehensively representative of the wide range of academic positions on creativity that have been discussed in the literature over the decades.
-However, the goal of this work is not to present a fine-grained analysis of language use drawn from this complete literature, nor to provide a comprehensive lexicon or dictionary of creativity.
-Rather, the goal is to identify the broader ontological themes or factors that recur in our understanding of the concept of creativity.
-For this purpose, what is required is a sufficiently representative sample of the academic discourse on creativity.
-This sample can be used to identify the way in which word use reflects key themes or factors that persist across different perspectives.
-
-Our objective is to identify what is distinctive in the language used to discuss creativity, in contrast to the language used to discuss other topics.
-As a basis for comparison, therefore, a further sample of 60 academic papers on topics unrelated to creativity -- the {\em non-creativity corpus} -- was assembled alongside the creativity corpus, in 2010.
-
-\vspace{0.25cm}
-\begin{center}
-\fbox{
-\begin{minipage}{0.8\linewidth}
-\textbf{Non-creativity corpus}: \\ 60 academic papers on topics unrelated to creativity, from the  same range of academic disciplines and publication years as  the creativity corpus papers.
-\end{minipage}
-}
-\end{center}
-\vspace{0.25cm}
-
-The non-creativity corpus papers were selected by a literature search retrieving, for each paper in the creativity corpus, the two most-cited papers in the same academic discipline (as categorised by  {\em Scopus}) and published in the same year, that did not contain any words with the prefix {\em creat\/} (i.e.
-{\em creativity\/}, {\em creative\/}, {\em creation\/}, and so on).
-In other words, the criteria for inclusion in this second corpus were whether a paper was one of the two papers that was most highly cited at the time of the search (2010), in the same academic discipline, and published in the same year, as a paper in the creativity corpus, and that satisfied the exclusion criteria of not containing any words with the above mentioned prefixes.
-The 60 papers selected for the creativity corpus are listed in \nameref{S2_Appendix}.
-The search strategy used to select papers for this non-creativity corpus is illustrated in a second flow diagram, in Fig.
-\ref{searchNonCC}.
-
-\begin{figure}
-\caption{ A flow diagram describing the search strategy used to identify papers for the non-creativity corpus.}
-% REMOVE IMAGES FROM SUBMITTED VERSION
-%\includegraphics[width=\textwidth]{images/Fig3}
-\label{searchNonCC}
-\end{figure}
-
-The non-creativity corpus is twice the size of the creativity corpus ($\approx$ 700,000 words and $\approx$ 300,000 words respectively), in acknowledgement of the fact that in general the set of academic papers on creativity is only a small subset of all academic papers.
-Both corpora are very small in comparison to corpora such as the British National Corpus, a relatively large  ($\approx$ 100M words) corpus of written and spoken English in general usage across a number of different contexts, and tiny in comparison to more recent web-derived text collections containing billions of words.
-There are, however, several benefits associated with using a corpus derived from specialist academic literature:
-
-\begin{itemize}
-\item Ease of locating relevant and appropriate papers: e.g.
-availability of tools to perform targeted literature searches, electronic publication of papers for download, tagging of paper content by keywords, citations in papers to other related papers.
-\item Ability to access timestamped textual materials over a range of decades.
-\item Publication of academic papers in an appropriate format for computational analysis: most papers that are available electronically are in formats such as PDF or HTML, which can be converted to text fairly easily.
-\item Availability of citation data as a measure of how influential a paper is on others: whilst not a perfect reflection of a paper's influence, citation data is often used for measuring the impact of a journal \cite{garfield72} or an individual researcher's output \cite{hirsch05}.
-\item Availability of provenance data, such as who wrote the paper and for what audience (from the disciplinary classification of the journal).
-\end{itemize}
-\noindent
-
-Some pre-processing was undertaken for each paper in both the creativity corpus and non-creativity corpus prior to analysis.
-A plain text file was generated for each paper, containing the full text of that paper.
-All journal headers and copyright notices were removed from each paper, as were the author names and affiliations, list of references and acknowledgements.
-All files were also checked for any non-ASCII characters and anomalies that may have arisen during the creation of the text file.
-
-\subsection*{Natural language processing}
-
-The corpus data was first pre-processed using the RASP natural language processing toolkit \cite{briscoe06} in order to perform {\em lemmatisation} and {\em part-of-speech} tagging.
-Lemmatisation permits inflectional variants of a given word to be identified with a common `dictonary headword' form or `lemma'.
-For example,  {\em performs\/}, {\em performed\/}  and {\em performing\/} all occur in the creativity corpus as distinct morphological variants of  the  verb, {\em perform\/}.
-Intuitively, we would like to count each of these inflectional variants as an instance of the same word, rather than as separate and distinct lexical tokens.
-Lemmatisation software enables us to do this by mapping such variants to a cannonical lemma form.
-As a further refinement, each lemma was also mapped to lower case to ensure that capitalised word forms (e.g.
-{\em Novel\/}) were not counted separately from their non-capitalised forms ({\em novel\/}).
-While this has the potential for occasional confusion between proper names and common nouns (e.g.
-{\em Apple\/} v.
-{\em apple\/}), it is not considered that the resulting level of `noise'  in the data is likely to adversely affect the results of the analysis.
-
-Each word was assigned a part-of-speech tag identifying its grammatical category (i.e.
-whether the word was a noun, verb, preposition, etc.).
-Such tagging is useful because it allows us to distinguish between different grammatical uses of a common orthographic form.
-For example, the use of {\em novel\/} as a noun in {\em a good novel\/} can be properly differentiated from its use as an adjective in {\em a novel idea\/}.
-The data was further simplified and filtered so that only words of the four `major' categories (i.e.
-noun, verb, adjective and adverb) were represented.
-Note that the major categories bear the semantic content of the papers making up the creativity corpus.
-They may be distinguished from minor categories or `function words', such as pronouns ({\em something\/}, {\em itself\/}) prepositions (e.g.
-{\em upon\/}, {\em by\/}) conjunctions ({\em but\/}, {\em or\/}) and quantifiers (e.g.
-{\em many\/}, {\em more\/}).
-Because such words have little independent semantic content, they are of limited interest for the present study and may be removed from the data.
-
-Following processing with RASP, a list of words found in the creativity corpus, together with their frequency counts was generated.
-The non-creativity corpus was pre-processed in the same way and a corresponding list of words and frequencies also generated.
-
-\subsection*{Identifying words associated with creativity}
-
-The word frequency data derived from the two corpora was used to establish which words occur significantly more often in the creativity corpus than in the non-creativity corpus.
-This in turn can be regarded as providing evidence of which words are salient to the concept of creativity.
-Salient words were identified using the log-likelihood ratio  (also referred to as the $G^2$ or G-squared statistic), which is a measure of how well observed data fit a model or expected distribution \cite{dunning93,kilgarriff01,rayson00,oakes98}.
-It provides an alternative to Pearson's chi-squared ($\chi^2$) test and has been advocated as the more appropriate measure of the two for corpus analysis as it does not rely on the (unjustifiable) assumption of normality in word distribution  \cite{dunning93,kilgarriff01,oakes98}.
-This is a particular issue when analysing smaller corpora, such as those used in the present work.
-The log likelihood ratio statistic is more accurate in its treatment of infrequent words in the data,  which often hold useful information.
-By contrast, the $\chi^2$ statistic tends to under-emphasise such outliers at the expense of very frequently occurring data points.
-
-Our use of the log-likelihood ratio follows that of Rayson and Garside \cite{rayson00}.
-Given two corpora (in our case, the creativity corpus $cc$ and the non-creativity corpus $nc$) the log-likelihood score for a given word is calculated as shown in equation~(\ref{LLR}) below:
-
-\begin{equation}
-\mbox{\em LL} =  O_{cc}\ln (\frac{O_{cc}}{E_{cc}} ) + O_{nc}\ln (\frac{O_{nc}}{E_{nc}} )
-\label{LLR} 
-\end{equation}
-\noindent
-where $O_{cc}$ ($O_{nc}$) is the observed frequence of the word in $cc$ ($nc$) and similarly $E_{cc}$ ($E_{nc}$) is its expected frequency. The expected frequency $E_{cc}$  is given by:
-
-\begin{equation}
-E_{cc} = \frac{N_{cc} \times (O_{cc} + O_{nc})}{N_{cc} + N_{nc}}
-\label{modelFreqs} 
-\end{equation}
-where $N_{cc}$ denotes the total number of words in corpus $cc$ (i.e.
-the sum of the frequencies of all words drawn from corpus $cc$).
-The expected frequency $E_{nc}$ is defined in a way analogous to Equation \ref{modelFreqs}.
-
-As computed above, the log-likelihood ratio measures the extent to which the distribution of a given word deviates from what might be expected if its distribution is not corpus dependent.
-The higher the log likelihood ratio score for a given word, the greater the deviation from what is expected.
-It should be noted however, that the statistic tells us only that  the observed distribution of a word in the two corpora is unexpected (and to what extent).
-It does not  tell us whether the word is more or less frequent than expected in the creativity corpus.
-To identify words significantly associated with creativity therefore, it was necessary to select just those words with observed counts higher than that expected in the creativity corpus.
-It should perhaps be further noted that the resulting words may be either positively or negatively connoted with respect to creativity.
-In practice this is not a problem, as the significance of a given word lies in its semantic connection to creativity, not in its sentiment or affect.
-Affect is taken into account as part of the later manual examination of the data used to identify components of creativity.
-
-The results of the calculations were filtered to remove any words with a log-likelihood score less than 10.83, representing a chi-squared significance value for p=0.001 (one degree of freedom).
-In this way, the filtering process reduced the set of candidate words to just those that appear to occur significantly more often than expected in the creativity corpus.
-To avoid extremely infrequent words disproportionately affecting the data, any word occurring fewer than five times was also removed from the data.
-Finally, the words were inspected to remove any `spurious' items such as proper nouns or misclassified or odd character sequences.
-This resulted in a total of 694 {\em creativity words\/}: a collection of 389 nouns, 205 adjectives, 72 verbs and 28 adverbs that occurred significantly more often than expected in the creativity corpus.
-Table \ref{creativityTop20} gives the top 20 results of these calculations.
-
-\begin{table}[!b]
-\begin{center}
-\begin{tabular}{c c | c c}
-\# & Word (\& POS tag) & LLR \\
-\hline
-\#1 & thinking (N) & 834.55  \\
-\#2 & process (N) & 612.05 \\
-\#3 & innovation (N) & 546.20 \\
-\#4 & idea (N) & 475.74  \\
-\#5 & program (N) & 474.41  \\
-\#6 & domain (N) & 436.58 \\
-\#7 & cognitive (J) & 393.79  \\
-\#8 & divergent (J) & 355.11 \\
-\#9 & openness (N) & 328.57  \\
-\#10 & discovery (N) & 327.38 \\
-\#11 & primary (J) & 326.65 \\
-\#12 & originality (N) & 315.60  \\
-\#13 & criterion (N) & 312.61  \\
-\#14 & intelligence (N) & 309.31 \\
-\#15 & ability (N) & 299.27 \\
-\#16 & knowledge (N) & 290.48  \\
-\#17 & create (V) & 280.06 \\
-\#18 & experiment (N) & 253.32 \\
-\#19 & plan (N) & 246.29 \\
-\#20 & agent (N) & 246.24  \\
-\end{tabular}
-\end{center}
-\caption{{\bf The top 20 results (in descending order) of the log-likelihood ratio (LLR) calculations.}\\ A significant LLR score at p=0.001 is 10.83.
-N.B.
-POS=Part Of Speech: N=noun, J=adjective, V=verb, R=adverb.}
-\label{creativityTop20}
-\end{table}%
-
-\subsection*{Identifying components of creativity}
-\label{creat-comps}
-
-It is important to note that our objective is to identify key themes in the lexical data, not to induce a comprehensive terminology of creativity.
-Despite the relatively small size of the corpora used, the resulting set of 694 creativity words is sufficiently rich for this purpose, but is still somewhat large to work with in its raw form.
-In previous, related work \cite{jordanous10a} an attempt was made to identify key components by manually clustering creativity words by inspection of the raw data.
-In practice, this proved laborious and made it impossible systematically to consider all of the identified words.
-It also raised issues of subjectivity and experimenter bias.
-These problems are addressed here, at least in part, by automatically clustering the words according to a statistical measure of {\em distributional similarity\/} \cite{lin98}.
-The more manageable collection of clusters may then be examined to identify key components or dimensions of creativity.
-
-The intuition underlying distributional measures of similarity derives from the {\em distributional hypothesis\/} due to Harris \cite{harris68}.
-This hypothesis  states that similarity of distribution correlates with similarity of meaning: two words that tend to appear in similar linguistic contexts will tend to have similar meanings.
-The notion of linguistic context here is not fixed and might plausibly be modelled in a variety of different ways.
-For example, two words might be considered to inhabit the same context if they appear in the same document or the same sentence or if they stand in the same grammatical relationship to some other word (e.g.
-both occur as {\em subject\/} of a particular verb or {\em modifier\/} of a given noun).
-In practice it has been shown that modelling distribution in terms of grammatical relations leads to a tighter correlation between distributional similarity and closeness of meaning \cite{kilgarriff00}.
-
-In the present work, grammatical relations are used to represent linguistic context  and distributional similarity is measured as a function of the number of  relations 
-that two words share. To illustrate, evidence that the words {\em concept} and {\em idea} are similar in meaning might be provided by occurrences such as the following:
-
-\begin{quote}
-(1) the {\em concept/idea} involves \hfill (subject of verb `involve')\\
-(2) applied the {\em concept/idea\/} \hfill (object of verb `apply') \\
-(3) the basic {\em concept/idea\/} \hfill (modified by adjective `basic')
-\end{quote}
-
-\noindent
-Grammatical relations were obtained from an analysis of the written portion of the British National Corpus \cite{leech92}, which had previously been processed using the RASP toolkit \cite{briscoe06} in order to extract them.
-Using this data, each word in the creativity corpus was associated with a list of grammatical relations in which it occurred, together with corresponding counts of occurrence.
-In practice, not all of the grammatical relation information output by RASP was used to calculate distributional similarity.
-Just the subject, object and modifier relation types are used as these tend to give the best results \cite{weeds03}.
-A potential difficulty with obtaining word similarity data based on the BNC (i.e.
-using data from sources of everyday usage of English, rather than from more specialist sources) would arise if the majority of the creativity words were used with distinctive or technical senses within the creativity corpus.
-From inspection and from knowledge of creativity literature, however, this situation was found to be unlikely.
-While some narrowly specialised usage may be present to some small degree in the set of creativity words, most words retain general senses as reflected in the wider BNC data set.
-An advantage of using the BNC is that its  size increases the chances of a comprehensive coverage of the general senses of each word of interest.
-
-Distributional similarity of two words is measured in terms of the similarity of their associated lists of grammatical relations.
-A variety of different methods for calculating distributional similarity have been investigated in the literature, including standard techniques such as the cosine measure \cite[for example]{mannschu99}.
-The present work adopts an information-theoretic measure due to Lin \cite{lin98}, which has been widely used in language processing applications as a means of automatically discovering semantic relationships between words.
-In comparison to other similarity measures it has been shown to perform particularly well as a means of identifying near-synonyms \cite{weedsweir03,mccanavi09}.
-
-Similarity scores were calculated between all pairs of creativity words of the same grammatical category.
-That is, scores were obtained separately for pairs of nouns, verbs, adjectives and adverbs.
-For a given set of words, word pair similarity data calculated in this way can be conveniently visualised as an edge-weighted graph, where nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0), as in Fig.
-\ref{conceptIdea}.
-
-\begin{figure}
-\caption{{\bf Word pairwise similarity data visualised as an edge-weighted graph.} \\Nodes  correspond to words and edges are weighted by similarity scores (for any score $>$ 0). }
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[width=\textwidth]{images/Fig4}
-\label{conceptIdea}
-\end{figure}
-
-Graphical representations of the similarity data like that shown in Fig.
-\ref{conceptIdea} provide a useful basis for analysing the creativity words and identifying recurring themes or components of creativity.
-Two complementary methods for identifying key components of the data were adopted:
-
-\begin{description}
-
-\item[Clustering:] The graph clustering software {\em Chinese Whispers} \cite{biemann06} was used to automatically identify word clusters (groups of closely interconnected words) in the dataset.
-This algorithm uses an iterative process to group together graph nodes that are located close to each other.
-By grouping words with similar meanings, the number of data items was effectively reduced and themes in the data could be recognised more readily from each distinct cluster.
-A sample of some of the resulting clusters can be seen in Fig.
-\ref{clustersZoom}.
-%To carry out Chinese Whispers, a preprocessing step was taken to categorise words according to their parts of speech, using the RASP software \cite{carrollRASP}.
-
-\item[Inspection:] To focus on the words most closely related to creativity, the top twenty creativity words (i.e.
-the twenty  words with the highest log likelihood scores) were selected.
-Each word was then visualised as the root node of its own individual subgraph using the graph drawing software {\em GraphViz} (http://www.graphviz.org/, last accessed August 2016).
-In order to reduce the amount of data to be examined, similarity scores were discarded if they fell below a threshold value (adjusted manually for each graph to highlight the most strongly connected words).
-This made the size and complexity of the graphs smaller and therefore easier to inspect and analyse visually.
-Fig.
-\ref{clusterToComponents} illustrates, in diagram form, the process of using manual inspection to identify components.
-
-\end{description}
-
-\begin{figure}
-\caption{{\bf Sample of clusters produced by the Chinese Whispers clustering step.}}
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[width=\textwidth]{images/Fig5}
-\label{clustersZoom}
-\end{figure}
-
-\begin{figure}
-\caption{{\bf Illustration of the process of using manual inspection for further clustering.}}
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[width=\textwidth]{images/Fig6}
-\label{clusterToComponents}
-\end{figure}
-
-As part of the manual inspection process, candidate components were further considered in terms of the {\em Four Ps} of creativity \cite{rhodes61,mooney63,mackinnon70,kaufman09} described earlier in this paper.
-This additional analysis provided a means of identifying alternative perspectives and revealing subtle (but still important) aspects of creativity.
-For example, {\em novelty} is commonly associated with the results of creative behaviour (Product): how novel is the artefact or idea that has been produced?
-However, we could similarly recognise as creative an approach to a task  (Process) that does things in a novel and different way.
-Also, if a product is new in a particular environment (Press), then it may well be regarded as creative to those in that environment.
-Viewing {\em novelty} from the perspectives of Product, Process and Press uncovers these subtle and interlinked distinctions.
-
-% Results and Discussion can be combined.
-\section*{Results and Discussion}
-\label{results}
-
-\subsection*{Components of creativity}\label{componentsResults}
-
-From the analysis steps described in the previous section it was possible to extract a set of fourteen key components of creativity. These components are summarised in Fig. \ref{components} 
-and are presented in more detail below.
-The components contribute collectively to the overall concept and may be regarded as providing an {\em ontology of creativity\/}.
-It is important to note, however that the fourteen components do not constitute a set of necessary and sufficient conditions for creativity, in all its possible manifestations.
-There are two reasons for this.
-Firstly, some of the components we have identified appear to be logically inconsistent with others in the set.
-Consider for example the apparent need for autonomous, independent behaviour identified in {\em Independence and Freedom\/} and contrast this with the requirement for social interaction implied by {\em Social Interaction and Communication\/}.
-%\hidden{These factors may appear logically opposed.}
-Secondly, of course, creativity %\hidden{does not lend itself to formal and precise definition and 
-%I added this bit to clarify the point a bit [does not lend itself to formal and precise definition and]
-also manifests itself in rather different ways across different domains \cite{plucker04} and components will vary in importance, according to the requirements of a particular domain.
-As an illustration of this second point, %Can we explicitly relate this illustration to one or more of the components that have been identified?
-creative behaviour in mathematical reasoning has more focus on finding a correct solution to a problem than is the case for creative behaviour in, say,  musical improvisation \cite{colton08,jordanous12jims}.
-
-\begin{figure} 
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-\caption{{\bf The fourteen key components of creativity identified through an analysis of the word clusters.}}
-%%\includegraphics[width=\textwidth]{images/Fig7}
-\label{components}
-\end{figure}
-
-The following set of fourteen components is therefore presented as a collection of dimensions -- attributes, abilities and behaviours, etc.
--- which contribute to our understanding of creativity.
-The components should be treated as {\em building blocks} for creativity that may be arranged in different ways and with different emphases to suit different modelling purposes.
-The analysis of creativity in terms of the dimensions should be informative for a human audience and provide a basis for machine-understanding of the concept.
-%This approach is informed by debates in cognitive linguistics, computational linguistics and through philosophical underpinnings (see Background section).
- Each component is presented here with a brief explanation or gloss. These explanations will later be used for part of the semantic content in the creativity ontology.
-
-%The current work illuminates the sorts of issues that arise in formal modelling of subjective or `soft' concepts such as creativity, which are unlikely to resolve to fixed, static meaning(s).
-For example,  some components appear  logically inconsistent with others in the set: e.g.
-the need for autonomous, independent behaviour ({\em Independence and Freedom\/}) versus the requirement for social interaction ({\em Social Interaction and Communication\/}).
-Also, creativity clearly manifests itself in different ways across different domains \cite{plucker04} and components will vary in importance, according to the requirements of a particular domain.
-For example, creative behaviour in mathematical reasoning has more focus on finding a correct solution to a problem than is the case for creative behaviour in, say,  musical improvisation \cite{colton08}.
-The set of creativity components are therefore presented as a collection of dimensions -- attributes, abilities and behaviours, etc.
--- which contribute to an overall improvement in the understanding of creativity that provides greater clarity and information both to a human audience and in machine-readable form for future Linked Data links and applications on the Semantic Web.
-This approach is informed by debates in cognitive linguistics, computational linguistics and through philosophical underpinnings (section \ref{cogPhil}).
-
-\begin{description}
-
-\item[Active Involvement and Persistence:] \mbox{}\\
-{\em Being actively involved; reacting to and having a deliberate effect on the creative process.\/}\\
-{\em The tenacity to persist with the creative process throughout, even during problematic points\/}.
-
-\item[Dealing with Uncertainty:] \mbox{}\\{\em
-Coping with incomplete, missing, inconsistent, contradictory, ambiguous and/or uncertain information. Element of risk and chance - no guarantee that information problems will be resolved.\\
-Not relying on every step of the process to be specified in detail; perhaps even avoiding routine or pre-existing methods and solutions.
-}
-
-\item[Domain Competence:] \mbox{}\\{\em
-Domain-specific intelligence, knowledge, talent, skills, experience and expertise.\\
-Knowing a domain well enough to be equipped to recognise gaps, needs or problems that need solving and to generate, validate, develop and promote new ideas in that domain.
-}
-
-\item[General Intellectual Ability:] \mbox{}\\{\em
-General intelligence and IQ.\\
-Good mental capacity.
-}
-
-\item[Generation of Results:] \mbox{}\\
-{\em Working towards some end target, goal, or result.\/}\\
-{\em Producing something (tangible or intangible) that previously did not exist.\/}
-
-\item[Independence and Freedom:] \mbox{}\\{\em 
-Working independently with autonomy over actions and decisions.\\
-Freedom to work without being bound to pre-existing solutions, processes or biases; perhaps challenging cultural or domain norms.
-}
-
-\item[Intention and Emotional Involvement:] \mbox{}\\{\em
-Personal and emotional investment, immersion, self-expression and involvement in the creative process.\\
-The intention and desire to be creative: creativity is its own reward, a positive process giving fulfilment and enjoyment.
-}
-
-\item[Originality:] \mbox{}\\{\em
-Novelty and originality; a new product, or doing something in a new way; seeing new links and relations between previously unassociated concepts.\\
-Results that are unpredictable, unexpected, surprising, unusual, out of the ordinary.
-}
-
-\item[Progression and Development:] \mbox{}\\{\em
-Movement, advancement, evolution and development during a process.\\
-Whilst progress may or may not be linear, and an actual end goal may be only loosely specified (if at all), the entire process should represent some progress in a particular domain or task. }
-
-\item[Social Interaction and Communication:] \mbox{}\\{\em
-Communicating and promoting work to others in a persuasive and positive manner.\\
-Mutual influence, feedback, sharing and collaboration between society and individual.
-}
-
-\item[Spontaneity/Subconscious Processing:] \mbox{}\\{\em 
-No need to be in control of the whole process; thoughts and activities may inform the process subconsciously without being inaccessible for conscious analysis, or may receive less attention than others.
-\\
-Being able to react quickly and spontaneously when appropriate, without needing to spend too much time thinking about the options.
-}
-
-\item[Thinking and Evaluation:] \mbox{}\\{\em 
-Consciously evaluating several options to recognise potential value in each and identify the best option, using reasoning and good judgement.\\
-Proactively selecting a decided choice from possible options, without allowing the process to stagnate under indecision.
-}
-
-\item[Value:] \mbox{}\\{\em 
-Making a useful contribution that is valued by others and recognised as an achievement and influential advancement; perceived as special, `not just something anybody would have done'.\\
-The end product is relevant and appropriate to the domain being worked in.
-}
-
-\item[Variety, Divergence and Experimentation:] \mbox{}\\{\em 
-Generating a variety of different ideas to compare and choose from, with the flexibility to be open to several perspectives and to experiment and try different options out without bias.\\
-Multi-tasking during the creative process.
-}
-\end{description}
-
-\subsection*{Implementing a machine-readable ontology of creativity}\label{creativityOntology}
-
-The fourteen components provide a fuller and clearer account of the constituent parts of the concept of creativity.
-An important aim of the current work is to make the components available as a resource for other researchers in computational creativity and to provide a basis for the automated evaluation of creative systems.
-As a step in this direction, the components have been expressed in an open, machine-readable form within the Semantic Web.
-In this way, the characterization of the components benefits from and is enriched by concepts that are already represented within the Semantic Web.
-%To achieve this, SKOS (Simple Knowledge Organisation System) \cite{skos} was used as a basis for constructing an OWL ontology representation of creativity and its components,
-
-In particular, the components are linked to the data in WordNet \cite{fellbaum98}, a large lexical database of English that has recently been made available as a Semantic Web ontology (http://wordnet.rkbexplorer.com/, last accessed August 2016).
-In WordNet, words are grouped by sense and interlinked by lexical and conceptual relations.
-Note that, although the WordNet definition of the word such as `creativity' is brief (`the ability to create'), its utility lies in how it is linked to various concepts, such as its sense, hyponyms, type, `gloss' (brief definition) and other related concepts.
-Each creativity component relates to a cluster of keywords from the original set of 694 creativity words.
-Following Linked Data principles, each can therefore be linked across the Semantic Web to an appropriate set of concepts from WordNet.
-In this way,  associated semantic information is provided for each component.
-%The SKOS ontology incorporates three main classes:  {\em skos:Concept}  (anything we may want to record information about), {\em skos:ConceptScheme} (a set that collectively defines a skos:Concept) and  {\em skos:Collection} (a collection of semantically-related information).
-An instance of {\em skos:ConceptScheme\/} was created as {\em CreativityComponents}, to represent the set of components that defines the {\em skos:Concept\/} of {\em Creativity}.
-Each component is represented as an individual {\em skos:Concept\/}.
-
-The resulting encoding can be visualised as a graph, as shown in Fig. \ref{ontologyGraph}. 
-The data has also been published under an Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} at:
-%as an OWL/XML file at:
-\begin{quote}
-\texttt{\scriptsize http://purl.org/creativity/ontology}
-\end{quote}
-%under a Open Data Commons Public Domain Dedication and Licence (PDDL) \cite{miller08} .
-%The {\em skos:Concept\/}  
-The concept labelled {\em Creativity} has the unique URI: 
-\begin{quote}
-\texttt{\scriptsize http://purl.org/creativity/ontology\#Creativity}
-\end{quote}%
-Any Linked Data that needs to refer to the concept can use this identifier.
-
-\begin{figure}
-\caption{{\bf The ontology of creativity generated from this work's results, in graph form.}}
-%% REMOVE IMAGES FROM SUBMITTED VERSION
-%%\includegraphics[scale=0.5]{images/Fig8}
-\label{ontologyGraph}
-\end{figure}
-
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-
-%\section*{Discussion}
-%\label{implications}
-
-%As already noted above, the need for a clearer, multi-perspective and broadly applicable account of creativity is evident: this point has been repeatedly underlined by creativity researchers \cite[for example]{rhodes61,torrance67,plucker04defn,kaufman09,hennessey10}.
-As Hennessey and Amabile point out \cite{hennessey10}, an accurate and comprehensive account assists our understanding of creativity and further research.
-It also helps smooth out individual differences of interpretation,   highlighting common ground and transcending discipline or domain bias \cite{plucker04}.
-The novel, language-driven approach to definition adopted in the present work draws together multiple perspectives across disciplinary divides and a confluence approach yields a broader understanding of the concept in the form of an ontology of creativity.
-
-%There are a number of ways to evaluate Semantic Web ontologies \cite{brank05}.
-For the purposes of the creativity ontology presented in this paper, evaluation based on matching any `golden standards' \cite{brank05} is not so appropriate given the lack of any such standards or baselines to adopt, as discussed above in the Introduction of this paper and elsewhere \cite{rhodes61,taylor88,sternberg99a,plucker04defn,kaufman09,jordanousphd,jordanous12cc}.
-It is hoped that publication of the creativity ontology can now facilitate future applications in description and evaluation of creativity, for application-based evaluation of the ontology, perhaps incorporating other data sources to enable data-driven evaluation.
-In areas of knowledge representation such as that tackled in this paper, it is not appropriate to test the ontology definitions against `a set of predefined criteria, standards, requirements, etc.' \cite{brank05} as these sets do not necessarily exist,  but the spirit of such recommendations can be followed by seeing how the ontology matches against human interpretations of the same concepts.
-One can also evaluate how the ontology data can be linked to other data sources \cite{bizer09}.
-Hence, as a reflection of the cross-disciplinary nature of this work, evaluation of the creativity ontology is two-fold, concerning both the cognitive accuracy of this representation of creativity and evaluation of the creativity data publication as an output of Semantic Web research.
-
-\section*{Evaluation}
-
-From a practical stand-point, the current work is part of an overarching project engaged with the question of the evaluation of creativity, particularly computational creativity \cite{jordanous12cc}.
-It is clear that a rigorous and comparative evaluation process needs clear standards to use as guidelines or benchmarks \cite{torrance88,kaufman09}.
-
-The components of creativity in this paper have been employed in two case studies to evaluate the creativity of computational systems \cite{jordanousphd,jordanous12jims,jordanous16aisb}.
-In these case studies, evaluation was carried out using the three step approach of the Standardised Procedure for Evaluating Creative Systems (SPECS) \cite{jordanous12cc}:
-
-\begin{quote}
-\begin{enumerate}
-\item Identify a definition of creativity that your system should satisfy to be considered creative:
-	\begin{enumerate}
-	\item What does it mean to be creative in a general context, independent of any domain specifics?
-	\item What aspects of creativity are particularly important in the domain your system works in (and what aspects of creativity are less important in that domain)?
-	\end{enumerate}
-\item Using Step 1, clearly state what standards you use to evaluate the creativity of your system.
-\item Test your creative system against the standards stated in Step 2 and report the results.
-\end{enumerate}    
-\end{quote}
-
-In both case studies, the components of creativity were chosen as the way of characterising creativity for step 1a of SPECS, and were weighted according to their importance and relevance for creativity in the creative domains under study for each case study (step 1b of SPECS).
-Each component was treated as one standard to be used to evaluate the creativity of the creative systems in the case studies (step 2 of SPECS).
-Each case study system was then tested against each component using feedback provided by judges (step 3 of SPECS), resulting in a detailed set of evaluative feedback on the creativity of each system in the case studies.
-
-Case Study 1 \cite{jordanousphd,jordanous12cc} evaluated the creativity of three different computational musical improvisation systems \cite{jordanous12cc}. 
-Case Study 2 used the components of creativity in an evaluation scenario where information and time was limited for evaluation, to simulate the forming of first impressions and snapshot judgements of the creativeness of a given computational creativity system \cite{jordanousphd,jordanous16aisb}.
-
-The resulting component-based evaluation yielded detailed information about creative strengths and weaknesses of the systems under investigation, highlighting those components where a system performs strongly.
-Crucially, the evaluation feedback also highlighted areas where a given system performed poorly.
-For example, in the musical improvisation study, Case Study 1, we found that, in general, creativity could be improved most by improving performance in {\em Social Interaction and Communication}, {\em Intention and Emotional Involvement} and {\em Domain Competence} (the three components found to be most important for creativity in musical improvisation).
-Similarly, it is useful to be able to quickly obtain formative feedback on strengths and weaknesses in time-limited scenarios such as that replicated in Case Study 2 during the development of creative systems (when ongoing evaluation of progress ideally needs to be both timely and time-efficient).
-Insight can then be obtained on where future development effort is best spent.
-
-The results described above were compared with those obtained from applying other evaluation models and with surveys of people's opinions, where people were asked how creative they thought each system was.
-There was general agreement between evaluation approaches on the most and least creative systems.
-The approaches differed in the formative feedback they provided, particularly for identifying strengths of the system at being creative, and weaknesses of the system to be improved.
-The model of creativity offered in this paper gave the most detailed feedback, but required most information to be collected.
-
-To support the usefulness of having the components as a tangible characterisation of creativity, an interesting finding was made as part of the first case study, in a separate evaluation carried out: asking for people's opinions on how creative the musical improvisation systems were.
-A striking observation was that a number of participants called for the word ``creativity'' to be defined before they felt comfortable with the task and confident in evaluating creativity in this setting, even though participants reported feeling generally positive or at least neutral towards the concept of computational creativity.
-This challenges the generally held view that people have a  common-sense working definition of creativity, at least in the context of judgement and evaluation.
-A representation of creativity is useful to:
-
-\begin{enumerate}
-\item establish what it means for something to be deemed creative; and
-\item identify appropriate evaluation standards that replicate typical human opinion on how creative something is or in comparing two or more creative systems.
-\end{enumerate}
-
-\subsection*{Conclusions and directions for future work}
-\label{conclusions}
-
-This paper has described the methods used to identify a set of {\em components of creativity} using corpus-based, statistical language processing techniques.
-The motivation for the work is the need for a shared, comprehensive and multi-perspective model of creativity.
-Such a model should be of great value to researchers investigating the nature of creativity and in particular those concerned with the evaluation of creative practice.
-More broadly, the inter-disciplinary approach described here exemplifies a general approach to the investigation and representation of semantically fuzzy and essentially-contested concepts.
-For this reason, we expect that it will interest researchers investigating computational methods for analysing and representing other such concepts.
-
-Rather than attempting to provide a unitary account of creativity, our approach extracts common, underlying themes that transcend discipline or domain bias.
-Our point of departure is the observation that the vocabulary used in discussions of the nature of creativity may be analysed in order to throw light on our understanding of the concept and its key attributes.
-Using techniques from corpus linguistics and natural language processing (as described in the Methods section), key components of creativity have been identified.
-The results of this novel, empirical analysis (presented in the Results section) inform the development of an {\em ontology of creativity\/} comprising a set of fourteen distinct components (see Fig.
-\ref{components}).
-It is noted that each component makes a separate contribution to the overall meaning of the concept.
-At the same time, because creativity manifests itself in different ways across different domains \cite{plucker04}, the individual components vary in importance and influence according to the requirements of a given domain.
-The components can be therefore be usefully thought of as 'building blocks' for the concept in its different manifestations.
-Taken together, the components make creativity more tractable to study and to evaluate.
-
-The fourteen components provide a multi-perspective model of creativity that has been successfully applied in a comparative analysis and evaluation of computational creativity systems \cite{jordanous12cc,jordanousphd,jordanous16aisb} (see the Discussions section).
-The outcome of the evaluation process provides relatively fine-grained information about the creative strengths of a given system.
-This information in turn evidences ways in which a system could be considered creative.
-In addition, evaluation based on the components is able to highlight areas of weakness.
-These can be used to inform future work aimed at further developing a system's creative potential.
-
-The components have been published in an open, machine-readable format, making them freely available to the research community.
-This has a number of implications.
-First, the set of components may be readily elaborated, extended or amended by other researchers investigating the concept of creativity.
-Second, the machine-readable format facilitates the development of creativity-aware applications, based on the components.
-Such applications might be developed to support manual evaluation of creative practice or as a significant step towards the development of methods for automated evaluation.
-
-The problem of developing automated evaluation has elsewhere been described as `the Achilles' heel of AI research on creativity' \cite{boden99}.
-An intriguing possibility that we are currently exploring is to further exploit language processing techniques to perform evaluation based on textual reviews, descriptions of system performance, or social media interactions \cite{jordanous15vem}.
-Such an approach would be analogous to the way sentiment analysis techniques are now in common use to evaluate attitude and opinion based on reviews of products or services \cite{panglee08}.
-This is a fascinating direction for future work, with great potential for real progress towards tackling computational creativity's `Achilles' heel'.
-
-\section*{Supporting Information}
-
 % Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
 
-\subsection*{S1 Appendix}\label{S1_Appendix}
-{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
-
-\begin{itemize}
-\item T. M. Amabile. The social psychology of creativity: A componential conceptualization. Journal of Personality and Social Psychology, 45(2):357-376, 1983.
-\item M. A. Boden. Precis of The Creative Mind: Myths and mechanisms. Behavioural and Brain Sciences, 17(3):519-570, 1994.
-\item D. T. Campbell. Blind variation and selective retentions in creative thought as in other knowledge processes. Psychological Review, 67(7):380-400, 1960.
-\item S.
+%\section*{S1 Appendix}\label{S1_Appendix}
+%{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
+%
+%\begin{itemize}
+%\item T. M. Amabile. The social psychology of creativity: A componential conceptualization. Journal of Personality and Social Psychology, 45(2):357-376, 1983.
+%\item M. A. Boden. Precis of The Creative Mind: Myths and mechanisms. Behavioural and Brain Sciences, 17(3):519-570, 1994.
+%\item D. T. Campbell. Blind variation and selective retentions in creative thought as in other knowledge processes. Psychological Review, 67(7):380-400, 1960.
+%\item S.
 Colton, A.
@@
 In Proceedings of Workshop Program of ICCBR-Creative Systems: Approaches to Creativity in AI and Cognitive Science, 2001.
-\item M. Csikszentmihalyi. Motivation and creativity: Toward a synthesis of structural and energistic approaches to cognition. New Ideas in Psychology, 6(2):159-176, 1988.
-\item M. Dellas and E. L. Gaier. Identification of creativity: The individual. Psychological Bulletin, 73(1):55- 73, 1970.
-\item A. Dietrich. The cognitive neuroscience of creativity. Psychonomic Bulletin \& Review, 11(6):1011-1026, 2004.
-\item G. Domino. Identification of potentially creative persons from the adjective check list. Journal of Consulting and Clinical Psychology, 35(1):48-51, 1970.
-\item W. Duch. Intuition, insight, imagination and creativity. IEEE Computational Intelligence Magazine, 2(3):40-52, 2007.
-\item C. S. Findlay and C. J. Lumsden. The creative mind: Toward an evolutionary theory of discovery and innovation. Journal of Social and Biological Systems, 11(1):3-55, 1988.
-\item C. M. Ford. A theory of individual creative action in multiple social domains. The Academy of Management Review, 21(4):1112-1142, 1996.
-\item J. Gero. Creativity, emergence and evolution in design. Knowledge-Based Systems, 9(7):435-448, 1996. 
-\item H. G. Gough. A creative personality scale for the adjective checklist. Journal of Personality and Social Psychology, 37(8):1398-1405, 1979.
-\item J. P. Guilford. Creativity. American Psychologist, 5:444-454, 1950.
-\item Z. Ivcevic. Creativity map: Toward the next generation of theories of creativity. Psychology of Aesthetics, Creativity, and the Arts, 3(1):17-21, 2009.
-\item K. H. Kim. Can we trust creativity tests? A review of the Torrance tests of creative thinking (TTCT). Creativity Research Journal, 18(1):3-14, 2006.
-\item L. A. King, L. McKee Walker, and S. J. Broyles. Creativity and the five-factor model. Journal of Research in Personality, 30(2):189-203, 1996.
-\item R. R. McCrae. Creativity, divergent thinking, and openness to experience. Journal of Personality and Social Psychology, 52(6):1258-1265, 1987.
-\item S. A. Mednick. The associative basis of the creative process. Psychological Review, 69(3):220-232, 1962. 
-\item M. D. Mumford and S. B. Gustafson. Creativity syndrome: Integration, application, and innovation. Psychological Bulletin, 103(1):27-43, 1988. 
-\item M. T. Pearce, D. Meredith, and G. A. Wiggins. Motivations and methodologies for automation of the compositional process. Musicae Scientae, 6(2):119-147, 2002.
-\item J.
+%\item M. Csikszentmihalyi. Motivation and creativity: Toward a synthesis of structural and energistic approaches to cognition. New Ideas in Psychology, 6(2):159-176, 1988.
+%\item M. Dellas and E. L. Gaier. Identification of creativity: The individual. Psychological Bulletin, 73(1):55- 73, 1970.
+%\item A. Dietrich. The cognitive neuroscience of creativity. Psychonomic Bulletin \& Review, 11(6):1011-1026, 2004.
+%\item G. Domino. Identification of potentially creative persons from the adjective check list. Journal of Consulting and Clinical Psychology, 35(1):48-51, 1970.
+%\item W. Duch. Intuition, insight, imagination and creativity. IEEE Computational Intelligence Magazine, 2(3):40-52, 2007.
+%\item C. S. Findlay and C. J. Lumsden. The creative mind: Toward an evolutionary theory of discovery and innovation. Journal of Social and Biological Systems, 11(1):3-55, 1988.
+%\item C. M. Ford. A theory of individual creative action in multiple social domains. The Academy of Management Review, 21(4):1112-1142, 1996.
+%\item J. Gero. Creativity, emergence and evolution in design. Knowledge-Based Systems, 9(7):435-448, 1996. 
+%\item H. G. Gough. A creative personality scale for the adjective checklist. Journal of Personality and Social Psychology, 37(8):1398-1405, 1979.
+%\item J. P. Guilford. Creativity. American Psychologist, 5:444-454, 1950.
+%\item Z. Ivcevic. Creativity map: Toward the next generation of theories of creativity. Psychology of Aesthetics, Creativity, and the Arts, 3(1):17-21, 2009.
+%\item K. H. Kim. Can we trust creativity tests? A review of the Torrance tests of creative thinking (TTCT). Creativity Research Journal, 18(1):3-14, 2006.
+%\item L. A. King, L. McKee Walker, and S. J. Broyles. Creativity and the five-factor model. Journal of Research in Personality, 30(2):189-203, 1996.
+%\item R. R. McCrae. Creativity, divergent thinking, and openness to experience. Journal of Personality and Social Psychology, 52(6):1258-1265, 1987.
+%\item S. A. Mednick. The associative basis of the creative process. Psychological Review, 69(3):220-232, 1962. 
+%\item M. D. Mumford and S. B. Gustafson. Creativity syndrome: Integration, application, and innovation. Psychological Bulletin, 103(1):27-43, 1988. 
+%\item M. T. Pearce, D. Meredith, and G. A. Wiggins. Motivations and methodologies for automation of the compositional process. Musicae Scientae, 6(2):119-147, 2002.
+%\item J.
 A.
@@
 Educational Psychologist, 39(2):83-96, 2004.
-\item R.
+%\item R.
 Richards, D.
@@
 Journal of Personality and Social Psychology, 54(3):476-485, 1988.
-\item G. Ritchie. The transformational creativity hypothesis. New Generation Computing, 24(3):241-266, 2006.
-\item G. Ritchie. Some empirical criteria for attributing creativity to a computer program. Minds and Machines, 17:67-99, 2007.
-\item D. L. Rubenson and M. A. Runco. The psychoeconomic approach to creativity. New Ideas in Psychology, 10(2):131-147, 1992.
-\item M. A. Runco and I. Chand. Cognition and creativity. Educational Psychology Review, 7(3):243-267, 1995.
-\item D. K. Simonton. Creativity: Cognitive, personal, developmental, and social aspects. American Psychologist, 55(1):151-158, 2000.
-\item J. R. Suler. Primary process thinking and creativity. Psychological Bulletin, 88(1):144-165, 1980.
-\item G. A. Wiggins. A preliminary framework for description, analysis and comparison of creative systems. Knowledge-Based Systems, 19(7):449-458, 2006.
-\end{itemize}
+%\item G. Ritchie. The transformational creativity hypothesis. New Generation Computing, 24(3):241-266, 2006.
+%\item G. Ritchie. Some empirical criteria for attributing creativity to a computer program. Minds and Machines, 17:67-99, 2007.
+%\item D. L. Rubenson and M. A. Runco. The psychoeconomic approach to creativity. New Ideas in Psychology, 10(2):131-147, 1992.
+%\item M. A. Runco and I. Chand. Cognition and creativity. Educational Psychology Review, 7(3):243-267, 1995.
+%\item D. K. Simonton. Creativity: Cognitive, personal, developmental, and social aspects. American Psychologist, 55(1):151-158, 2000.
+%\item J. R. Suler. Primary process thinking and creativity. Psychological Bulletin, 88(1):144-165, 1980.
+%\item G. A. Wiggins. A preliminary framework for description, analysis and comparison of creative systems. Knowledge-Based Systems, 19(7):449-458, 2006.
+%\end{itemize}
+%
+%
 
-\subsection*{S2 Appendix}\label{S2_Appendix}
+%
+\section*{S2 Appendix}\label{S2_Appendix}
 {\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:

### 2016-09-12 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
detaching SI from main manuscript

@@
 
-\begin{itemize}
-\item T. M. Amabile. The social psychology of creativity: A componential conceptualization. Journal of Personality and Social Psychology, 45(2):357-376, 1983.
-\item M. A. Boden. Precis of The Creative Mind: Myths and mechanisms. Behavioural and Brain Sciences, 17(3):519-570, 1994.
-\item D. T. Campbell. Blind variation and selective retentions in creative thought as in other knowledge processes. Psychological Review, 67(7):380-400, 1960.
-\item S.
+%\begin{itemize}
+%\item T. M. Amabile. The social psychology of creativity: A componential conceptualization. Journal of Personality and Social Psychology, 45(2):357-376, 1983.
+%\item M. A. Boden. Precis of The Creative Mind: Myths and mechanisms. Behavioural and Brain Sciences, 17(3):519-570, 1994.
+%\item D. T. Campbell. Blind variation and selective retentions in creative thought as in other knowledge processes. Psychological Review, 67(7):380-400, 1960.
+%\item S.
 Colton, A.
@@
 Journal of Personality and Social Psychology, 54(3):476-485, 1988.
-\item G. Ritchie. The transformational creativity hypothesis. New Generation Computing, 24(3):241-266, 2006.
-\item G. Ritchie. Some empirical criteria for attributing creativity to a computer program. Minds and Machines, 17:67-99, 2007.
-\item D. L. Rubenson and M. A. Runco. The psychoeconomic approach to creativity. New Ideas in Psychology, 10(2):131-147, 1992.
-\item M. A. Runco and I. Chand. Cognition and creativity. Educational Psychology Review, 7(3):243-267, 1995.
-\item D. K. Simonton. Creativity: Cognitive, personal, developmental, and social aspects. American Psychologist, 55(1):151-158, 2000.
-\item J. R. Suler. Primary process thinking and creativity. Psychological Bulletin, 88(1):144-165, 1980.
-\item G. A. Wiggins. A preliminary framework for description, analysis and comparison of creative systems. Knowledge-Based Systems, 19(7):449-458, 2006.
-\end{itemize}
+%\item G. Ritchie. The transformational creativity hypothesis. New Generation Computing, 24(3):241-266, 2006.
+%\item G. Ritchie. Some empirical criteria for attributing creativity to a computer program. Minds and Machines, 17:67-99, 2007.
+%\item D. L. Rubenson and M. A. Runco. The psychoeconomic approach to creativity. New Ideas in Psychology, 10(2):131-147, 1992.
+%\item M. A. Runco and I. Chand. Cognition and creativity. Educational Psychology Review, 7(3):243-267, 1995.
+%\item D. K. Simonton. Creativity: Cognitive, personal, developmental, and social aspects. American Psychologist, 55(1):151-158, 2000.
+%\item J. R. Suler. Primary process thinking and creativity. Psychological Bulletin, 88(1):144-165, 1980.
+%\item G. A. Wiggins. A preliminary framework for description, analysis and comparison of creative systems. Knowledge-Based Systems, 19(7):449-458, 2006.
+%\end{itemize}
+%
+%
 
@@
 
-\begin{itemize}
-\item C.
+%\begin{itemize}
+%\item C.
 Ames and J.

### 2016-09-12 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
updated SI captions

@@
 \subsection*{S1 Appendix}\label{S1_Appendix}
-{\bf Creativity Corpus.}  The following 30 papers were used as the {\em creativity corpus} for this work:
+{\bf Creativity Corpus.}  These 30 papers were used as the {\em creativity corpus} for this work.
 
@@
 \subsection*{S2 Appendix}\label{S2_Appendix}
-{\bf Non-Creativity Corpus.} The following 60 papers were used as the {\em non-creativity corpus} for this work:
+{\bf Non-Creativity Corpus.} These 60 papers were used as the {\em non-creativity corpus} for this work.
 

### 2016-09-22 plosOneJordanousKeller/PAPER/RevisedManuscript.tex
removed box formatting around definitions of corpora following Plos One instructions

@@
 
-\vspace{0.25cm}
-\begin{center}
-\fbox{
-\begin{minipage}{0.8\linewidth}
-\textbf{Creativity corpus}: \\ a collection of thirty academic papers which explicitly discuss the nature of creativity.
-\end{minipage}
-}
-\end{center}
-\vspace{0.25cm}
+\begin{itemize}
+\item[] {\em \textbf{Creativity corpus}: a collection of thirty academic papers which explicitly discuss the nature of creativity.\\}
+\end{itemize}
+%\vspace{0.25cm}
+%\begin{center}
+%\fbox{
+%\begin{minipage}{0.8\linewidth}
+%
+%\end{minipage}
+%}
+%\end{center}
+%\vspace{0.25cm}
 
@@
 
-\vspace{0.25cm}
-\begin{center}
-\fbox{
-\begin{minipage}{0.8\linewidth}
-\textbf{Non-creativity corpus}: \\ 60 academic papers on topics unrelated to creativity, from the  same range of academic disciplines and publication years as  the creativity corpus papers.
-\end{minipage}
-}
-\end{center}
-\vspace{0.25cm}
+%\vspace{0.25cm}
+%\begin{center}
+%\fbox{
+%\begin{minipage}{0.8\linewidth}
+\begin{itemize}
+\item[] {\em \textbf{Non-creativity corpus}:  a collection of sixty academic papers on topics unrelated to creativity, from the  same range of academic disciplines and publication years as  the creativity corpus papers.}
+\end{itemize}
+%\end{minipage}
+%}
+%\end{center}
+%\vspace{0.25cm}
 
